### 2016-11-08 Presentation/gpm_november2016_vianello.tex
Added the tex file for gpm slides and shotlist

\documentclass[10pt, compress]{beamer}
\usetheme[conference=23rd SOLDiv ITPA,venue=Naka, date=25/10/2016, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{../biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Latest results from TCV}
\date{25 October 2016}
\author[N.Vianello]{presented by N. Vianello}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
\centering{N. Vianello$^{1,2}$, C. Tsui$^{3,2}$, C. Theiler$^2$,
  S. Allan$^4$, J. Boedo$^3$, B. Labit$^2$, H. Reimerdes$^2$, K. Verhaegh$^{5}$,
  W. Vijvers$^6$, N. Walkden$^4$,  S. Costea$^7$, J. Kovacic$^{8}$, C. Ionita$^{7}$, 
V. Naulin$^9$, A. H. Nielsen$^9$, J. J. Rasmussen$^9$, B. Schneider$^7$, 
R. Schrittwieser$^7$, M. Spolaore$^1$, 
D. Carralero$^{10}$, J. Madsen$^9$, the TCV Team and the EUROfusion MST1 Team}

\centering{\footnotesize
\textit{$^1$Consorzio
RFX,  Padova, Italy, $^2$Swiss Plasma Center (SPC), EPFL Lausanne, Switzerland,
  $^3$UCSD,  La Jolla, USA, $^4$CCFE,  Culham UK, $^5$York Plasma Institute, University of York, York, UK,
$^6$FOM Institute DIFFER, The Netherlands, $^7$Institute for Ion Physics and Applied Physics,
Innsbruck,  Austria, $^{8}$Jozef Stefan Institute, Ljubljana, $^9$DTU,  Copenhagen, Denmark, $^{10}$Max-Plank-Institut fur Plasmaphysik, Garching, Germany}}
\end{frame}
\begin{frame}{Background and objectives}
\only<1>{
\begin{itemize}
\item Role of turbulence transport in the SOL saturation is a well
  know
  feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
  density, even without reaching detachment SOL profile tend to flatten}
\end{itemize}}
\only<2-3>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item Present understanding suggests that a transition of filament
        propagation regime is dominated by effective
        collisionality $\Lambda$ \parencite{Myra:2006p2754}
        \begin{equation*}
          \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
        \end{equation*}
        \item<3> \textcolor{red}{At constant blob size, increasing
            collisionality provide a change in the filaments velocity
            scaling properties}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
%      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
        \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/FigMyra}
          \only<3>{
            \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
        \end{tikzonimage}
    \end{column}
  \end{columns}
}
\only<4-6>{
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
        process and a transition from
        \textcolor{ta3chameleon}{sheath-limited}
        \onslide<5-6>{to \textcolor{blue}{inertial regime}} 
        \item<6> \textcolor{red}{Tested by changing n$_e$
            and $T_e$ through fueling/seeding/heating}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/KoMFig2.png}
        \only<4-6>{
          \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
      }
        \only<5-6>{
          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
      }
        \only<6>{
          \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
      }
    \end{tikzonimage}
  \end{column}
  \end{columns}
}
\only<7->{
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item MAST \parencite{Militello:2016hk} and old TCV
        \parencite{Garcia:2007p2615} data 
        suggested and I$_P$ dependence. 
          \textcolor{red}{At higher current and
        same density SOL shoulder disappear} 
      \item<8> \textcolor{ta3chameleon}{Being shoulder formation
          induced by a change of $\Gamma_{\perp}$ \textit{vs}
          $\Gamma_{\parallel}$ balance we will try to test dependence
          on L$_{\parallel}$}
    \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=\textwidth]{../pdfbox/Presentation/FigMilitello.pdf}
    \end{column}
  \end{columns}
}
\centering{\includegraphics<1>[width=1.1\textwidth]{../pdfbox/Presentation/Fig1Presentation}}
\end{frame}

\begin{frame}{Flux expansion scan/1}
\vspace{-1cm}
  \Fontvi
  % \begin{columns}
  %   \begin{column}{0.3\textwidth}
      \centering{\includegraphics[width=.75\textwidth]{../pdfbox/Fig1a}}
      \begin{itemize}
      \item Parallel connection length varied by scanning 
        flux expansion during density
        ramps in ohmically heated discharges. \textcolor{red}{$\nabla B_i$ towards the X-point}
        %\begin{equation*}
        \[  f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}\]
        %\end{equation*}
        \item Variation of $f_x$ change the volume of flux tube as
          well as parallel connection length (Increased up to 70\%)
      \end{itemize}
    % \end{column}
    % \begin{column}{0.7\textwidth}
  %   \end{column}
  % \end{columns}
\end{frame}

\begin{frame}{Flux expansion scan/2}
  \Fontvi
      \begin{itemize}
      \item<1-> Flux expansion variation induce modification at the target
      \item<1-> Radiation front from bolometry  moves earlier in
        density at larger f$_x$. Front movement trails CIII cut-off
        movement (Reimerdes IAEA 2016)
      \item<2-> Volumetric recombination rates from $n=6, 7$ balmer line
        emission \parencite{kevin:jnm} indicates that \textcolor{red}{recombination occurs
          earlier in density at high $f_x$}
      \item<3|only@3> \textcolor{ta3skyblue}{This is not confirmed in reversed B$_t$ where
        increasing the f$_x$ lead to deeper detachment without}
        changing density threshold  
    \end{itemize}
    \only<1-2>{\begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig2c}
      \only<1>{\fill[white] (0.,0) rectangle (0.52,1); }    
      \draw [->, ultra thick, black] (0.79,0.69) -- (0.75,0.51);
    \end{tikzonimage}}
\centering{\includegraphics<3>[width=.5\textwidth]{../pdfbox/Presentation/XD_detach_HM}}
  \end{frame}

\begin{frame}{Flux expansion scan/3}
  \vspace{-1cm}
\Fontvi
      \begin{itemize}
      \item Target and upstream profile measured at the same density
        but different f$_x$
      \item<3-> Target profiles in the near SOL modified with broader profile at higher
        f$_x$. \textcolor{red}{Huge variation on $\Lambda_{div}$
          without upstream modification}
      \item<4|only@4> \textcolor{ta3chameleon}{Only further increase
          of density (although $\Lambda_{div}$ in the far SOL
          decreases) leads to profile broadening}
      \end{itemize}
      \centering{\includegraphics<1>[width=.65\textwidth]{../pdfbox/Fig4Series_1}}
      \centering{\includegraphics<2>[width=.65\textwidth]{../pdfbox/Fig4Series_2}}
      \centering{\includegraphics<3>[width=.65\textwidth]{../pdfbox/Fig4Series_3}}
      \centering{\includegraphics<4>[width=.65\textwidth]{../pdfbox/Fig4Series_4}}
\end{frame}

\begin{frame}{Filaments effect}
  \vspace{-1cm}
\Fontvi
      \begin{itemize}
      \item<1-3> Blob properties deduced from fast reciprocating as done in \parencite{Boedo:2001tt}
      \item<1|only@1> Blob size deduced as $\delta_b = \tau_b v_{\perp}$
        % \begin{equation*}
        %   \tau_b = \text{FWHM of CAS} \qquad v_{\perp} = \sqrt{v_{E\times B, r}^2 +
        %     v_{E\times B, p}^2}
        % \end{equation*}
      \item<2-3> No clear dependence on
          $\Lambda_{div}$ during f$_x$ scan
      \item<3> \textcolor{ta3chameleon}{When we increase the
          density filaments are bigger at same $\Lambda_{div}$}
      \item<4-> \textcolor{ta3skyblue}{On a statistical basis,
          blob size increases with density without clear dependence on
          f$_x$ \onslide<5>{\textcolor{red}{as well as $\lambda_n$ in the Far SOL}}}
      \item<6> \textcolor{ta3chameleon}{Behavior at very high
          density to be confirmed}  
      \end{itemize}
      \centering{\includegraphics<1>[width=.53\textwidth]{../pdfbox/Fig14b}}
      \centering{\includegraphics<2>[width=.63\textwidth]{../pdfbox/Fig7}}
      \centering{\includegraphics<3>[width=.63\textwidth]{../pdfbox/Fig7b}}
      \centering{\includegraphics<4>[width=.85\textwidth]{../pdfbox/Fig12}}
      \centering{\includegraphics<5>[width=.85\textwidth]{../pdfbox/Fig12b}}
      \only<6>{
        \begin{center}
          \begin{tikzonimage}[width=.85\textwidth]{../pdfbox/Fig12b}
          \draw [thick, ta3chameleon, thick] (0.75,0.5) ellipse (0.1 and 0.1);
          \end{tikzonimage}
        \end{center}
      }
\end{frame}

\begin{frame}{Current scan/1}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-3> On a single shape (f$_x \approx 4$) current scan with
        similar density ramps performed
      \item<2-3> \textcolor{red}{At lower current indication of shoulder for $R-R_{sep}
        \geq 1$ cm which disappear at higher current (same density)}
      \item<3> \textcolor{ta3chameleon}{At even higher current we need to substantially
        increase the fueling (even if at the same $n/n_G$)}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<1-2>{
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series1}
        \only<2>{
          \draw [thick, red, thick] (0.75,0.75) ellipse (0.2 and 0.1);
        }
      \end{tikzonimage} }
    \only<3>{
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series2}
          \draw [thick, ta3chameleon, thick] (0.67,0.35) ellipse (0.22 and 0.1);
          \draw [thick, ta3chameleon, thick] (0.5,0.14) ellipse (0.3 and 0.03);
        \end{tikzonimage}      
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Current scan/2}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item On a statistical basis we have a slight
        reduction of radial velocity of the filaments as in MAST \parencite{Kirk:2016jj} with unclear
        effect on blob-size
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
     \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig8}
       \draw [->, ultra thick, red, dashed] (0.33,0.37) -- (0.7,0.27);
     \end{tikzonimage}
   \end{column}
  \end{columns}
  \end{frame}

\begin{frame}{Lower Single Null (LSN) and Double Null (DN)}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> We compare LSN \textit{vs} DN on a single discharge at
        two levels of density
        \item<2|only@2> At lower density values the radiation is spread among
          upper and lower X-points, whereas at higher density radiation
          is higher at lower X-point
        \item<6|only@6> Blob size increases with density with DN cases always
          exhibiting larger blobs. Still compatible with general density
          scaling. \textcolor{orange}{Radial velocity seems to decrease for DN}
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \includegraphics<1>[trim={0 7.6cm 0 0}, clip, width=\textwidth]{../pdfbox/Fig5}
      \includegraphics<2>[width=\textwidth]{../pdfbox/Fig5c}
      \only<6>{
        \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig9}
          \draw [->, thick, orange] (0.33, 0.33) -- (0.83, 0.21);
        \end{tikzonimage}
      }
    \end{column}
  \end{columns}
  \only<3>{
    \begin{itemize}
      \item At the LFS target, DN density profile at lower level of
        density is reduced and closer to 
        what observed at higher density
      \end{itemize}
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5e}
        \draw [dashed, red, ultra thick] (0.7, 0.37) -- (0.3, 0.37);
        \draw [->, dashed, red, ultra thick] (0.3, 0.7) -- (0.3, 0.38);
      \end{tikzonimage}
    }
  \only<4-5>{
    \begin{itemize}
      \item Upstream profile suggests that a stronger tendency of
        developing density shoulder is observed in DN 
      \end{itemize}
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5d}
        \only<5>{\draw[dashed, red, thick] (1.0, 0.55) -- (0.1, 0.55);}
      \end{tikzonimage}
    }

\end{frame}

\begin{frame}{Upper, Lower and Double Null}
    \Fontvi
    \begin{itemize}
      \item The same density ramp performed in Upper, Lower and Double
        null with all the Strikes points at the inner wall
      \item This allow to test any possible dependence from $\nabla
        B_i$ drift direction. C-Mod suggests difference in the medium
        density range \parencite{LaBombard:2004kg}
    \end{itemize}
    \centering{\includegraphics[width=0.9\textwidth]{../pdfbox/Fig1b}}
\end{frame}
\begin{frame}{Upper, Lower and Double Null}
    \Fontvi
    \begin{itemize}
      \item<2-> Lower and Double null blob size scale consistently with
        density scaling
      \item<3->  Upper Single null always exhibits
        larger blob
      \end{itemize}
      \vspace{-0.27cm}
    \centering{\includegraphics<1>[width=.6\textwidth]{../pdfbox/Fig11b_Series1}}
    \centering{\includegraphics<2>[width=.6\textwidth]{../pdfbox/Fig11b_Series2}}
    \centering{\includegraphics<3>[width=.6\textwidth]{../pdfbox/Fig11b_Series3}}
\end{frame}

\begin{frame}{Summary}
  \Fontvi
  \begin{itemize}
  \item<1-> $\lambda_n = |\nabla n_e/n_e|^{-1}$ computed around 1cm from the
    separatrix
  \item<2-> $\lambda_n$ clearly increases with $\Theta = (\delta_b
        R^{1/5}/L_{\parallel}^{2/5}\rho_s^{4/5})^{5/2}$,
    i.e. with blob-size
  \item<3-> \alert{The dependence on L$_{\parallel}$ is marginal
      although we obtain 
      larger $\Theta$ at smaller $L_{\parallel}$}.
  \item<4-> The increase of $\lambda_n$ is consistent with an increase
    of perpendicular to parallel losses
  \item<5-> The dependence on $\Lambda_{div}$ is weaker than in
    AUG/JET. \onslide<6>{\textcolor{ta3chameleon}{ Large $\Lambda$ is not
        sufficient for flat profile.}}

  \end{itemize}
  \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig10c}
    \only<1>{\fill[white] (0, 0) rectangle (1, 1);}
    \only<2>{\fill[white] (0.348,0) rectangle (1,1); }    
    \only<3>{\fill[white] (0.348,0) rectangle (0.897,1); }    
    \only<4>{\fill[white] (0.62,0) rectangle (0.897,1); }    
    \only<6>{
      \draw [thick, ta3chameleon, thick, rotate = 4] (0.865,0.2) ellipse (0.04 and 0.2);
      \draw [thick, ta3chameleon, thick, rotate = 3] (0.72,0.6) ellipse (0.03 and 0.15);
 }    
    \end{tikzonimage}
\end{frame}

\end{document}
%\draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);

### 2016-11-08 Presentation/gpm_november2016_vianello.tex
Start the presentation

@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=23rd SOLDiv ITPA,venue=Naka, date=25/10/2016, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
-\bibliography{../biblio}
+\bibliography{biblio}
 \renewcommand*{\bibfont}{\footnotesize}
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Latest results from TCV}
-\date{25 October 2016}
-\author[N.Vianello]{presented by N. Vianello}
+\title{Topic 21: Filamentary transport in high-power H-mode conditions and in
+  no/small-ELM regimes to predict heat and particle loads on PFCs for
+  future devices}
+\date{15 November 2016}
+\author[N.Vianello]{J. Madsen and N. Vianello}
 \begin{document}
@@
 \maketitle
-\begin{frame}{Scientific team}
-\centering{N. Vianello$^{1,2}$, C. Tsui$^{3,2}$, C. Theiler$^2$,
-  S. Allan$^4$, J. Boedo$^3$, B. Labit$^2$, H. Reimerdes$^2$, K. Verhaegh$^{5}$,
-  W. Vijvers$^6$, N. Walkden$^4$,  S. Costea$^7$, J. Kovacic$^{8}$, C. Ionita$^{7}$, 
-V. Naulin$^9$, A. H. Nielsen$^9$, J. J. Rasmussen$^9$, B. Schneider$^7$, 
-R. Schrittwieser$^7$, M. Spolaore$^1$, 
-D. Carralero$^{10}$, J. Madsen$^9$, the TCV Team and the EUROfusion MST1 Team}
+\begin{frame}{Present status}
+  \setbeamercovered{transparent}
+  \begin{enumerate}[<+(1) | invisible@-+>]
+    \item Recent experimental and theoretical investigation agrees on
+      suggesting SOL density profiles is determined by a balance
+      between outward convective filamentary transport and parallel dynamics
+    \item The
 
-\centering{\footnotesize
-\textit{$^1$Consorzio
-RFX,  Padova, Italy, $^2$Swiss Plasma Center (SPC), EPFL Lausanne, Switzerland,
-  $^3$UCSD,  La Jolla, USA, $^4$CCFE,  Culham UK, $^5$York Plasma Institute, University of York, York, UK,
-$^6$FOM Institute DIFFER, The Netherlands, $^7$Institute for Ion Physics and Applied Physics,
-Innsbruck,  Austria, $^{8}$Jozef Stefan Institute, Ljubljana, $^9$DTU,  Copenhagen, Denmark, $^{10}$Max-Plank-Institut fur Plasmaphysik, Garching, Germany}}
+  \end{itemize}
 \end{frame}
-\begin{frame}{Background and objectives}
-\only<1>{
-\begin{itemize}
-\item Role of turbulence transport in the SOL saturation is a well
-  know
-  feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
-  density, even without reaching detachment SOL profile tend to flatten}
-\end{itemize}}
-\only<2-3>{
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item Present understanding suggests that a transition of filament
-        propagation regime is dominated by effective
-        collisionality $\Lambda$ \parencite{Myra:2006p2754}
-        \begin{equation*}
-          \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
-        \end{equation*}
-        \item<3> \textcolor{red}{At constant blob size, increasing
-            collisionality provide a change in the filaments velocity
-            scaling properties}
-      \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-%      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
-        \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/FigMyra}
-          \only<3>{
-            \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
-        \end{tikzonimage}
-    \end{column}
-  \end{columns}
-}
-\only<4-6>{
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
-        process and a transition from
-        \textcolor{ta3chameleon}{sheath-limited}
-        \onslide<5-6>{to \textcolor{blue}{inertial regime}} 
-        \item<6> \textcolor{red}{Tested by changing n$_e$
-            and $T_e$ through fueling/seeding/heating}
-      \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/KoMFig2.png}
-        \only<4-6>{
-          \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
-      }
-        \only<5-6>{
-          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
-      }
-        \only<6>{
-          \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
-      }
-    \end{tikzonimage}
-  \end{column}
-  \end{columns}
-}
-\only<7->{
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item MAST \parencite{Militello:2016hk} and old TCV
-        \parencite{Garcia:2007p2615} data 
-        suggested and I$_P$ dependence. 
-          \textcolor{red}{At higher current and
-        same density SOL shoulder disappear} 
-      \item<8> \textcolor{ta3chameleon}{Being shoulder formation
-          induced by a change of $\Gamma_{\perp}$ \textit{vs}
-          $\Gamma_{\parallel}$ balance we will try to test dependence
-          on L$_{\parallel}$}
-    \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \includegraphics[width=\textwidth]{../pdfbox/Presentation/FigMilitello.pdf}
-    \end{column}
-  \end{columns}
-}
-\centering{\includegraphics<1>[width=1.1\textwidth]{../pdfbox/Presentation/Fig1Presentation}}
-\end{frame}
-
-\begin{frame}{Flux expansion scan/1}
-\vspace{-1cm}
-  \Fontvi
+% \begin{frame}{Background and objectives}
+% \only<1>{
+% \begin{itemize}
+% \item Role of turbulence transport in the SOL saturation is a well
+%   know
+%   feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
+%   density, even without reaching detachment SOL profile tend to flatten}
+% \end{itemize}}
+% \only<2-3>{
 %   \begin{columns}
-  %   \begin{column}{0.3\textwidth}
-      \centering{\includegraphics[width=.75\textwidth]{../pdfbox/Fig1a}}
-      \begin{itemize}
-      \item Parallel connection length varied by scanning 
-        flux expansion during density
-        ramps in ohmically heated discharges. \textcolor{red}{$\nabla B_i$ towards the X-point}
-        %\begin{equation*}
-        \[  f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}\]
-        %\end{equation*}
-        \item Variation of $f_x$ change the volume of flux tube as
-          well as parallel connection length (Increased up to 70\%)
-      \end{itemize}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item Present understanding suggests that a transition of filament
+%         propagation regime is dominated by effective
+%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
+%         \begin{equation*}
+%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
+%         \end{equation*}
+%         \item<3> \textcolor{red}{At constant blob size, increasing
+%             collisionality provide a change in the filaments velocity
+%             scaling properties}
+%       \end{itemize}
 %     \end{column}
-    % \begin{column}{0.7\textwidth}
+%     \begin{column}{0.5\textwidth}
+% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
+%         \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/FigMyra}
+%           \only<3>{
+%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
+%         \end{tikzonimage}
 %     \end{column}
 %   \end{columns}
-\end{frame}
+% }
+% \only<4-6>{
+%   \begin{columns}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
+%         process and a transition from
+%         \textcolor{ta3chameleon}{sheath-limited}
+%         \onslide<5-6>{to \textcolor{blue}{inertial regime}} 
+%         \item<6> \textcolor{red}{Tested by changing n$_e$
+%             and $T_e$ through fueling/seeding/heating}
+%       \end{itemize}
+%     \end{column}
+%     \begin{column}{0.5\textwidth}
+%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/KoMFig2.png}
+%         \only<4-6>{
+%           \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
+%       }
+%         \only<5-6>{
+%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
+%       }
+%         \only<6>{
+%           \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
+%       }
+%     \end{tikzonimage}
+%   \end{column}
+%   \end{columns}
+% }
+% \only<7->{
+%   \begin{columns}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item MAST \parencite{Militello:2016hk} and old TCV
+%         \parencite{Garcia:2007p2615} data 
+%         suggested and I$_P$ dependence. 
+%           \textcolor{red}{At higher current and
+%         same density SOL shoulder disappear} 
+%       \item<8> \textcolor{ta3chameleon}{Being shoulder formation
+%           induced by a change of $\Gamma_{\perp}$ \textit{vs}
+%           $\Gamma_{\parallel}$ balance we will try to test dependence
+%           on L$_{\parallel}$}
+%     \end{itemize}
+%     \end{column}
+%     \begin{column}{0.5\textwidth}
+%       \includegraphics[width=\textwidth]{../pdfbox/Presentation/FigMilitello.pdf}
+%     \end{column}
+%   \end{columns}
+% }
+% \centering{\includegraphics<1>[width=1.1\textwidth]{../pdfbox/Presentation/Fig1Presentation}}
+% \end{frame}
 
-\begin{frame}{Flux expansion scan/2}
-  \Fontvi
-      \begin{itemize}
-      \item<1-> Flux expansion variation induce modification at the target
-      \item<1-> Radiation front from bolometry  moves earlier in
-        density at larger f$_x$. Front movement trails CIII cut-off
-        movement (Reimerdes IAEA 2016)
-      \item<2-> Volumetric recombination rates from $n=6, 7$ balmer line
-        emission \parencite{kevin:jnm} indicates that \textcolor{red}{recombination occurs
-          earlier in density at high $f_x$}
-      \item<3|only@3> \textcolor{ta3skyblue}{This is not confirmed in reversed B$_t$ where
-        increasing the f$_x$ lead to deeper detachment without}
-        changing density threshold  
-    \end{itemize}
-    \only<1-2>{\begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig2c}
-      \only<1>{\fill[white] (0.,0) rectangle (0.52,1); }    
-      \draw [->, ultra thick, black] (0.79,0.69) -- (0.75,0.51);
-    \end{tikzonimage}}
-\centering{\includegraphics<3>[width=.5\textwidth]{../pdfbox/Presentation/XD_detach_HM}}
-  \end{frame}
+% \begin{frame}{Flux expansion scan/1}
+% \vspace{-1cm}
+%   \Fontvi
+%   % \begin{columns}
+%   %   \begin{column}{0.3\textwidth}
+%       \centering{\includegraphics[width=.75\textwidth]{../pdfbox/Fig1a}}
+%       \begin{itemize}
+%       \item Parallel connection length varied by scanning 
+%         flux expansion during density
+%         ramps in ohmically heated discharges. \textcolor{red}{$\nabla B_i$ towards the X-point}
+%         %\begin{equation*}
+%         \[  f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}\]
+%         %\end{equation*}
+%         \item Variation of $f_x$ change the volume of flux tube as
+%           well as parallel connection length (Increased up to 70\%)
+%       \end{itemize}
+%     % \end{column}
+%     % \begin{column}{0.7\textwidth}
+%   %   \end{column}
+%   % \end{columns}
+% \end{frame}
 
-\begin{frame}{Flux expansion scan/3}
-  \vspace{-1cm}
-\Fontvi
-      \begin{itemize}
-      \item Target and upstream profile measured at the same density
-        but different f$_x$
-      \item<3-> Target profiles in the near SOL modified with broader profile at higher
-        f$_x$. \textcolor{red}{Huge variation on $\Lambda_{div}$
-          without upstream modification}
-      \item<4|only@4> \textcolor{ta3chameleon}{Only further increase
-          of density (although $\Lambda_{div}$ in the far SOL
-          decreases) leads to profile broadening}
-      \end{itemize}
-      \centering{\includegraphics<1>[width=.65\textwidth]{../pdfbox/Fig4Series_1}}
-      \centering{\includegraphics<2>[width=.65\textwidth]{../pdfbox/Fig4Series_2}}
-      \centering{\includegraphics<3>[width=.65\textwidth]{../pdfbox/Fig4Series_3}}
-      \centering{\includegraphics<4>[width=.65\textwidth]{../pdfbox/Fig4Series_4}}
-\end{frame}
+% \begin{frame}{Flux expansion scan/2}
+%   \Fontvi
+%       \begin{itemize}
+%       \item<1-> Flux expansion variation induce modification at the target
+%       \item<1-> Radiation front from bolometry  moves earlier in
+%         density at larger f$_x$. Front movement trails CIII cut-off
+%         movement (Reimerdes IAEA 2016)
+%       \item<2-> Volumetric recombination rates from $n=6, 7$ balmer line
+%         emission \parencite{kevin:jnm} indicates that \textcolor{red}{recombination occurs
+%           earlier in density at high $f_x$}
+%       \item<3|only@3> \textcolor{ta3skyblue}{This is not confirmed in reversed B$_t$ where
+%         increasing the f$_x$ lead to deeper detachment without}
+%         changing density threshold  
+%     \end{itemize}
+%     \only<1-2>{\begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig2c}
+%       \only<1>{\fill[white] (0.,0) rectangle (0.52,1); }    
+%       \draw [->, ultra thick, black] (0.79,0.69) -- (0.75,0.51);
+%     \end{tikzonimage}}
+% \centering{\includegraphics<3>[width=.5\textwidth]{../pdfbox/Presentation/XD_detach_HM}}
+%   \end{frame}
 
-\begin{frame}{Filaments effect}
-  \vspace{-1cm}
-\Fontvi
-      \begin{itemize}
-      \item<1-3> Blob properties deduced from fast reciprocating as done in \parencite{Boedo:2001tt}
-      \item<1|only@1> Blob size deduced as $\delta_b = \tau_b v_{\perp}$
-        % \begin{equation*}
-        %   \tau_b = \text{FWHM of CAS} \qquad v_{\perp} = \sqrt{v_{E\times B, r}^2 +
-        %     v_{E\times B, p}^2}
-        % \end{equation*}
-      \item<2-3> No clear dependence on
-          $\Lambda_{div}$ during f$_x$ scan
-      \item<3> \textcolor{ta3chameleon}{When we increase the
-          density filaments are bigger at same $\Lambda_{div}$}
-      \item<4-> \textcolor{ta3skyblue}{On a statistical basis,
-          blob size increases with density without clear dependence on
-          f$_x$ \onslide<5>{\textcolor{red}{as well as $\lambda_n$ in the Far SOL}}}
-      \item<6> \textcolor{ta3chameleon}{Behavior at very high
-          density to be confirmed}  
-      \end{itemize}
-      \centering{\includegraphics<1>[width=.53\textwidth]{../pdfbox/Fig14b}}
-      \centering{\includegraphics<2>[width=.63\textwidth]{../pdfbox/Fig7}}
-      \centering{\includegraphics<3>[width=.63\textwidth]{../pdfbox/Fig7b}}
-      \centering{\includegraphics<4>[width=.85\textwidth]{../pdfbox/Fig12}}
-      \centering{\includegraphics<5>[width=.85\textwidth]{../pdfbox/Fig12b}}
-      \only<6>{
-        \begin{center}
-          \begin{tikzonimage}[width=.85\textwidth]{../pdfbox/Fig12b}
-          \draw [thick, ta3chameleon, thick] (0.75,0.5) ellipse (0.1 and 0.1);
-          \end{tikzonimage}
-        \end{center}
-      }
-\end{frame}
+% \begin{frame}{Flux expansion scan/3}
+%   \vspace{-1cm}
+% \Fontvi
+%       \begin{itemize}
+%       \item Target and upstream profile measured at the same density
+%         but different f$_x$
+%       \item<3-> Target profiles in the near SOL modified with broader profile at higher
+%         f$_x$. \textcolor{red}{Huge variation on $\Lambda_{div}$
+%           without upstream modification}
+%       \item<4|only@4> \textcolor{ta3chameleon}{Only further increase
+%           of density (although $\Lambda_{div}$ in the far SOL
+%           decreases) leads to profile broadening}
+%       \end{itemize}
+%       \centering{\includegraphics<1>[width=.65\textwidth]{../pdfbox/Fig4Series_1}}
+%       \centering{\includegraphics<2>[width=.65\textwidth]{../pdfbox/Fig4Series_2}}
+%       \centering{\includegraphics<3>[width=.65\textwidth]{../pdfbox/Fig4Series_3}}
+%       \centering{\includegraphics<4>[width=.65\textwidth]{../pdfbox/Fig4Series_4}}
+% \end{frame}
 
-\begin{frame}{Current scan/1}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1-3> On a single shape (f$_x \approx 4$) current scan with
-        similar density ramps performed
-      \item<2-3> \textcolor{red}{At lower current indication of shoulder for $R-R_{sep}
-        \geq 1$ cm which disappear at higher current (same density)}
-      \item<3> \textcolor{ta3chameleon}{At even higher current we need to substantially
-        increase the fueling (even if at the same $n/n_G$)}
-      \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \only<1-2>{
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series1}
-        \only<2>{
-          \draw [thick, red, thick] (0.75,0.75) ellipse (0.2 and 0.1);
-        }
-      \end{tikzonimage} }
-    \only<3>{
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series2}
-          \draw [thick, ta3chameleon, thick] (0.67,0.35) ellipse (0.22 and 0.1);
-          \draw [thick, ta3chameleon, thick] (0.5,0.14) ellipse (0.3 and 0.03);
-        \end{tikzonimage}      
-      }
-    \end{column}
-  \end{columns}
-\end{frame}
+% \begin{frame}{Filaments effect}
+%   \vspace{-1cm}
+% \Fontvi
+%       \begin{itemize}
+%       \item<1-3> Blob properties deduced from fast reciprocating as done in \parencite{Boedo:2001tt}
+%       \item<1|only@1> Blob size deduced as $\delta_b = \tau_b v_{\perp}$
+%         % \begin{equation*}
+%         %   \tau_b = \text{FWHM of CAS} \qquad v_{\perp} = \sqrt{v_{E\times B, r}^2 +
+%         %     v_{E\times B, p}^2}
+%         % \end{equation*}
+%       \item<2-3> No clear dependence on
+%           $\Lambda_{div}$ during f$_x$ scan
+%       \item<3> \textcolor{ta3chameleon}{When we increase the
+%           density filaments are bigger at same $\Lambda_{div}$}
+%       \item<4-> \textcolor{ta3skyblue}{On a statistical basis,
+%           blob size increases with density without clear dependence on
+%           f$_x$ \onslide<5>{\textcolor{red}{as well as $\lambda_n$ in the Far SOL}}}
+%       \item<6> \textcolor{ta3chameleon}{Behavior at very high
+%           density to be confirmed}  
+%       \end{itemize}
+%       \centering{\includegraphics<1>[width=.53\textwidth]{../pdfbox/Fig14b}}
+%       \centering{\includegraphics<2>[width=.63\textwidth]{../pdfbox/Fig7}}
+%       \centering{\includegraphics<3>[width=.63\textwidth]{../pdfbox/Fig7b}}
+%       \centering{\includegraphics<4>[width=.85\textwidth]{../pdfbox/Fig12}}
+%       \centering{\includegraphics<5>[width=.85\textwidth]{../pdfbox/Fig12b}}
+%       \only<6>{
+%         \begin{center}
+%           \begin{tikzonimage}[width=.85\textwidth]{../pdfbox/Fig12b}
+%           \draw [thick, ta3chameleon, thick] (0.75,0.5) ellipse (0.1 and 0.1);
+%           \end{tikzonimage}
+%         \end{center}
+%       }
+% \end{frame}
 
-\begin{frame}{Current scan/2}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item On a statistical basis we have a slight
-        reduction of radial velocity of the filaments as in MAST \parencite{Kirk:2016jj} with unclear
-        effect on blob-size
-      \end{itemize}
-    \end{column}
-      \begin{column}{0.5\textwidth}
-     \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig8}
-       \draw [->, ultra thick, red, dashed] (0.33,0.37) -- (0.7,0.27);
-     \end{tikzonimage}
-   \end{column}
-  \end{columns}
-  \end{frame}
+% \begin{frame}{Current scan/1}
+%   \begin{columns}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item<1-3> On a single shape (f$_x \approx 4$) current scan with
+%         similar density ramps performed
+%       \item<2-3> \textcolor{red}{At lower current indication of shoulder for $R-R_{sep}
+%         \geq 1$ cm which disappear at higher current (same density)}
+%       \item<3> \textcolor{ta3chameleon}{At even higher current we need to substantially
+%         increase the fueling (even if at the same $n/n_G$)}
+%       \end{itemize}
+%     \end{column}
+%     \begin{column}{0.5\textwidth}
+%       \only<1-2>{
+%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series1}
+%         \only<2>{
+%           \draw [thick, red, thick] (0.75,0.75) ellipse (0.2 and 0.1);
+%         }
+%       \end{tikzonimage} }
+%     \only<3>{
+%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series2}
+%           \draw [thick, ta3chameleon, thick] (0.67,0.35) ellipse (0.22 and 0.1);
+%           \draw [thick, ta3chameleon, thick] (0.5,0.14) ellipse (0.3 and 0.03);
+%         \end{tikzonimage}      
+%       }
+%     \end{column}
+%   \end{columns}
+% \end{frame}
 
-\begin{frame}{Lower Single Null (LSN) and Double Null (DN)}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1|only@1> We compare LSN \textit{vs} DN on a single discharge at
-        two levels of density
-        \item<2|only@2> At lower density values the radiation is spread among
-          upper and lower X-points, whereas at higher density radiation
-          is higher at lower X-point
-        \item<6|only@6> Blob size increases with density with DN cases always
-          exhibiting larger blobs. Still compatible with general density
-          scaling. \textcolor{orange}{Radial velocity seems to decrease for DN}
-      \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \includegraphics<1>[trim={0 7.6cm 0 0}, clip, width=\textwidth]{../pdfbox/Fig5}
-      \includegraphics<2>[width=\textwidth]{../pdfbox/Fig5c}
-      \only<6>{
-        \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig9}
-          \draw [->, thick, orange] (0.33, 0.33) -- (0.83, 0.21);
-        \end{tikzonimage}
-      }
-    \end{column}
-  \end{columns}
-  \only<3>{
-    \begin{itemize}
-      \item At the LFS target, DN density profile at lower level of
-        density is reduced and closer to 
-        what observed at higher density
-      \end{itemize}
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5e}
-        \draw [dashed, red, ultra thick] (0.7, 0.37) -- (0.3, 0.37);
-        \draw [->, dashed, red, ultra thick] (0.3, 0.7) -- (0.3, 0.38);
-      \end{tikzonimage}
-    }
-  \only<4-5>{
-    \begin{itemize}
-      \item Upstream profile suggests that a stronger tendency of
-        developing density shoulder is observed in DN 
-      \end{itemize}
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5d}
-        \only<5>{\draw[dashed, red, thick] (1.0, 0.55) -- (0.1, 0.55);}
-      \end{tikzonimage}
-    }
+% \begin{frame}{Current scan/2}
+%   \begin{columns}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item On a statistical basis we have a slight
+%         reduction of radial velocity of the filaments as in MAST \parencite{Kirk:2016jj} with unclear
+%         effect on blob-size
+%       \end{itemize}
+%     \end{column}
+%       \begin{column}{0.5\textwidth}
+%      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig8}
+%        \draw [->, ultra thick, red, dashed] (0.33,0.37) -- (0.7,0.27);
+%      \end{tikzonimage}
+%    \end{column}
+%   \end{columns}
+%   \end{frame}
 
-\end{frame}
+% \begin{frame}{Lower Single Null (LSN) and Double Null (DN)}
+%   \begin{columns}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item<1|only@1> We compare LSN \textit{vs} DN on a single discharge at
+%         two levels of density
+%         \item<2|only@2> At lower density values the radiation is spread among
+%           upper and lower X-points, whereas at higher density radiation
+%           is higher at lower X-point
+%         \item<6|only@6> Blob size increases with density with DN cases always
+%           exhibiting larger blobs. Still compatible with general density
+%           scaling. \textcolor{orange}{Radial velocity seems to decrease for DN}
+%       \end{itemize}
+%     \end{column}
+%     \begin{column}{0.5\textwidth}
+%       \includegraphics<1>[trim={0 7.6cm 0 0}, clip, width=\textwidth]{../pdfbox/Fig5}
+%       \includegraphics<2>[width=\textwidth]{../pdfbox/Fig5c}
+%       \only<6>{
+%         \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig9}
+%           \draw [->, thick, orange] (0.33, 0.33) -- (0.83, 0.21);
+%         \end{tikzonimage}
+%       }
+%     \end{column}
+%   \end{columns}
+%   \only<3>{
+%     \begin{itemize}
+%       \item At the LFS target, DN density profile at lower level of
+%         density is reduced and closer to 
+%         what observed at higher density
+%       \end{itemize}
+%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5e}
+%         \draw [dashed, red, ultra thick] (0.7, 0.37) -- (0.3, 0.37);
+%         \draw [->, dashed, red, ultra thick] (0.3, 0.7) -- (0.3, 0.38);
+%       \end{tikzonimage}
+%     }
+%   \only<4-5>{
+%     \begin{itemize}
+%       \item Upstream profile suggests that a stronger tendency of
+%         developing density shoulder is observed in DN 
+%       \end{itemize}
+%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5d}
+%         \only<5>{\draw[dashed, red, thick] (1.0, 0.55) -- (0.1, 0.55);}
+%       \end{tikzonimage}
+%     }
 
-\begin{frame}{Upper, Lower and Double Null}
-    \Fontvi
-    \begin{itemize}
-      \item The same density ramp performed in Upper, Lower and Double
-        null with all the Strikes points at the inner wall
-      \item This allow to test any possible dependence from $\nabla
-        B_i$ drift direction. C-Mod suggests difference in the medium
-        density range \parencite{LaBombard:2004kg}
-    \end{itemize}
-    \centering{\includegraphics[width=0.9\textwidth]{../pdfbox/Fig1b}}
-\end{frame}
-\begin{frame}{Upper, Lower and Double Null}
-    \Fontvi
-    \begin{itemize}
-      \item<2-> Lower and Double null blob size scale consistently with
-        density scaling
-      \item<3->  Upper Single null always exhibits
-        larger blob
-      \end{itemize}
-      \vspace{-0.27cm}
-    \centering{\includegraphics<1>[width=.6\textwidth]{../pdfbox/Fig11b_Series1}}
-    \centering{\includegraphics<2>[width=.6\textwidth]{../pdfbox/Fig11b_Series2}}
-    \centering{\includegraphics<3>[width=.6\textwidth]{../pdfbox/Fig11b_Series3}}
-\end{frame}
+% \end{frame}
 
-\begin{frame}{Summary}
-  \Fontvi
-  \begin{itemize}
-  \item<1-> $\lambda_n = |\nabla n_e/n_e|^{-1}$ computed around 1cm from the
-    separatrix
-  \item<2-> $\lambda_n$ clearly increases with $\Theta = (\delta_b
-        R^{1/5}/L_{\parallel}^{2/5}\rho_s^{4/5})^{5/2}$,
-    i.e. with blob-size
-  \item<3-> \alert{The dependence on L$_{\parallel}$ is marginal
-      although we obtain 
-      larger $\Theta$ at smaller $L_{\parallel}$}.
-  \item<4-> The increase of $\lambda_n$ is consistent with an increase
-    of perpendicular to parallel losses
-  \item<5-> The dependence on $\Lambda_{div}$ is weaker than in
-    AUG/JET. \onslide<6>{\textcolor{ta3chameleon}{ Large $\Lambda$ is not
-        sufficient for flat profile.}}
+% \begin{frame}{Upper, Lower and Double Null}
+%     \Fontvi
+%     \begin{itemize}
+%       \item The same density ramp performed in Upper, Lower and Double
+%         null with all the Strikes points at the inner wall
+%       \item This allow to test any possible dependence from $\nabla
+%         B_i$ drift direction. C-Mod suggests difference in the medium
+%         density range \parencite{LaBombard:2004kg}
+%     \end{itemize}
+%     \centering{\includegraphics[width=0.9\textwidth]{../pdfbox/Fig1b}}
+% \end{frame}
+% \begin{frame}{Upper, Lower and Double Null}
+%     \Fontvi
+%     \begin{itemize}
+%       \item<2-> Lower and Double null blob size scale consistently with
+%         density scaling
+%       \item<3->  Upper Single null always exhibits
+%         larger blob
+%       \end{itemize}
+%       \vspace{-0.27cm}
+%     \centering{\includegraphics<1>[width=.6\textwidth]{../pdfbox/Fig11b_Series1}}
+%     \centering{\includegraphics<2>[width=.6\textwidth]{../pdfbox/Fig11b_Series2}}
+%     \centering{\includegraphics<3>[width=.6\textwidth]{../pdfbox/Fig11b_Series3}}
+% \end{frame}
 
-  \end{itemize}
-  \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig10c}
-    \only<1>{\fill[white] (0, 0) rectangle (1, 1);}
-    \only<2>{\fill[white] (0.348,0) rectangle (1,1); }    
-    \only<3>{\fill[white] (0.348,0) rectangle (0.897,1); }    
-    \only<4>{\fill[white] (0.62,0) rectangle (0.897,1); }    
-    \only<6>{
-      \draw [thick, ta3chameleon, thick, rotate = 4] (0.865,0.2) ellipse (0.04 and 0.2);
-      \draw [thick, ta3chameleon, thick, rotate = 3] (0.72,0.6) ellipse (0.03 and 0.15);
- }    
-    \end{tikzonimage}
-\end{frame}
+% \begin{frame}{Summary}
+%   \Fontvi
+%   \begin{itemize}
+%   \item<1-> $\lambda_n = |\nabla n_e/n_e|^{-1}$ computed around 1cm from the
+%     separatrix
+%   \item<2-> $\lambda_n$ clearly increases with $\Theta = (\delta_b
+%         R^{1/5}/L_{\parallel}^{2/5}\rho_s^{4/5})^{5/2}$,
+%     i.e. with blob-size
+%   \item<3-> \alert{The dependence on L$_{\parallel}$ is marginal
+%       although we obtain 
+%       larger $\Theta$ at smaller $L_{\parallel}$}.
+%   \item<4-> The increase of $\lambda_n$ is consistent with an increase
+%     of perpendicular to parallel losses
+%   \item<5-> The dependence on $\Lambda_{div}$ is weaker than in
+%     AUG/JET. \onslide<6>{\textcolor{ta3chameleon}{ Large $\Lambda$ is not
+%         sufficient for flat profile.}}
+
+%   \end{itemize}
+%   \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig10c}
+%     \only<1>{\fill[white] (0, 0) rectangle (1, 1);}
+%     \only<2>{\fill[white] (0.348,0) rectangle (1,1); }    
+%     \only<3>{\fill[white] (0.348,0) rectangle (0.897,1); }    
+%     \only<4>{\fill[white] (0.62,0) rectangle (0.897,1); }    
+%     \only<6>{
+%       \draw [thick, ta3chameleon, thick, rotate = 4] (0.865,0.2) ellipse (0.04 and 0.2);
+%       \draw [thick, ta3chameleon, thick, rotate = 3] (0.72,0.6) ellipse (0.03 and 0.15);
+%  }    
+%     \end{tikzonimage}
+% \end{frame}
 

### 2016-11-08 Presentation/gpm_november2016_vianello.tex
update of presentation

@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Topic 21: Filamentary transport in high-power H-mode conditions and in
+\title{Filamentary transport in high-power H-mode conditions and in
   no/small-ELM regimes to predict heat and particle loads on PFCs for
@@
 \date{15 November 2016}
-\author[N.Vianello]{J. Madsen and N. Vianello}
+\author[J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
 \begin{document}
@@
       suggesting SOL density profiles is determined by a balance
-      between outward convective filamentary transport and parallel dynamics
-    \item The
+      between radial convective filamentary transport and parallel dynamics
+    \item The balance is observed to change at high density in L-Mode
+      and this is at the basis of the \emph{shoulder formation}
+    \item This is observed in a variety of devices including AUG \parencite{Carralero:2014gs},
+      TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
+    \item The observations exhibit a dependence on I$_p$ (increasing
+      the current at constant B$_{\phi}$ shoulder tends to disappear)
+    \item The H-Mode behavior is still a work in progress and exhibit
+      a dependence on the level of \alert{fueling}
+    \item L-Mode and H-Mode behavior are not yet reconciled and
+      different devices show somehow contradictory behavior
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}{L-Mode studies}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
+        process and a transition from
+        \textcolor{ta3chameleon}{sheath-limited}
+        to \textcolor{blue}{inertial regime}
+        \item<2-> \textcolor{red}{Tested by changing n$_e$
+            and $T_e$ through fueling/seeding/heating}
+        \item<3> This determines a change of the velocity-size scaling
 
       \end{itemize}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \only<1-2>{
+      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15a}
+          \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
+          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
+        \only<2>{
+          \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
+        }
+      \end{tikzonimage}}
+    \only<3>{
+      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15b}
+          \draw [ultra thick, ta3chameleon, thick, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
+          \draw [thick, blue, ultra thick, rotate=18] (0.65,0.05) ellipse (0.35 and 0.1);
+      \end{tikzonimage}
+    }
+    \end{column}
+  \end{columns}
 \end{frame}

### 2016-11-09 Presentation/gpm_november2016_vianello.tex
Added a bunch of figures and update to slides
Finished the L-Mode description from AUG/TCV/JET

--- 2016-11-08 Presentation/gpm_november2016_vianello.tex
@@
       suggesting SOL density profiles is determined by a balance
-      between outward convective filamentary transport and parallel dynamics
-    \item The
+      between radial convective filamentary transport and parallel dynamics
+    \item The balance is observed to change at high density in L-Mode
+      and this is at the basis of the \emph{shoulder formation}
+    \item This is observed in a variety of devices including AUG \parencite{Carralero:2014gs},
+      TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
+    \item The observations exhibit various dependence on Divertor
+      Collisionality, Plasma current,  seeding. \alert{Results from
+        different devices not fully reconciled.}
+    \item The H-Mode behavior is still a work in progress and exhibit
+      a dependence on the level of \alert{fueling}
+    \item First we will report a summary of the achievements and then
+     personal comments and plans
+    \end{enumerate}
+\end{frame}
+\section{L-Mode}
+\begin{frame}{L-Mode studies: AUG/1}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that
+        \begin{equation*}
+        \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
+      \end{equation*}
+      dominates this
+        process and a transition from
+        \textcolor{ta3chameleon}{sheath-limited}
+        to \textcolor{blue}{inertial regime}
+        \item<2-> \textcolor{red}{Tested by changing n$_e$
+            and $T_e$ through fueling/seeding/heating}
+        \item<3-> This determines a change of the velocity-size
+          scaling. \onslide<4>{\alert{$\Lambda_{div}$ rules the density profile scale
+          length}} 
+        \end{itemize}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \only<1-2>{
+      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15a}
+          \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
+          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
+        \only<2>{
+          \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
+        }
+      \end{tikzonimage}}
+    \only<3>{
+      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15b}
+          \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
+          \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
+      \end{tikzonimage}
+    }
+    \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15c}
+    \end{column}
+  \end{columns}
+\end{frame}
+\begin{frame}{L-Mode studies: AUG/2}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1-> Profile modified by increase of blob-size and change of
+        \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
+        \onslide<2->{\textcolor{blue}{and filament relative density}
+          {\footnotesize (Carralero 2016 in preparation)}}
+      \item<3-> As a consequence the contribution of filaments to
+        radial transport increases
+      \item<4> Parallel flow is strongly reduced whenever we increase
+        the divertor collisionality
+      \end{itemize}
+    \end{column}
+      \begin{column}{0.5\textwidth}
+        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16a}
+        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16b}
+        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16c}
+        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16d}
+      \end{column}
+    \end{columns}
+  \end{frame}
 
+  \begin{frame}{L-Mode studies:AUG/3}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1-> Electron and ions behave differently
+      \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
+        accross the SOL and slightly affected by the increase of
+        divertor collisionality
+      \item<3|only@3> Ions are strongly affected: for
+        \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
+          and $\lambda_{T_i} \sim 30$
+          mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
+          T$_{i, bk}\sim 25$ eV
+          and $\lambda_{T_i} \sim 8$ mm}
+       \item<4-> Ion energy spectrum from
+         $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
+         energy for $\Lambda_{div} > 1$
+       \item<5> EMC3-Eirene simulation suggests that such a reduction
+         can't be accounted for thermalization process. An
+         \alert{ionization front builds in front of the limiter shadow}   
        \end{itemize}
+    \end{column}
+      \begin{column}{0.5\textwidth}
+        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16e}
+        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16f}
+        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16g}
+        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16h}
+      \end{column}
+    \end{columns}
   \end{frame}
-% \begin{frame}{Background and objectives}
+
+  \begin{frame}{L-Mode: TCV}
+    \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
+        dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
+        \begin{equation*}
+          f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
+        \end{equation*}
+        in ohmic density ramps \parencite{vianello:iaea2016}
+      \item<2|only@2> Slight variation of density profiles at the target but
+        due to direct dependence on L$_{\parallel}$ large increase of
+        $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
+        we reach a certain amount of $\langle n_e \rangle$}
+       \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
+        \onslide<4-5>{\textcolor{red}{also on a statistical
+            basis}}. \onslide<5>{Strong dependence on average density,
+          independent of L$_{\parallel}$}}
+       \item<6|only@6> $\lambda_n$ depends clearly on blob-size
+         whereas the dependence on divertor condition is less
+         obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
+      \end{itemize}
+    \end{column}
+      \begin{column}{0.5\textwidth}
+        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16a}
+        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16b}
+        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16c}
+        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16d}
+        \includegraphics<6>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16e}
+      \end{column}
+    \end{columns}
+  \end{frame}
+
+  \begin{frame}{L-Mode: JET}
+    \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1|only@1> The shoulder formation strongly depends on
+        divertor geometry, disappear with vertical target and strike
+        point closest to cryogenics pumps \parencite{Wynn:EPS2016}
+      \item<2|only@2> The midplane pressure from baratrons is
+        equivalent between the different divertor. \alert{This would
+          indicate that SOL neutral density does not play any role}
+       \item<3|only@3> In the horizontal target configuration the
+         results indicate that the shoulder forms right at the
+         transition from sheath-limited to high-recycling where also
+         $\Lambda_{div}$ strongly increase
+       \item<4|only@4> Shoulder amplitude correlates with strike
+         points position. \alert{Shoulder, ionization and
+           $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
+         from the pump}
+       \item<5|only@5> In seeded discharges the transition observed at
+         very high level of $\Lambda_{div} >> 1$
+      \end{itemize}
+    \end{column}
+      \begin{column}{0.5\textwidth}
+        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16a}
+        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16b}
+        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16c}
+        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16d}
+        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16e}
+      \end{column}
+    \end{columns}
+
+  \end{frame}
   % \only<1>{

### 2016-11-09 Presentation/gpm_november2016_vianello.tex
Update to the presentation
Included MAST L-Mode, AUG H-Mode and open issues

@@
     \end{columns}
+  \end{frame}
+
+  \begin{frame}{L-Mode: MAST}
+    \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item<1|only@1> Strong dependence on
+        I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
+        constant toroidal field shoulder disapper. Consistent with
+        observation in other devices
+      \item<2|only@2> Filaments binormal dimension increases with
+        current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
+       \item<3|only@3> Filament radial velocity decreases with current
+         as well as the radial dimension \parencite{Kirk:2016jj}
+      \end{itemize}
+    \end{column}
+      \begin{column}{0.5\textwidth}
+        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MilitelloNF16a}
+        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16a}
+        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16c}
+      \end{column}
+    \end{columns}
+  \end{frame}
+
+  \section{H-Mode}
+  \begin{frame}{AUG: H-Mode}
+    \begin{columns}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+      \item<1|only@1> SOL profiles in H-Mode so far investigated on
+        AUG \parencite{Muller:2015jt,Sun:2015bu}
+      \item<2|only@2> Differently from L-Mode, complete detachment
+        suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
+       \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
+         shoulder depends on a combination of $\Lambda_{div}$ and
+         fueling rate
+      \end{itemize}
+    \end{column}
+      \begin{column}{0.6\textwidth}
+        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MuellerJNM15a}
+        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/SunPPCF15a}
+        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16i}
+      \end{column}
+    \end{columns}
+  \end{frame}
+
+  \section{Open issue}
+  \begin{frame}{Open and unresolved issues}
+  \setbeamercovered{transparent}
+  \begin{enumerate}[<+(1) | invisible@-+>]
+    \item Does $\Lambda_{div}$ unifies the picture among the devices?
+      \alert{No, a dependence on neutral pressure is likely to play a role}
+    \item If neutrals play a role is the divertor or midplane?
+      \alert{Contradictory results if one include experiments with
+        midplane puffing, JET and EIRENE simulations}
+    \item Does L$_\parallel$ plays any role? \alert{So far TCV suggests no
+      dependence from f$_x$ scan but both TCV and MAST observe an
+      I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
+      increases with L$_{\parallel}$ }
+    \item Cooling the divertor with fueling or seeding is really
+      equivalent? \alert{Contradictory observation in AUG and JET}
+    \item Can be translate straightforward from L to H-Mode? \alert{So
+      far no as shown in H-Mode AUG. We need higher detachment
+      condition and we need enough fueling}
+    \end{enumerate}
 

### 2016-11-10 Presentation/gpm_november2016_vianello.tex
after crash bare stikord

@@
-\documentclass[10pt, compress]{beamer}
+\documentclass[10pt, compress, draft]{beamer}
 \usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
-\usepackage{tangocolors}
-\usepackage{rfxcolor}
+\usepackage{../beamerclass/tangocolors}
+\usepackage{../beamerclass/rfxcolor}
 % for drawing
@@
 \usetikzlibrary{arrows,shapes,backgrounds}
-\usepackage{onimage}
+\usepackage{../beamerclass/onimage}
 \usepackage[export]{adjustbox}
@@
     \end{enumerate}
+
+  \end{frame}
+
+\section{Topic 21 experiments }
+\begin{frame}{more proposed shots than allocated}
+	\begin{itemize}
+		\item totla number propose shots 449
+		\item ebven though combined we have to prioritize
+		\item prioritize cross comparison 
+		\item 
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{Focal points}
+	Hmode (Proponentrs)
+	L-mode :  neutrals Ip scan
+\end{frame}
+
+\begin{frame}{requirements form cross machine comparison }
+same configuration, SN Btimes grad b, cryo pumps, greenwald fraction, heating
+
+same diagnostics Isat blob speed, density profiles (Libes reflectometry), , divertor n and Te, fast camera plus n and te measure at OM
+
+status of cameras on devices
 

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
try to recreate changes made bvefore xrash 	modified:   gpm_november2016_vianello.tex

@@
 \date{15 November 2016}
-\author[J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
+\author[Topic 21. J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
 \begin{document}
@@
 \maketitle
+
+\begin{frame}{Main focus of topic 21 is shoulder formation}
+\vspace{-1cm}
+Objectives:
+\begin{enumerate}
+\item Use the new HHF probe on AUG to study filamentary transport under
+high-power H-mode conditions and under different plasma configurations (SN,
+DN).
+\item Study the role of ELM regimes, neutral compression, and particle density in
+filamentary transport and related shoulder formation.
+\item Identify the contribution of collisionality and seeding on filamentary transport
+and related shoulder formation.
+\item Extend the studies to quiescent H-modes as well as to other small-ELM regimes.
+\item Determine the effect of filaments and shoulder formation on target heat loads
+in different H-mode plasmas.
+\item Investigate the effect of plasma shape and configuration on ELM-induced heat
+loads.
+\end{enumerate}
+\underline{Motivation}: Particle and energy transport in the SOL is crucial for the lifetime of plasma facing components in ITER and DEMO
+\end{frame}
+
+\section{Background}
 \begin{frame}{Present status}
@@
   \begin{enumerate}[<+(1) | invisible@-+>]
-    \item Recent experimental and theoretical investigation agrees on
-      suggesting SOL density profiles is determined by a balance
-      between radial convective filamentary transport and parallel dynamics
-    \item The balance is observed to change at high density in L-Mode
-      and this is at the basis of the \emph{shoulder formation}
-    \item This is observed in a variety of devices including AUG \parencite{Carralero:2014gs},
+    \item Experimental and theoretical investigations suggest that SOL density profiles are  determined by the balance between radial filamentary transport and parallel dynamics
+    \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
+    \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
       TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
-    \item The observations exhibit various dependence on Divertor
-      Collisionality, Plasma current,  seeding. \alert{Results from
-        different devices not fully reconciled.}
-    \item The H-Mode behavior is still a work in progress and exhibit
-      a dependence on the level of \alert{fueling}
-    \item First we will report a summary of the achievements and then
-     personal comments and plans
+    \item Observations exhibit various dependencies on divertor
+      collisionality, plasma current,  seeding. \alert{Results from
+        different devices not fully reconciled and the underlying mechanism is not fully understood.}
+    \item Studies of shoulder formation in H-Mode are so far limited 
+	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
+%    \item First we will report a summary of the achievements and then
+ %    personal comments and plans
     \end{enumerate}
@@
       \end{equation*}
-      dominates this
-        process and a transition from
-        \textcolor{ta3chameleon}{sheath-limited}
-        to \textcolor{blue}{inertial regime}
+      controls shoulder formation
         \item<2-> \textcolor{red}{Tested by changing n$_e$
@@
         \item<3-> This determines a change of the velocity-size
-          scaling. \onslide<4>{\alert{$\Lambda_{div}$ rules the density profile scale
+          scaling from
+        \textcolor{ta3chameleon}{sheath-limited}
+        to \textcolor{blue}{inertial regime}. \onslide<4>{\alert{$\Lambda_{div}$ rules the density profile scale
           length}} 
@@
         equivalent between the different divertor. \alert{This would
-          indicate that SOL neutral density does not play any role}
+          indicate that SOL neutral density at the outboard midplane does not play any role}
        \item<3|only@3> In the horizontal target configuration the
@@
         I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
-        constant toroidal field shoulder disapper. Consistent with
+        constant toroidal field shoulder disappears. Consistent with
         observation in other devices
@@
          shoulder depends on a combination of $\Lambda_{div}$ and
-         fueling rate
+         fueling rate. Complete detachment not necessary.
       \end{itemize}
@@
   \begin{enumerate}[<+(1) | invisible@-+>]
-    \item Does $\Lambda_{div}$ unifies the picture among the devices?
+    \item Does $\Lambda_{div}$ unify the picture among the devices?
       \alert{No, a dependence on neutral pressure is likely to play a role}
-    \item If neutrals play a role is the divertor or midplane?
+    \item If neutrals play a role is it at the divertor and/or at the midplane?
       \alert{Contradictory results if one include experiments with
         midplane puffing, JET and EIRENE simulations}
-    \item Does L$_\parallel$ plays any role? \alert{So far TCV suggests no
+    \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
       dependence from f$_x$ scan but both TCV and MAST observe an
@@
       increases with L$_{\parallel}$ }
-    \item Cooling the divertor with fueling or seeding is really
-      equivalent? \alert{Contradictory observation in AUG and JET}
-    \item Can be translate straightforward from L to H-Mode? \alert{So
+    \item Is cooling the divertor with fueling or with equivalent? \alert{Contradictory observations in AUG and JET}
+    \item Do we observe same behavior in L and H-Mode? \alert{So
       far no as shown in H-Mode AUG. We need higher detachment
       condition and we need enough fueling}
+      \item What are the underlying mechanisms? 
     \end{enumerate}
-
   \end{frame}
@@
 same configuration, SN Btimes grad b, cryo pumps, greenwald fraction, heating
+
+things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,
 

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
staring to add slides after background 	modified:   gpm_november2016_vianello.tex

@@
 
-  \section{Open issue}
+  \section{Open issues}
   \begin{frame}{Open and unresolved issues}
@@
 \section{Topic 21 experiments }
-\begin{frame}{more proposed shots than allocated}
+\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
 	\begin{itemize}
-		\item totla number propose shots 449
-		\item ebven though combined we have to prioritize
-		\item prioritize cross comparison 
+		\item 15 proposals submitted to Topic 21
+		\item Proposals include experiments on all three machines 
+		\item There are overlaps between several of the proposals 
+		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
+		\item However, total number of proposed shots:  \textbf{449}
+		\item \underline{We must prioritize}
 		\item
+
 	\end{itemize}
@@
 status of cameras on devices
+
+\end{frame}
+
+\begin{frame}{Proposed shot plan}
+	piggybaggers (Mclements, relfectometry guys)
+
+	COMPASS
+\end{frame}
+
+\begin{frame}{Discussion agenda}
+
+\end{frame}
+
+\begin{frame}{Future}
+	meetings
+
+	wiki
 

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
adding preliminary shotplans

@@
-\documentclass[10pt, compress, draft]{beamer}
+\documentclass[10pt, compress]{beamer}
 \usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
@@
 \usepackage[export]{adjustbox}
+\usepackage{bm}
 % for font
@@
 		\item However, total number of proposed shots:  \textbf{449}
-		\item \underline{We must prioritize}
-		\item
-
+		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
 	\end{itemize}
@@
 \begin{frame}{Focal points}
-	Hmode (Proponentrs)
-	L-mode :  neutrals Ip scan
+\begin{itemize}
+	\item MST1 uniquely facilitates cross comparison between machines
+	\item Several of the proposed experiments overlap 
+	\item A cross machine experiment has the makings of settling open issues
+	\item Therefore, we will allocate shots for cross-machine comparison
+	\item L-mode experiments: 
+	\begin{enumerate}
+		\item Investigate the role of neutrals 
+		\item $I_p$ and $q_{95}$ scans
+	\end{enumerate}
+	\item H-mode experiments. 
+\end{itemize}	
 \end{frame}
 
-\begin{frame}{requirements form cross machine comparison }
-same configuration, SN Btimes grad b, cryo pumps, greenwald fraction, heating
+\begin{frame}{L-mode experiments}
+	\begin{itemize}
+		\item The role of neutrals in the shoulder formation is not understood 		{\scriptsize(proponents: Carralero, Militello, Vianello, Walkden)}
+		\begin{enumerate}
+			\item We envisage to measure neutral gas profiles at the outboard 		midplane using fast cameras and reciprocating Langmuir probes
+			\item Reciprocating probes and fast cameras available on all machines
+		\end{enumerate}
+		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$. {\scriptsize(proponents: Carralero, Militello, Vianello, Tsui, Walkden)}
+		\begin{enumerate}
+			\item Carry out parameter scans on all machines
+			\item Strive after similar machine configurations
+		\end{enumerate}
+	\end{itemize}
+\end{frame}
 
-things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,
-
-same diagnostics Isat blob speed, density profiles (Libes reflectometry), , divertor n and Te, fast camera plus n and te measure at OM
-
-status of cameras on devices
+\begin{frame}{H-mode experiments}
+\begin{itemize}
+	\item ITER and DEMO will operate in H-mode
+	\item We must know what parameters control shoulder formation 
+	\item Shoulder formation parameter regime is unclear on all machines
+	\item Main priorities: 
+	\begin{enumerate}
+		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
+		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
+		\item Experiments must gradually increase power and density. 
+	\end{enumerate}
+\end{itemize}
 
@@
 
-\begin{frame}{Proposed shot plan}
+\begin{frame}{Optimizing cross machine comparison}
+\begin{itemize}
+	\item Machines are fundamentally differently designed
+	\item Strive for similar configurations of the machines:
+	\begin{enumerate} 
+		\item Single-Null
+		\item $\bm{B} \times \nabla B$ towards active divertor 
+		\item Strike-point and cryo pump location (AUG and MAST-U)
+		\item Heating 
+	\end{enumerate}
+\end{itemize} 
+%things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,
+
+\end{frame}
+
+\begin{frame}{Required diagnostics}
+In order to compare experiments the following diagnostics must be available: 
+\begin{enumerate}
+	\item Reciprocating probe at OM measuring: 
+	\begin{itemize} 
+		\item $I_sat$ on minimum three pins poloidally and radially separated
+		 (filamens speed and size). 
+		\item Electron temperature
+		\item If possible $M_{\|}$
+	 \end{itemize}
+	 \item Camera viewing OM for measuring neutrals 
+	 \item Divertor measurements of $n$ and $T_e$ (probes). Collisionallity
+	 \item Density profile measurements (Li-Bes, Reflectometry, Edge Thomson scattering) 
+%	\item H-mode quality diagnostics(div current, magnetics)
+\end{enumerate}
+\end{frame}
+
+\begin{frame}{Proposed shot plan - AUG}
+Allocated shots $\sim$ 14 + contingency 
+\begin{itemize}
+	\item L-Mode (6 shots)
+	\begin{enumerate}
+		\item 
+	\end{enumerate}
+\end{itemize}
+
+Choose fueling levels for reference shot at 0.8 MA from AUG14-2.2-3 30276. Perform the same density ramp at 0.6 MA by keeping the same Toroidal Field
+Repeat Shot  1 by keeping the same q95 as reference
+Repeat Shot  30276 @ 1MA with the same toroidal field
+Repeat  3 by keeping the same q95 as the reference
+Repeat  30276 with Reverse Bt
+Repeat  5 with Probe at different insertion
+H-Mode investigation: Foreseen number 9
+
+The reference shot is 33059 (AUG15-2.2-3) with the aim to reach the condition found in 31607 (Sun PPCF 2015)
+
+Scenario development.
+Start from succesful shot 33059 (Total heating 3.1 MW), keep the probe head in a safe position (FAR SOL) increase the heating power (two steps to 4.5 and 6) up to 6 MW monitoring midplane probe by IR and Divertor through Langmuir.
+Repeat  1 Fueling ramps according to reference. Monitor of Divertor condition
+Repeat  2 adjusting eventually the fueling and N seeding ramp monitoring the Divertor condition
+Repeat  4 with optimum level of Fueling/Seeding 1st Radial position of probe
+Repeat  5, different probe position
+Repeat  6, different probe position
+Repeat  6 with Strike-point sweeping (if feasible)
+Contingency
+Contingency
+
 	piggybaggers (Mclements, relfectometry guys)
@@
 	wiki
+
+	Decisions made here uploaded to wiki
 

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
finished AUG shotplan 	modified:   gpm_november2016_vianello.tex

@@
 		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
+		\item Reaching all goals is not possible with the current number of allocated shots.
 	\end{itemize}
@@
 	\end{enumerate}
+	\item Fueling in H-mode is problematic due to transport barrier? 
 \end{itemize}
@@
 	\begin{itemize} 
-		\item $I_sat$ on minimum three pins poloidally and radially separated
+		\item $I_{sat}$  on minimum three pins poloidally and radially separated
 		 (filamens speed and size). 
@@
 \begin{frame}{Proposed shot plan - AUG}
+\vspace{-1cm}
 Allocated shots $\sim$ 14 + contingency 
@@
 	\begin{enumerate}
-		\item 
+		\item Reference shot \# 30276
+		\item Perform $I_p$ scan (three values) with fixed $B_T$
+		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
+		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
+		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello
+
+	\end{enumerate}
+	\item H-mode (9 shots)
+	\begin{enumerate}
+		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
+		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
+		\item Strike-point sweep if feasible? 
+		\item In all shots, particle acceleration in ELMs will be studied using microwaves, soft X-rays, and FILD (proposal by McClements) 
+		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
+		\item These shots combine experiments proposed by: Aguiam, Carralero, McClements, Militello, Vianello, Vicente
+
 	\end{enumerate}
 \end{itemize}
+\end{frame}
 
-Choose fueling levels for reference shot at 0.8 MA from AUG14-2.2-3 30276. Perform the same density ramp at 0.6 MA by keeping the same Toroidal Field
-Repeat Shot  1 by keeping the same q95 as reference
-Repeat Shot  30276 @ 1MA with the same toroidal field
-Repeat  3 by keeping the same q95 as the reference
-Repeat  30276 with Reverse Bt
-Repeat  5 with Probe at different insertion
-H-Mode investigation: Foreseen number 9
+\begin{frame}{Proposed shot plan - TCV}
 
-The reference shot is 33059 (AUG15-2.2-3) with the aim to reach the condition found in 31607 (Sun PPCF 2015)
+\end{frame}
 
-Scenario development.
-Start from succesful shot 33059 (Total heating 3.1 MW), keep the probe head in a safe position (FAR SOL) increase the heating power (two steps to 4.5 and 6) up to 6 MW monitoring midplane probe by IR and Divertor through Langmuir.
-Repeat  1 Fueling ramps according to reference. Monitor of Divertor condition
-Repeat  2 adjusting eventually the fueling and N seeding ramp monitoring the Divertor condition
-Repeat  4 with optimum level of Fueling/Seeding 1st Radial position of probe
-Repeat  5, different probe position
-Repeat  6, different probe position
-Repeat  6 with Strike-point sweeping (if feasible)
-Contingency
-Contingency
+\begin{frame}{With aloocated shot we cannot do interesting stuff }
+\begin{itemize}
+	\item Ion temp measurements
+	\item Topology investigations
+	\item Strikepoint sweeping and cryo pump
+	\item Parameters scans in H-mode
+	\item Strike-point sweep
 
-	piggybaggers (Mclements, relfectometry guys)
+\end{itemize}
+\end{frame}
 
-	COMPASS
+\begin{frame}{piggybag on Quescient H-mode shots}
 \end{frame}
@@
 	Decisions made here uploaded to wiki
+
+	Form experiment planning groups for each machine
 

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
stareting to do TCV shot plan
ALmost done

@@
 		\item There are overlaps between several of the proposals 
-		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23
+		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 !!!!!!!1SHOULD WE ADD PRELIMINARY DATES FOR THE EXPERIMENTS??
 		\item However, total number of proposed shots:  \textbf{449}
@@
 	\end{enumerate}
-	\item Fueling in H-mode is problematic due to transport barrier? 
+	\item Fueling in H-mode is problematic due to transport barrier? NBI fueling?
+	\item H-mode density limit\parencite{Bernert:2015ppcf} must be avoided
 \end{itemize}
@@
 		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
+		\item should we add OM puff to validate neutral measurements?
 		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello
@@
 \begin{frame}{Proposed shot plan - TCV}
-
+	\begin{itemize}
+		\item L-mode (11 shots)
+		\begin{enumerate}
+			\item Reference shot \# 53514
+			\item Same $I_p$ and $q_{95}$ scans as on AUG
+			\item Two shots with reversed $\bm{B} \times \nabla B$
+			\item Move plasma vertically. Disentangle $q_{95}$ and $L_{\|}$			
+		\end{enumerate}
+		\item H-mode (12 shots)
+		\begin{enumerate}
+			\item Reference shot \# 53352
+			\item Since H-mode shoulder is new territory on TCV first shots will be scenario development
+			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
+		\end{enumerate}
+	\end{itemize}
 \end{frame}
 
-\begin{frame}{With aloocated shot we cannot do interesting stuff }
+\begin{frame}{Preliminary shot plan  - MAST-U}
+	\begin{itemize}
+		\item 
+	\end{itemize}
+\end{frame}
+
+\begin{frame}{There are urgent experiment which cannot be addressed}
 \begin{itemize}
@@
 
-\begin{frame}{piggybag on Quescient H-mode shots}
+\begin{frame}{Future and Miscellaneous}
+	\begin{itemize}
+		\item piggybag on Quescient H-mode shots
+		\item Shortly after this meeting we will organize a follow-up meeting to reconcile ideas from this discussion (date not fixed yet)
+		\item All information will be gathered on the wiki
+
+		\end{itemize}
 \end{frame}
@@
 \begin{frame}{Discussion agenda}
-
+	\begin{enumerate}
+		\item Priorities. Do we agree? 
+		\item Common measurement techniques. E.g. $I_{sat}$ instead if $\phi_f$ for filament velocities?
+		\item Publications
+ 	\end{enumerate}
 \end{frame}
 
-\begin{frame}{Future}
-	meetings
-
-	wiki
-
-	Decisions made here uploaded to wiki
-
-	Form experiment planning groups for each machine
-
-\end{frame}
   % \only<1>{

### 2016-11-11 Presentation/gpm_november2016_vianello.tex
Further modifications
Nicola please take a look

	modified:   gpm_november2016_vianello.tex

@@
 
+\begin{frame}{Outline}
+	\begin{itemize}
+		\item Background 
+		\item Plans
+		\item Discussion
+	\end{itemize}	
+\end{frame}
+
 \section{Background}
@@
       TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
-    \item Observations exhibit various dependencies on divertor
+    \item Observations exhibit various other dependencies e.g., divertor
       collisionality, plasma current, seeding. \alert{Results from
@@
       \begin{itemize}
-      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that
+      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
         \begin{equation*}
@@
       controls shoulder formation
-        \item<2-> \textcolor{red}{Tested by changing n$_e$
-            and $T_e$ through fueling/seeding/heating}
-        \item<3-> This determines a change of the velocity-size
+        \item<2-> ... which is associated with a change of the velocity-size
           scaling from
             \textcolor{ta3chameleon}{sheath-limited}
-        to \textcolor{blue}{inertial regime}. \onslide<4>{\alert{$\Lambda_{div}$ rules the density profile scale
+        to \textcolor{blue}{inertial regime}.
+        \item<3-> \textcolor{red}{Tested by changing n$_e$
+            and $T_e$ through fueling/seeding/heating}
+
+       \onslide<4>{\alert{$\Lambda_{div}$ rules the density profile scale
           length}} 
@@
 \end{frame}
+
 \begin{frame}{L-Mode studies: AUG/2}
@@
       \begin{itemize}
-      \item<1-> Profile modified by increase of blob-size and change of
+      \item<1-> Profile modified by an increase of blob-size and change of
         \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
@@
       condition and we need enough fueling}
-      \item What are the underlying mechanisms? 
+      \item Is the density shoulder accompanied with an ion temperature shoulder?
+%      \item What are the underlying mechanisms? 
     \end{enumerate}
@@
 	\begin{itemize}
-		\item 15 proposals submitted to Topic 21
+		\item 15 were proposals submitted to Topic 21
 		\item Proposals include experiments on all three machines 
@@
 	\item Therefore, we will allocate shots for cross-machine comparison
-	\item L-mode experiments: 
+	\item ....but also to other proposed experiments
+	\item Cross machine L-mode experiments: 
 	\begin{enumerate}
@@
 	\end{enumerate}
-	\item H-mode experiments. 
+	\item Cross machine H-mode experiments. 
 \end{itemize}	
@@
 	\end{enumerate}
-	\item Fueling in H-mode is problematic due to transport barrier? NBI fueling?
-	\item H-mode density limit\parencite{Bernert:2015ppcf} must be avoided
+	\item Fueling in H-mode is problematic due to transport barrier? NBI, pellet fueling?
+	\item H-mode density limit\parencite{Bernert:2015ppcf} must be dealt with
 \end{itemize}
@@
 		\item Heating 
+		\item Fueling location 
+		\item Seeding (species, location, rate)
 	\end{enumerate}
@@
 		\item should we add OM puff to validate neutral measurements?
+		\item Possibility of strike-point sweeping during shot
+		\item RFEA measurements in internal program. 
 		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello
@@
 	\begin{itemize}
-		\item 
+		\item L-mode (6 shots)
+		\begin{enumerate}		
+			\item New machine. No reference shot yet			
+			\item Same $I_p$ and $q_{95}$ scans as on AUG. Availability of multi pin probe? 
+			\item Try varying fueling location
+			\item RFEA measurements during shoulder formation 
+		\end{enumerate}
+		\item H-mode (7 shots)
+		\begin{enumerate}
+			\item These experiments require the existence of H-mode reference shot. Perhaps not available in 2017
+			\item Similar scenario development as on other machines
+		\end{enumerate}
+
+					\item Same $I_p$ and $q_{95}$ scans as on AUG
 	\end{itemize}
@@
 \begin{itemize}
-	\item Ion temp measurements
+	\item Detailed ion temp measurements 
 	\item Topology investigations
@@
 	\item Parameters scans in H-mode
-	\item Strike-point sweep
-
+	\item X-point probes
 \end{itemize}
@@
 	\begin{itemize}
-		\item piggybag on Quescient H-mode shots
+		\item Possibility to piggybag on Quescient/small ELM H-mode shots (Topic 5,6, 18)
 		\item Shortly after this meeting we will organize a follow-up meeting to 						reconcile ideas from this discussion (date not fixed yet)
 		\item All information will be gathered on the wiki
-
+		\item Filament database		
 	\end{itemize}

### 2016-11-14 Presentation/gpm_november2016_vianello.tex
Finished

@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=MST1-GPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=MST1-EPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 
-\begin{frame}{Main focus of topic 21 is shoulder formation}
+\begin{frame}{Main focus of topic as listed in MST1 call}
 \vspace{-1cm}
@@
 		\item Background 
-		\item Plans
+		\item Plans (we will not make a detailed list of the
+                  proposal, we already tried to combine and summarize them)
 		\item Discussion
@@
   \begin{enumerate}[<+(1) | invisible@-+>]
-    \item Experimental and theoretical investigations suggest that SOL density profiles are  determined by the balance between radial filamentary transport and parallel dynamics
+    \item Experimental and theoretical investigations suggest that SOL density profiles are
+      determined by the balance between radial filamentary transport and parallel dynamics
     \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
@@
       \end{equation*}
-      controls shoulder formation
-        \item<2-> ... which is associated with a change of the velocity-size
+      controls filaments size
+        \item<2-> \textcolor{red}{Tested by changing n$_e$
+            and $T_e$ through fueling/seeding/heating}
+        \item<3-> This determines a change of the velocity-size
           scaling from
@@
         to \textcolor{blue}{inertial regime}.
-        \item<3-> \textcolor{red}{Tested by changing n$_e$
-            and $T_e$ through fueling/seeding/heating}
-
-       \onslide<4>{\alert{$\Lambda_{div}$ rules the density profile scale
+       \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
            length}}
+       \item<5> This finally determines the shoulder formation
         \end{itemize}
@@
       \end{tikzonimage}}
-    \only<3>{
+    \only<3-4>{
       \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15b}
@@
     }
-    \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15c}
+    \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15c}
     \end{column}
@@
         radial transport increases
-      \item<4> Parallel flow is strongly reduced whenever we increase
+      \item<4|only@4> \alert{Beware the change of frequency may be due to a
+        modification of fluctuation velocity which is know to vary
+        with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
+      \item<5> Parallel flow is strongly reduced whenever we increase
         the divertor collisionality
@@
         \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16c}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16d}
+        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/AgostiniNF2011}
+        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16d}
       \end{column}
@@
       \item<1|only@1> SOL profiles in H-Mode so far investigated on
-        AUG \parencite{Muller:2015jt,Sun:2015bu}
+        AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
       \item<2|only@2> Differently from L-Mode, complete detachment
@@
          shoulder depends on a combination of $\Lambda_{div}$ and
-         fueling rate. Complete detachment not necessary.
+         fueling rate. Complete detachment seems instead not necessary
+         although very weak shoulder
       \end{itemize}
@@
     \item Does $\Lambda_{div}$ unify the picture among the devices?
-      \alert{No, a dependence on neutral pressure is likely to play a role}
+      \alert{No, deos neutral pressure play a role?}
     \item If neutrals play a role is it at the divertor and/or at the midplane?
@@
 		\item There are overlaps between several of the proposals 
-		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 !!!!!!!1SHOULD WE ADD PRELIMINARY DATES FOR THE EXPERIMENTS??
+		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 
 		\item However, total number of proposed shots:  \textbf{449}
@@
 	\item MST1 uniquely facilitates cross comparison between machines
-	\item Several of the proposed experiments overlap 
+	\item Several of the proposed experiments overlap and will be combined
 	\item A cross machine experiment has the makings of settling open issues
@@
 	\begin{itemize}
-		\item The role of neutrals in the shoulder formation is not understood 		{\scriptsize(proponents: Carralero, Militello, Vianello, Walkden)}
+		\item The role of neutrals in the shoulder formation is not understood
+                  {\scriptsize(proponents: Carralero (\# 7), Militello
+                    (\# 1, 2), Vianello (\# 13), Walkden (\# 9))}
 		\begin{enumerate}
-			\item We envisage to measure neutral gas profiles at the outboard 		midplane using fast cameras and reciprocating Langmuir probes
-			\item Reciprocating probes and fast cameras available on all machines
+		\item We envisage to measure neutral gas profiles at the outboard midplane
+                  using fast cameras with D$_{\alpha}$ filter, density
+                  and temperature SOL profiles and appropriate code
+                  (e.g. KN1D as in \parencite{Lipschultz:2005gg,Lipschultz:2016vk})
+		\item Reciprocating probes and profiles available on
+                  all machines
+                \item Investigate role of fueling location (MAST)
 		\end{enumerate}
-		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$. {\scriptsize(proponents: Carralero, Militello, Vianello, Tsui, Walkden)}
+		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$.
+                  {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, WalkdenCarralero (\# 7), Militello
+                    (\# 1, 2), Vianello (\# 13), Walkden (\# 9), Tsui
+                    (\# 15))}
 		\begin{enumerate}
@@
 		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
-		\item Investigate the SOL (filamentary) transport properties. Main diagnostic is reciprocating probes $\rightarrow$ limits heating power
+		\item Investigate the SOL (filamentary) transport properties.
+                  Whenever main diagnostic is reciprocating probes $\rightarrow$ limits heating power
 		\item Experiments must gradually increase power and density. 
 	\end{enumerate}
-	\item Fueling in H-mode is problematic due to transport barrier? NBI, pellet fueling?
-	\item H-mode density limit\parencite{Bernert:2015ppcf} must be dealt with
+	\item Fueling in H-mode is problematic due to transport
+          barrier. Is there a way to overcome it? NBI, pellet fueling?
+	\item H-mode density limit \parencite{Bernert:2015bq} must be dealt with
 \end{itemize}
@@
 
-\begin{frame}{Required diagnostics}
+\begin{frame}{Required diagnostics and competences}
 In order to compare experiments the following diagnostics must be available: 
 \begin{enumerate}
-	\item Reciprocating probe at OM measuring: 
+	\item Filaments analysis in the Outboard midplane: 
 	\begin{itemize} 
-		\item $I_{sat}$  on minimum three pins poloidally and radially separated
-		 (filamens speed and size). 
-		\item Electron temperature
+		\item Through Reciprocating probe then $I_{sat}$  on minimum three pins poloidally and radially separated
+		 (filaments speed and size). 
+		\item Electron temperature (fast T$_e$ measurements
+                  can be achieved with BPP in MAST-U {\footnotesize
+                    (N. Walkden \#11)})
 		\item If possible $M_{\|}$
@@
 	 \item Camera viewing OM for measuring neutrals 
-	 \item Divertor measurements of $n$ and $T_e$ (probes). Collisionallity
-	 \item Density profile measurements (Li-Bes, Reflectometry, Edge Thomson scattering) 
+	 \item Divertor measurements of $n$ and $T_e$ (probes) plus
+           spectroscopy and bolometry 
+	 \item Density profile measurements (Li-Bes, Reflectometry (\#
+           6 Acquiam, \# 8 Vicente), Edge Thomson scattering) 
+         \item Sami and Field for fast particles accelleration (piggy
+           back on developed scenarion \# 4 McClements)
 %	\item H-mode quality diagnostics(div current, magnetics)
@@
 
-\begin{frame}{Proposed shot plan - AUG}
+\begin{frame}[allowframebreaks]{Proposed shot plan - AUG}
 \vspace{-1cm}
@@
 		\item RFEA measurements in internal program. 
-		\item These shots combines experiments proposed by: Carralero, Militello, 	Vianello
+		\item These shots combines experiments proposed by:
+                  Carralero (\# 7), Militello (\#1), Vianello (\#13)
 
@@
 	\begin{enumerate}
-		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
+		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions
+                  in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
 		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
 		\item Strike-point sweep if feasible? 
-		\item In all shots, particle acceleration in ELMs will be studied using microwaves, soft X-rays, and FILD (proposal by McClements) 
+		\item In all shots, particle acceleration in ELMs will be studied using microwaves,
+                  soft X-rays, and FILD 
 		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
-		\item These shots combine experiments proposed by: Aguiam, Carralero, McClements, Militello, Vianello, Vicente
+		\item These shots combine experiments proposed by:
+                  Aguiam (\#6), Carralero (\#7), McClements (\#4),
+                  Militello (\# 1, 2), Vianello (\#13), Vicente (\#8)
 
@@
 			\item Two shots with reversed $\bm{B} \times \nabla B$
-			\item Move plasma vertically. Disentangle $q_{95}$ and $L_{\|}$			
+			\item Move plasma vertically. Disentangle
+                          $q_{95}$ and $L_{\|}$	
+                        \item These shots combines proposal: Vianello
+                          (\#13), Tsui (\#15), Militello (\#1, 2)
 		\end{enumerate}
@@
 			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
+                        \item These shots combines proposal: Vianello
+                          (\#13), Tsui (\#15), Militello (\#1, 2)
 		\end{enumerate}
@@
 			\item New machine. No reference shot yet			
-			\item Same $I_p$ and $q_{95}$ scans as on AUG. Availability of multi pin probe? 
+			\item Same $I_p$ and $q_95$ scan to allow
+                          cross-machine comparison. Availability of multi pin probe? 
 			\item Try varying fueling location
-			\item RFEA measurements during shoulder formation 
+			\item RFEA measurements during shoulder
+                          formation 
+                        \item These shots combines proposal: Militello
+                          (\#1, 2, 3), Walkden (\#11), Vianello (\#13)
 		\end{enumerate}
@@
 			\item These experiments require the existence of H-mode reference shot. Perhaps not available in 2017
-			\item Similar scenario development as on other machines
+			\item Similar scenario development as on other emachines
+                        \item These shots combines proposal: Militello
+                          (\#1, 2, 3),  Vianello (\#13)
 		\end{enumerate}
-
-					\item Same $I_p$ and $q_{95}$ scans as on AUG
+		\item Probe head must be changed to allow
+                  investigation of both fast T$_e$ (BPP),  and T$_i$
+                  (RFEA) but this require careful schedule of machine time
 	\end{itemize}
@@
 \begin{itemize}
-	\item Detailed ion temp measurements 
-	\item Topology investigations
+	\item Detailed ion temp measurements. Must eventually be
+          completed in internal programs. Are you willing to share the
+          information among Topic 21 even though done internally?
+	\item Topology investigations? For example the comparison
+          USN/LSN/DN is not possible. Upper divertor information is
+          actually less detailed. Better to use reverse B$_t$ or ion
+          $\mathbf{B}\times\nabla\mathbf{B}$ pointing away from
+          X-Point which is know to have influences in detachment as
+          well \parencite{McLean}
 	\item Strikepoint sweeping and cryo pump
@@
 
+\begin{frame}{Modelling require}
+  \begin{enumerate}
+    \item Mean field modelling available for AUG (EMC3-EIRENCE) and
+      MAST-U (SOLPS). So far we lack investigation for these scenario
+      targeting TCV. Manpower needed from edge and SOL modelling
+    \item Turbulence code: we should need self-consistent interaction
+      with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
+      \texttt{GBS}. Some of them can be run by people who will, very
+      likely, apply for this topic, some other not
+  \end{enumerate}
+\end{frame}
+
 \begin{frame}{Future and Miscellaneous}
@@
 		\item Possibility to piggybag on Quescient/small ELM H-mode shots (Topic 5,6, 18)
-		\item Shortly after this meeting we will organize a follow-up meeting to 						reconcile ideas from this discussion (date not fixed yet)
+		\item Shortly after this meeting we will organize a follow-up meeting to reconcile ideas
+                  from this discussion (date not fixed yet)
 		\item All information will be gathered on the wiki
-		\item Filament database		
+                \item Other channels for discussion/sharing. Slack
+                  (mst1-topic21.slack.com), Github for code sharing
+		\item We aim to arrive to a proper shared database of
+                  filaments between the machines, where properties
+                  will be obtained using agreed approaches so that a
+                  cross-machine comparison paper could at the end be
+                  finalized at a certain point		
 	\end{itemize}
@@
 	\begin{enumerate}
-		\item Priorities. Do we agree? 
-		\item Common measurement techniques. E.g. $I_{sat}$ instead if $\phi_f$ for filament velocities?
-		\item Publications 
+		\item Priorities. These are our personal ideas. Do we agree? 
+		\item \underline{Common measurement techniques}. Filament
+                  properties, $\Lambda_{div}$ estimate and location,
+                  Neutrals, \ldots 
  	\end{enumerate}
@@
 
-  % \only<1>{
-% \begin{itemize}
-% \item Role of turbulence transport in the SOL saturation is a well
-%   know
-%   feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
-%   density, even without reaching detachment SOL profile tend to flatten}
-% \end{itemize}}
-% \only<2-3>{
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item Present understanding suggests that a transition of filament
-%         propagation regime is dominated by effective
-%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
-%         \begin{equation*}
-%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
-%         \end{equation*}
-%         \item<3> \textcolor{red}{At constant blob size, increasing
-%             collisionality provide a change in the filaments velocity
-%             scaling properties}
-%       \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
-%         \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/FigMyra}
-%           \only<3>{
-%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
-%         \end{tikzonimage}
-%     \end{column}
-%   \end{columns}
-% }
-% \only<4-6>{
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item AUG and JET \parencite{Carralero:2015gu} suggest that $\Lambda_{div}$ dominates this
-%         process and a transition from
-%         \textcolor{ta3chameleon}{sheath-limited}
-%         \onslide<5-6>{to \textcolor{blue}{inertial regime}} 
-%         \item<6> \textcolor{red}{Tested by changing n$_e$
-%             and $T_e$ through fueling/seeding/heating}
-%       \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Presentation/KoMFig2.png}
-%         \only<4-6>{
-%           \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
-%       }
-%         \only<5-6>{
-%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
-%       }
-%         \only<6>{
-%           \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
-%       }
-%     \end{tikzonimage}
-%   \end{column}
-%   \end{columns}
-% }
-% \only<7->{
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item MAST \parencite{Militello:2016hk} and old TCV
-%         \parencite{Garcia:2007p2615} data 
-%         suggested and I$_P$ dependence. 
-%           \textcolor{red}{At higher current and
-%         same density SOL shoulder disappear} 
-%       \item<8> \textcolor{ta3chameleon}{Being shoulder formation
-%           induced by a change of $\Gamma_{\perp}$ \textit{vs}
-%           $\Gamma_{\parallel}$ balance we will try to test dependence
-%           on L$_{\parallel}$}
-%     \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-%       \includegraphics[width=\textwidth]{../pdfbox/Presentation/FigMilitello.pdf}
-%     \end{column}
-%   \end{columns}
-% }
-% \centering{\includegraphics<1>[width=1.1\textwidth]{../pdfbox/Presentation/Fig1Presentation}}
-% \end{frame}
-
-% \begin{frame}{Flux expansion scan/1}
-% \vspace{-1cm}
-%   \Fontvi
-%   % \begin{columns}
-%   %   \begin{column}{0.3\textwidth}
-%       \centering{\includegraphics[width=.75\textwidth]{../pdfbox/Fig1a}}
-%       \begin{itemize}
-%       \item Parallel connection length varied by scanning 
-%         flux expansion during density
-%         ramps in ohmically heated discharges. \textcolor{red}{$\nabla B_i$ towards the X-point}
-%         %\begin{equation*}
-%         \[  f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}\]
-%         %\end{equation*}
-%         \item Variation of $f_x$ change the volume of flux tube as
-%           well as parallel connection length (Increased up to 70\%)
-%       \end{itemize}
-%     % \end{column}
-%     % \begin{column}{0.7\textwidth}
-%   %   \end{column}
-%   % \end{columns}
-% \end{frame}
-
-% \begin{frame}{Flux expansion scan/2}
-%   \Fontvi
-%       \begin{itemize}
-%       \item<1-> Flux expansion variation induce modification at the target
-%       \item<1-> Radiation front from bolometry  moves earlier in
-%         density at larger f$_x$. Front movement trails CIII cut-off
-%         movement (Reimerdes IAEA 2016)
-%       \item<2-> Volumetric recombination rates from $n=6, 7$ balmer line
-%         emission \parencite{kevin:jnm} indicates that \textcolor{red}{recombination occurs
-%           earlier in density at high $f_x$}
-%       \item<3|only@3> \textcolor{ta3skyblue}{This is not confirmed in reversed B$_t$ where
-%         increasing the f$_x$ lead to deeper detachment without}
-%         changing density threshold  
-%     \end{itemize}
-%     \only<1-2>{\begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig2c}
-%       \only<1>{\fill[white] (0.,0) rectangle (0.52,1); }    
-%       \draw [->, ultra thick, black] (0.79,0.69) -- (0.75,0.51);
-%     \end{tikzonimage}}
-% \centering{\includegraphics<3>[width=.5\textwidth]{../pdfbox/Presentation/XD_detach_HM}}
-%   \end{frame}
-
-% \begin{frame}{Flux expansion scan/3}
-%   \vspace{-1cm}
-% \Fontvi
-%       \begin{itemize}
-%       \item Target and upstream profile measured at the same density
-%         but different f$_x$
-%       \item<3-> Target profiles in the near SOL modified with broader profile at higher
-%         f$_x$. \textcolor{red}{Huge variation on $\Lambda_{div}$
-%           without upstream modification}
-%       \item<4|only@4> \textcolor{ta3chameleon}{Only further increase
-%           of density (although $\Lambda_{div}$ in the far SOL
-%           decreases) leads to profile broadening}
-%       \end{itemize}
-%       \centering{\includegraphics<1>[width=.65\textwidth]{../pdfbox/Fig4Series_1}}
-%       \centering{\includegraphics<2>[width=.65\textwidth]{../pdfbox/Fig4Series_2}}
-%       \centering{\includegraphics<3>[width=.65\textwidth]{../pdfbox/Fig4Series_3}}
-%       \centering{\includegraphics<4>[width=.65\textwidth]{../pdfbox/Fig4Series_4}}
-% \end{frame}
-
-% \begin{frame}{Filaments effect}
-%   \vspace{-1cm}
-% \Fontvi
-%       \begin{itemize}
-%       \item<1-3> Blob properties deduced from fast reciprocating as done in \parencite{Boedo:2001tt}
-%       \item<1|only@1> Blob size deduced as $\delta_b = \tau_b v_{\perp}$
-%         % \begin{equation*}
-%         %   \tau_b = \text{FWHM of CAS} \qquad v_{\perp} = \sqrt{v_{E\times B, r}^2 +
-%         %     v_{E\times B, p}^2}
-%         % \end{equation*}
-%       \item<2-3> No clear dependence on
-%           $\Lambda_{div}$ during f$_x$ scan
-%       \item<3> \textcolor{ta3chameleon}{When we increase the
-%           density filaments are bigger at same $\Lambda_{div}$}
-%       \item<4-> \textcolor{ta3skyblue}{On a statistical basis,
-%           blob size increases with density without clear dependence on
-%           f$_x$ \onslide<5>{\textcolor{red}{as well as $\lambda_n$ in the Far SOL}}}
-%       \item<6> \textcolor{ta3chameleon}{Behavior at very high
-%           density to be confirmed}  
-%       \end{itemize}
-%       \centering{\includegraphics<1>[width=.53\textwidth]{../pdfbox/Fig14b}}
-%       \centering{\includegraphics<2>[width=.63\textwidth]{../pdfbox/Fig7}}
-%       \centering{\includegraphics<3>[width=.63\textwidth]{../pdfbox/Fig7b}}
-%       \centering{\includegraphics<4>[width=.85\textwidth]{../pdfbox/Fig12}}
-%       \centering{\includegraphics<5>[width=.85\textwidth]{../pdfbox/Fig12b}}
-%       \only<6>{
-%         \begin{center}
-%           \begin{tikzonimage}[width=.85\textwidth]{../pdfbox/Fig12b}
-%           \draw [thick, ta3chameleon, thick] (0.75,0.5) ellipse (0.1 and 0.1);
-%           \end{tikzonimage}
-%         \end{center}
-%       }
-% \end{frame}
-
-% \begin{frame}{Current scan/1}
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1-3> On a single shape (f$_x \approx 4$) current scan with
-%         similar density ramps performed
-%       \item<2-3> \textcolor{red}{At lower current indication of shoulder for $R-R_{sep}
-%         \geq 1$ cm which disappear at higher current (same density)}
-%       \item<3> \textcolor{ta3chameleon}{At even higher current we need to substantially
-%         increase the fueling (even if at the same $n/n_G$)}
-%       \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-%       \only<1-2>{
-%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series1}
-%         \only<2>{
-%           \draw [thick, red, thick] (0.75,0.75) ellipse (0.2 and 0.1);
-%         }
-%       \end{tikzonimage} }
-%     \only<3>{
-%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig4d_series2}
-%           \draw [thick, ta3chameleon, thick] (0.67,0.35) ellipse (0.22 and 0.1);
-%           \draw [thick, ta3chameleon, thick] (0.5,0.14) ellipse (0.3 and 0.03);
-%         \end{tikzonimage}      
-%       }
-%     \end{column}
-%   \end{columns}
-% \end{frame}
-
-% \begin{frame}{Current scan/2}
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item On a statistical basis we have a slight
-%         reduction of radial velocity of the filaments as in MAST \parencite{Kirk:2016jj} with unclear
-%         effect on blob-size
-%       \end{itemize}
-%     \end{column}
-%       \begin{column}{0.5\textwidth}
-%      \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig8}
-%        \draw [->, ultra thick, red, dashed] (0.33,0.37) -- (0.7,0.27);
-%      \end{tikzonimage}
-%    \end{column}
-%   \end{columns}
-%   \end{frame}
-
-% \begin{frame}{Lower Single Null (LSN) and Double Null (DN)}
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1|only@1> We compare LSN \textit{vs} DN on a single discharge at
-%         two levels of density
-%         \item<2|only@2> At lower density values the radiation is spread among
-%           upper and lower X-points, whereas at higher density radiation
-%           is higher at lower X-point
-%         \item<6|only@6> Blob size increases with density with DN cases always
-%           exhibiting larger blobs. Still compatible with general density
-%           scaling. \textcolor{orange}{Radial velocity seems to decrease for DN}
-%       \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-%       \includegraphics<1>[trim={0 7.6cm 0 0}, clip, width=\textwidth]{../pdfbox/Fig5}
-%       \includegraphics<2>[width=\textwidth]{../pdfbox/Fig5c}
-%       \only<6>{
-%         \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig9}
-%           \draw [->, thick, orange] (0.33, 0.33) -- (0.83, 0.21);
-%         \end{tikzonimage}
-%       }
-%     \end{column}
-%   \end{columns}
-%   \only<3>{
-%     \begin{itemize}
-%       \item At the LFS target, DN density profile at lower level of
-%         density is reduced and closer to 
-%         what observed at higher density
-%       \end{itemize}
-%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5e}
-%         \draw [dashed, red, ultra thick] (0.7, 0.37) -- (0.3, 0.37);
-%         \draw [->, dashed, red, ultra thick] (0.3, 0.7) -- (0.3, 0.38);
-%       \end{tikzonimage}
-%     }
-%   \only<4-5>{
-%     \begin{itemize}
-%       \item Upstream profile suggests that a stronger tendency of
-%         developing density shoulder is observed in DN 
-%       \end{itemize}
-%       \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig5d}
-%         \only<5>{\draw[dashed, red, thick] (1.0, 0.55) -- (0.1, 0.55);}
-%       \end{tikzonimage}
-%     }
-
-% \end{frame}
-
-% \begin{frame}{Upper, Lower and Double Null}
-%     \Fontvi
-%     \begin{itemize}
-%       \item The same density ramp performed in Upper, Lower and Double
-%         null with all the Strikes points at the inner wall
-%       \item This allow to test any possible dependence from $\nabla
-%         B_i$ drift direction. C-Mod suggests difference in the medium
-%         density range \parencite{LaBombard:2004kg}
-%     \end{itemize}
-%     \centering{\includegraphics[width=0.9\textwidth]{../pdfbox/Fig1b}}
-% \end{frame}
-% \begin{frame}{Upper, Lower and Double Null}
-%     \Fontvi
-%     \begin{itemize}
-%       \item<2-> Lower and Double null blob size scale consistently with
-%         density scaling
-%       \item<3->  Upper Single null always exhibits
-%         larger blob
-%       \end{itemize}
-%       \vspace{-0.27cm}
-%     \centering{\includegraphics<1>[width=.6\textwidth]{../pdfbox/Fig11b_Series1}}
-%     \centering{\includegraphics<2>[width=.6\textwidth]{../pdfbox/Fig11b_Series2}}
-%     \centering{\includegraphics<3>[width=.6\textwidth]{../pdfbox/Fig11b_Series3}}
-% \end{frame}
-
-% \begin{frame}{Summary}
-%   \Fontvi
-%   \begin{itemize}
-%   \item<1-> $\lambda_n = |\nabla n_e/n_e|^{-1}$ computed around 1cm from the
-%     separatrix
-%   \item<2-> $\lambda_n$ clearly increases with $\Theta = (\delta_b
-%         R^{1/5}/L_{\parallel}^{2/5}\rho_s^{4/5})^{5/2}$,
-%     i.e. with blob-size
-%   \item<3-> \alert{The dependence on L$_{\parallel}$ is marginal
-%       although we obtain 
-%       larger $\Theta$ at smaller $L_{\parallel}$}.
-%   \item<4-> The increase of $\lambda_n$ is consistent with an increase
-%     of perpendicular to parallel losses
-%   \item<5-> The dependence on $\Lambda_{div}$ is weaker than in
-%     AUG/JET. \onslide<6>{\textcolor{ta3chameleon}{ Large $\Lambda$ is not
-%         sufficient for flat profile.}}
-
-%   \end{itemize}
-%   \begin{tikzonimage}[width=\textwidth]{../pdfbox/Fig10c}
-%     \only<1>{\fill[white] (0, 0) rectangle (1, 1);}
-%     \only<2>{\fill[white] (0.348,0) rectangle (1,1); }    
-%     \only<3>{\fill[white] (0.348,0) rectangle (0.897,1); }    
-%     \only<4>{\fill[white] (0.62,0) rectangle (0.897,1); }    
-%     \only<6>{
-%       \draw [thick, ta3chameleon, thick, rotate = 4] (0.865,0.2) ellipse (0.04 and 0.2);
-%       \draw [thick, ta3chameleon, thick, rotate = 3] (0.72,0.6) ellipse (0.03 and 0.15);
-%  }    
-%     \end{tikzonimage}
-% \end{frame}
-
 \end{document}
-%\draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);

### 2016-11-14 Presentation/gpm_november2016_vianello.tex
Include COMPASS into presentation

@@
 
+\begin{frame}{COMPASS collaboration}
+\begin{itemize}
+\item COMPASS is not an MST1 device, therefore no operational cost
+  will be provided by MST1
+\item However GA agree that MST1 can provide part of the ppy for
+  running experiments in line with MST1 topics
+\item Proposal \# 14 is focused filaments dynamics and shoulder
+  formation both in L and H-Mode
+\item Experimental plan can be therefore agreed in order to perform
+  similar experiments (e.g. I$_p$ and $q_{95}$ scan in L-Mode)
+  ensuring proper comparison between devices
+\item COMPASS suppose 3ppy for running and evaluation of experiment
+  pertaining Topic-21, among Czeck and other european laboratories.
+\end{itemize}
+\end{frame}
+
 \begin{frame}{There are urgent experiment which cannot be addressed}
@@
 
-\begin{frame}{Modelling require}
+\begin{frame}{Modeling require}
   \begin{enumerate}

### 2016-11-15 Presentation/gpm_november2016_vianello.tex
Added last correction from Jens to EPM presentation

@@
       \item<4|only@4> \alert{Beware the change of frequency may be due to a
-        modification of fluctuation velocity which is know to vary
+        modification of fluctuation velocity which is known to vary
         with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
@@
     \item Does $\Lambda_{div}$ unify the picture among the devices?
-      \alert{No, deos neutral pressure play a role?}
+      \alert{No, does neutral pressure play a role?}
     \item If neutrals play a role is it at the divertor and/or at the midplane?
@@
       increases with L$_{\parallel}$ }
-    \item Is cooling the divertor with fueling or with equivalent? \alert{Contradictory observations in AUG and JET}
+    \item Is cooling the divertor with fueling or seeding equivalent? \alert{Contradictory observations in AUG and JET}
     \item Do we observe same behavior in L and H-Mode? \alert{So
@@
 	\item A cross machine experiment has the makings of settling open issues
-	\item Therefore, we will allocate shots for cross-machine comparison
+	\item Therefore, we will allocate shots for cross-machine
+          comparison but we must strive after similar machine configuration
 	\item ....but also to other proposed experiments
@@
 	\begin{itemize}
-		\item The role of neutrals in the shoulder formation is not understood
+		\item The role of neutrals in the shoulder
+                  formation is not understood
                   {\scriptsize(proponents: Carralero (\# 7), Militello
@@
 		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$.
-                  {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, WalkdenCarralero (\# 7), Militello
+                  {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, Carralero (\# 7), Militello
                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9), Tsui
@@
 			\item Carry out parameter scans on all machines
-			\item Strive after similar machine configurations
+
 		\end{enumerate}
@@
   will be provided by MST1
-\item However GA agree that MST1 can provide part of the ppy for
+\item However GA agrees that MST1 can provide part of the ppy for
   running experiments in line with MST1 topics
@@
 	\item Topology investigations? For example the comparison
-          USN/LSN/DN is not possible. Upper divertor information is
-          actually less detailed. Better to use reverse B$_t$ or ion
-          $\mathbf{B}\times\nabla\mathbf{B}$ pointing away from
-          X-Point which is know to have influences in detachment as
+          USN/LSN/DN is not included. Diagnostic capability of upper
+          divertor is weaker than the lower one.
+          Better to use reverse B$_t$  which is known
+          to have influences in detachment as
           well \parencite{McLean}
@@
   \begin{enumerate}
-    \item Mean field modelling available for AUG (EMC3-EIRENCE) and
+    \item Mean field modeling, in particular for neutral investigation.
+      Available for AUG (EMC3-EIRENCE) and
       MAST-U (SOLPS). So far we lack investigation for these scenario
-      targeting TCV. Manpower needed from edge and SOL modelling
+      targeting TCV. Manpower needed from edge and SOL modeling
     \item Turbulence code: we should need self-consistent interaction
       with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
-      \texttt{GBS}. Some of them can be run by people who will, very
+      \texttt{GBS}, \texttt{Tokam-3X}.
+      Some of them can be run by people who will, very
       likely, apply for this topic, some other not
@@
 	\begin{itemize}
-		\item Possibility to piggybag on Quescient/small ELM H-mode shots (Topic 5,6, 18)
-		\item Shortly after this meeting we will organize a follow-up meeting to reconcile ideas
+		\item Possibility to piggybag on
+                  Quiescent/small ELM H-mode shots (Topic 5,6, 18)
+		\item Shortly after this meeting we will organize
+                  a follow-up meeting to reconcile ideas
                   from this discussion (date not fixed yet)
 		\item All information will be gathered on the wiki
-                \item Other channels for discussion/sharing. Slack
-                  (mst1-topic21.slack.com), Github for code sharing
+                \item Other channels for discussion/sharing. e.g. Slack
+                  (mst1-topic21.slack.com), Github for code sharing, \ldots
 		\item We aim to arrive to a proper shared database of
@@
                   properties, $\Lambda_{div}$ estimate and location,
-                  Neutrals, \ldots 
+                  Neutrals, packing fraction, \ldots 
  	\end{enumerate}

### 2017-03-02 Meetings/GPMNov2016/gpm_november2016_vianello.tex
changes in the structure of the folder plus addition of KoM presentation

--- 2016-11-15 Presentation/gpm_november2016_vianello.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=MST1-EPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=KoM,venue=Remote, date=02/03/2017, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
   future devices}
-\date{15 November 2016}
+\date{03 March 2017}
 \author[Topic 21. J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
@@
       \only<1-2>{
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15a}
+      \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15a}
           \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
@@
     \only<3-4>{
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15b}
+      \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15b}
           \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
@@
     }
-    \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15c}
+    \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15c}
     \end{column}
@@
       \begin{column}{0.5\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16b}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16c}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/AgostiniNF2011}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16d}
+        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16a}
+        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16b}
+        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16c}
+        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/AgostiniNF2011}
+        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16d}
       \end{column}
@@
       \begin{column}{0.5\textwidth}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16e}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16f}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16g}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16h}
+        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16e}
+        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16f}
+        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16g}
+        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16h}
       \end{column}
@@
       \begin{column}{0.5\textwidth}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16a}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16b}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16c}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16d}
-        \includegraphics<6>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16e}
+        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16a}
+        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16b}
+        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16c}
+        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16d}
+        \includegraphics<6>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16e}
       \end{column}
@@
       \begin{column}{0.5\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16b}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16c}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16d}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16e}
+        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16a}
+        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16b}
+        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16c}
+        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16d}
+        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16e}
       \end{column}
@@
       \begin{column}{0.5\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MilitelloNF16a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16a}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16c}
+        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MilitelloNF16a}
+        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16a}
+        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16c}
       \end{column}
@@
       \begin{column}{0.6\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MuellerJNM15a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/SunPPCF15a}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16i}
+        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MuellerJNM15a}
+        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/SunPPCF15a}
+        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16i}
       \end{column}

### 2017-03-02 Meetings/KoM02March17/kom_020317_madsen_vianello.tex
changes in the structure of the folder plus addition of KoM presentation
added the presentation for the KoM

--- 2016-11-14 Presentation/gpm_november2016_vianello.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=MST1-EPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=KoM,venue=Remote, date=03/13/2017, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Filamentary transport in high-power H-mode conditions and in
-  no/small-ELM regimes to predict heat and particle loads on PFCs for
-  future devices}
-\date{15 November 2016}
+\title{Topic 21: AUG experiment KoM}
+\date{03 March 2017}
 \author[Topic 21. J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
@@
 
-\begin{frame}{Main focus of topic as listed in MST1 call}
+\begin{frame}{AUG experimental plan}
 \vspace{-1cm}
-Objectives:
+\only<1>{The present experimental plan addressed some of the proposed
+experimental plan for both the \textcolor{ta3chameleon}{L-Mode} and
+\textcolor{ta3scarletred}{H-Mode} part. \\
+}
+\only<2>{
+We will conclude the \textcolor{ta3chameleon}{L-Mode}
+part in Week 15 where we also would like to include part of the \textcolor{ta3scarletred}{H-Mode}
+scenario development\\
+\textbf{Week 15} \\
   \begin{enumerate}
-\item Use the new HHF probe on AUG to study filamentary transport under
-high-power H-mode conditions and under different plasma configurations (SN,
-DN).
-\item Study the role of ELM regimes, neutral compression, and particle density in
-filamentary transport and related shoulder formation.
-\item Identify the contribution of collisionality and seeding on filamentary transport
-and related shoulder formation.
-\item Extend the studies to quiescent H-modes as well as to other small-ELM regimes.
-\item Determine the effect of filaments and shoulder formation on target heat loads
-in different H-mode plasmas.
-\item Investigate the effect of plasma shape and configuration on ELM-induced heat
-loads.
+    \item \textcolor{ta3chameleon}{Take Shot \# 30269 as Reference, Reduce current to 0.6 MA
+      keeping the same toroidal field $B_{\phi}$ adjust the fueling
+      rate (\emph{Current scan})}
+    \item \textcolor{ta3chameleon}{Repeat shot \#1 keeping the same $q_{95}$ as reference
+      (\emph{Current scan at fixed $q_{95}$})}
+    \item \textcolor{ta3chameleon}{Repeat \#1 at higher current 1 MA adjusting the fueling rate}
+    \item \textcolor{ta3chameleon}{Repeat \# 3 keeping the same
+        $q_{95}$ as reference shot}
     \end{enumerate}
-\underline{Motivation}: Particle and energy transport in the SOL is crucial for the lifetime of plasma facing components in ITER and DEMO
+  }
+  \only<3>{
+  \textbf{Week 15} \\
+    For the \textcolor{ta3scarletred}{H-Mode} scenario development we start from the best shot found in
+    2016 (\# 33478) and increase the heating power
+    \begin{enumerate}
+      \item \textcolor{ta3scarletred}{Start from shot \# 33478 but
+          with increased heating power (6MW). Adjust fueling rate from
+        reference by increasing by a factor of 30 \%. 1 Plunge of
+        probe head at the end of the discharge still in a safe
+        position and IR monitoring}
+    \item \textcolor{ta3scarletred}{Repeat \# 1 eventually adjusting
+        the fueling rate. Start the N seeding in feedforward starting
+        fro the level found in reference}
+    \item \textcolor{ta3scarletred}{Trade off between \#1 and \#2
+        Fueling/Seeding. Additional plunge of probe at the end of the discharge}
+    \end{enumerate}
+  }
+  \only<4>{
+  \textbf{Week 17} \\
+    \begin{enumerate}
+    \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in Week 15 1st Radial position of probe}
+    \item \textcolor{ta3scarletred}{Repeat \#1, different probe position}
+    \item \textcolor{ta3scarletred}{Repeat \#1, different probe
+        position}
+    \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
+        week 15 and reduce the cryopumps}
+    \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
+        week 15 and puff from midplane}
+    \item \textcolor{ta3scarletred}{Contingency}
+    \item \textcolor{ta3scarletred}{Contingency}
+    \end{enumerate}
+  }
+  \only<5>{
+    Among the contingency we propose the following 4 possibilities to
+    be discussed
+    \begin{enumerate}
+    \item \textcolor{ta3chameleon}{Reversing B$_t$ direction and repeat one identical shot (e.g \# 30269) to investigate
+   the role of SOL flows in SOL shoulder formation and filamentary
+   transport}
+    \item \textcolor{ta3chameleon}{DN discharge with similar density ramps as in reference. Possibly the two X-point should
+   sit on the same flux surface}
+   \item \textcolor{ta3scarletred}{Attempt a scenario similar to Topic-06 which will be performed later in time. See for example
+   shot \# 29816 (Presented by T. Eich in the GPM) which is at even
+   higher power (8 MW) or \# 25740
+   which is actually in DN. If we choose for this we could actually compare with the priority 3 of L-Mode
+   contingency}
+ \item \textcolor{ta3scarletred}{Reverse B$_{t}$ operation. In this case the L-H treshold is different and we might end
+   by careful adjusting the power into I-Mode scenario}
+\end{enumerate}
+  }
 \end{frame}
-
-\begin{frame}{Outline}
+\begin{frame}{Required diagnostic and analysis}
   \begin{itemize}
-		\item Background 
-		\item Plans (we will not make a detailed list of the
-                  proposal, we already tried to combine and summarize them)
-		\item Discussion
+    \item[$\boxtimes$] Midplane Manipulator
+    \item[$\square$] Li-Beam. \emph{Are fluctuations and profiles
+        available simultaneously}
+    \item[$\square$] RFA \#2
+    \item[$\square$] Divertor probes
+    \item[$\boxtimes$] Neutral profiles
+    \item[$\square$] Infrared for probe head monitoring. \emph{Are Target
+      infrared measurements available/useful?}
+    \item[$\square$] GPI
+    \item[$\boxtimes$] Reflectometer. \emph{The operation at 2T can be
+      obtained during the q$_{95}$ scan}
+    \item[$\boxtimes$] Fast probes on the limiter
+    \item[$\square$] Bolometer/AXUV in the divertor region
   \end{itemize}
@@
 
-\section{Background}
-\begin{frame}{Present status}
-  \setbeamercovered{transparent}
-  \begin{enumerate}[<+(1) | invisible@-+>]
-    \item Experimental and theoretical investigations suggest that SOL density profiles are
-      determined by the balance between radial filamentary transport and parallel dynamics
-    \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
-    \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
-      TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
-    \item Observations exhibit various other dependencies e.g., divertor
-      collisionality, plasma current, seeding. \alert{Results from
-        different devices not fully reconciled and the underlying mechanism is not fully understood.}
-    \item Studies of shoulder formation in H-Mode are so far limited 
-	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
-%    \item First we will report a summary of the achievements and then
- %    personal comments and plans
+\begin{frame}{Work to be accomplished before the experiment}
+  \begin{enumerate}
+    \item Check the shape modification during the current/q$_{95}$
+      scan
+    \item Probe conditioning?
+    \item Check the status of the diagnostics including GPI (issue
+      regarding the puffing)
+    \item Code preparation for analysis and
+      visualization. \emph{GITHUB repository?}
+    \item Other?
   \end{enumerate}
 \end{frame}
-\section{L-Mode}
-\begin{frame}{L-Mode studies: AUG/1}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
-        \begin{equation*}
-        \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
-      \end{equation*}
-      controls filaments size
-        \item<2-> \textcolor{red}{Tested by changing n$_e$
-            and $T_e$ through fueling/seeding/heating}
-        \item<3-> This determines a change of the velocity-size
-          scaling from
-            \textcolor{ta3chameleon}{sheath-limited}
-        to \textcolor{blue}{inertial regime}.
-       \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
-           length}}
-       \item<5> This finally determines the shoulder formation
-        \end{itemize}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \only<1-2>{
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15a}
-          \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
-          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
-        \only<2>{
-          \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
-        }
-      \end{tikzonimage}}
-    \only<3-4>{
-      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15b}
-          \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
-          \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
-      \end{tikzonimage}
-    }
-    \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15c}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}{L-Mode studies: AUG/2}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1-> Profile modified by an increase of blob-size and change of
-        \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
-        \onslide<2->{\textcolor{blue}{and filament relative density}
-          {\footnotesize (Carralero 2016 in preparation)}}
-      \item<3-> As a consequence the contribution of filaments to
-        radial transport increases
-      \item<4|only@4> \alert{Beware the change of frequency may be due to a
-        modification of fluctuation velocity which is know to vary
-        with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
-      \item<5> Parallel flow is strongly reduced whenever we increase
-        the divertor collisionality
-      \end{itemize}
-    \end{column}
-      \begin{column}{0.5\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16b}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16c}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/AgostiniNF2011}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16d}
-      \end{column}
-    \end{columns}
-  \end{frame}
-
-  \begin{frame}{L-Mode studies:AUG/3}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1-> Electron and ions behave differently
-      \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
-        accross the SOL and slightly affected by the increase of
-        divertor collisionality
-      \item<3|only@3> Ions are strongly affected: for
-        \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
-          and $\lambda_{T_i} \sim 30$
-          mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
-          T$_{i, bk}\sim 25$ eV
-          and $\lambda_{T_i} \sim 8$ mm}
-       \item<4-> Ion energy spectrum from
-         $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
-         energy for $\Lambda_{div} > 1$
-       \item<5> EMC3-Eirene simulation suggests that such a reduction
-         can't be accounted for thermalization process. An
-         \alert{ionization front builds in front of the limiter shadow}   
-       \end{itemize}
-    \end{column}
-      \begin{column}{0.5\textwidth}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16e}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16f}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16g}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16h}
-      \end{column}
-    \end{columns}
-  \end{frame}
-
-  \begin{frame}{L-Mode: TCV}
-    \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
-        dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
-        \begin{equation*}
-          f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
-        \end{equation*}
-        in ohmic density ramps \parencite{vianello:iaea2016}
-      \item<2|only@2> Slight variation of density profiles at the target but
-        due to direct dependence on L$_{\parallel}$ large increase of
-        $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
-        we reach a certain amount of $\langle n_e \rangle$}
-       \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
-        \onslide<4-5>{\textcolor{red}{also on a statistical
-            basis}}. \onslide<5>{Strong dependence on average density,
-          independent of L$_{\parallel}$}}
-       \item<6|only@6> $\lambda_n$ depends clearly on blob-size
-         whereas the dependence on divertor condition is less
-         obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
-      \end{itemize}
-    \end{column}
-      \begin{column}{0.5\textwidth}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16a}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16b}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16c}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16d}
-        \includegraphics<6>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16e}
-      \end{column}
-    \end{columns}
-  \end{frame}
-
-  \begin{frame}{L-Mode: JET}
-    \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1|only@1> The shoulder formation strongly depends on
-        divertor geometry, disappear with vertical target and strike
-        point closest to cryogenics pumps \parencite{Wynn:EPS2016}
-      \item<2|only@2> The midplane pressure from baratrons is
-        equivalent between the different divertor. \alert{This would
-          indicate that SOL neutral density at the outboard midplane does not play any role}
-       \item<3|only@3> In the horizontal target configuration the
-         results indicate that the shoulder forms right at the
-         transition from sheath-limited to high-recycling where also
-         $\Lambda_{div}$ strongly increase
-       \item<4|only@4> Shoulder amplitude correlates with strike
-         points position. \alert{Shoulder, ionization and
-           $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
-         from the pump}
-       \item<5|only@5> In seeded discharges the transition observed at
-         very high level of $\Lambda_{div} >> 1$
-      \end{itemize}
-    \end{column}
-      \begin{column}{0.5\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16b}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16c}
-        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16d}
-        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16e}
-      \end{column}
-    \end{columns}
-  \end{frame}
-
-  \begin{frame}{L-Mode: MAST}
-    \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item<1|only@1> Strong dependence on
-        I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
-        constant toroidal field shoulder disappears. Consistent with
-        observation in other devices
-      \item<2|only@2> Filaments binormal dimension increases with
-        current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
-       \item<3|only@3> Filament radial velocity decreases with current
-         as well as the radial dimension \parencite{Kirk:2016jj}
-      \end{itemize}
-    \end{column}
-      \begin{column}{0.5\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MilitelloNF16a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16a}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16c}
-      \end{column}
-    \end{columns}
-  \end{frame}
-
-  \section{H-Mode}
-  \begin{frame}{AUG: H-Mode}
-    \begin{columns}
-    \begin{column}{0.4\textwidth}
-      \begin{itemize}
-      \item<1|only@1> SOL profiles in H-Mode so far investigated on
-        AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
-      \item<2|only@2> Differently from L-Mode, complete detachment
-        suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
-       \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
-         shoulder depends on a combination of $\Lambda_{div}$ and
-         fueling rate. Complete detachment seems instead not necessary
-         although very weak shoulder
-      \end{itemize}
-    \end{column}
-      \begin{column}{0.6\textwidth}
-        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MuellerJNM15a}
-        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/SunPPCF15a}
-        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16i}
-      \end{column}
-    \end{columns}
-  \end{frame}
-
-  \section{Open issues}
-  \begin{frame}{Open and unresolved issues}
-  \setbeamercovered{transparent}
-  \begin{enumerate}[<+(1) | invisible@-+>]
-    \item Does $\Lambda_{div}$ unify the picture among the devices?
-      \alert{No, deos neutral pressure play a role?}
-    \item If neutrals play a role is it at the divertor and/or at the midplane?
-      \alert{Contradictory results if one include experiments with
-        midplane puffing, JET and EIRENE simulations}
-    \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
-      dependence from f$_x$ scan but both TCV and MAST observe an
-      I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
-      increases with L$_{\parallel}$ }
-    \item Is cooling the divertor with fueling or with equivalent? \alert{Contradictory observations in AUG and JET}
-    \item Do we observe same behavior in L and H-Mode? \alert{So
-      far no as shown in H-Mode AUG. We need higher detachment
-      condition and we need enough fueling}
-      \item Is the density shoulder accompanied with an ion temperature shoulder?
-%      \item What are the underlying mechanisms? 
-    \end{enumerate}
-  \end{frame}
-
-\section{Topic 21 experiments }
-\begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
-	\begin{itemize}
-		\item 15 were proposals submitted to Topic 21
-		\item Proposals include experiments on all three machines 
-		\item There are overlaps between several of the proposals 
-		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 
-		\item However, total number of proposed shots:  \textbf{449}
-		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
-		\item Reaching all goals is not possible with the current number of allocated shots.
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Focal points}
-\begin{itemize}
-	\item MST1 uniquely facilitates cross comparison between machines
-	\item Several of the proposed experiments overlap and will be combined
-	\item A cross machine experiment has the makings of settling open issues
-	\item Therefore, we will allocate shots for cross-machine comparison
-	\item ....but also to other proposed experiments
-	\item Cross machine L-mode experiments: 
-	\begin{enumerate}
-		\item Investigate the role of neutrals 
-		\item $I_p$ and $q_{95}$ scans
-	\end{enumerate}
-	\item Cross machine H-mode experiments. 
-\end{itemize}	
-\end{frame}
-
-\begin{frame}{L-mode experiments}
-	\begin{itemize}
-		\item The role of neutrals in the shoulder formation is not understood
-                  {\scriptsize(proponents: Carralero (\# 7), Militello
-                    (\# 1, 2), Vianello (\# 13), Walkden (\# 9))}
-		\begin{enumerate}
-		\item We envisage to measure neutral gas profiles at the outboard midplane
-                  using fast cameras with D$_{\alpha}$ filter, density
-                  and temperature SOL profiles and appropriate code
-                  (e.g. KN1D as in \parencite{Lipschultz:2005gg,Lipschultz:2016vk})
-		\item Reciprocating probes and profiles available on
-                  all machines
-                \item Investigate role of fueling location (MAST)
-		\end{enumerate}
-		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$.
-                  {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, WalkdenCarralero (\# 7), Militello
-                    (\# 1, 2), Vianello (\# 13), Walkden (\# 9), Tsui
-                    (\# 15))}
-		\begin{enumerate}
-			\item Carry out parameter scans on all machines
-			\item Strive after similar machine configurations
-		\end{enumerate}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{H-mode experiments}
-\begin{itemize}
-	\item ITER and DEMO will operate in H-mode
-	\item We must know what parameters control shoulder formation 
-	\item Shoulder formation parameter regime is unclear on all machines
-	\item Main priorities: 
-	\begin{enumerate}
-		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
-		\item Investigate the SOL (filamentary) transport properties.
-                  Whenever main diagnostic is reciprocating probes $\rightarrow$ limits heating power
-		\item Experiments must gradually increase power and density. 
-	\end{enumerate}
-	\item Fueling in H-mode is problematic due to transport
-          barrier. Is there a way to overcome it? NBI, pellet fueling?
-	\item H-mode density limit \parencite{Bernert:2015bq} must be dealt with
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Optimizing cross machine comparison}
-\begin{itemize}
-	\item Machines are fundamentally differently designed
-	\item Strive for similar configurations of the machines:
-	\begin{enumerate} 
-		\item Single-Null
-		\item $\bm{B} \times \nabla B$ towards active divertor 
-		\item Strike-point and cryo pump location (AUG and MAST-U)
-		\item Heating 
-		\item Fueling location 
-		\item Seeding (species, location, rate)
-	\end{enumerate}
-\end{itemize} 
-%things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,
-
-\end{frame}
-
-\begin{frame}{Required diagnostics and competences}
-In order to compare experiments the following diagnostics must be available: 
-\begin{enumerate}
-	\item Filaments analysis in the Outboard midplane: 
-	\begin{itemize} 
-		\item Through Reciprocating probe then $I_{sat}$  on minimum three pins poloidally and radially separated
-		 (filaments speed and size). 
-		\item Electron temperature (fast T$_e$ measurements
-                  can be achieved with BPP in MAST-U {\footnotesize
-                    (N. Walkden \#11)})
-		\item If possible $M_{\|}$
-	 \end{itemize}
-	 \item Camera viewing OM for measuring neutrals 
-	 \item Divertor measurements of $n$ and $T_e$ (probes) plus
-           spectroscopy and bolometry 
-	 \item Density profile measurements (Li-Bes, Reflectometry (\#
-           6 Acquiam, \# 8 Vicente), Edge Thomson scattering) 
-         \item Sami and Field for fast particles accelleration (piggy
-           back on developed scenarion \# 4 McClements)
-%	\item H-mode quality diagnostics(div current, magnetics)
-\end{enumerate}
-\end{frame}
-
-\begin{frame}[allowframebreaks]{Proposed shot plan - AUG}
-\vspace{-1cm}
-Allocated shots $\sim$ 14 + contingency 
-\begin{itemize}
-	\item L-Mode (6 shots)
-	\begin{enumerate}
-		\item Reference shot \# 30276
-		\item Perform $I_p$ scan (three values) with fixed $B_T$
-		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
-		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
-		\item should we add OM puff to validate neutral measurements?
-		\item Possibility of strike-point sweeping during shot
-		\item RFEA measurements in internal program. 
-		\item These shots combines experiments proposed by:
-                  Carralero (\# 7), Militello (\#1), Vianello (\#13)
-
-	\end{enumerate}
-	\item H-mode (9 shots)
-	\begin{enumerate}
-		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions
-                  in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
-		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
-		\item Strike-point sweep if feasible? 
-		\item In all shots, particle acceleration in ELMs will be studied using microwaves,
-                  soft X-rays, and FILD 
-		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
-		\item These shots combine experiments proposed by:
-                  Aguiam (\#6), Carralero (\#7), McClements (\#4),
-                  Militello (\# 1, 2), Vianello (\#13), Vicente (\#8)
-
-	\end{enumerate}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Proposed shot plan - TCV}
-	\begin{itemize}
-		\item L-mode (11 shots)
-		\begin{enumerate}
-			\item Reference shot \# 53514
-			\item Same $I_p$ and $q_{95}$ scans as on AUG
-			\item Two shots with reversed $\bm{B} \times \nabla B$
-			\item Move plasma vertically. Disentangle
-                          $q_{95}$ and $L_{\|}$	
-                        \item These shots combines proposal: Vianello
-                          (\#13), Tsui (\#15), Militello (\#1, 2)
-		\end{enumerate}
-		\item H-mode (12 shots)
-		\begin{enumerate}
-			\item Reference shot \# 53352
-			\item Since H-mode shoulder is new territory on TCV first shots will be scenario development
-			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
-                        \item These shots combines proposal: Vianello
-                          (\#13), Tsui (\#15), Militello (\#1, 2)
-		\end{enumerate}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Preliminary shot plan  - MAST-U}
-	\begin{itemize}
-		\item L-mode (6 shots)
-		\begin{enumerate}		
-			\item New machine. No reference shot yet			
-			\item Same $I_p$ and $q_95$ scan to allow
-                          cross-machine comparison. Availability of multi pin probe? 
-			\item Try varying fueling location
-			\item RFEA measurements during shoulder
-                          formation 
-                        \item These shots combines proposal: Militello
-                          (\#1, 2, 3), Walkden (\#11), Vianello (\#13)
-		\end{enumerate}
-		\item H-mode (7 shots)
-		\begin{enumerate}
-			\item These experiments require the existence of H-mode reference shot. Perhaps not available in 2017
-			\item Similar scenario development as on other emachines
-                        \item These shots combines proposal: Militello
-                          (\#1, 2, 3),  Vianello (\#13)
-		\end{enumerate}
-		\item Probe head must be changed to allow
-                  investigation of both fast T$_e$ (BPP),  and T$_i$
-                  (RFEA) but this require careful schedule of machine time
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{COMPASS collaboration}
-\begin{itemize}
-\item COMPASS is not an MST1 device, therefore no operational cost
-  will be provided by MST1
-\item However GA agree that MST1 can provide part of the ppy for
-  running experiments in line with MST1 topics
-\item Proposal \# 14 is focused filaments dynamics and shoulder
-  formation both in L and H-Mode
-\item Experimental plan can be therefore agreed in order to perform
-  similar experiments (e.g. I$_p$ and $q_{95}$ scan in L-Mode)
-  ensuring proper comparison between devices
-\item COMPASS suppose 3ppy for running and evaluation of experiment
-  pertaining Topic-21, among Czeck and other european laboratories.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{There are urgent experiment which cannot be addressed}
-\begin{itemize}
-	\item Detailed ion temp measurements. Must eventually be
-          completed in internal programs. Are you willing to share the
-          information among Topic 21 even though done internally?
-	\item Topology investigations? For example the comparison
-          USN/LSN/DN is not possible. Upper divertor information is
-          actually less detailed. Better to use reverse B$_t$ or ion
-          $\mathbf{B}\times\nabla\mathbf{B}$ pointing away from
-          X-Point which is know to have influences in detachment as
-          well \parencite{McLean}
-	\item Strikepoint sweeping and cryo pump
-	\item Parameters scans in H-mode
-	\item X-point probes
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Modeling require}
-  \begin{enumerate}
-    \item Mean field modelling available for AUG (EMC3-EIRENCE) and
-      MAST-U (SOLPS). So far we lack investigation for these scenario
-      targeting TCV. Manpower needed from edge and SOL modelling
-    \item Turbulence code: we should need self-consistent interaction
-      with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
-      \texttt{GBS}. Some of them can be run by people who will, very
-      likely, apply for this topic, some other not
-  \end{enumerate}
-\end{frame}
-
-\begin{frame}{Future and Miscellaneous}
-	\begin{itemize}
-		\item Possibility to piggybag on Quescient/small ELM H-mode shots (Topic 5,6, 18)
-		\item Shortly after this meeting we will organize a follow-up meeting to reconcile ideas
-                  from this discussion (date not fixed yet)
-		\item All information will be gathered on the wiki
-                \item Other channels for discussion/sharing. Slack
-                  (mst1-topic21.slack.com), Github for code sharing
-		\item We aim to arrive to a proper shared database of
-                  filaments between the machines, where properties
-                  will be obtained using agreed approaches so that a
-                  cross-machine comparison paper could at the end be
-                  finalized at a certain point		
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Discussion agenda}
-	\begin{enumerate}
-		\item Priorities. These are our personal ideas. Do we agree? 
-		\item \underline{Common measurement techniques}. Filament
-                  properties, $\Lambda_{div}$ estimate and location,
-                  Neutrals, \ldots 
- 	\end{enumerate}
-\end{frame}
-
 \end{document}

### 2017-03-02 Meetings/KoM02March17/kom_020317_crossexperiment.tex
added the suggestion from Jesn and te cross-machine slide

--- 2017-03-02 Meetings/KoM02March17/kom_020317_madsen_vianello.tex
@@
 \date{03 March 2017}
-\author[Topic 21. J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
+\author[N.Vianello]{N. Vianello}
 \begin{document}
@@
 
-\begin{frame}{AUG experimental plan}
+\begin{frame}{Cross-machine comparison}
 \vspace{-1cm}
-\only<1>{The present experimental plan addressed some of the proposed
-experimental plan for both the \textcolor{ta3chameleon}{L-Mode} and
-\textcolor{ta3scarletred}{H-Mode} part. \\
-}
-\only<2>{
-We will conclude the \textcolor{ta3chameleon}{L-Mode}
-part in Week 15 where we also would like to include part of the \textcolor{ta3scarletred}{H-Mode}
-scenario development\\
-\textbf{Week 15} \\
-  \begin{enumerate}
-    \item \textcolor{ta3chameleon}{Take Shot \# 30269 as Reference, Reduce current to 0.6 MA
-      keeping the same toroidal field $B_{\phi}$ adjust the fueling
-      rate (\emph{Current scan})}
-    \item \textcolor{ta3chameleon}{Repeat shot \#1 keeping the same $q_{95}$ as reference
-      (\emph{Current scan at fixed $q_{95}$})}
-    \item \textcolor{ta3chameleon}{Repeat \#1 at higher current 1 MA adjusting the fueling rate}
-    \item \textcolor{ta3chameleon}{Repeat \# 3 keeping the same
-        $q_{95}$ as reference shot}
-    \end{enumerate}
-  }
-  \only<3>{
-  \textbf{Week 15} \\
-    For the \textcolor{ta3scarletred}{H-Mode} scenario development we start from the best shot found in
-    2016 (\# 33478) and increase the heating power
-    \begin{enumerate}
-      \item \textcolor{ta3scarletred}{Start from shot \# 33478 but
-          with increased heating power (6MW). Adjust fueling rate from
-        reference by increasing by a factor of 30 \%. 1 Plunge of
-        probe head at the end of the discharge still in a safe
-        position and IR monitoring}
-    \item \textcolor{ta3scarletred}{Repeat \# 1 eventually adjusting
-        the fueling rate. Start the N seeding in feedforward starting
-        fro the level found in reference}
-    \item \textcolor{ta3scarletred}{Trade off between \#1 and \#2
-        Fueling/Seeding. Additional plunge of probe at the end of the discharge}
-    \end{enumerate}
-  }
-  \only<4>{
-  \textbf{Week 17} \\
-    \begin{enumerate}
-    \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in Week 15 1st Radial position of probe}
-    \item \textcolor{ta3scarletred}{Repeat \#1, different probe position}
-    \item \textcolor{ta3scarletred}{Repeat \#1, different probe
-        position}
-    \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
-        week 15 and reduce the cryopumps}
-    \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
-        week 15 and puff from midplane}
-    \item \textcolor{ta3scarletred}{Contingency}
-    \item \textcolor{ta3scarletred}{Contingency}
-    \end{enumerate}
-  }
-  \only<5>{
-    Among the contingency we propose the following 4 possibilities to
-    be discussed
-    \begin{enumerate}
-    \item \textcolor{ta3chameleon}{Reversing B$_t$ direction and repeat one identical shot (e.g \# 30269) to investigate
-   the role of SOL flows in SOL shoulder formation and filamentary
-   transport}
-    \item \textcolor{ta3chameleon}{DN discharge with similar density ramps as in reference. Possibly the two X-point should
-   sit on the same flux surface}
-   \item \textcolor{ta3scarletred}{Attempt a scenario similar to Topic-06 which will be performed later in time. See for example
-   shot \# 29816 (Presented by T. Eich in the GPM) which is at even
-   higher power (8 MW) or \# 25740
-   which is actually in DN. If we choose for this we could actually compare with the priority 3 of L-Mode
-   contingency}
- \item \textcolor{ta3scarletred}{Reverse B$_{t}$ operation. In this case the L-H treshold is different and we might end
-   by careful adjusting the power into I-Mode scenario}
-\end{enumerate}
-  }
-\end{frame}
-\begin{frame}{Required diagnostic and analysis}
   \begin{itemize}
-    \item[$\boxtimes$] Midplane Manipulator
-    \item[$\square$] Li-Beam. \emph{Are fluctuations and profiles
-        available simultaneously}
-    \item[$\square$] RFA \#2
-    \item[$\square$] Divertor probes
-    \item[$\boxtimes$] Neutral profiles
-    \item[$\square$] Infrared for probe head monitoring. \emph{Are Target
-      infrared measurements available/useful?}
-    \item[$\square$] GPI
-    \item[$\boxtimes$] Reflectometer. \emph{The operation at 2T can be
-      obtained during the q$_{95}$ scan}
-    \item[$\boxtimes$] Fast probes on the limiter
-    \item[$\square$] Bolometer/AXUV in the divertor region
+    \item Brief summary of proposals done by N.Vianello and
+      F. Militello who suggest the repetition of similar experiments
+      in the 3 devices to provide appropriate comparison
+    \item<2|only@2> \textbf{L-Mode}
+      \begin{itemize}
+        \item Current scan both at fixed and varied q$_{95}$
+        \item Equivalent density ramp in favorable/unfavorable
+          $B\times \nabla B$ direction
+        \item Probe at a fixed position for long time statistics
+        \item Parallel flow and modification accordingly to
+          favorable/unfavorable direction
+        \end{itemize}
+      \item<3|only@3> \textbf{H-Mode}
+      \begin{itemize}
+        \item H-Mode with density ramps/seeding proposed by all the proponents
+        \item Similar density ramps/seeded experiments performed in
+          LSN/USN/DN configuration and monitor of filaments at the
+          target and at the midplane
+        \item QH-mode or Type-III ELMy regime
+        \end{itemize}
 \end{itemize}
 \end{frame}
-
-\begin{frame}{Work to be accomplished before the experiment}
-  \begin{enumerate}
-    \item Check the shape modification during the current/q$_{95}$
-      scan
-    \item Probe conditioning?
-    \item Check the status of the diagnostics including GPI (issue
-      regarding the puffing)
-    \item Code preparation for analysis and
-      visualization. \emph{GITHUB repository?}
-    \item Other?
-  \end{enumerate}
-\end{frame}
 \end{document}

### 2017-03-02 Meetings/KoM02March17/kom_020317_madsen_vianello.tex
added the suggestion from Jesn and te cross-machine slide

@@
 \vspace{-1cm}
-\only<1>{The present experimental plan addressed some of the proposed
+\only<1>{
+  \begin{itemize}
+  \item For Topic-21 on AUG 14 shots forseen, split into two blocks of
+    7 shot each on week 15 and week 17 respectively
+  \item The proposed experimental plan address some of the proposed
 experimental plan for both the \textcolor{ta3chameleon}{L-Mode} and
-\textcolor{ta3scarletred}{H-Mode} part. \\
+\textcolor{ta3scarletred}{H-Mode} part.
+\end{itemize}
 }
@@
 part in Week 15 where we also would like to include part of the \textcolor{ta3scarletred}{H-Mode}
-scenario development\\
+scenario development. This would give us an additional week between
+the experiments to address possible issues in particular for the
+H-mode part\\
 \textbf{Week 15} \\
   \begin{enumerate}
-    \item \textcolor{ta3chameleon}{Take Shot \# 30269 as Reference, Reduce current to 0.6 MA
+    \item \textcolor{ta3chameleon}{Take Shot \# 30269 as Reference
+        (0.8 MA). Reduce current to 0.6 MA
       keeping the same toroidal field $B_{\phi}$ adjust the fueling
-      rate (\emph{Current scan})}
-    \item \textcolor{ta3chameleon}{Repeat shot \#1 keeping the same $q_{95}$ as reference
-      (\emph{Current scan at fixed $q_{95}$})}
-    \item \textcolor{ta3chameleon}{Repeat \#1 at higher current 1 MA adjusting the fueling rate}
+      rate (\emph{Current scan with modification of $q_{95}$})}
+    \item \textcolor{ta3chameleon}{Repeat shot \#1 changing
+        the toroidal field in order to match the same $q_{95}$ as reference
+      (\emph{Current scan at fixed $q_{95}$}). We can adjust the
+      current level in order to match the request for operation with
+      B$_{t} = 2$T (Alves)}
+    \item \textcolor{ta3chameleon}{Repeat \#1 at higher current 1 MA
+        adjusting the fueling rate and keeping the same toroidal field
+      as reference}
     \item \textcolor{ta3chameleon}{Repeat \# 3 keeping the same
@@
     \item \textcolor{ta3scarletred}{Trade off between \#1 and \#2
-        Fueling/Seeding. Additional plunge of probe at the end of the discharge}
+        Fueling/Seeding. Additional plunge of probe at the end of the
+        discharge}
+      \item \textcolor{ta3skyblue}{This scenario would allow the
+          exploitation of particle accelleration (McClements) physics as piggy-back}
     \end{enumerate}
@@
   \only<4>{
-  \textbf{Week 17} \\
+  \textbf{Week 17: This strongly depends on the achievement of H-Mode
+    scenario obtained in Week 15 } \\
     \begin{enumerate}
@@
     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
-        week 15 and reduce the cryopumps}
+        week 15 and reduced the cryopumps}
     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
@@
    higher power (8 MW) or \# 25740
-   which is actually in DN. If we choose for this we could actually compare with the priority 3 of L-Mode
+   which is actually in DN (see proposal from J. Vicente). If we choose for this we could actually compare with the priority 3 of L-Mode
    contingency}
@@
      by careful adjusting the power into I-Mode scenario}
+   \item \textcolor{ta3skyblue}{Working at 2T in H-Mode would require
+       additional development}
 \end{enumerate}
@@
       regarding the puffing)
+    \item Methodology ($\Lambda_{div}$ computation and profile)
+      $\lambda_n$ filaments properties etc.  
     \item Code preparation for analysis and
       visualization. \emph{GITHUB repository?}
-    \item Other?
+    \item Optimization of the effort: please provide us a more
+      detailed plan of your analysis in order to limit superposition
+      or work duplication
   \end{enumerate}

### 2017-03-03 Meetings/KoM02March17/kom_020317_madsen_vianello.tex
update to KoM presentation with clarification for the current scan

@@
 \textbf{Week 15} \\
+We choose are reference shot \# 30269 (I$_p$ = 0.8 MA, B$_{\phi}$ = 2.5T, q$_{95}\approx 4.5$)
   \begin{enumerate}
-    \item \textcolor{ta3chameleon}{Take Shot \# 30269 as Reference
-        (0.8 MA). Reduce current to 0.6 MA
-      keeping the same toroidal field $B_{\phi}$ adjust the fueling
+    \item \textcolor{ta3chameleon}{Shot at I$_p$=0.6 MA
+      keeping the same toroidal field $B_{\phi}$ = 2.5T as the reference adjust the fueling
       rate (\emph{Current scan with modification of $q_{95}$})}
-    \item \textcolor{ta3chameleon}{Repeat shot \#1 changing
-        the toroidal field in order to match the same $q_{95}$ as reference
-      (\emph{Current scan at fixed $q_{95}$}). We can adjust the
-      current level in order to match the request for operation with
-      B$_{t} = 2$T (Alves)}
-    \item \textcolor{ta3chameleon}{Repeat \#1 at higher current 1 MA
-        adjusting the fueling rate and keeping the same toroidal field
-      as reference}
-    \item \textcolor{ta3chameleon}{Repeat \# 3 keeping the same
-        $q_{95}$ as reference shot}
+  \item \textcolor{ta3chameleon}{Shot at I$_p$ = 0.6MA
+      reduce the toroidal field B$_{\phi}\approx $2T in order to match q$_{95}\approx 4.5$, 
+      (\emph{Current scan at fixed $q_{95}$}). This would accommodate
+      the diagnostic request of D. Aguiam}
+    \item \textcolor{ta3chameleon}{Density ramp with I$_p$ = 1MA and
+        B$_{\phi}$ = 2.5T}
+    \item \textcolor{ta3chameleon}{Density ramp with I$_{p}$ = 1MA,
+        increasing the toroidal field in order to match q$_{95}\approx
+        4.5$}
     \end{enumerate}
@@
        additional development}
+   \item \textcolor{ta3skyblue}{Given that the upper divertor is less
+       diagnosed then the lower one we prefer eventually to operate
+       with reverse B$_{\phi}$}
+
 \end{enumerate}

### 2017-03-31 Experiments/AUG/analysis/python/scriptPreparationShot.py
added more clear figures for comparison

@@ -109,10 +109,93 @@ for shot, col, i in zip(shotList, colorL, range(len(shotList))):
         for key in rg.iterkeys():
             axE.plot(rg[key], zg[key], 'k')
     axE.contour(Eq.R, Eq.Z, Eq.psiN(Eq.R, Eq.Z), np.linspace(0, 1, 5), colors=col)
-    axE.contour(Eq.R, Eq.Z, Eq.psiN(Eq.R, Eq.Z), np.linspace(1, 1.09, 3), colors=col, linestyles='--')
+    axE.contour(Eq.R, Eq.Z, Eq.psiN(Eq.R, Eq.Z), np.linspace(1, 1.09, 3),
+                colors=col, linestyles='--')
     axE.set_xlabel('R')
     axE.set_ylabel('Z')
     axE.set_aspect('equal')
 
 ax[0, 0].legend(loc='best', numpoints=1, fontsize=10, frameon=False)
 mpl.pylab.savefig('../pdfbox/ComparisonCurrentQScan.pdf', bbox_to_inches='tight')
+
+# check current scan at constant q95
+shotL = (29311, 30276, 29315)
+colorL = ('#1E4682', '#DD6D3D', '#69675E')
+fig, ax  = mpl.pyplot.subplots(figsize=(13, 8), nrows = 2, ncols = 1)
+fig.subplots_adjust(wspace=0.3, left=0.6, top=0.95, bottom=0.12, right=0.98)
+_xlim = [0, 7]
+axE = fig.add_axes([0.05, 0.3, 0.5, 0.5])
+for shot, col, i in zip(shotL, colorL, range(len(shotL))):
+    diag = dd.shotfile('MAG', shot)
+    iP = diag('Ipa')
+    diag.close()
+    # load the toroidal field
+    diag = dd.shotfile('MAI', shot)
+    bT = diag('BTF')
+    diag.close()
+    # load the equilibrium
+    Eq = equilibrium(device='AUG', shot=shot, time=2.9)
+    ax[0].plot(iP.time, iP.data/1e6, col, ls='-', lw=1.7, label=r'Shot # %5i' % shot)
+    ax[0].axes.get_xaxis().set_visible(False)
+    ax[0].set_ylabel(r'I$_p$ [MA]')
+    ax[0].set_xlim(_xlim)
+
+
[…]

### 2017-03-31 Experiments/AUG/analysis/python/scriptPreparationShot.py
changes of referenc shot for AUG week 17

@@ -119,7 +119,7 @@ ax[0, 0].legend(loc='best', numpoints=1, fontsize=10, frameon=False)
 mpl.pylab.savefig('../pdfbox/ComparisonCurrentQScan.pdf', bbox_to_inches='tight')
 
 # check current scan at constant q95
-shotL = (29311, 30276, 29315)
+shotL = (29311, 30269, 29315)
 colorL = ('#1E4682', '#DD6D3D', '#69675E')
 fig, ax  = mpl.pyplot.subplots(figsize=(13, 8), nrows = 2, ncols = 1)
 fig.subplots_adjust(wspace=0.3, left=0.6, top=0.95, bottom=0.12, right=0.98)
@@ -160,7 +160,7 @@ ax[0].legend(loc='best', numpoints=1, fontsize=10, frameon=False)
 mpl.pylab.savefig('../pdfbox/CurrentScanConstantQ95.pdf', bbox_to_inches='tight')
 
 # constant scan at constant Bt
-shotL = (29302, 30276, 28738)
+shotL = (29302, 30269, 28738)
 colorL = ('#1E4682', '#DD6D3D', '#69675E')
 fig, ax  = mpl.pyplot.subplots(figsize=(13, 8), nrows = 2, ncols = 1)
 fig.subplots_adjust(wspace=0.3, left=0.6, top=0.95, bottom=0.12, right=0.98)

### 2017-03-31 Experiments/AUG/analysis/python/scriptPreparationShot.py
add figure for AUG H-Mode reference shot

@@ -185,7 +185,7 @@ for shot, col, i in zip(shotL, colorL, range(len(shotL))):
     ax[1].set_xlabel(r't[s]')
     ax[1].set_ylabel(r'q$_{95}$')
     ax[1].set_xlim(_xlim)
-    ax[1].set_ylim([2, 6])
+    ax[1].set_ylim([2, 8])
     # ora plottiamo l'equilibrio in un asse a parte
     if i ==0:
         rg, zg = map_equ.get_gc()
@@ -199,3 +199,114 @@ for shot, col, i in zip(shotL, colorL, range(len(shotL))):
     axE.set_aspect('equal')
 ax[0].legend(loc='best', numpoints=1, fontsize=10, frameon=False)
 mpl.pylab.savefig('../pdfbox/CurrentScanConstantBT.pdf', bbox_to_inches='tight')
+
+# reference H-Mode
+shot = 33478
+fig, ax  = mpl.pyplot.subplots(figsize=(18, 12), nrows = 4, ncols = 2)
+fig.subplots_adjust(wspace=0.3, hspace=0.07, right=0.6, top=0.95, bottom=0.12, left=0.1)
+_xlim = [0, 7]
+axE = fig.add_axes([0.61, 0.3, 0.4, 0.4])
+
+diag = dd.shotfile('MAG', shot)
+iP = diag('Ipa')
+diag.close()
+# load the toroidal field
+diag = dd.shotfile('MAI', shot)
+bT = diag('BTF')
+diag.close()
+# load the edge density
+diag = dd.shotfile('DCN', shot)
+enE = diag('H-5')
+diag.close()
+# greenwald fraction
+diag = dd.shotfile('TOT', shot)
+nG = diag('n/nGW')
+diag.close()    
+# load the Prad
+diag = dd.shotfile('BPD', shot)
+pRad = diag('Pradtot')
+diag.close()
+# load the total fueling
+diag = dd.shotfile('UVS', shot)
+iD2 = diag('D_tot')
+iN2 = diag('N_tot')
+diag.close()
+# load the equilibrium
+Eq = equilibrium(device='AUG', shot=shot, time=2.9)
+
+# load the current
+
+col = '#0F2D40'
[…]

### 2017-03-31 Experiments/AUG/Preparation/week17_plan.tex
AUG week 17 shot list prepared

\documentclass[10pt, compress]{beamer}
\usetheme[conference=Preparation,venue=Remote, date=31/13/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: Week 17 Experimental preparation}
\date{31 March 2017}
\author[Topic 21]{Topic 21 ST}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\section{L-Mode}
\begin{frame}{Current scan at constant q$_{95}$}
  \vspace{-1cm}
  \Fontvi
  \centering{\includegraphics[width=0.85\textwidth]{../analysis/pdfbox/CurrentScanConstantQ95}}
  \begin{itemize}
    \item The shot at lower and higher current has NBI which need to
      be substituted with ECRH (I guess the amount used in \# 30269 is
      sufficent)
    \item The fueling rate needs to be adjusted for lower current in
      order not to disrupt to early
    \item The higher current (it is the only reference I have for 1MA
      with this value of q$_{95}$) encounter an early
      disruption. \alert{Contact SL in order to check and avoid the reason}
  \end{itemize}    
\end{frame}

\begin{frame}{Current scan at constant B$_t$}
  \Fontvi
  \centering{\includegraphics[width=0.85\textwidth]{../analysis/pdfbox/CurrentScanConstantBT}}
  \begin{itemize}
    \item We have a slightly different upper triangularity for the
      reference shot. \alert{Is this an issue?}
    \item The fueling rate needs to be adjusted for lower current in
      order not to disrupt to early
  \end{itemize}    
\end{frame}

\begin{frame}{Shot list: L-Mode}
  \begin{enumerate}
    \item Repeat \# 23902, with fuelling rate reduced with respect to
      \# 30269 by 20\%. No NBI, 300 kW (\alert{Sufficient? shall we increase?}) ECRH central heating.
    \item Repeat \# 29311 with the same fuelling rate and heating as
      the previous. Should be fine for Reflectometer measurements
    \item Repeat \# 28738 with 300 kW ECRH central heating and same
      fueling as reference
    \item Repeat \# 29315 with correction in order to avoid disruption
  \end{enumerate}
  \end{frame}
  \section{H-Mode}
  \begin{frame}{H-Mode reference}
\vspace{-1cm}
    \Fontvi
  \centering{\includegraphics[width=0.85\textwidth]{../analysis/pdfbox/ReferenceHMode}}
  \begin{itemize}
    \item This should be the best reference mode we have from last year
    \item We should run this shot with P$_{NBI}\approx $4MW
    \item I'm not sure we can increase further the fueling since we
      already reach $n/n_G\approx 0.8$. Eventually we can start
      earlier and reduce the rate a bit
  \end{itemize}    
  \end{frame}
  \begin{frame}{H-Mode list}
    \begin{enumerate}
      \item Repeat \# 33478 with P$_{NBI}$ = 4MW and without seeding. Start D$_2$
        puffing earlier @ 4s reaching 25$\times 10^{21}$ @
        6s. Plunge of probe head at 5.2s.
        \item Repeat \#1 eventually with modification to fueling
          Add seeding in feed-forward as in reference shot. Plunge of
          the probe head @ 5.2 s
        \item Trade off between \#1 and \#2. If the probe does not
          exhibit problem 2 plunges @4.8 and 5.6
    \end{enumerate}
  \end{frame}
  \begin{frame}{To be done}
  \begin{itemize}
    \item[$\square$] Contact Reference Session Leader. E. Wolfrum (?)
    \item[$\square$] Check consistency of the equilibria in term of
      SOL field line. \alert{seems reasonable}
    \item[$\square$] Together with reference session leader check \#
      29315 for early disruption
    \item[$\square$] Prepare analysis tools for inter-shot evaluation
    \item[$\square$] Camera for neutral profile has been
      calibrated. Contact for CAD and field line tracing
    \item[$\square$] Check presence of relevant people in control room
      for operation of Bolometer/SXR/Langmuir/Gauges
    \item[$\square$] Prepare a task list for control room. We need
      people evaluating data on the fly
  \end{itemize}
\end{frame}

\end{document}

### 2017-04-25 Meetings/AUGrelated/preparation_240417.tex
added FILD as manned diagnostic into slides

\documentclass[10pt, compress]{beamer}
\usetheme[conference=KoM,venue=Remote, date=03/13/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: AUG experiment}
\date{24 April 2017}
\author[Topic 21 Scientific Team]{Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

\begin{frame}{L-Mode}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \centering{\includegraphics[height=\textheight]{pdfbox/30269Shape}}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{description}
      \item[\# 1] \textbf{EOC} Shape, 0.8MA, B$_{\phi}$ = -2.5 T, 0.5MW NBI heating,
        fueling as reference 30269, heating starting together with
        fueling
      \item[\# 2] Same density ramp and heating with I$_p$ = 0.61 MA,
        B$_{\phi}$ = -1.9T (reduced current with the same q$_{95}$)
      \item[\# 3] Same density ramp and heating with I$_p$ = 0.99 MA,
        B$_{\phi}$ = -3.1T (increased current with the same q$_{95}$)
      \item[\# 4] Same density ramp and heating B$_{\phi}$ = -2.5T and I$_{p}$ = 0.99 MA
      \item[\# 5] Same density ramp and heating B$_{\phi}$ = -2.5T and I$_{p}$ = 0.61 MA
    \end{description}

  \end{column}
\end{columns}
\end{frame}

\begin{frame}{H-Mode}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \centering{\includegraphics[height=\textheight]{pdfbox/30269Shape}}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{description}
      \item[\# 6] \textbf{EOC} Shape, repeat \# 33478 with P$_{NBI}$ =
        4MW, D$_2$ puffing starting at 4s up to 35$\times 10^{21}$ @
        6s. 1 Plunge of probe in safe position
      \item[\# 7] Repeat 6 adding N in feed-forward. Keep similar
        value as reference (since we are already increasing the fueling)
    \end{description}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Required diagnostic and analysis}
  \begin{itemize}
    \item[$\boxtimes$] Midplane Manipulator
    \item[$\boxtimes$] Li-Beam profiles (inter-ELMs one in the H-Mode
      shots) and fluctuations
    \item[$\boxtimes$] RFA \#2
    \item[$\boxtimes$] Divertor probes. Evaluation inter-shot of
      profiles and rollover density. Divertor collisionality
    \item[$\boxtimes$] Neutral profiles
    \item[$\square$] Infrared for probe head monitoring
    \item[$\boxtimes$] Reflectometer including the multi-channel one
      for the operation at 1.9 T
    \item[$\square$] Bolometer/AXUV in the divertor region. We need
      the monitoring of radiation front movement. Can we get inverted
      and tomography inter shot?
    \item[$\square$] Gauges and neutral measurement
    \item[$\boxtimes$] SXR
    \item[$\boxtimes$] FILD  
    \end{itemize}
\end{frame}

\begin{frame}{HFF probe head}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics[width=.9\textwidth, angle=-10]{pdfbox/HeadConfiguration}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item \textcolor{red}{Ion saturation current}
      \item \textcolor{blue}{Floating potential}
        \item \textcolor{green}{Swept probe for T$_e$ and $n_e$}
        \item Intershot analysis for blob-size, autocorrelation
      \end{itemize}
    \end{column}
  \end{columns}

\end{frame}
\end{document}

### 2017-04-25 Codes/python/aug/augFilaments.py
augFilaments class implemented but not yet finished

@@ -2,6 +2,9 @@ import timeseries
 import dd
 import eqtools
 import numpy as np
+import matplotlib as mpl
+import copy
+
 
 class Filaments(object):
     """
@@ -12,16 +15,27 @@ class Filaments(object):
     ----------
     Shot : :obj: `int`
         Shot number
+    Xprobe : :obj: `float`
+        Probe starting point decided on a shot to shot basis during
+        the radial scan
     Probe: :obj: `string`
         String indicating the probe head used. Possible values are 
         - `HFF`: for High Heat Flux probe for fluctuation measurements
         - 'IPP': Innsbruck-Padua probe head
+
+    Requirements
+    ------------
+    timeseries : Class in https://github.com/nicolavianello/topic21
+    dd : Class on AUG toks cluster for AUG signal reading
+    eqtools : https://github.com/PSFCPlasmaTools/eqtools
+
     """
 
-    def __init__(self, shot, Probe='HFF'):
+    def __init__(self, shot, Probe='HFF', Xprobe=None):
         self.shot = shot
         # load the equilibria
         self.Eq = eqtools.AUGDDData(self.shot)
+        self.Xprobe = Xprobe
         # open the shot file
         self.Probe = Probe
         if self.Probe == 'HFF':
@@ -36,27 +50,27 @@ class Filaments(object):
         each of the probe tip of the HHF probe
         """
         self.Zmem = 312
-        self.Xprobe = None
-        RZgrid = {'m01':{'r':10, 'z':16.5},
-                  'm02':{'r':3.5, 'z':16.5},
-                  'm03':{'r':-3.5, 'z':16.5}, 
-                  'm04':{'r':-10, 'z':16.5},
-                  'm05':{'r':10, 'z':5.5},
-                  'm06':{'r':3.5, 'z':5.5},
-                  'm07':{'r':-3.5, 'z':5.5},
-                  'm08':{'r':-10, 'z':5.5},
-                  'm09':{'r':10, 'z':-5.5},
-                  'm10':{'r':3.5, 'z':-5.5},
-                  'm11':{'r':-3.5, 'z':-5.5},
-                  'm12':{'r':-10, 'z':-5.5}, 
-                  'm13':{'r':10, 'z':-16.5},
-                  'm14':{'r':3.5, 'z':-16.5},
-                  'm15':{'r':-3.5, 'z':-16.5},
[…]

### 2017-04-27 Experiments/AUG/analysis/python/scriptAnalysisShot.py
small script for quick analysis after shot

@@ -1,0 +1,130 @@
+# script in order to compare heating fueling and equilibria
+# for shot at different current/bt/q95 for the proper scan
+from __future__ import print_function
+import numpy as np
+import sys
+import dd
+import itertools
+import matplotlib as mpl
+from scipy.interpolate import UnivariateSpline
+mpl.rcParams['font.family'] = 'sans-serif'
+mpl.rc("font", size=18)
+mpl.rc('font',**{'family':'sans-serif','sans-serif':['Tahoma']})
+shotList = (34103, 34102, 34104)
+currentL = (0.6, 0.8, 0.99)
+colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
+tList = (1.18, 2.6, 3.43)
+fig = mpl.pylab.figure(figsize=(16, 12))
+fig.subplots_adjust(hspace=0.25)
+ax1 = mpl.pylab.subplot2grid((2, 3), (0, 0), colspan=3)
+ax2 = mpl.pylab.subplot2grid((2, 3), (1, 0))
+ax3 = mpl.pylab.subplot2grid((2, 3), (1, 1))
+ax4 = mpl.pylab.subplot2grid((2, 3), (1, 2))
+axL = (ax2, ax3, ax4)
+
+for shot, ip, cc, i, _ax in itertools.izip(
+    shotList, currentL, colorLS, range(len(shotList)), axL):
+    # this is the line average density
+    diag = dd.shotfile('TOT', shot)
+    neAvg = diag('H-1/(2a)')
+    diag.close()
+    ax1.plot(neAvg.time, neAvg.data/1e20, '-', color=cc, lw=2,
+             label = r'Shot # %5i' % shot +' I$_p$ = %2.1f' % ip +' MA')
+    ax1.set_ylim([0, 1])
+    ax1.set_xlim([0, 4.5])
+    for t, col in zip(tList, colorL):
+        ax1.axvspan(t-0.02, t+0.02, ec='none', fc=col, alpha=0.5)
+    # load the Li-Beam profiles
+    try:
+        LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
+    except:
+        LiBD = dd.shotfile('LIN', shot, experiment='LIBE')
+    neLB = LiBD('ne').data
+    neLBtime = LiBD('ne').time
+    rhoP = LiBD('ne').area
+    LiBD.close()
[…]

### 2017-04-27 Experiments/AUG/analysis/python/scriptAnalysisShot.py
Included a new figure for summary

@@ -10,121 +10,164 @@ from scipy.interpolate import UnivariateSpline
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=18)
 mpl.rc('font',**{'family':'sans-serif','sans-serif':['Tahoma']})
-shotList = (34103, 34102, 34104)
-currentL = (0.6, 0.8, 0.99)
-colorL = ('#82A17E', '#1E4682', '#DD6D3D')
-colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
-tList = (1.18, 2.6, 3.43)
-fig = mpl.pylab.figure(figsize=(16, 12))
-fig.subplots_adjust(hspace=0.25)
-ax1 = mpl.pylab.subplot2grid((2, 3), (0, 0), colspan=3)
-ax2 = mpl.pylab.subplot2grid((2, 3), (1, 0))
-ax3 = mpl.pylab.subplot2grid((2, 3), (1, 1))
-ax4 = mpl.pylab.subplot2grid((2, 3), (1, 2))
-axL = (ax2, ax3, ax4)
 
-for shot, ip, cc, i, _ax in itertools.izip(
-    shotList, currentL, colorLS, range(len(shotList)), axL):
-    # this is the line average density
-    diag = dd.shotfile('TOT', shot)
-    neAvg = diag('H-1/(2a)')
-    diag.close()
-    ax1.plot(neAvg.time, neAvg.data/1e20, '-', color=cc, lw=2,
-             label = r'Shot # %5i' % shot +' I$_p$ = %2.1f' % ip +' MA')
-    ax1.set_ylim([0, 1])
-    ax1.set_xlim([0, 4.5])
-    for t, col in zip(tList, colorL):
-        ax1.axvspan(t-0.02, t+0.02, ec='none', fc=col, alpha=0.5)
-    # load the Li-Beam profiles
-    try:
-        LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
-    except:
-        LiBD = dd.shotfile('LIN', shot, experiment='LIBE')
-    neLB = LiBD('ne').data
-    neLBtime = LiBD('ne').time
-    rhoP = LiBD('ne').area
-    LiBD.close()
-    rhoFake = np.linspace(0.9, 1.11, 200)
-    for t, col in zip(tList, colorL):
-        _idx = np.where((neLBtime >= t-0.02) & (neLBtime <= t+0.02))[0]
[…]

### 2017-04-27 Codes/python/aug/augFilaments.py
added the pdf for Wmhd vs ne

@@ -4,7 +4,7 @@ import eqtools
 import numpy as np
 import matplotlib as mpl
 import copy
-
+from scipy.signal import savgol_filter
 
 class Filaments(object):
     """
@@ -34,7 +34,10 @@ class Filaments(object):
     def __init__(self, shot, Probe='HFF', Xprobe=None):
         self.shot = shot
         # load the equilibria
-        self.Eq = eqtools.AUGDDData(self.shot)
+        try:
+            self.Eq = eqtools.AUGDDData(self.shot)
+        else:
+            print('Equilibrium not loaded')
         self.Xprobe = Xprobe
         # open the shot file
         self.Probe = Probe
@@ -160,7 +163,8 @@ class Filaments(object):
             else:
                 col='black'
 
-            tip = mpl.pyplot.Circle((self.RZgrid[probe]['x'], self.RZgrid[probe]['z']-self.Zmem), 2, fc=col)
+            tip = mpl.pyplot.Circle((self.RZgrid[probe]['x'],
+                                     self.RZgrid[probe]['z']-self.Zmem), 2, fc=col)
             ax.add_artist(tip)
             ax.text(self.RZgrid[probe]['x']-10, self.RZgrid[probe]['z']-2-self.Zmem, probe,
                     fontsize=8)
@@ -225,6 +229,10 @@ class Filaments(object):
 
         # firs of all limit the isAt and vfFloat to the desired time interval
         isSignal, vfSignal = self._defineTime(trange=trange)
+        if interELM:
+            self._interElmMask = self._interElm()
+
+
         self.blockmin=block[0]
         self.blockmax=block[1]
         if Probe is not self.isName + self.vfName:
@@ -239,11 +247,12 @@ class Filaments(object):
 
         if Probe[:4] == 'Isat':
             # for the ion saturation current
-            # we need to mask for the
-            # 
-            _idx = ((isSignal[Probe]['data'] > self.blockmin) &
+            # we need to mask for the arcless system
+            # and propagate the mask for 
+            self._idx = ((isSignal[Probe]['data'] > self.blockmin) &
                     (isSignal[Probe]['data'] < self.blockmax))
-            dt  = (isSignal[Probe]['t'].max()-isSignal[Probe]['t'].min())/(isSignal[Probe]['t'].size-1)
+            dt  = (isSignal[Probe]['t'].max()-isSignal[Probe]['t'].min())/(
+                isSignal[Probe]['t'].size-1)
             # we need to generate a dummy time basis
[…]

### 2017-04-27 Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -1,6 +1,6 @@
 # script in order to compare heating fueling and equilibria
 # for shot at different current/bt/q95 for the proper scan
-from __future__ import print_function
+#from __future__ import print_function
 import numpy as np
 import sys
 import dd
@@ -148,8 +148,9 @@ while loop:
 
     elif selection == 3:
         shotList = (34108, 34115)
-        fig, ax = mpl.pylab.subplots(figsize=(8, 14), nrows=2, ncols=1, sharex=True)
-        for shot, i in zip(shotlist, range(len(shotList))):
+        fig, ax = mpl.pylab.subplots(figsize=(8, 10),
+                                     nrows=2, ncols=1, sharex=True)
+        for shot, i in zip(shotList, range(len(shotList))):
             FPG = dd.shotfile('FPG', shot)
             Wmhd = FPG('Wmhd')
             FPG.close()
@@ -159,12 +160,15 @@ while loop:
             # interpolate h5 on the same time basis of Wmh
             S = UnivariateSpline(h5.time, h5.data/1e19, s=0)
             _id=np.where(((Wmhd.time >= 3) & (Wmhd.time <= 6.3)))[0]
-            ax[i].plot(S(Wmhd.time[_id]), Wmhd[_id]/1e5)
+            ax[i].plot(S(Wmhd.time[_id]), Wmhd.data[_id]/1e5)
+            ax[i].text(0.7, 0.9, 'Shot # %5i' %shot,
+                       transform=ax[i].transAxes)
         ax[0].axes.get_xaxis().set_visible(False)
         ax[0].set_ylabel(r'W$_{mhd}[10^5$ J]')
         ax[1].set_ylabel(r'W$_{mhd}[10^5$ J]')
-        ax[1].set_xlabel(r'$\overbar{n_e}$ H-5 [10$^$19$m$^{-3}$]')
-        ax[1].set_xlim([1, 8])
+        ax[1].set_xlabel(r'$\overline{n_e}$ H-5 [10$^{19}$m$^{-3}$]')
+        ax[1].set_xlim([2, 7])
+        
         mpl.pylab.savefig('../pdfbox/DegradedHMode.pdf', bbox_to_inches='tight')
     elif selection == 99:
         loop = False

### 2017-04-27 Experiments/AUG/analysis/python/scriptAnalysisShot.py
changes n degradeHmode plot

@@ -148,9 +148,12 @@ while loop:
 
     elif selection == 3:
         shotList = (34108, 34115)
+        tmaxL=(6.33, 6.26)
         fig, ax = mpl.pylab.subplots(figsize=(8, 10),
                                      nrows=2, ncols=1, sharex=True)
-        for shot, i in zip(shotList, range(len(shotList))):
+        for shot, i, tm in zip(shotList,
+                               range(len(shotList)),
+                               tmaxL):
             FPG = dd.shotfile('FPG', shot)
             Wmhd = FPG('Wmhd')
             FPG.close()
@@ -159,7 +162,7 @@ while loop:
             dcn.close
             # interpolate h5 on the same time basis of Wmh
             S = UnivariateSpline(h5.time, h5.data/1e19, s=0)
-            _id=np.where(((Wmhd.time >= 3) & (Wmhd.time <= 6.3)))[0]
+            _id=np.where(((Wmhd.time >= 3) & (Wmhd.time <= tm)))[0]
             ax[i].plot(S(Wmhd.time[_id]), Wmhd.data[_id]/1e5)
             ax[i].text(0.7, 0.9, 'Shot # %5i' %shot,
                        transform=ax[i].transAxes)

### 2017-04-28 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the radiation from degraded H-Mode figure which is not satisfying"

@@ -7,6 +7,7 @@ import dd
 import itertools
 import matplotlib as mpl
 from scipy.interpolate import UnivariateSpline
+import pandas as pd
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=18)
 mpl.rc('font',**{'family':'sans-serif','sans-serif':['Tahoma']})
@@ -16,6 +17,7 @@ def print_menu():
     print "1. Li-Beam density profile Ip scan constant q95"
     print "2. Li-Beam density profile Ip scan constant Bt"
     print "3. Degraded H-Mode Wmhd vs Edge density"
+    print "4. Radiation profiles "
     print "99: End"
     print 67 * "-"
 loop = True
@@ -171,8 +173,41 @@ while loop:
         ax[1].set_ylabel(r'W$_{mhd}[10^5$ J]')
         ax[1].set_xlabel(r'$\overline{n_e}$ H-5 [10$^{19}$m$^{-3}$]')
         ax[1].set_xlim([2, 7])
-        
         mpl.pylab.savefig('../pdfbox/DegradedHMode.pdf', bbox_to_inches='tight')
+    elif selection == 4:
+        shotL = (34108, 34115)
+        diodsL = ['S2L3A00','S2L3A01','S2L3A02','S2L3A03', 
+         'S2L3A12','S2L3A13','S2L3A14','S2L3A15', 
+         'S2L3A08','S2L3A09','S2L3A10','S2L3A11', 
+         'S2L3A04','S2L3A05','S2L3A06','S2L3A07']
+        fig, ax = mpl.pylab.subplots(figsize=(8, 12),
+                                     nrows=2, ncols=1)
+        for shot, _is in zip(shotL, range(len(shotL))):
+            Xvs = dd.shotfile('XVS', shot)
+            t = Xvs(diodsL[0]).time
+            nsamp = t.size
+            diods = np.zeros((len(diodsL), nsamp))
+            for d, i in zip(diodsL, range(len(diodsL))):
+                _dummy = Xvs(d).data-Xvs(d).data[1000:50000].mean()
+                diods[i, :] = pd.rolling_mean(_dummy, 5000)
+                del _dummy
+            # now create the appropriate image
+            # limit to a smaller time intervals since
+            # we only need the end
+            _idx = np.where((t>= 5.5) & (t<= 6.3))[0]
+            ax[_is].imshow(diods[:, _idx],
+                      origin='lower', aspect='auto',
[…]

### 2017-04-28 Meetings/AUGrelated/summaryWeek17_280417.tex
Slides for summary of 28 of April

--- 2017-04-25 Meetings/AUGrelated/preparation_240417.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=KoM,venue=Remote, date=03/13/2017, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=KoM,venue=Remote, date=28/04/2017, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Topic 21: AUG experiment}
-\date{24 April 2017}
+\title{Topic 21: AUG experiment Week 17 Summary}
+\date{28 April 2017}
 \author[Topic 21 Scientific Team]{Topic 21 Scientific Team}
@@
 
+\begin{frame}{Current scan at constant q$_95$}
+  \Fontvi
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantq95_density}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item Succesfull plasma current scan at constant
+          q$_{95}$ (\# 34102,  34103, 34104).
+        \item Actually at higher current $\overline{n}_e$ too
+          high?
+        \item It is true the flattening occurs earlier in density at
+          lower current?
+      \end{itemize}
+    \end{column}
+  \end{columns}
+
+\end{frame}
+
+\begin{frame}{Current scan at constant q$_95$}
+  \Fontvi
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_density}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item At constant B$_t$ the flattening is less robust? Compare
+          for example higher current at same density
+      \end{itemize}
+    \end{column}
+  \end{columns}
+\end{frame}
+
 \begin{frame}{H-Mode}
@@
 
-\begin{frame}{Required diagnostic and analysis}
+\begin{frame}{H-Mode}
+  \Fontvi
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/DegradedHModeMarked}
+    \end{column}
+    \begin{column}{0.4\textwidth}
       \begin{itemize}
-    \item[$\boxtimes$] Midplane Manipulator
-    \item[$\boxtimes$] Li-Beam profiles (inter-ELMs one in the H-Mode
-      shots) and fluctuations
-    \item[$\boxtimes$] RFA \#2
-    \item[$\boxtimes$] Divertor probes. Evaluation inter-shot of
-      profiles and rollover density. Divertor collisionality
-    \item[$\boxtimes$] Neutral profiles
-    \item[$\square$] Infrared for probe head monitoring
-    \item[$\boxtimes$] Reflectometer including the multi-channel one
-      for the operation at 1.9 T
-    \item[$\square$] Bolometer/AXUV in the divertor region. We need
-      the monitoring of radiation front movement. Can we get inverted
-      and tomography inter shot?
-    \item[$\square$] Gauges and neutral measurement
-    \item[$\boxtimes$] SXR
-    \item[$\boxtimes$] FILD  
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{HFF probe head}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \includegraphics[width=.9\textwidth, angle=-10]{pdfbox/HeadConfiguration}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-      \begin{itemize}
-      \item \textcolor{red}{Ion saturation current}
-      \item \textcolor{blue}{Floating potential}
-        \item \textcolor{green}{Swept probe for T$_e$ and $n_e$}
-        \item Intershot analysis for blob-size, autocorrelation
+        \item 3 Shots obtained (1 not in our budget?) \# 34107
+          (3.4MW), 34108 (5.4MW),
+          34115(5.4MW)
+        \item The last two shots encountered at the end a phase of
+          degraded H-Mode.
+        \item Reducing the N seeding in \# 34115 allows to skip part
+          of the phases. Can we try to reduce further? \alert{Keep in
+            mind we need to readjust all considering the lack of cryopumps}
       \end{itemize}
@@
   \end{columns}
+\end{frame}
 
+\begin{frame}{Analysis to be done: brainstorming}
+  \begin{itemize}
+    \item Blob size, velocity, collisionality scaling
+      (D. Carralero). Proper calculaton of L$_{\parallel}$ (N. Vianello)
+    \item Limiter probe analysis (S. Costea)
+    \item Profile and$\lambda_n$ evolution also in inter-ELM phases Li-Beam
+      (F. Laggner)
+    \item Reflectometry. Profile evolution and Fluctuations (IST)
+    \item Fast ions (K. McClements and J. Galdon-Quiroga)
+    \item Divertor evolution and rollover time (W. Zhang)
+    \item Radiation (M. Bernert and N.Vianello)
+    \item Further statistical analysis (structure function, increments
+      PDF scaling) (M.Spolaore)
+    \item Others??
+  \end{itemize}
 \end{frame}

### 2017-05-05 Codes/python/aug/augFilaments.py
various figures for Monday meeting presentation

@@ -36,7 +36,7 @@ class Filaments(object):
         # load the equilibria
         try:
             self.Eq = eqtools.AUGDDData(self.shot)
-        else:
+        except:
             print('Equilibrium not loaded')
         self.Xprobe = Xprobe
         # open the shot file
@@ -235,7 +235,7 @@ class Filaments(object):
 
         self.blockmin=block[0]
         self.blockmax=block[1]
-        if Probe is not self.isName + self.vfName:
+        if Probe not in self.isName + self.vfName:
             print('Available Ion saturation current signals are')
             for p in self.isName:
                 print p
@@ -254,9 +254,9 @@ class Filaments(object):
             dt  = (isSignal[Probe]['t'].max()-isSignal[Probe]['t'].min())/(
                 isSignal[Probe]['t'].size-1)
             # we need to generate a dummy time basis
-            tDummy = np.arange(np.count_nonzero(_idx))*dt + trange[0]
+            tDummy = np.arange(np.count_nonzero(self._idx))*dt + trange[0]
             
-            self.blob = timeseries.Timeseries(isSignal[Probe]['data'][_idx], tDummy)
+            self.blob = timeseries.Timeseries(isSignal[Probe]['data'][self._idx], tDummy)
             self.refSignal = Probe
         else:
             self.blob = timeseries.Timeseries(vfSignal[Probe]['data'], isSignal[Probe]['t'])

### 2017-05-05 Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -7,17 +7,35 @@ import dd
 import itertools
 import matplotlib as mpl
 from scipy.interpolate import UnivariateSpline
+from scipy.signal import savgol_filter
+from scipy.signal import find_peaks_cwt
 import pandas as pd
+sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/submodules/pycwt/')
+sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/')
+sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/aug/')
+sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/signalprocessing/')
+import augFilaments
+import neutrals
+import peakdetect
+from matplotlib.colors import LogNorm
 mpl.rcParams['font.family'] = 'sans-serif'
-mpl.rc("font", size=18)
+mpl.rc("font", size=22)
 mpl.rc('font',**{'family':'sans-serif','sans-serif':['Tahoma']})
 
 def print_menu():
     print 30 * "-", "MENU", 30 * "-"
     print "1. Li-Beam density profile Ip scan constant q95"
     print "2. Li-Beam density profile Ip scan constant Bt"
-    print "3. Degraded H-Mode Wmhd vs Edge density"
-    print "4. Radiation profiles "
+    print "3. General figure Ip scan constant q95"
+    print "4. General figure Ip scan constant Bt"
+    print "5. H-Mode general figure during the scan"
+    print "6. H-Mode comparison with respect to reference"
+    print "7. Edge ne image vs Time/rho for constant q95"
+    print "8. Edge ne image vs Time/rho for constant Bt"
+    print "9. Auto-correlation time vs Ip"
+    print "10. Degraded H-Mode Wmhd vs Edge density"
+    print "11. Radiation profiles "
+    print "12. ELM frequency vs H-5 for H-mode shots"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -26,8 +44,6 @@ while loop:
     print_menu()
     selection = input("Enter your choice [1-99] ")
     if selection == 1:
-
-
 
         shotList = (34103, 34102, 34104)
         currentL = (0.6, 0.8, 0.99)
@@ -147,8 +163,446 @@ while loop:
         ax2.set_ylabel(r'n$_e$/n$_e \rho_p = 1)$')
[…]

### 2017-05-05 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added further figures for monday morning meeting

@@ -558,14 +558,22 @@ while loop:
         colorL = ('#C90015', '#7B0Ce7', '#F0CA37')
         fig, ax = mpl.pylab.subplots(figsize=(14, 14), nrows=2, ncols=2)
         for shot, ip, _col in zip(shotQ95L, currentL, colorL):
+
             Probe = augFilaments.Filaments(shot)
             if shot == 34103:
-                trange = [3.5, 3.6]
+                trange = [3.48, 3.53]
             else:
                 trange = [3.7, 3.8]
+            dcn = dd.shotfile('DCN', shot)
+            h5 = dcn('H-5')           
+            en = h5.data[np.where(
+                    ((h5.time >= trange[0]) &
+                     (h5.time <= trange[1])))[0]].mean()/1e19
+            dcn.close()
             Probe.blobAnalysis(Probe='Isat_m06', trange=trange, block=[0.015, 0.5])
             h, b = Probe.blob.pdf(bins='freedman', density=True, normed=True)
-            ax[0, 0].plot((b[1:]+b[:-1])/2, h, color=_col, lw=3, label=r'I$_p$=%1.2f' % ip)
+            ax[0, 0].plot((b[1:]+b[:-1])/2, h, color=_col, lw=3, label=r'I$_p$=%1.2f' % ip +
+                          r' $\overline{n}_e$ = %2.1f' % en)
 
             ax[1, 0].plot(ip, Probe.blob.act*1e6, 's', color=_col, ms=15)
 
@@ -574,8 +582,9 @@ while loop:
         ax[0, 0].set_title(r'Constant q$_{95}$')
         ax[1, 0].set_xlabel(r'I$_p$ [MA]')
         ax[1, 0].set_ylabel(r'$\tau_{ac} [\mu$s]')
-        ax[1, 0].set_ylim([20, 150])
+        ax[1, 0].set_ylim([5, 120])
         ax[1, 0].set_xlim([0.5, 1.1])
+        ax[0, 0].legend(loc='best', numpoints=1, frameon=False)
         # repeat the same for constant Bt
         shotBtL = (34105, 34102, 34106)
         currentL = (0.6, 0.8, 0.99)
@@ -586,9 +595,16 @@ while loop:
                 trange = [3.1, 3.2]
             else:
                 trange = [3.7, 3.8]
+            dcn = dd.shotfile('DCN', shot)
+            h5 = dcn('H-5')
[…]

### 2017-05-05 Meetings/AUGrelated/mondaymorning_080517.tex
added slides for AUG

\documentclass[10pt, compress]{beamer}
\usetheme[conference=AUG Monday,venue=Remote, date=08/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: AUG experiment Week 17 Summary}
\date{08 May 2017}
\author[Topic 21 Scientific Team]{Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \begin{center}
bla bla bla
  \end{center}
\end{frame}
\begin{frame}{Objective of Week 17 campaign}
  \begin{itemize}[<+-|alert@+>]
    \item Check shoulder formation and filamentary transport behavior
      at different current keeping $q_{95}$ constant in L-Mode
    \item Check shoulder formation and filamentary transport behavior
      at different current keeping $B_{t}$ constant in L-Mode
    \item Find suitable H-Mode scenario at \emph{high power}
      (compatible with probe operation) for shoulder behavior and
      filamentary transport studies in H-Mode
  \end{itemize}    
\end{frame}
\begin{frame}{L-Mode: Current scan at constant $q_{95}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \centering{\includegraphics<1>[height=\textheight]{pdfbox/30269Shape}}
    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantq95}}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{itemize}
      \item Reference shot with \textbf{EOC} Shape, 0.8MA, B$_{\phi}$ = -2.5 T, 0.5MW NBI heating,
        fueling in order to keep heating approximately constant during
        the current scan
      \item<2-> The fueling has been reduced at lower current for not
        encountering disruption too early
      \item<3-> Up to 3 seconds 0.6 and 0.8 discharge exibits close
        edge and core density as well as neutral pressure from gauges
        under the dome
      \item<4> In all the cases the profiles evolve and tends to
        become flatter. Preliminary indication suggest this occurs at
        similar $\Lambda_{div}$
    \end{itemize}

  \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode: Current scan at constant $B_{t}$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \centering{\includegraphics<1-2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantBt}}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{itemize}
      \item<1-> The fueling has been reduced at lower current for not
        encountering disruption too early
      \item<2-> Up to 3 seconds 0.6 and 0.8 MA discharges exibits close
        edge and core density as well as neutral pressure from gauges
        under the dome
      \item<3> In all the cases the profiles evolve and tends to
        become flatter. Work in progress to evaluate development as a
        function of divertor collisionality $\Lambda_{div}$
    \end{itemize}

  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Fluctuations}
  \begin{columns}
\begin{column}{0.5\textwidth}
    \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/ScalingAutoCorrelation}
  \end{column}
\begin{column}{0.5\textwidth}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{H-Mode}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot34107_GeneralHmod}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot34108_GeneralHmod}}    
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/DegradedHModeShot34108}}    
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot34115_GeneralHmod}}    
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/DegradedHModeShot34115}}    
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot33478_34115}}    
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{itemize}
      \item<1-> \textbf{EOC} shape, initially with 2MW NBI + 1.4MW ECRH
        density ramp without N seeding
      \item<2-> We increase the NBI power up to 4MW with the same ECRH
        adding N in feedforward
      \item<3-> We end up in a degraded H-Mode with all the 4
        phases. Fluctuations from MEM available in all the phases
      \item<4-> We reduce the N dosing finding a proper scenario
        \alert{but without cryopumps}
      \item<5-> In this cases we still encounters a degraded H-Mode but
        without all the phases
      \item<6-> With respect to the reference we achieve higher power
        and higher neutral pressure in the divertor. We will need to
        adjust once the cryopump will operate in the next session 
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Fast particle accelleration}
  \Fontvi
  \begin{columns}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/KenAnalysis} \\
      \textcolor{red}{K. McClements \& J. Galdon-Quiroga}
    \end{column}
    \begin{column}{0.6\textwidth}
    \begin{itemize}
\item L-mode shots: no evidence of electron or ion acceleration during flat-top, but TAE excitation (top) \&
  neutron time traces during current ramp-up in three shots suggest bulk ion acceleration
\item H-mode shots: many examples found of SXR spikes from plasma edge at start of ELMs $\rightarrow$ electron acceleration),
  although enhancements are less dramatic than in earlier H-mode pulses with lower pedestal $\nu^{*}$ (lower plot)
\item ELMs also linked to enhanced fast ion losses, as in previous H-mode pulses –
  not yet clear whether beam ions are accelerated during ELMs, but fast ion loss detector settings will be optimised in remaining pulses of this experiment
\end{itemize}
\end{column}
\end{columns}
\end{frame}

\end{document}

### 2017-05-07 Meetings/AUGrelated/mondaymorning_080517.tex
Last version of Monday morning 08.05 Meeting

@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Topic 21: AUG experiment Week 17 Summary}
+\title{{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }}
 \date{08 May 2017}
-\author[Topic 21 Scientific Team]{Topic 21 Scientific Team}
+\author[Topic 21 Scientific Team]{N. Vianello for the Topic 21 Scientific Team}
 \begin{document}
@@
   \begin{center}
-bla bla bla
+N. Vianello, D. Carralero, Z. Wei, J. Madsen, K. McClements,
+M. Agostini, M.Spolaore, D. Aguiam, E. Wolfrum, J. Vicente,
+L. Florian, E. Seliunin, J. Galdon-Quiroga, C. Ionita, S. Costea ...
   \end{center}
@@
 \begin{columns}
-  \begin{column}{0.5\textwidth}
+  \begin{column}{0.65\textwidth}
     \centering{\includegraphics<1>[height=\textheight]{pdfbox/30269Shape}}
     \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantq95}}
+    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/LambdaDivVsTime}}
+    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantq95}}
   \end{column}
-  \begin{column}{0.5\textwidth}
+  \begin{column}{0.35\textwidth}
     \begin{itemize}
@@
         under the dome
-      \item<4> In all the cases the profiles evolve and tends to
+      \item<4-> During the discharge complete scan of $\Lambda_{div}$
+        from well below to well above 1.
+      \item<5> In all the cases the profiles evolve and tends to
         become flatter. Preliminary indication suggest this occurs at
@@
 \begin{columns}
-  \begin{column}{0.5\textwidth}
+  \begin{column}{0.65\textwidth}
     \centering{\includegraphics<1-2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
@@
   \end{column}
-  \begin{column}{0.5\textwidth}
+  \begin{column}{0.35\textwidth}
     \begin{itemize}

### 2017-05-09 Codes/python/general/timeseries.py
Debug of timeseries now working with latest version of pycwt and working version of waitingTimeFit class with two different method

@@ -7,6 +7,7 @@ import scipy
 import pycwt as wav
 import astropy.stats as Astats
 from scipy.interpolate import UnivariateSpline
+import copy
 
 
 class Timeseries(object):
@@ -40,8 +41,8 @@ class Timeseries(object):
 
     def __init__(self, signal, time):
 
-        self.sig = signal
-        self.time = time
+        self.sig = copy.deepcopy(signal)
+        self.time = copy.deepcopy(time)
         self.dt = (self.time.max() - self.time.min()) / (self.time.size - 1)
         self.nsamp = self.time.size
         self.signorm = (self.sig - self.sig.mean()) / self.sig.std()
@@ -218,6 +219,7 @@ class Timeseries(object):
             nw=None,
             detrend=True,
             normalize=False,
+            thresh=None,
             **kwargs):
         """
         Conditional Average Sampling
@@ -271,17 +273,17 @@ class Timeseries(object):
             self.__locationindex = (maxima == 1)
             self.__allmaxima = allmax
             if nw is None:
-                nw = np.round(1. / self.freq / self.dt)
+                nw = np.int(np.round(2. / self.freq / self.dt))
             if nw % 2 == 0:
                 iwin = nw / 2
                 nw += 1
             else:
                 iwin = (nw - 1) / 2
-
+            iwin = np.int(iwin)
             maxima[0: iwin - 1] = 0
-            maxima[- iwin:] = 0
+            maxima[-iwin:] = 0
             print 'Number of structures mediated ' + str(maxima.sum())
-            csTot = np.ones((nw, maxima.sum()))
+            csTot = np.ones((int(nw), np.sum(maxima, dtype='int')))
             d_ev = np.asarray(np.where(maxima >= 1))
             for i in range(d_ev.size):
                 if detrend is True:
@@ -304,22 +306,24 @@ class Timeseries(object):
                 csTot[:, i] = _dummy
 
         else:
-            thresh = kwargs.get('thresh', np.sqrt(self.variance) * 2.5)
+            if thresh is None:
+                thresh = 3*np.sqrt(self.variance)+self.mean
             if nw is None:
                 print('Window length not set assumed 501 points')
                 nw = 501
             if nw % 2 == 0:
                 nw += 1
             Nbursts, ratio, av_width, windows = self.identify_bursts(thresh)
-            csTot = np.ones((nw, len(windows)))
+            csTot = np.ones((nw, Nbursts))
             inds = []
[…]

### 2017-05-10 Codes/python/general/multifractal.py
first prototype of multifractal

@@ -1,75 +1,227 @@
-def castaing(self, x, s0, l, sk, am):
+import lmfit
+import numpy as np
+import pycwt as wav
+import scipy
+import astropy.stats as Astats
+
+
+class Multifractal(object):
+    """
+    Class for multifractal and intermittency analysis
+
+    Attributes
+    ----------
+    fr : Float
+        Fourier frequency used for the analysis
+    scale : Float
+        Time scale corresponding to the given Fourier Frequency
+        and computed accordingly to the chosen mother wavelet
+    dt : Float
+        Time sampling
+    Fs : float
+        Frequency sampling
+    mother : str
+        String indicating the type of wavelet used for the analysis
+
+    Dependences
+    -----------
+    lmfit http://lmfit.github.io/lmfit-py/index.html
+    pycwt
+    astropy
+    """
+
+    def __init__(self, signal, time, frequency=100e3, wavelet='Mexican'):
+
         """
-        Define the castaing - like function to fit the Probability
-        density function of normalized fluctuations.  The function is intoduced in
-        B. Castaing et ak, Physica D: Nonlinear Phenomena 46, 177 (1990) and further developed in
-        order to take into account possible asymmetric function in
-        L. Sorriso-Valvo, R. Marino, L. Lijoi, S. Perri, and V. Carbone, Astrophys J 807, 86 (2015).
 
-        P(\delta v) =  am / \sqrt(2\pi)\int G_{\lambda}(\sigma)\exp( - \delta v^2 / 2\sigma^2) * (1 +
-        a_s\frac{dv / sigma}{np.sqrt{1 + dv^2 / sigma^2}})d\sigma / sigma
-        G_{\lambda}(\sigma) =  \frac{1}{\sqrt{2}\lambda}\exp( - \ln^2(\sigma / sigma_0) / 2\lambda)
-
-        Parameters:
-           x  =  these are the increments which represents the bins of the PDF of the increments
-           s0 =  2.  Is \sigma_0
-           l  =  \lambda
-           sk = skewness
-           am = Amplitude for proper normalization
-        out:  the computed function
+        Parameters
+        ----------
+        signal : ndarray
+            Signal to be analyzed
+        time : ndarray
+            Time basis
+        frequency : Float
+            Fourier frequency for the analysis
+        wavelet : :obj: `str`
+            String indicating the type of wavelet used
+            for the analysis. Default is 'Mexican'
 
         """
-        # we need this for a proper definition of the integral
-        def integrand(sigma, s, lamb, dv, skw):
[…]

### 2017-05-10 Codes/python/general/multifractal.py
autopep8 applied on multifractal

@@ -28,10 +28,14 @@ class Multifractal(object):
     lmfit http://lmfit.github.io/lmfit-py/index.html
     pycwt
     astropy
+
+    To Do
+    -----
+    - Add the stretched function fit
+    - Add the computation of fractal dimension
     """
 
     def __init__(self, signal, time, frequency=100e3, wavelet='Mexican'):
-
         """
 
         Parameters
@@ -63,8 +67,8 @@ class Multifractal(object):
         self.sig = signal.copy()
         self.nsamp = signal.size
         self.time = time.copy()
-        self.dt = (time.max()-time.min())/(self.nsamp-1)
-        self.Fs = 1./self.dt
+        self.dt = (time.max() - time.min()) / (self.nsamp - 1)
+        self.Fs = 1. / self.dt
         self.cwt()
 
     def cwt(self):
@@ -86,11 +90,11 @@ class Multifractal(object):
         """
         try:
             wt, sc, freqs, coi, fft, fftfreqs = wav.cwt(
-                    self.sig, self.dt, 0.25, self.scale, 0, self.mother)
+                self.sig, self.dt, 0.25, self.scale, 0, self.mother)
             self.wt = np.real(np.squeeze(wt))
-            self.wtN = (self.wt-self.wt.mean())/self.wt.std()
+            self.wtN = (self.wt - self.wt.mean()) / self.wt.std()
             return True
-        except:
+        except BaseException:
             return False
 
     def lim(self):
@@ -174,16 +178,16 @@ class Multifractal(object):
         """
 
         hist, bins_e = Astats.histogram(
-                self.wtN, bins=bins, range=xrange,
-                weights=weights, density=True, **kwargs)
-        xpdf = (bins_e[1:]+bins_e[:-1])/2.
+            self.wtN, bins=bins, range=xrange,
+            weights=weights, density=True, **kwargs)
+        xpdf = (bins_e[1:] + bins_e[:-1]) / 2.
         if xrange is None:
-                xrange = [self.wtN.min(), self.wtN.max()]
+            xrange = [self.wtN.min(), self.wtN.max()]
         err = np.sqrt(hist / (
-                np.count_nonzero(
-                        ((self.wtN >=
-                          xrange[0]) &
-                         (self.wtN <= xrange[1]))) * (bins_e[1] - bins_e[0])))
+            np.count_nonzero(
+                ((self.wtN >=
[…]

### 2017-05-11 Meetings/TCVrelated/kom_150517_vianello.tex
started to prepare slides for TCV KOM Meeting

\documentclass[10pt, compress]{beamer}
\usetheme[conference=TCV-Topic21 KoM,venue=Lausanne, date=15/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: TCV experiment KoM}
\date{15 March 2017}
\author[N. Vianello,  V. Naulin]{N . Vianello and V. Naulin}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

\begin{frame}{TCV experiments: boundary condition}
\vspace{-1cm}
\Fontvi
\only<1>{
  \begin{itemize}
  \item 2017 \textbf{objectives} listed after the General Planning Meeting
    \begin{enumerate}
      \item Provide cross-machine \alert{L-Mode} shoulder dependence on
        current both at constant Bt and at constant q$_{95}$
      \item Establish robust scenario for density shoulder profile in
        H-mode and establish dependence on fuelling/neutral
        profiles/divertor condition
      \item Study the role of ELM regimes, neutral compression, and
        particle density in filamentary transport and related shoulder
        formation.
      \item Identify the contribution of collisionality and
        seeding on filamentary transport and related shoulder
        formation.
      \item Determine the effect of filaments and shoulder
        formation on target heat loads in different Hmode plasmas.
    \end{enumerate}
  \item We have a total number of \textbf{\# 23 Shots} split into two
    operational window. Calendar week 24 (12.06-16.06) and Calendar
    week 43 (23.10-27.10)
\end{itemize}
}
\only<2>{
  \begin{itemize}
    \item 15 people listed in the team for TCV experiment
      \begin{description}
        \item[EPFL:] H. De Oliveira, R. Maurizio, B. Labit,
          C. Tsui, K. Verhaegh, H. Reimerdes, C. Theiler
        \item[DTU:] J.J. Rasmussen and V. Naulin
        \item[RFX:] N. Vianello, M. Spolaore, M. Agostini
        \item[OEAW:] B. Schneider, S. Costea, C. Ionita
        \item[CCFE:] F. Militello
        \item[JSI:] J. Kovacic
      \end{description}
    \end{itemize}
  }
\end{frame}
\begin{frame}{Results obtained during TCV15-2.2-3 Experiment}

\end{frame}
% \only<2>{
% We will conclude the \textcolor{ta3chameleon}{L-Mode}
% part in Week 15 where we also would like to include part of the \textcolor{ta3scarletred}{H-Mode}
% scenario development. This would give us an additional week between
% the experiments to address possible issues in particular for the
% H-mode part\\
% \textbf{Week 15} \\
% We choose are reference shot \# 30269 (I$_p$ = 0.8 MA, B$_{\phi}$ = 2.5T, q$_{95}\approx 4.5$)
%   \begin{enumerate}
%     \item \textcolor{ta3chameleon}{Shot at I$_p$=0.6 MA
%       keeping the same toroidal field $B_{\phi}$ = 2.5T as the reference adjust the fueling
%       rate (\emph{Current scan with modification of $q_{95}$})}
%   \item \textcolor{ta3chameleon}{Shot at I$_p$ = 0.6MA
%       reduce the toroidal field B$_{\phi}\approx $2T in order to match q$_{95}\approx 4.5$, 
%       (\emph{Current scan at fixed $q_{95}$}). This would accommodate
%       the diagnostic request of D. Aguiam}
%     \item \textcolor{ta3chameleon}{Density ramp with I$_p$ = 1MA and
%         B$_{\phi}$ = 2.5T}
%     \item \textcolor{ta3chameleon}{Density ramp with I$_{p}$ = 1MA,
%         increasing the toroidal field in order to match q$_{95}\approx
%         4.5$}
%     \end{enumerate}
%   }
%   \only<3>{
%   \textbf{Week 15} \\
%     For the \textcolor{ta3scarletred}{H-Mode} scenario development we start from the best shot found in
%     2016 (\# 33478) and increase the heating power
%     \begin{enumerate}
%       \item \textcolor{ta3scarletred}{Start from shot \# 33478 but
%           with increased heating power (6MW). Adjust fueling rate from
%         reference by increasing by a factor of 30 \%. 1 Plunge of
%         probe head at the end of the discharge still in a safe
%         position and IR monitoring}
%     \item \textcolor{ta3scarletred}{Repeat \# 1 eventually adjusting
%         the fueling rate. Start the N seeding in feedforward starting
%         fro the level found in reference}
%     \item \textcolor{ta3scarletred}{Trade off between \#1 and \#2
%         Fueling/Seeding. Additional plunge of probe at the end of the
%         discharge}
%       \item \textcolor{ta3skyblue}{This scenario would allow the
%           exploitation of particle accelleration (McClements) physics as piggy-back}
%     \end{enumerate}
%   }
%   \only<4>{
%   \textbf{Week 17: This strongly depends on the achievement of H-Mode
%     scenario obtained in Week 15 } \\
%     \begin{enumerate}
%     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in Week 15 1st Radial position of probe}
%     \item \textcolor{ta3scarletred}{Repeat \#1, different probe position}
%     \item \textcolor{ta3scarletred}{Repeat \#1, different probe
%         position}
%     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
%         week 15 and reduced the cryopumps}
%     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
%         week 15 and puff from midplane}
%     \item \textcolor{ta3scarletred}{Contingency}
%     \item \textcolor{ta3scarletred}{Contingency}
%     \end{enumerate}
%   }
%   \only<5>{
%     Among the contingency we propose the following 4 possibilities to
%     be discussed
%     \begin{enumerate}
%     \item \textcolor{ta3chameleon}{Reversing B$_t$ direction and repeat one identical shot (e.g \# 30269) to investigate
%    the role of SOL flows in SOL shoulder formation and filamentary
%    transport}
%     \item \textcolor{ta3chameleon}{DN discharge with similar density ramps as in reference. Possibly the two X-point should
%    sit on the same flux surface}
%    \item \textcolor{ta3scarletred}{Attempt a scenario similar to Topic-06 which will be performed later in time. See for example
%    shot \# 29816 (Presented by T. Eich in the GPM) which is at even
%    higher power (8 MW) or \# 25740
%    which is actually in DN (see proposal from J. Vicente). If we choose for this we could actually compare with the priority 3 of L-Mode
%    contingency}
%  \item \textcolor{ta3scarletred}{Reverse B$_{t}$ operation. In this case the L-H treshold is different and we might end
%      by careful adjusting the power into I-Mode scenario}
%    \item \textcolor{ta3skyblue}{Working at 2T in H-Mode would require
%        additional development}
%    \item \textcolor{ta3skyblue}{Given that the upper divertor is less
%        diagnosed then the lower one we prefer eventually to operate
%        with reverse B$_{\phi}$}

% \end{enumerate}
%   }
% \end{frame}
% \begin{frame}{Required diagnostic and analysis}
%   \begin{itemize}
%     \item[$\boxtimes$] Midplane Manipulator
%     \item[$\square$] Li-Beam. \emph{Are fluctuations and profiles
%         available simultaneously}
%     \item[$\square$] RFA \#2
%     \item[$\square$] Divertor probes
%     \item[$\boxtimes$] Neutral profiles
%     \item[$\square$] Infrared for probe head monitoring. \emph{Are Target
%       infrared measurements available/useful?}
%     \item[$\square$] GPI
%     \item[$\boxtimes$] Reflectometer. \emph{The operation at 2T can be
%       obtained during the q$_{95}$ scan}
%     \item[$\boxtimes$] Fast probes on the limiter
%     \item[$\square$] Bolometer/AXUV in the divertor region
%   \end{itemize}
% \end{frame}

% \begin{frame}{Work to be accomplished before the experiment}
%   \begin{enumerate}
%     \item Check the shape modification during the current/q$_{95}$
%       scan
%     \item Probe conditioning?
%     \item Check the status of the diagnostics including GPI (issue
%       regarding the puffing)
%     \item Methodology ($\Lambda_{div}$ computation and profile)
%       $\lambda_n$ filaments properties etc.  
%     \item Code preparation for analysis and
%       visualization. \emph{GITHUB repository?}
%     \item Optimization of the effort: please provide us a more
%       detailed plan of your analysis in order to limit superposition
%       or work duplication
%   \end{enumerate}
% \end{frame}
\end{document}

### 2017-05-12 Meetings/TCVrelated/kom_150517_vianello.tex
Presentation for TCV KoM meeting of 15 of May

@@
         \item[RFX:] N. Vianello, M. Spolaore, M. Agostini
-        \item[OEAW:] B. Schneider, S. Costea, C. Ionita
+        \item[OEAW:] B. Schneider, S. Costea, R. Schrittwieser
         \item[CCFE:] F. Militello
@@
 \end{frame}
-\begin{frame}{Results obtained during TCV15-2.2-3 Experiment}
+\begin{frame}{Results obtained during MST1 Campaigns 2015-2016}
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+      \includegraphics<1>[width=\textwidth]{pdfbox/KoM150517/Fig0}
+      \includegraphics<2>[width=\textwidth]{pdfbox/KoM150517/Fig1}
+      \includegraphics<3>[width=\textwidth]{pdfbox/KoM150517/Fig2}
+      \includegraphics<4>[width=\textwidth]{pdfbox/KoM150517/Fig4}
+      \includegraphics<5>[width=\textwidth]{pdfbox/KoM150517/Fig5}
+      \includegraphics<6>[width=\textwidth]{pdfbox/KoM150517/Fig6}
+      \includegraphics<7>[height=.8\textheight]{pdfbox/KoM150517/Fig7}
+      \includegraphics<8>[height=.8\textheight]{pdfbox/KoM150517/Fig8}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item<1|only@1> Performed a series of L-Mode shots with
+          density ramp and different poloidal flux expansion to check
+          L$_{\parallel}$ effect
+        \item<2|only@2> Upstream profiles at same densities but
+          different $\Lambda_{div}$ (well above 1 all along the
+          profiles) are similar. Weak effect of parallel connection
+          length modification
+        \item<3|only@3> Density decay length $\lambda_n$ modified
+          strongly with increasing density in the near SOL region
+        \item<4|only@4> Blob size increases with density independently
+          from the Flux expansion
+        \item<5|only@5> In the Far SOL the decay length scales with
+          divertor collisionality but examples with high $\Lambda_n$
+          and steep profile clearly exhists
+        \item<6|only@6> Steep profile clearly seen in the
+          Sheath-connected regime. Unclear if Resistive balloning and
+          resistive X-point blobs behaves differently
+        \item<7|only@7> Change in the Flux expansion does not change
+          detachment density threshold, whereas divertor leg length
+          has a clear impact (\textit{Theiler, NF17 and Reimerdes IAEA
+            2016})
+        \item<8|only@8> Also any differences observed between single
+          and double null. Major modification only induced by density increase
 
+      \end{itemize}
+    \end{column}
+  \end{columns}
 \end{frame}
+
+\begin{frame}{Proposed experimental plan: L-mode}
+  \Fontvi
+  The first shots are needed in order to have comparable scenario
+  between all the machines
+  \begin{itemize}
+    \item Current scan at constant q$_{95}$
+      \begin{enumerate}
+      \item Reference shot is \# 54867, I$_p$=240 kA, q$_{95}$=3.5,
+        B$_t$ = 1.41T with the same density ramp (\alert{Do we need a density ramp? can we
+          go directly at high density as in \# 53516? and repeat the
+          shot at low density?})
+      \item Repeat Shot \# 1 with I$_p$=180 kA (20\% decrease similarly
+        to AUG) with the same q$_{95}$ and adjusting the toroidal field
+      \item Repeat Shot \# 1 with I$_p$=300 kA (20\% increase similarly
+        to AUG) with the same q$_{95}$ and adjusting the toroidal
+        field. \alert{In case this causes a transition into Ohmic H-Mode we
+        might think to perform the shot in reverse B$_t$. This
+        eventually needs additional shots at lower current as
+        well. \emph{Why not operate all the shots in Reverse B$_t$?}}
+      \end{enumerate}
+    \item Current scan at constant B$_t$
+      \begin{enumerate}
+        \setcounter{enumi}{3}
+      \item I$_p$=180 kA,  B$_t$ = 1.41 as in shot \# 1 
+      \item I$_p$=300 kA, B$_t$=1.41 as in shot \# 1
+      \end{enumerate}
+    \end{itemize}      
+  \end{frame}
+
+  \begin{frame}{Proposed experimental plan: L-Mode}
+    \begin{itemize}
+      \item Divertor leg length/L$_{parallel}$ scan
+      \begin{enumerate}
+        \setcounter{enumi}{5}
+      \item Repeat \# 1 at $Z=+23$.
+      \item Repeat \# 1 at $Z=-10$  
+      \end{enumerate}
+      \item This can have issues in terms of probe operation because
+        of shadowing effect. 
+      \item Double Null. Repeat the current scan at constant q$_{95}$ in
+        DN configuration in order to provide suitable comparable
+        scenario with foreseen MAST-U operation
+        \begin{enumerate}
+          \setcounter{enumi}{7}
+          \item Repeat the density ramp of \# 1 in DN configuration
+            I$_p$ = 240kA
+          \item Repeat density ramp of shot \# 2 in DN configuration
+            I$_p$ = 180 kA
+          \item Repeat density ramp of shot \# 2 in DN configuration
+            I$_p$ = 300 kA
+          \end{enumerate}
+        \end{itemize}
+      \end{frame}
+
+      \begin{frame}{Proposed experimental plan: H-Mode}
+        The NBI heated plasma is still a partially uncovered scenario
+        for TCV. We have a good reference shot \# 53352 with a good
+        type-I Elmy regime. We propose to use the 3 shots for proper
+        scenario development
+        \begin{enumerate}
+          \setcounter{enumi}{10}
+          \item Repeat \# 53352 same setting. 1MW NBI power 0.4
+            s starting at 0.8s. At 0.82s start a density ramp keeping
+            the same rate as in \# 1. Power ramp down from 1.2 second
+            in order to check ELMy regime. \alert{We need a good
+              monitoring of divertor condition and modification}
+          \item The second shot will depend on \# 11. We will need to
+            adjust the fueling rate accordingly. Include N seeding
+            \alert{check for appropriate reference from past
+              experiment}
+          \item Repeat \# 12 with best trade off between seeding and fueling
+          \end{enumerate}
+          The hypothesis to reach ECRH high density H-Mode is limited, to my
+          knowledge, to operation in vertically shifted plasma and
+          X3. Can be explored in W23
+        \end{frame}
+
+        \begin{frame}{Diagnostic and open issues}
+          %\Fontvi
+          \begin{itemize}
+          \item Fast Camera
+          \item DBS radial localization
+          \item Neutrals from gauges. D$_{\alpha}$ calibrated camera
+            to be used together with \texttt{KN1D} code
+          \item Fast reciprocating probe. Can it work with radially
+            spaced I$_s$ measurements?
+          \item Do we miss something in L-Mode which is worth to be
+            done?
+          \item Do we have experience of nitrogen seeded NBI heated
+            discharge?
+          \item Do we have other references for high density H-Mode operation?
+          \end{itemize}
+        \end{frame}
+
       % \only<2>{

### 2017-05-26 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added further comparisons for shots

@@ -40,6 +40,9 @@ def print_menu():
     print "14. Compare Neutral compression with reference 2016"
     print "15. Compare divertor/midplane puffing w/o cryopumps"
     print "16. Compare compression with puffing from divertor/midplane w/o cryompumps"
+    print "17. Compare shots same puffing with and wo cryompumps"
+    print "18. Compare shots with/wo cryopumps try to match edge density"
+    print "19. Compare Li-Beam contour profiles"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -918,21 +921,227 @@ while loop:
         shotList = (34276, 34277)
         pufL = ('Div', 'Mid')
         colorList = ('#C90015', '#7B0Ce7')
-        fig, ax = mpl.pylab.subplots(figsize=(8, 5), nrows=1, ncols=1)
+        fig, ax = mpl.pylab.subplots(figsize=(8, 10), nrows=2, ncols=1, sharex=True)
         fig.subplots_adjust(bottom=0.15)
         for shot, col, p in zip(shotList, colorList, pufL):
             Gas = neutrals.Neutrals(shot)
-            ax.plot(Gas.signal['F01']['t'],
+            ax[0].plot(Gas.signal['F01']['t'],
                     Gas.signal['F01']['data']/Gas.signal['F14']['data'],
                     color=col, lw=2, label=r'Shot # %5i' % shot + 'Puff from '+p)
-
-        ax.set_xlabel('t [s]')
-        ax.set_ylabel(r'Compression F01/F14')
-        ax.legend(loc='best', fontsize=14, frameon=False, numpoints=1)
-        ax.set_xlim([0, 8])
+            Msp = dd.shotfile('MSP', shot)
+            Press = 100.*Msp('B25_08Fu').data/(0.0337*np.log10(Msp('B25_08Fu').data*100.)+0.7304)
+            ax[1].plot(Msp('B25_08Fu').time, Press, color=col, lw=2)
+            Msp.close()
+        ax[1].set_xlabel('t [s]')
+        ax[0].set_ylabel(r'Compression F01/F14')
+        ax[0].legend(loc='best', fontsize=14, frameon=False, numpoints=1)
+        ax[0].set_xlim([0, 7])
+        ax[0].axes.get_xaxis().set_visible(False)
+        ax[1].set_ylabel(r'P$_{div}$ [Pa]')
+        ax[1].text(0.1, 0.9, r'100*B25_08Fu/(0.0337*log(B25_08Fu*100) + 0.7304)',
[…]

### 2017-05-26 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added new figure for MondayMorning meeting

@@ -42,7 +42,7 @@ def print_menu():
     print "16. Compare compression with puffing from divertor/midplane w/o cryompumps"
     print "17. Compare shots same puffing with and wo cryompumps"
     print "18. Compare shots with/wo cryopumps try to match edge density"
-    print "19. Compare Li-Beam contour profiles"
+    print "19. Compare Li-Beam contour profiles with/wo crypumps when trying to math edge density"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -1142,6 +1142,66 @@ while loop:
                           str(int(shotList[1]))+'.pdf',
                           bbox_to_inches='tight')
 
+    elif selection == 19:
+        shotList = (34276, 34280)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        colorLS = ('#C90015', '#7B0Ce7')
+        tList = (1.8, 2.4, 4.0)
+        fig = mpl.pylab.figure(figsize=(12, 12))
+        fig.subplots_adjust(hspace=0.25, right=0.86)
+        ax1 = mpl.pylab.subplot2grid((2, 2), (0, 0), colspan=2)
+        ax2 = mpl.pylab.subplot2grid((2, 2), (1, 0))
+        ax3 = mpl.pylab.subplot2grid((2, 2), (1, 1))
+        axL = (ax2, ax3)
+        Cryo = ('No', 'On')
+        for shot, cc, _ax, _cr in itertools.izip(
+            shotList, colorLS, axL, Cryo):
+            # this is the line average density
+            diag = dd.shotfile('TOT', shot)
+            neAvg = diag('H-1/(2a)')
+            diag.close()
+            ax1.plot(neAvg.time, neAvg.data/1e20, '-', color=cc, lw=2,
+                     label = r'Shot # %5i' % shot +' Cryo ' + _cr)
+            ax1.set_ylim([0, 1])
+            ax1.set_xlim([0, 7])
+            for t, col in zip(tList, colorL):
+                ax1.axvspan(t-0.01, t+0.01, ec='none', fc=col, alpha=0.5)
+            # load the Li-Beam profiles
+            LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
+            neLB = LiBD('ne').data
+            neLBtime = LiBD('ne').time
+            rhoP = LiBD('ne').area
+            LiBD.close()
[…]

### 2017-05-26 Experiments/AUG/analysis/python/scriptAnalysisShot.py
new figure comparing Li-Be Divertor/midplane

@@ -43,6 +43,7 @@ def print_menu():
     print "17. Compare shots same puffing with and wo cryompumps"
     print "18. Compare shots with/wo cryopumps try to match edge density"
     print "19. Compare Li-Beam contour profiles with/wo crypumps when trying to math edge density"
+    print "20. Compare Li-Be contour div/midplane puffing"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -1144,6 +1145,67 @@ while loop:
 
     elif selection == 19:
         shotList = (34276, 34280)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        colorLS = ('#C90015', '#7B0Ce7')
+        tList = (1.8, 2.4, 4.0)
+        fig = mpl.pylab.figure(figsize=(12, 12))
+        fig.subplots_adjust(hspace=0.25, right=0.86)
+        ax1 = mpl.pylab.subplot2grid((2, 2), (0, 0), colspan=2)
+        ax2 = mpl.pylab.subplot2grid((2, 2), (1, 0))
+        ax3 = mpl.pylab.subplot2grid((2, 2), (1, 1))
+        axL = (ax2, ax3)
+        Cryo = ('No', 'On')
+        for shot, cc, _ax, _cr in itertools.izip(
+            shotList, colorLS, axL, Cryo):
+            # this is the line average density
+            diag = dd.shotfile('TOT', shot)
+            neAvg = diag('H-1/(2a)')
+            diag.close()
+            ax1.plot(neAvg.time, neAvg.data/1e20, '-', color=cc, lw=2,
+                     label = r'Shot # %5i' % shot +' Cryo ' + _cr)
+            ax1.set_ylim([0, 1])
+            ax1.set_xlim([0, 7])
+            for t, col in zip(tList, colorL):
+                ax1.axvspan(t-0.01, t+0.01, ec='none', fc=col, alpha=0.5)
+            # load the Li-Beam profiles
+            LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
+            neLB = LiBD('ne').data
+            neLBtime = LiBD('ne').time
+            rhoP = LiBD('ne').area
+            LiBD.close()
+            rhoFake = np.linspace(0.98, 1.06, 50)
+            profFake = np.zeros((neLBtime.size, 50))
[…]

### 2017-05-26 Experiments/AUG/analysis/python/scriptAnalysisShot.py
new figure comparing Li-Be Same fueling with/without cryo

@@ -44,6 +44,7 @@ def print_menu():
     print "18. Compare shots with/wo cryopumps try to match edge density"
     print "19. Compare Li-Beam contour profiles with/wo crypumps when trying to math edge density"
     print "20. Compare Li-Be contour div/midplane puffing"
+    print "21. Compare Li-Be contour same fueling with/without cryo"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -1206,6 +1207,67 @@ while loop:
 
     elif selection == 20:
         shotList = (34276, 34277)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        colorLS = ('#C90015', '#7B0Ce7')
+        tList = (1.8, 2.4, 4.0)
+        fig = mpl.pylab.figure(figsize=(12, 12))
+        fig.subplots_adjust(hspace=0.25, right=0.86)
+        ax1 = mpl.pylab.subplot2grid((2, 2), (0, 0), colspan=2)
+        ax2 = mpl.pylab.subplot2grid((2, 2), (1, 0))
+        ax3 = mpl.pylab.subplot2grid((2, 2), (1, 1))
+        axL = (ax2, ax3)
+        Cryo = ('No', 'On')
+        for shot, cc, _ax, _cr in itertools.izip(
+            shotList, colorLS, axL, Cryo):
+            # this is the line average density
+            diag = dd.shotfile('TOT', shot)
+            neAvg = diag('H-1/(2a)')
+            diag.close()
+            ax1.plot(neAvg.time, neAvg.data/1e20, '-', color=cc, lw=2,
+                     label = r'Shot # %5i' % shot +' Cryo ' + _cr)
+            ax1.set_ylim([0, 1])
+            ax1.set_xlim([0, 7])
+            for t, col in zip(tList, colorL):
+                ax1.axvspan(t-0.01, t+0.01, ec='none', fc=col, alpha=0.5)
+            # load the Li-Beam profiles
+            LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
+            neLB = LiBD('ne').data
+            neLBtime = LiBD('ne').time
+            rhoP = LiBD('ne').area
+            LiBD.close()
+            rhoFake = np.linspace(0.98, 1.06, 50)
+            profFake = np.zeros((neLBtime.size, 50))
[…]

### 2017-05-26 Meetings/AUGrelated/mondaymorning_290517.tex
add the monday morning tex file for 29 May

--- 2017-05-07 Meetings/AUGrelated/mondaymorning_080517.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=AUG Monday,venue=Remote, date=08/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=AUG Monday,venue=Remote, date=29/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 \title{{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }}
-\date{08 May 2017}
+\date{29 May 2017}
 \author[Topic 21 Scientific Team]{N. Vianello for the Topic 21 Scientific Team}
@@
 \end{frame}
-\begin{frame}{Objective of Week 17 campaign}
+\begin{frame}{Objective of Week 21 campaign}
   \begin{itemize}[<+-|alert@+>]
-    \item Check shoulder formation and filamentary transport behavior
-      at different current keeping $q_{95}$ constant in L-Mode
-    \item Check shoulder formation and filamentary transport behavior
-      at different current keeping $B_{t}$ constant in L-Mode
-    \item Find suitable H-Mode scenario at \emph{high power}
-      (compatible with probe operation) for shoulder behavior and
-      filamentary transport studies in H-Mode
+    \item Compare divertor/midplane fueling effect on filamentary
+      transport and profiles without cryo-pumps
+    \item Compare profiles with the same fueling with/without cryopums
+    \item Determine an H-Mode with the cryopumps matching similar
+      divertor pressure and SOL profiles
   \end{itemize}    
 \end{frame}
-\begin{frame}{L-Mode: Current scan at constant $q_{95}$}
+\begin{frame}{Compare divertor/midplane fueling}
 \Fontvi
@@
   \begin{column}{0.65\textwidth}
-    \centering{\includegraphics<1>[height=\textheight]{pdfbox/30269Shape}}
-    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/LambdaDivVsTime}}
-    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantq95}}
+    \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
   \end{column}

### 2017-05-26 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to Li-Beam images. Just cosmetiques

@@ -1166,8 +1166,6 @@ while loop:
                      label = r'Shot # %5i' % shot +' Cryo ' + _cr)
             ax1.set_ylim([0, 1])
             ax1.set_xlim([0, 7])
-            for t, col in zip(tList, colorL):
-                ax1.axvspan(t-0.01, t+0.01, ec='none', fc=col, alpha=0.5)
             # load the Li-Beam profiles
             LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
             neLB = LiBD('ne').data
@@ -1227,8 +1225,6 @@ while loop:
                      label = r'Shot # %5i' % shot +' Cryo ' + _cr)
             ax1.set_ylim([0, 1])
             ax1.set_xlim([0, 7])
-            for t, col in zip(tList, colorL):
-                ax1.axvspan(t-0.01, t+0.01, ec='none', fc=col, alpha=0.5)
             # load the Li-Beam profiles
             LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
             neLB = LiBD('ne').data
@@ -1288,8 +1284,6 @@ while loop:
                      label = r'Shot # %5i' % shot +' Cryo ' + _cr)
             ax1.set_ylim([0, 1])
             ax1.set_xlim([0, 7])
-            for t, col in zip(tList, colorL):
-                ax1.axvspan(t-0.01, t+0.01, ec='none', fc=col, alpha=0.5)
             # load the Li-Beam profiles
             LiBD = dd.shotfile('LIN', shot, experiment='AUGD')
             neLB = LiBD('ne').data

### 2017-05-26 Meetings/AUGrelated/mondaymorning_290517.tex
Update to presentation

@@
   \begin{column}{0.65\textwidth}
-    \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}}
   \end{column}
@@
     \begin{itemize}
-      \item Reference shot with \textbf{EOC} Shape, 0.8MA, B$_{\phi}$ = -2.5 T, 0.5MW NBI heating,
-        fueling in order to keep heating approximately constant during
-        the current scan
-      \item<2-> The fueling has been reduced at lower current for not
-        encountering disruption too early
-      \item<3-> Up to 3 seconds 0.6 and 0.8 discharge exibits close
-        edge and core density as well as neutral pressure from gauges
-        under the dome
-      \item<4-> During the discharge complete scan of $\Lambda_{div}$
-        from well below to well above 1.
-      \item<5> In all the cases the profiles evolve and tends to
-        become flatter. Preliminary indication suggest this occurs at
-        similar $\Lambda_{div}$
+      \item Similar puff from the divertor or from the midplane
+        without Cryopumps. The
+        shots are pretty similar also in terms of Divertor pressure
+      \item<2-> Edge density profiles from Li-Beam evolution are
+        pretty similar
     \end{itemize}
@@
 
-\begin{frame}{L-Mode: Current scan at constant $B_{t}$}
+\begin{frame}{Compare Similar fueling with/without cryopumps}
 \Fontvi
@@
   \begin{column}{0.65\textwidth}
-    \centering{\includegraphics<1-2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
-    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfileConstantBt}}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
   \end{column}
@@
     \begin{itemize}
-      \item<1-> The fueling has been reduced at lower current for not
-        encountering disruption too early
-      \item<2-> Up to 3 seconds 0.6 and 0.8 MA discharges exibits close
-        edge and core density as well as neutral pressure from gauges
-        under the dome
-      \item<3> In all the cases the profiles evolve and tends to
-        become flatter. Work in progress to evaluate development as a
-        function of divertor collisionality $\Lambda_{div}$
+      \item<1-> Same fueling but with cryo-pumps. Clearly different in
+        terms of Edge density and Divertor pressure
+      \item<2-> Also with this amount of fueling any instance of SOL
+        saturation observed
     \end{itemize}
@@
 
-\begin{frame}{Fluctuations}
-  \begin{columns}
-\begin{column}{0.5\textwidth}
-    \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/ScalingAutoCorrelation}
-  \end{column}
-\begin{column}{0.5\textwidth}
-\end{column}
-\end{columns}
-\end{frame}
-
-\begin{frame}{H-Mode}
+\begin{frame}{Matching scenarios with cryo-pumps}
 \Fontvi
@@
 \begin{columns}
-  \begin{column}{0.5\textwidth}
-    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot34107_GeneralHmod}}
-    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot34108_GeneralHmod}}    
-    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/DegradedHModeShot34108}}    
-    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot34115_GeneralHmod}}    
-    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/DegradedHModeShot34115}}    
-    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot33478_34115}}    
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34280}}
   \end{column}
-  \begin{column}{0.5\textwidth}
+  \begin{column}{0.35\textwidth}
     \begin{itemize}
-      \item<1-> \textbf{EOC} shape, initially with 2MW NBI + 1.4MW ECRH
-        density ramp without N seeding
-      \item<2-> We increase the NBI power up to 4MW with the same ECRH
-        adding N in feedforward
-      \item<3-> We end up in a degraded H-Mode with all the 4
-        phases. Fluctuations from MEM available in all the phases
-      \item<4-> We reduce the N dosing finding a proper scenario
-        \alert{but without cryopumps}
-      \item<5-> In this cases we still encounters a degraded H-Mode but
-        without all the phases
-      \item<6-> With respect to the reference we achieve higher power
-        and higher neutral pressure in the divertor. We will need to
-        adjust once the cryopump will operate in the next session 
+      \item<1-> To match similar edge density and divertor pressure
+        and to reach the same level of detachment we increase the
+        fueling by almost a factor of 3, increasing also the rate. In
+        addition to that we also increase substantially the N puffing
+      \item<2-> Li-beam profile not yet produced for the same
+        shots. With a lower level of N (no detachment observed) the
+        SOL profiles does not flatten as in the case with the cryo-pumps
     \end{itemize}
@@
 
-\begin{frame}{Fast particle accelleration}
-  \Fontvi
-  \begin{columns}
-    \begin{column}{0.4\textwidth}
-      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/KenAnalysis} \\
-      \textcolor{red}{K. McClements \& J. Galdon-Quiroga}
-    \end{column}
-    \begin{column}{0.6\textwidth}
+\begin{frame}{Work in progress}
   \begin{itemize}
-\item L-mode shots: no evidence of electron or ion acceleration during flat-top, but TAE excitation (top) \&
-  neutron time traces during current ramp-up in three shots suggest bulk ion acceleration
-\item H-mode shots: many examples found of SXR spikes from plasma edge at start of ELMs $\rightarrow$ electron acceleration),
-  although enhancements are less dramatic than in earlier H-mode pulses with lower pedestal $\nu^{*}$ (lower plot)
-\item ELMs also linked to enhanced fast ion losses, as in previous H-mode pulses –
-  not yet clear whether beam ions are accelerated during ELMs, but fast ion loss detector settings will be optimised in remaining pulses of this experiment
+    \item Confirmed SXR spikes correlated with the start of ELMs,
+      strongly suggesting electron accelleration during ELM filament
+      eruption
+    \item Evaluation progressing in terms of fluctuation analysis from
+      MEM, Reflectometry, Li-Beam
+    \item GPI data available in different density scenarios and also
+      during L-H transition
   \end{itemize}
-\end{column}
-\end{columns}
 \end{frame}
-
 \end{document}

### 2017-05-26 Codes/python/aug/get_ricProfiles.py
add script get_ricProfiles.py to read the RIC profiles from AUG data base and plot it. The script uses additional script findindx.py to get the indexes of a value from a matrix

@@ -1,0 +1,126 @@
+"""
+Script reads the processed profiles of ICRF reflectometry system (RIC)
+from AUG data bese.
+
+Note:
+    To use the script from a command line use argparse notation:
+    e.g. to get a profile in a shot number 34283 from antenna 4 
+    at time instance 2.5 sec type following in a command line:
+
+    python get_ricProfiles.py -s 34283 -a 4 -t 2.5
+
+
+Author:
+    Egor Seliunin
+    eseliunin@ipfn.tecnico.ulisboa.pt
+"""
+
+import dd
+import findindx
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+
+def get_ric_profile(shotnumber, antenna, time, accuracy=1e-4):
+    """
+    Script to read the RIC profiles from data base
+
+    Input:
+        shotnumber: int,
+                    Number of the requiring shot
+        antenna: int,
+                 Number of requiring antenna.
+                 Note: there are 3 antennas in RIC with following 
+                       numbers: 1 : upper plane, 
+                                4 : mid plane,
+                                8 : lower plane.
+        time: float,
+              Time instance of a profile in [s]
+        accuracy: float,
+                  time accuracy to find a value in a time base in 
+                  order to get the index
+        
+    Output:
+        p: dictionary,
+           Dictionary, that contains the following keys:
+           time: float 
+                 time instance of a profile 
+           area: numpy array, float
+                 rho poloidal base of a profile
+           data: numpy array, float
+                 electron density array
+           persistance: float,
+                        number of frequency sweeps that was used
+                        to calculate the profile
+    """
+
+    # Antenna name
+
+    antenna = "Ne_Ant" + str(antenna)
+
+    # Getting data routin
+
+    shotfile = dd.shotfile('RIC', shotnumber)
+    ne = shotfile(antenna)
+    shotfile.close()
+
+    # Find time index
+
+    (indx1, indy) = findindx.findin(ne.time, time, accuracy)
+
+    # Generating the time, area and data
+
+    time = ne.time[indx1]
+    area = ne.area[indx1,:]
+    data = ne.data[indx1,:]
+
+    # Constructing dictionary
+
+    p = {"time":time,"area":area, "data":data}
+    return p
+
+def plot_ric_profile(shotnumber, antenna, time, accuracy=1e-4):
+    """
+    Script to plot a profile
+    """
+    p = get_ric_profile(shotnumber, antenna, time, accuracy=1e-4)
[…]

### 2017-05-30 Experiments/TCV/analysis/python/scriptPreparation.py
add script and figure for the preparation of TCV experiment

@@ -1,0 +1,145 @@
+import matplotlib as mpl
+import MDSplus as mds
+import pandas as pd
+import numpy as np
+from tcv.diag.frp import FastRP
+from scipy.interpolate import UnivariateSpline
+from scipy import constants
+mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica']})
+mpl.rc("font", size=18)
+mpl.rc("lines", linewidth=2)
+
+
+def print_menu():
+    print 30 * "-", "MENU", 30 * "-"
+    print "1. Current scan from Topic 25"
+    print "2. Loop on Topic 25 Upstream profile evolution"
+    print "99: End"
+    print 67 * "-"
+
+
+loop = True
+while loop:
+    print_menu()
+    selection = input("Enter your choice [1-99] ")
+    if selection == 1:
+        shotList = (57082, 57086, 57087, 57088, 57089)
+        colorList = ('#1f77b4', '#ff7f0e', '#2ca02c', '#d62728',
+                     '#17becf')
+        fig, ax = mpl.pylab.subplots(figsize=(10, 14), nrows=3, ncols=1)
+        fig.subplots_adjust(hspace=0.2, top=0.98, left=0.17, right=0.98)
+        for shot, col in zip(shotList, colorList):
+            Tree = mds.Tree('tcv_shot', shot)
+            # retrieve the current
+            iP = Tree.getNode(r'\magnetics::iplasma:trapeze').data()
+            iPt = Tree.getNode(
+                r'\magnetics::iplasma:trapeze').getDimensionAt().data()
+            ax[0].plot(iPt, iP/1e3, lw=3, color=col,
+                       label=r'# %5i' % shot)
+            ax[0].set_xlim([0, 2])
+            ax[0].set_ylim([0, 450])
+            ax[0].axes.get_xaxis().set_visible(False)
+            # get the density in 10^19
+            eN = Tree.getNode(r'\results::fir:n_average').data()/1e19
+            eNT = Tree.getNode(
+                r'\results::fir:n_average').getDimensionAt().data()
+            ax[1].plot(eNT, eN, lw=3, color=col)
+            ax[1].set_xlim([0, 2])
+            ax[1].set_ylim([0, 15])
+            # get the UnivariateSpline represenation of the density
+            enS = UnivariateSpline(eNT, eN, s=0)
+            # now retrieve the information for the jSat from Langmuir
[…]

### 2017-05-30 Experiments/TCV/analysis/python/scriptPreparation.py
added proposed density ramp

@@ -14,6 +14,7 @@ def print_menu():
     print 30 * "-", "MENU", 30 * "-"
     print "1. Current scan from Topic 25"
     print "2. Loop on Topic 25 Upstream profile evolution"
+    print "3. Plot proposed density ramp"
     print "99: End"
     print 67 * "-"
 
@@ -126,7 +127,8 @@ while loop:
                     err = Profile.err
                     spline = UnivariateSpline(x, y, ext=0)
                     xFake = np.linspace(0, 0.035, 50)
-                    ax[2].plot(x*1e2, y, 'o', mfc=c, mec='white', markersize=16)
+                    ax[2].plot(x*1e2, y, 'o', mfc=c, mec='white',
+                               markersize=16)
                     ax[2].errorbar(x*1e2, y, yerr=err, ecolor=c, fmt='none')
                     ax[2].plot(xFake*1e2, spline(xFake), '--', color=c)
                     ax[2].set_xlabel(r'R-R$_s$ [cm]')
@@ -139,6 +141,28 @@ while loop:
             mpl.pylab.savefig('../pdfbox/UpstreamProfileShot_'
                               + str(int(shot)) + '.pdf',
                               bbox_to_inches='tight')
+    elif selection == 3:
+        tFake = np.asarray([0, 0.2, 0.4, 0.54, 1.6])
+        enFake = np.asarray([0, 2.8, 3.6, 3.6, 11])
+        shotL = (57082, 57088, 51178, 57089)
+        iPL = (330, 245, 160, 185)
+        fig, ax = mpl.pylab.subplots(figsize=(8, 5), nrows=1, ncols=1)
+        fig.subplots_adjust(left=0.17, top=0.98, bottom=0.16)
+        colorList = ('#1f77b4', '#ff7f0e', '#2ca02c', '#d62728')
+        for shot, col, ip in zip(shotL, colorList, iPL):
+            Tree = mds.Tree('tcv_shot', shot)
+            eN = Tree.getNode(r'\results::fir:n_average').data()/1e19
+            eNT = Tree.getNode(
+                r'\results::fir:n_average').getDimensionAt().data()
+            ax.plot(eNT, eN, lw=2, color=col, label=r'# %5i' % shot +
+                    r' I$_p$ = %3i' % ip)
+        ax.plot(tFake, enFake, 'k--', lw=3)
+        ax.set_xlabel(r't[s]')
[…]

### 2017-05-30 Meetings/TCVrelated/revised_shotlist.tex
Added a short presentation for revised TCV shotlist

\documentclass[10pt, compress]{beamer}
\usetheme[conference=TCV-Topic21,venue=Lausanne, date=30/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21: TCV experimental plan for Week 24}
\date{30 March 2017}
\author[N. Vianello,  V. Naulin]{N . Vianello and V. Naulin}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

\begin{frame}{Taking advantage of already performed experiment}
\vspace{-1cm}
\Fontvi
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanTopic25}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item Topic 25 already performed a current scan at
          constant B$_{\phi}$ but as far as I checked we don't have
          fast reciprocating probe data for all the scan \alert{To be
            confirmed by Cedric}
        \item Furthermore the density was not optimized for lower
          current, as it start to high
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Proposed density ramp}
\Fontvi
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/ProposedDensityRamp}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item I propose to perform with the same density ramp at all
          the current as shown in dashed line. Less demanding for the
          higher current case we could end up into disruption for the
          lower current case
      \end{itemize}
    \end{column}
  \end{columns}
  \end{frame}

  \begin{frame}{Proposed experimental plan}
\Fontvi
    \alert{For the first week of operation we propose to perform only
  L-Mode shot and we have accommodated the low collisionality request
  from cedric}
\begin{enumerate}
\item Shape from 57088, I$_p$ = 245 kA,  Reverse B$_t$,
    density ramp from Line Average Density = 3.8e19 @ 0.5 s to 11e19 @ 1.6s,  Bt = 1.4T. Plunge @ 0.65, 1.52
\item  Repeat \# 1 with I$_p$=330 kA Bt=1.4T, same density ramp, same timing for plunges
\item  Repeat \# 1 with I$_p$=180 kA, Bt=1.4T, same density ramp, same timing for plunges
\item  Repeat \# 1 with q95=2.44 as \# 2, adjust Bt consequently (Bt = 1.02T)
\item  Repeat \# 3 with q95=2.44 as \# 2, adjust Bt consequently (Bt=0.8T)
\item  Shape and current from \# 1. Stop puffing once the divertor is formed to get low collisionality case
\item  Repeat \# 6 with density feedback controlled at value 50 \%
  higher then \# 6. 
\item  Repeat density ramp of Shot \# 2 in DN configuration 
\item  Repeat density ramp of Shot \# 3 in DN configuration 
\item Repeat \# 1 in forward field
\item Repeat \# 3 in forward field
\end{enumerate}
\end{frame}
\end{document}

### 2017-05-31 Meetings/TCVrelated/revised_shotlist.tex
Update to TCV shotlist

@@
         \item Furthermore the density was not optimized for lower
-          current, as it start to high
+          current, as it starts to high
       \end{itemize}
@@
       \begin{itemize}
-        \item I propose to perform with the same density ramp at all
-          the current as shown in dashed line. Less demanding for the
-          higher current case we could end up into disruption for the
+        \item The proposal is to use the same density ramp for all
+          the currents as shown in dashed line. Less demanding for the
+          higher current case. Risk to end with disruption for the
           lower current case
@@
 \Fontvi
-    \alert{For the first week of operation we propose to perform only
-  L-Mode shot and we have accommodated the low collisionality request
-  from cedric}
+    \alert{For the first week of operation we propose L-mode shots
+      only. We have accomodated the low collisionality request from
+      Cedric. Shots 1-3 I$_p$ scan at constant toroidal field. Shots
+      1, 4 and 5 I$_p$ scan at constant q$_{95}$ to be compared with
+      analogous experiments in AUG and MAST-U. Shots 6-7 Low
+      collisionality scan. Shots 8-9 DN current scan: this will be
+      compared directly with Mast-U which will run predominantly in DN
+    configuration. Shot 10-11 Current scan in forward field to check
+    the role of $\nabla\times B$ direction.}
 \begin{enumerate}
@@
 \item  Repeat \# 3 with q95=2.44 as \# 2, adjust Bt consequently (Bt=0.8T)
-\item  Shape and current from \# 1. Stop puffing once the divertor is formed to get low collisionality case
-\item  Repeat \# 6 with density feedback controlled at value 50 \%
-  higher then \# 6. 
+\item  Shape and current from \# 1. Stop puffing once the divertor is
+  formed to get low collisionality case. ECRH ramp from 0.9s (150
+  kW--500 kW)
+\item  Repeat \# 6 with intermediate density value between \# 6 and
+  \#1 density at 0.65s. 
 \item  Repeat density ramp of Shot \# 2 in DN configuration 

### 2017-06-23 Experiments/TCV/analysis/python/scriptAnalysis.py
added the script and figure for evaluation of the profile in L-Mode in TCV

@@ -1,6 +1,5 @@
 import numpy as np
 import sys
-import itertools
 import matplotlib as mpl
 from scipy.interpolate import UnivariateSpline
 from scipy.signal import savgol_filter
@@ -26,6 +25,8 @@ def print_menu():
     print "2. General plot with current scan at constant q95"
     print "3. Compare profiles scan at constant Bt"
     print "4. Compare profiles scan at constant q95"
+    print "5. Compare profiles scan at constat Bt only SOL"
+    print "6. Compare profiles scan at constat q95 only SOL"
     print "99: End"
     print 67 * "-"
 
@@ -91,7 +92,8 @@ while loop:
                               POhm.data()/1e6, '-', color=col,
                               label='Ohmic')
             try:
-                ax[2, 0].plot(Bolo.time, (Bolo.LfsSol() + Bolo.LfsLeg())/1e3, '--',
+                ax[2, 0].plot(Bolo.time, (Bolo.LfsSol() +
+                                          Bolo.LfsLeg())/1e3, '--',
                               color=col, label=r'LFS SOL + Leg')
             except:
                 pass
@@ -257,11 +259,400 @@ while loop:
 
         mpl.pylab.savefig('../pdfbox/CurrentScanConstantQ95.pdf',
                           bbox_to_inches='tight')
-        
     elif selection == 3:
-        pass
+        shotList = (57437, 57425, 57497)
+        colorList = ('#1f77b4', '#ff7f0e', '#2ca02c')
+        currentList = ('190','240', '330')
+        fig, ax = mpl.pylab.subplots(figsize=(16, 10), nrows=2, ncols=3)
+        for shot, _col, _idx, _cur in zip(shotList, colorList,
+                                          range(len(shotList)),
+                                          currentList):
+            # read the average density data
+            Tree = mds.Tree('tcv_shot', shot)
+            enAVG = Tree.getNode(r'\results::fir:n_average')
+            # plot the data
+            ax[0, _idx].plot(enAVG.getDimensionAt().data(),
+                             enAVG.data()/1e19, color='k', lw=2,
+                             label=r' I$_p$ = ' + _cur+' kA')
+            ax[0, _idx].set_xlabel(r't [s]')
+            ax[0, _idx].set_ylim([0, 12])
+            ax[0, _idx].legend(loc='best', numpoints=1, frameon=False)
+            ax[0, _idx].set_title(r'Shot # %5i' % shot)
[…]

### 2017-06-23 Experiments/TCV/analysis/python/topic21_survey.py

@@ -207,7 +207,7 @@ if doubleP is not None:
     yO = doubleP['Dens(m-3)'][
         :np.argmin(doubleP['rrsep(m)'])].values/1e19
     eRO = doubleP['DensErr(cm-3)'][
-        :np.argmin(doubleP['rrsep(m)'])].values/10.
+         :np.argmin(doubleP['rrsep(m)'])].values/10.
     Profile = FastRP._getprofileR(xO, yO, npoint=35)
     x = Profile.rho.values
     y = Profile.values

### 2017-06-23 Meetings/TCVrelated/mondaymeeting_260617_vianello.tex
started the slide for Monday morning meeting on TCV

--- 2017-05-12 Meetings/TCVrelated/kom_150517_vianello.tex
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Topic 21: TCV experiment KoM}
-\date{15 March 2017}
-\author[N. Vianello,  V. Naulin]{N . Vianello and V. Naulin}
+\title{Topic 21 experiment Week 24}
+\date{26 June 2017}
+\author[N. Vianello,  V. Naulin]{N . Vianello and V. Naulin for the
+  Topic 21 SC team}
 \begin{document}
@@
 \maketitle
-
+\begin{frame}{Scientific Team}
+  \begin{description}
+  \item[EPFL:] H. De Oliveira, R. Maurizio, B. Labit,
+    C. Tsui, K. Verhaegh, H. Reimerdes, C. Theiler
+  \item[DTU:] J.J. Rasmussen and V. Naulin
+  \item[RFX:] N. Vianello, M. Spolaore, M. Agostini
+  \item[OEAW:] B. Schneider, S. Costea, R. Schrittwieser
+  \item[CCFE:] F. Militello
+  \item[JSI:] J. Kovacic
+  \end{description}
+\end{frame}
 \begin{frame}{TCV experiments: boundary condition}
@@
 \Fontvi
-\only<1>{
 \begin{itemize}
@@
   \end{enumerate}
-  \item We have a total number of \textbf{\# 23 Shots} split into two
+\item We have a total number of \textbf{\# 23 Shots} originally split into two
     operational window. Calendar week 24 (12.06-16.06) and Calendar
@@
 \end{itemize}
-}
-\only<2>{
-  \begin{itemize}
-    \item 15 people listed in the team for TCV experiment
-      \begin{description}
-        \item[EPFL:] H. De Oliveira, R. Maurizio, B. Labit,
-          C. Tsui, K. Verhaegh, H. Reimerdes, C. Theiler
-        \item[DTU:] J.J. Rasmussen and V. Naulin
-        \item[RFX:] N. Vianello, M. Spolaore, M. Agostini
-        \item[OEAW:] B. Schneider, S. Costea, R. Schrittwieser
-        \item[CCFE:] F. Militello
-        \item[JSI:] J. Kovacic
-      \end{description}
-    \end{itemize}
-  }
 \end{frame}
+
+\begin{frame}{Experimental plan}
+  \begin{frame}{Proposed experimental plan}
+\Fontvi
+    \alert{For the first week of operation we originally planned L-mode shots
+      only. Shots 1-3 I$_p$ scan at constant toroidal field. Shots
+      1, 4 and 5 I$_p$ scan at constant q$_{95}$ to be compared with
+      analogous experiments in AUG and MAST-U. Shots 6-7 Low
+      collisionality scan. Shots 8-9 DN current scan: this will be
+      compared directly with Mast-U which will run predominantly in DN
+    configuration. Shot 10-11 Current scan in forward field to check
+    the role of $\nabla\times B$ direction.}
+\begin{enumerate}
+\item Shape from 57088, I$_p$ = 245 kA,  Reverse B$_t$,
+    density ramp from Line Average Density = 3.8e19 @ 0.5 s to 11e19 @ 1.6s,  Bt = 1.4T. Plunge @ 0.65, 1.52
+\item  Repeat \# 1 with I$_p$=330 kA Bt=1.4T, same density ramp, same timing for plunges
+\item  Repeat \# 1 with I$_p$=180 kA, Bt=1.4T, same density ramp, same timing for plunges
+\item  Repeat \# 1 with q95=2.44 as \# 2, adjust Bt consequently (Bt = 1.02T)
+\item  Repeat \# 3 with q95=2.44 as \# 2, adjust Bt consequently (Bt=0.8T)
+\item  Shape and current from \# 1. Stop puffing once the divertor is
+  formed to get low collisionality case. ECRH ramp from 0.9s (150
+  kW--500 kW)
+\item  Repeat \# 6 with intermediate density value between \# 6 and
+  \#1 density at 0.65s. 
+\item  Repeat density ramp of Shot \# 2 in DN configuration 
+\item  Repeat density ramp of Shot \# 3 in DN configuration 
+\item Repeat \# 1 in forward field
+\item Repeat \# 3 in forward field
+\end{enumerate}
+\end{frame}
+
+\begin{frame}{Current scan at constant Magnetic field}
+  \begin{columns}[c]
+    \begin{column}{0.65\textwidth}
+      \includegraphics[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/}
+    \end{column}
+  \end{columns}
+
 \begin{frame}{Results obtained during MST1 Campaigns 2015-2016}
@@
         \end{frame}
-
-      % \only<2>{
-% We will conclude the \textcolor{ta3chameleon}{L-Mode}
-% part in Week 15 where we also would like to include part of the \textcolor{ta3scarletred}{H-Mode}
-% scenario development. This would give us an additional week between
-% the experiments to address possible issues in particular for the
-% H-mode part\\
-% \textbf{Week 15} \\
-% We choose are reference shot \# 30269 (I$_p$ = 0.8 MA, B$_{\phi}$ = 2.5T, q$_{95}\approx 4.5$)
-%   \begin{enumerate}
-%     \item \textcolor{ta3chameleon}{Shot at I$_p$=0.6 MA
-%       keeping the same toroidal field $B_{\phi}$ = 2.5T as the reference adjust the fueling
-%       rate (\emph{Current scan with modification of $q_{95}$})}
-%   \item \textcolor{ta3chameleon}{Shot at I$_p$ = 0.6MA
-%       reduce the toroidal field B$_{\phi}\approx $2T in order to match q$_{95}\approx 4.5$, 
-%       (\emph{Current scan at fixed $q_{95}$}). This would accommodate
-%       the diagnostic request of D. Aguiam}
-%     \item \textcolor{ta3chameleon}{Density ramp with I$_p$ = 1MA and
-%         B$_{\phi}$ = 2.5T}
-%     \item \textcolor{ta3chameleon}{Density ramp with I$_{p}$ = 1MA,
-%         increasing the toroidal field in order to match q$_{95}\approx
-%         4.5$}
-%     \end{enumerate}
-%   }
-%   \only<3>{
-%   \textbf{Week 15} \\
-%     For the \textcolor{ta3scarletred}{H-Mode} scenario development we start from the best shot found in
-%     2016 (\# 33478) and increase the heating power
-%     \begin{enumerate}
-%       \item \textcolor{ta3scarletred}{Start from shot \# 33478 but
-%           with increased heating power (6MW). Adjust fueling rate from
-%         reference by increasing by a factor of 30 \%. 1 Plunge of
-%         probe head at the end of the discharge still in a safe
-%         position and IR monitoring}
-%     \item \textcolor{ta3scarletred}{Repeat \# 1 eventually adjusting
-%         the fueling rate. Start the N seeding in feedforward starting
-%         fro the level found in reference}
-%     \item \textcolor{ta3scarletred}{Trade off between \#1 and \#2
-%         Fueling/Seeding. Additional plunge of probe at the end of the
-%         discharge}
-%       \item \textcolor{ta3skyblue}{This scenario would allow the
-%           exploitation of particle accelleration (McClements) physics as piggy-back}
-%     \end{enumerate}
-%   }
-%   \only<4>{
-%   \textbf{Week 17: This strongly depends on the achievement of H-Mode
-%     scenario obtained in Week 15 } \\
-%     \begin{enumerate}
-%     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in Week 15 1st Radial position of probe}
-%     \item \textcolor{ta3scarletred}{Repeat \#1, different probe position}
-%     \item \textcolor{ta3scarletred}{Repeat \#1, different probe
-%         position}
-%     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
-%         week 15 and reduced the cryopumps}
-%     \item \textcolor{ta3scarletred}{Repeat best H-Mode shot found in
-%         week 15 and puff from midplane}
-%     \item \textcolor{ta3scarletred}{Contingency}
-%     \item \textcolor{ta3scarletred}{Contingency}
-%     \end{enumerate}
-%   }
-%   \only<5>{
-%     Among the contingency we propose the following 4 possibilities to
-%     be discussed
-%     \begin{enumerate}
-%     \item \textcolor{ta3chameleon}{Reversing B$_t$ direction and repeat one identical shot (e.g \# 30269) to investigate
-%    the role of SOL flows in SOL shoulder formation and filamentary
-%    transport}
-%     \item \textcolor{ta3chameleon}{DN discharge with similar density ramps as in reference. Possibly the two X-point should
-%    sit on the same flux surface}
-%    \item \textcolor{ta3scarletred}{Attempt a scenario similar to Topic-06 which will be performed later in time. See for example
-%    shot \# 29816 (Presented by T. Eich in the GPM) which is at even
-%    higher power (8 MW) or \# 25740
-%    which is actually in DN (see proposal from J. Vicente). If we choose for this we could actually compare with the priority 3 of L-Mode
-%    contingency}
-%  \item \textcolor{ta3scarletred}{Reverse B$_{t}$ operation. In this case the L-H treshold is different and we might end
-%      by careful adjusting the power into I-Mode scenario}
-%    \item \textcolor{ta3skyblue}{Working at 2T in H-Mode would require
-%        additional development}
-%    \item \textcolor{ta3skyblue}{Given that the upper divertor is less
-%        diagnosed then the lower one we prefer eventually to operate
-%        with reverse B$_{\phi}$}
-
-% \end{enumerate}
-%   }
-% \end{frame}
-% \begin{frame}{Required diagnostic and analysis}
-%   \begin{itemize}
-%     \item[$\boxtimes$] Midplane Manipulator
-%     \item[$\square$] Li-Beam. \emph{Are fluctuations and profiles
-%         available simultaneously}
-%     \item[$\square$] RFA \#2
-%     \item[$\square$] Divertor probes
-%     \item[$\boxtimes$] Neutral profiles
-%     \item[$\square$] Infrared for probe head monitoring. \emph{Are Target
-%       infrared measurements available/useful?}
-%     \item[$\square$] GPI
-%     \item[$\boxtimes$] Reflectometer. \emph{The operation at 2T can be
-%       obtained during the q$_{95}$ scan}
-%     \item[$\boxtimes$] Fast probes on the limiter
-%     \item[$\square$] Bolometer/AXUV in the divertor region
-%   \end{itemize}
-% \end{frame}
-
-% \begin{frame}{Work to be accomplished before the experiment}
-%   \begin{enumerate}
-%     \item Check the shape modification during the current/q$_{95}$
-%       scan
-%     \item Probe conditioning?
-%     \item Check the status of the diagnostics including GPI (issue
-%       regarding the puffing)
-%     \item Methodology ($\Lambda_{div}$ computation and profile)
-%       $\lambda_n$ filaments properties etc.  
-%     \item Code preparation for analysis and
-%       visualization. \emph{GITHUB repository?}
-%     \item Optimization of the effort: please provide us a more
-%       detailed plan of your analysis in order to limit superposition
-%       or work duplication
-%   \end{enumerate}
-% \end{frame}
 \end{document}

### 2017-06-23 Meetings/TCVrelated/mondaymeeting_260617_vianello.tex
Added the monday morning meeting slides for TCV

@@
 \date{26 June 2017}
-\author[N. Vianello,  V. Naulin]{N . Vianello and V. Naulin for the
+\author[Topic 21 ST]{N . VianTllo and V. Naulin for the
   Topic 21 SC team}
@@
 \begin{frame}{Experimental plan}
-  \begin{frame}{Proposed experimental plan}
 \Fontvi
@@
 
-\begin{frame}{Current scan at constant Magnetic field}
+\begin{frame}{Current scan at constant B$_{\phi}$}
+\Fontvi
   \begin{columns}[c]
-    \begin{column}{0.65\textwidth}
-      \includegraphics[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/}
+    \begin{column}{0.7\textwidth}
+      \includegraphics<1>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
+      \includegraphics<2>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantBtSOL}
+      \includegraphics<3>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantBt}
     \end{column}
-  \end{columns}
-
-\begin{frame}{Results obtained during MST1 Campaigns 2015-2016}
-  \begin{columns}
-    \begin{column}{0.6\textwidth}
-      \includegraphics<1>[width=\textwidth]{pdfbox/KoM150517/Fig0}
-      \includegraphics<2>[width=\textwidth]{pdfbox/KoM150517/Fig1}
-      \includegraphics<3>[width=\textwidth]{pdfbox/KoM150517/Fig2}
-      \includegraphics<4>[width=\textwidth]{pdfbox/KoM150517/Fig4}
-      \includegraphics<5>[width=\textwidth]{pdfbox/KoM150517/Fig5}
-      \includegraphics<6>[width=\textwidth]{pdfbox/KoM150517/Fig6}
-      \includegraphics<7>[height=.8\textheight]{pdfbox/KoM150517/Fig7}
-      \includegraphics<8>[height=.8\textheight]{pdfbox/KoM150517/Fig8}
-    \end{column}
-    \begin{column}{0.4\textwidth}
+    \begin{column}{0.3\textwidth}
       \begin{itemize}
-        \item<1|only@1> Performed a series of L-Mode shots with
-          density ramp and different poloidal flux expansion to check
-          L$_{\parallel}$ effect
-        \item<2|only@2> Upstream profiles at same densities but
-          different $\Lambda_{div}$ (well above 1 all along the
-          profiles) are similar. Weak effect of parallel connection
-          length modification
-        \item<3|only@3> Density decay length $\lambda_n$ modified
-          strongly with increasing density in the near SOL region
-        \item<4|only@4> Blob size increases with density independently
-          from the Flux expansion
-        \item<5|only@5> In the Far SOL the decay length scales with
-          divertor collisionality but examples with high $\Lambda_n$
-          and steep profile clearly exhists
-        \item<6|only@6> Steep profile clearly seen in the
-          Sheath-connected regime. Unclear if Resistive balloning and
-          resistive X-point blobs behaves differently
-        \item<7|only@7> Change in the Flux expansion does not change
-          detachment density threshold, whereas divertor leg length
-          has a clear impact (\textit{Theiler, NF17 and Reimerdes IAEA
-            2016})
-        \item<8|only@8> Also any differences observed between single
-          and double null. Major modification only induced by density increase
-
+        \item Confirming results from Topic-25 increasing the current
+          reduces the ion flux rollover density threshold
+        \item Neutral compression seems slightly reduced at higher current
+        \item<2-> Profiles from RCP are not yet clear, with the only
+          robust variation between 245 and 330 kA
+        \item<3-> If we combine with Thomson scattering there are still
+          unresolved issue
         \end{itemize}
@@
 
-\begin{frame}{Proposed experimental plan: L-mode}
+\begin{frame}{Current scan at constant q$_{95}$}
 \Fontvi
-  The first shots are needed in order to have comparable scenario
-  between all the machines
+  \begin{columns}[c]
+    \begin{column}{0.7\textwidth}
+      \includegraphics<1>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
+      \includegraphics<2>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantQ95SOL}
+      \includegraphics<3>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantQ95}
+    \end{column}
+    \begin{column}{0.3\textwidth}
       \begin{itemize}
-    \item Current scan at constant q$_{95}$
-      \begin{enumerate}
-      \item Reference shot is \# 54867, I$_p$=240 kA, q$_{95}$=3.5,
-        B$_t$ = 1.41T with the same density ramp (\alert{Do we need a density ramp? can we
-          go directly at high density as in \# 53516? and repeat the
-          shot at low density?})
-      \item Repeat Shot \# 1 with I$_p$=180 kA (20\% decrease similarly
-        to AUG) with the same q$_{95}$ and adjusting the toroidal field
-      \item Repeat Shot \# 1 with I$_p$=300 kA (20\% increase similarly
-        to AUG) with the same q$_{95}$ and adjusting the toroidal
-        field. \alert{In case this causes a transition into Ohmic H-Mode we
-        might think to perform the shot in reverse B$_t$. This
-        eventually needs additional shots at lower current as
-        well. \emph{Why not operate all the shots in Reverse B$_t$?}}
-      \end{enumerate}
-    \item Current scan at constant B$_t$
-      \begin{enumerate}
-        \setcounter{enumi}{3}
-      \item I$_p$=180 kA,  B$_t$ = 1.41 as in shot \# 1 
-      \item I$_p$=300 kA, B$_t$=1.41 as in shot \# 1
-      \end{enumerate}
+        \item Unusual scenarios with B$_{phi}$ up to 0.8T. \alert{No rollover
+          on at any of the current}
+        \item Expected higher target neutral pressure increase at
+          higher current
+        \item<2-> Profiles from RCP suggest slight flattening in the
+          far SOL at higher current
+        \item<3-> Confirmed even combining with Thomson data
         \end{itemize}
+    \end{column}
+  \end{columns}
+\end{frame}
+\begin{frame}{Attempt for low collisionality}
+  \begin{columns}[c]
+    \begin{column}{0.7\textwidth}
+      \includegraphics[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/LowCollisionalityAttempt}
+    \end{column}
+    \begin{column}{0.3\textwidth}
+      All the attempt to perform a low collisionality case disrupted
+      whenever density decreases below a certain threshold
+    \end{column}
+  \end{columns}
 \end{frame}
 
-  \begin{frame}{Proposed experimental plan: L-Mode}
-    \begin{itemize}
-      \item Divertor leg length/L$_{parallel}$ scan
+\begin{frame}{Conclusion}
+  \Fontvi
 \begin{enumerate}
-        \setcounter{enumi}{5}
-      \item Repeat \# 1 at $Z=+23$.
-      \item Repeat \# 1 at $Z=-10$  
+\item \textcolor{green}{Shape from 57088, I$_p$ = 245 kA,  Reverse B$_t$,
+    density ramp from Line Average Density = 3.8e19 @ 0.5 s to 11e19 @ 1.6s,  Bt = 1.4T. Plunge @ 0.65, 1.52}
+\item  \textcolor{green}{Repeat \# 1 with I$_p$=330 kA Bt=1.4T, same density ramp, same timing for plunges}
+\item  \textcolor{green}{Repeat \# 1 with I$_p$=180 kA, Bt=1.4T, same density ramp, same timing for plunges}
+\item  \textcolor{green}{Repeat \# 1 with q95=2.44 as \# 2, adjust Bt consequently (Bt = 1.02T)}
+\item  \textcolor{green}{Repeat \# 3 with q95=2.44 as \# 2, adjust Bt consequently (Bt=0.8T)}
+\item  \textcolor{red}{Shape and current from \# 1. Stop puffing once the divertor is
+  formed to get low collisionality case. ECRH ramp from 0.9s (150
+  kW--500 kW)}
+\item  \textcolor{red}{Repeat \# 6 with intermediate density value between \# 6 and
+  \#1 density at 0.65s.} 
+\item  \textcolor{red}{Repeat density ramp of Shot \# 2 in DN configuration} 
+\item  \textcolor{red}{Repeat density ramp of Shot \# 3 in DN configuration} 
+\item \textcolor{red}{Repeat \# 1 in forward field}
+\item \textcolor{red}{Repeat \# 3 in forward field}
 \end{enumerate}
-      \item This can have issues in terms of probe operation because
-        of shadowing effect. 
-      \item Double Null. Repeat the current scan at constant q$_{95}$ in
-        DN configuration in order to provide suitable comparable
-        scenario with foreseen MAST-U operation
-        \begin{enumerate}
-          \setcounter{enumi}{7}
-          \item Repeat the density ramp of \# 1 in DN configuration
-            I$_p$ = 240kA
-          \item Repeat density ramp of shot \# 2 in DN configuration
-            I$_p$ = 180 kA
-          \item Repeat density ramp of shot \# 2 in DN configuration
-            I$_p$ = 300 kA
-          \end{enumerate}
-        \end{itemize}
+
 \end{frame}
 
-      \begin{frame}{Proposed experimental plan: H-Mode}
-        The NBI heated plasma is still a partially uncovered scenario
-        for TCV. We have a good reference shot \# 53352 with a good
-        type-I Elmy regime. We propose to use the 3 shots for proper
-        scenario development
-        \begin{enumerate}
-          \setcounter{enumi}{10}
-          \item Repeat \# 53352 same setting. 1MW NBI power 0.4
-            s starting at 0.8s. At 0.82s start a density ramp keeping
-            the same rate as in \# 1. Power ramp down from 1.2 second
-            in order to check ELMy regime. \alert{We need a good
-              monitoring of divertor condition and modification}
-          \item The second shot will depend on \# 11. We will need to
-            adjust the fueling rate accordingly. Include N seeding
-            \alert{check for appropriate reference from past
-              experiment}
-          \item Repeat \# 12 with best trade off between seeding and fueling
-          \end{enumerate}
-          The hypothesis to reach ECRH high density H-Mode is limited, to my
-          knowledge, to operation in vertically shifted plasma and
-          X3. Can be explored in W23
-        \end{frame}
-
-        \begin{frame}{Diagnostic and open issues}
-          %\Fontvi
-          \begin{itemize}
-          \item Fast Camera
-          \item DBS radial localization
-          \item Neutrals from gauges. D$_{\alpha}$ calibrated camera
-            to be used together with \texttt{KN1D} code
-          \item Fast reciprocating probe. Can it work with radially
-            spaced I$_s$ measurements?
-          \item Do we miss something in L-Mode which is worth to be
-            done?
-          \item Do we have experience of nitrogen seeded NBI heated
-            discharge?
-          \item Do we have other references for high density H-Mode operation?
-          \end{itemize}
-        \end{frame}
 \end{document}

### 2017-09-14 Codes/python/aug/langmuir.py
modificaton to langmuir with a new method for computation of LCFS in equilibria which use hidden method of matplotlib

@@ -3,7 +3,9 @@ import dd
 import map_equ
 from scipy.interpolate import UnivariateSpline
 import numpy as np
+import scipy
 import matplotlib as mpl
+import matplotlib._cntr as cntr
 from mpl_toolkits.mplot3d import Axes3D
 from cyfieldlineTracer import get_fieldline_tracer
 from scipy.interpolate import interp1d
@@ -751,48 +753,7 @@ class Target(object):
            based on a smoothed
         """
 
-        t0 = (trange[0]+trange[1])/2.
-        # reload the equilibrium at the appropriate time instant
-        self._setTimeEq(time=t0)
-        # save into a dummy gfile to be loaded by the Tracer
-        self.dump_geqdsk(filename='tmp.g')
-        # We need to reload the equilibrium since there is no way
-        # for the moment to pass an istance of equilibrium to the
-        # tracer CLASS
-        self.Tracer = get_fieldline_tracer('RK4', gfile='tmp.g',
-                                           interp='quintic', rev_bt=True)
-        # height of magnetic axis
-        zMAxis = self.axis.__dict__['z']
-        # height of Xpoint
-        zXPoint = self.xpoints['xpl'].__dict__['z']
-        rXPoint = self.xpoints['xpl'].__dict__['r']
-        # now determine at the height of the zAxis the R of the LCFS
-        Boundary = self.get_fluxsurface(1.0)
-        RLcfs = Boundary.R
-        ZLcfs = Boundary.Z
-        # only the part greater then xaxis
-        ZLcfs = ZLcfs[RLcfs > self.axis.__dict__['r']]
-        RLcfs = RLcfs[RLcfs > self.axis.__dict__['r']]
-        Rout = RLcfs[np.argmin(np.abs(ZLcfs[~np.isnan(ZLcfs)]-zMAxis))]
-        rmin = np.linspace(Rout+0.001, 2.19, num=30)            
-        # this is the R-Rsep
-        rMid = rmin-Rout
-        # get the corrisponding Rho
-        rho = self.Eqm.rz2rho(rmin, np.repeat(zMAxis, rmin.size), self._time,
-                              extrapolate=True).squeeze()
-
-        # compute the field lines
-        fieldLines = [self.Tracer.trace(r, zMAxis, mxstep=100000, ds=1e-2, tor_lim=20.0*np.pi) for r in rmin]
-        # compute the parallel connection length from the divertor plate to the X-point
[…]

### 2017-09-14 Codes/python/aug/augFilaments.py
added to scriptAnalysis point 25-28

@@ -213,11 +213,13 @@ class Filaments(object):
         # convert into absolute value according to transformation
         R = (2188 - (self.Xprobe - self.Xlim) - sPos + 100) / 1e3
         # convert in Rhopoloidal
-        self.rhoProbe = self.Eq.rz2psinorm(
-            R, np.repeat(self.Zmem * 1e-3), tPos, sqrt=True)
-        # then we need to compute for each of the different probe tips
-        # this quantity and save them into a dictionary
+        
+        self.rhoProbe = np.zeros(R.size)
+        for r, t, i in zip(R, tPos, range(R.size)):
+            self.rhoProbe[i]=self.Eq.rz2psinorm(r, self.Zmem*1e-3, t, sqrt=True)
+        self.tPos = tPos
 
+        
     def blobAnalysis(self, Probe='Isat_m01', trange=[2, 3],
                      interELM=False, block=[0.015, 0.12],
                      usedda=False, threshold=3000):

### 2017-09-14 Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -14,10 +14,14 @@ sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/submodules/pycwt/')
 sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/')
 sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/aug/')
 sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/signalprocessing/')
+sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/cyFieldlineTracer')
 import augFilaments
 import neutrals
 import peakdetect
+import langmuir
 from matplotlib.colors import LogNorm
+from cyfieldlineTracer import get_fieldline_tracer
+import eqtools
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=22)
 mpl.rc('font',**{'family':'sans-serif','sans-serif':['Tahoma']})
@@ -47,6 +51,11 @@ def print_menu():
     print "21. Compare Li-Be contour same fueling with/without cryo"
     print "22. Compare Shot constant q95 same edge density"
     print "23. Compare Li-Beam contour profiles with/wo crypumps, Density and Fueling"
+    print "24. Compare Li-Beam and Lambda_Div Ip scan constant q95"
+    print "25. Compare Li-Beam and Lambda_Div Ip scan constant Bt"
+    print "26. Compare Lparallel constant q95 constant Bt"
+    print "27. Equilibria and Lparallel at constant q95"
+    print "28. Equilibria and Lparallel at constant q95"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -1494,6 +1503,439 @@ while loop:
         mpl.pylab.savefig('../pngbox/EvolutionEdgeProfiles_' + str(int(shotList[0])) +
                           '_'+str(int(shotList[1]))+'.png',
                           bbox_to_inches='tight', dpi=300)   
+
+    elif selection == 24:
+        shotList = (34103, 34102, 34104)
+        colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
+        tList = ((2.57, 2.9),
+                 (2.57, 3.03, 3.5),
+                 (1.83, 2.44, 3.15))
+        fig = mpl.pylab.figure(figsize=(16, 17))
+        fig.subplots_adjust(hspace=0.25)
+
+        ax1 = mpl.pylab.subplot2grid((4, 3), (0, 0), colspan=3)
[…]

### 2017-09-14 Meetings/AUGrelated/interim_meeting_150917.tex
start of interim meeting presentation for AUG

\documentclass[10pt, compress]{beamer}
\usetheme[conference=Topic 21,venue=Remote, date=15/09/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Topic 21: AUG experiment analsysis meeting }}
\date{15 September 2017}
\author[Topic 21 Scientific Team]{N. Vianello and V. Naulin for the
  Topic 21 Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Summary of the campaigns}
  \begin{itemize}[<+-|alert@+>]
  \item L-Mode experiment, CW 17.
    \begin{enumerate}
      \item<1> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
      \item<1> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
    \end{enumerate}    
    \item H-Mode experiment, CW 21. 
      \begin{enumerate}
    \item<2> Compare divertor/midplane fueling effect on filamentary
      transport and profiles without cryo-pumps
    \item<2> Compare profiles with the same fueling with/without cryopums
    \item<2> Determine an H-Mode with the cryopumps matching similar
      divertor pressure and SOL profiles
    \end{enumerate}
  \end{itemize}    
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_95$}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> We have comparable edge density and divertor neutral
        pressure 
      \item<3> At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

% \begin{frame}{Compare Similar fueling with/without cryopumps}
% \Fontvi
%   \vspace{-1cm}
% \begin{columns}
%   \begin{column}{0.65\textwidth}
%     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
%   \end{column}
%   \begin{column}{0.35\textwidth}
%     \begin{itemize}
%       \item<1-> Same fueling but with cryo-pumps. Clearly different in
%         terms of Edge density and Divertor pressure
%       \item<2-> Also with this amount of fueling any instance of SOL
%         saturation observed
%     \end{itemize}

%   \end{column}
% \end{columns}
% \end{frame}

% \begin{frame}{Matching scenarios with cryo-pumps}
% \Fontvi
%   \vspace{-1cm}
% \begin{columns}
%   \begin{column}{0.65\textwidth}
%     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34280}}
%   \end{column}
%   \begin{column}{0.35\textwidth}
%     \begin{itemize}
%       \item<1-> To match similar edge density and divertor pressure
%         and to reach the same level of detachment we increase the
%         fueling by almost a factor of 3, increasing also the rate. In
%         addition to that we also increase substantially the N puffing
%       \item<2-> Li-beam profile not yet produced for the same
%         shots. With a lower level of N (no detachment observed) the
%         SOL profiles does not flatten as in the case with the cryo-pumps
%     \end{itemize}
%   \end{column}
% \end{columns}
% \end{frame}

% \begin{frame}{Work in progress}
%   \begin{itemize}
%     \item Confirmed SXR spikes correlated with the start of ELMs,
%       strongly suggesting electron accelleration during ELM filament
%       eruption
%     \item Evaluation progressing in terms of fluctuation analysis from
%       MEM, Reflectometry, Li-Beam
%     \item GPI data available in different density scenarios and also
%       during L-H transition
%   \end{itemize}
% \end{frame}
\end{document}

### 2017-09-14 Experiments/AUG/analysis/python/scriptAnalysisShot.py
new version of figures

@@ -56,6 +56,7 @@ def print_menu():
     print "26. Compare Lparallel constant q95 constant Bt"
     print "27. Equilibria and Lparallel at constant q95"
     print "28. Equilibria and Lparallel at constant q95"
+    print "29. Fluctuations and PDF during Ip scan constant q95"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -1613,7 +1614,7 @@ while loop:
         for i in range(3):
             axLamL[i].set_xlabel(r'$\rho_p$')
             axLamL[i].set_xlim([0.98, 1.05])
-            axLamL[i].set_ylim([1e-3, 15])
+            axLamL[i].set_ylim([1e-2, 15])
             axLamL[i].axhline(1, ls='--', color='grey', lw=3)
             axLamL[i].legend(loc='best', numpoints=1, frameon=False, fontsize=14)
             axLamL[i].set_yscale('log')
@@ -1731,7 +1732,7 @@ while loop:
         for i in range(3):
             axLamL[i].set_xlabel(r'$\rho_p$')
             axLamL[i].set_xlim([0.98, 1.05])
-            axLamL[i].set_ylim([1e-3, 15])
+            axLamL[i].set_ylim([1e-2, 15])
             axLamL[i].axhline(1, ls='--', color='grey', lw=3)
             axLamL[i].legend(loc='best', numpoints=1, frameon=False, fontsize=14)
             axLamL[i].set_yscale('log')
@@ -1801,10 +1802,10 @@ while loop:
 
     elif selection == 27:
         sL = (34103, 34102, 34104)
-        fig, Ax = mpl.pylab.subplots(figsize=(10, 6),
-                                     nrows=1, ncols=2)
+        fig, Ax = mpl.pylab.subplots(figsize=(6, 10),
+                                     nrows=2, ncols=1)
         colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
-        fig.subplots_adjust(bottom=0.12, right=0.98)
+        fig.subplots_adjust(bottom=0.12, right=0.98, wspace=0.2, left=0.15)
         for shot, col, ip in zip(sL, colorLS, ('0.6', '0.8', '1')):
             Eq = eqtools.AUGDDData(shot)
             Eq.remapLCFS()
@@ -1870,10 +1871,10 @@ while loop:
 
     elif selection == 28:
         sL = (34105, 34102, 34106)
[…]

### 2017-09-14 Meetings/AUGrelated/interim_meeting_150917.tex
Update to the slides for AUG meeting 15 of September

@@
     \begin{enumerate}
-      \item<1> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
-      \item<1> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
+      \item<1-> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
+      \item<1-> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
     \end{enumerate}    

### 2017-09-14 Meetings/AUGrelated/interim_meeting_150917.tex
update to TeX file and inclusion of agenda to Minutes

@@
 
-\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_95$}
+\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
 \Fontvi
@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
+    \centering{\includegraphics<3->[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
 
@@
         pressure 
-      \item<3> At comparable edge density Upstream profiles are
+      \item<3-> At comparable edge density Upstream profiles are
         different with the tendency to develop shoulder easier at
         lower current
+      \item<4-> Still need to provide detail evolution of edge
+        profiles as a function
+        of $\Lambda_{div}$ which are different at different current
+        although same L$_{\parallel}$
+      \end{itemize}
+    \end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_t$}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
+    \centering{\includegraphics<3->[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
+
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1|only@1> We matched correctly the shape the parallel
+        connection length L$_{\parallel}$ is modified consistently
+      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
+        MA) whereas we reduced it at lower current to avoid early disruption
+      \item<2|only@2> We have comparable edge density and divertor neutral
+        pressure even though pressure increase earlier at higher current
+      \item<3-> At comparable edge density Upstream profiles are
+        different with the tendency to develop shoulder easier at
+        lower current
+      \item<4-> Still need to provide detail evolution of edge
+        profiles as a function
+        of $\Lambda_{div}$ which are different at different current
+        although same L$_{\parallel}$
       \end{itemize}

### 2017-09-14 Experiments/AUG/analysis/python/scriptAnalysisShot.py
modification to files and script for AUG analysis"

@@ -47,7 +47,7 @@ def print_menu():
     print "17. Compare shots same puffing with and wo cryompumps"
     print "18. Compare shots with/wo cryopumps try to match edge density"
     print "19. Compare Li-Beam contour profiles with/wo crypumps when trying to math edge density"
-    print "20. Compare Li-Be contour div/midplane puffing"
+    print "20. Compare Li-Be contour Lower/Upper divertor puffing"
     print "21. Compare Li-Be contour same fueling with/without cryo"
     print "22. Compare Shot constant q95 same edge density"
     print "23. Compare Li-Beam contour profiles with/wo crypumps, Density and Fueling"
@@ -57,6 +57,9 @@ def print_menu():
     print "27. Equilibria and Lparallel at constant q95"
     print "28. Equilibria and Lparallel at constant q95"
     print "29. Fluctuations and PDF during Ip scan constant q95"
+    print "30. Fluctuations and PDF during Ip scan constant Bt"
+    print "31. Fluctuations and PDF Cryo On/OFF"
+    print "32. Fluctuations and PDF Match Cryo ON/OFF"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -845,7 +848,7 @@ while loop:
 
     elif selection == 15:
         shotList = (34276, 34277)
-        pufL = ('Div', 'Mid')
+        pufL = ('Low Div', 'Up Mid')
         colorList = ('#C90015', '#7B0Ce7')
         fig, ax = mpl.pylab.subplots(figsize=(17, 17),
                                      nrows=4, ncols=2, sharex=True)
@@ -934,7 +937,7 @@ while loop:
                           bbox_to_inches='tight')
     elif selection == 16:
         shotList = (34276, 34277)
-        pufL = ('Div', 'Mid')
+        pufL = ('Low Div', 'Up Div')
         colorList = ('#C90015', '#7B0Ce7')
         fig, ax = mpl.pylab.subplots(figsize=(8, 10), nrows=2, ncols=1, sharex=True)
         fig.subplots_adjust(bottom=0.15)
@@ -1034,8 +1037,10 @@ while loop:
             ax[2, 1].set_ylabel(r'N$_2$ [10$^{21}$]')
             Uvs.close()
[…]

### 2017-09-15 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to figures with PdfStructures

@@ -2045,6 +2045,8 @@ while loop:
         axStr[0].set_ylabel(r'$\delta$I$_s$')
         ax.set_xlabel(r'$\Lambda_{div}$ @ $\rho = 1.01$')
         ax.set_ylabel(r'$\tau_{ac}[\mu$s]')
+        ax.set_xscale('log')
+        ax.set_ylim([0, 200])
         mpl.pylab.savefig('../pdfbox/PdfStructureCurrentScan_ConstantQ95.pdf',
                           bbox_to_inches='tight')
 
@@ -2112,6 +2114,8 @@ while loop:
         axStr[0].set_ylabel(r'$\delta$I$_s$')
         ax.set_xlabel(r'$\Lambda_{div}$ @ $\rho = 1.01$')
         ax.set_ylabel(r'$\tau_{ac}[\mu$s]')
+        ax.set_xscale('log')
+        ax.set_ylim([0, 200])
         mpl.pylab.savefig('../pdfbox/PdfStructureCurrentScan_ConstantBt.pdf',
                           bbox_to_inches='tight')
 

### 2017-09-15 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added comparison of fluctuations in H-mode with/without cryopumps

@@ -2174,7 +2174,7 @@ while loop:
         IpLabel = ('Off', 'On')
         colorL = ('#82A17E', '#1E4682')
         fig, ax = mpl.pylab.subplots(figsize=(8, 14), nrows=3, ncols=1)
-        fig.subplots_adjust(wspace=0.3, hspace=0.3)
+        fig.subplots_adjust(wspace=0.3, hspace=0.3, left=0.2)
 
         for shot, strokes, col, ip, _idx in zip(shotL, strokeL,
                                                 colorL, IpLabel, range(len(ax))):
@@ -2203,17 +2203,18 @@ while loop:
 
             
         ax[0].set_xlabel(r'$\tilde{I}_s/\sigma$')
-        ax[0].set_ylim([1e-4, 1])
+        ax[0].set_ylim([1e-4, 3])
         ax[0].set_yscale('log')
         ax[0].legend(loc='best', numpoints=1, frameon=False, fontsize=12)
         ax[1].set_xlabel(r't[$\mu$s]')
         ax[1].set_xlim([-50, 50])
-        ax[1].set_ylim([-0.02, 0.15])
+        ax[1].set_ylim([-0.02, 0.35])
         ax[1].legend(loc='best', numpoints=1, frameon=False, fontsize=12)
         ax[0].set_ylabel(r'Pdf')
         ax[1].set_ylabel(r'$\delta$I$_s$')
         ax[2].set_xlabel(r'$\Lambda_{div}$ @ $\rho = 1.01$')
         ax[2].set_ylabel(r'$\tau_{ac}[\mu$s]')
+        ax[2].set_xscale('log')
         mpl.pylab.savefig('../pdfbox/PdfStructureHmodeCryoOnOffMatch.pdf',
                           bbox_to_inches='tight')
 

### 2017-09-15 Experiments/AUG/analysis/python/scriptAnalysisShot.py
modification to scriptAnalysis

@@ -1482,16 +1482,19 @@ while loop:
         colorL = ('#82A17E', '#1E4682', '#DD6D3D')
         colorLS = ('#C90015', '#7B0Ce7')
         tList = (1.8, 2.4, 4.0)
-        fig = mpl.pylab.figure(figsize=(12, 12))
+        fig = mpl.pylab.figure(figsize=(12, 16))
         fig.subplots_adjust(hspace=0.25, right=0.86, top=0.98)
-        ax1 = mpl.pylab.subplot2grid((3, 2), (0, 0), colspan=2)
-        ax12 = mpl.pylab.subplot2grid((3, 2), (1, 0), colspan=2)
-        ax2 = mpl.pylab.subplot2grid((3, 2), (2, 0))
-        ax3 = mpl.pylab.subplot2grid((3, 2), (2, 1))
+        ax1 = mpl.pylab.subplot2grid((4, 2), (0, 0), colspan=2)
+        ax12 = mpl.pylab.subplot2grid((4, 2), (1, 0), colspan=2)
+        ax2 = mpl.pylab.subplot2grid((4, 2), (2, 0))
+        ax3 = mpl.pylab.subplot2grid((4, 2), (2, 1))
         axL = (ax2, ax3)
+        ax4 = mpl.pylab.subplot2grid((4, 2), (2, 0))
+        ax5 = mpl.pylab.subplot2grid((4, 2), (2, 1))
+        axD = (ax4, ax5)
         Cryo = ('No', 'On')
-        for shot, cc, _ax, _cr in itertools.izip(
-            shotList, colorLS, axL, Cryo):
+        for shot, cc, _ax, _ax2, _cr in itertools.izip(
+            shotList, colorLS, axL, axD, Cryo):
             
             Gas = neutrals.Neutrals(shot)
             ax1.plot(Gas.gas['D2']['t'], Gas.gas['D2']['data']/1e21,
@@ -1532,6 +1535,25 @@ while loop:
             _ax.set_xlabel(r't [s]')
             _ax.set_title(r'Shot # % 5i' %shot)
             _ax.set_ylim([0.99, 1.05])
+            try:
+                shotfile = dd.shotfile('RIC', shot)
+                En = shotfile('Ne_Ant4')
+                RicFake = np.zeros((En.time.size, 50))
+                for n in range(En.time.size):
+                    S = UnivariateSpline(En.area[n, :], En.data[n, :], s=0)
+                    RicFake[n, :] = S(rhoFake)
+
[…]

### 2017-09-15 Experiments/AUG/analysis/python/scriptAnalysisShot.py
modification to figures

@@ -1871,7 +1871,7 @@ while loop:
         fig, Ax = mpl.pylab.subplots(figsize=(6, 10),
                                      nrows=2, ncols=1)
         colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
-        fig.subplots_adjust(bottom=0.12, right=0.98, wspace=0.2, left=0.19)
+        fig.subplots_adjust(bottom=0.12, right=0.98, wspace=0.2, left=0.25)
         for shot, col, ip in zip(sL, colorLS, ('0.6', '0.8', '1')):
             Eq = eqtools.AUGDDData(shot)
             Eq.remapLCFS()
@@ -1940,7 +1940,7 @@ while loop:
         fig, Ax = mpl.pylab.subplots(figsize=(6, 10),
                                      nrows=2, ncols=1)
         colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
-        fig.subplots_adjust(bottom=0.12, right=0.98, wspace=0.2, left=0.19)
+        fig.subplots_adjust(bottom=0.12, right=0.98, wspace=0.2, left=0.25)
         for shot, col, ip in zip(sL, colorLS, ('0.6', '0.8', '1')):
             Eq = eqtools.AUGDDData(shot)
             Eq.remapLCFS()
@@ -2192,7 +2192,7 @@ while loop:
                           bbox_to_inches='tight')
 
     elif selection == 32:
-        shotL = (34276, 34278)
+        shotL = (34276, 34281)
         strokeL = ((3.75714, 3.80528), (3.73724, 3.83))
         IpLabel = ('Off', 'On')
         colorL = ('#82A17E', '#1E4682')
@@ -2207,8 +2207,9 @@ while loop:
             Turbo.blobAnalysis(Probe='Isat_m06', trange=[strokes[0], strokes[1]],
                                block=[0.012, 1])
                 # compute the corresponding Lambda at the location of the probe
-            rho, Lambda = Target.computeLambda(trange=[time[0], time[1]], Plot=False)
-            _iidx = np.where((Turbo.tPos >= time[0]) & (Turbo.tPos <= time[1]))[0]
+            rho, Lambda = Target.computeLambda(trange=[strokes[0],
+                                                       strokes[1]], Plot=False)
+            _iidx = np.where((Turbo.tPos >= strokes[0]) & (Turbo.tPos <= strokes[1]))[0]
[…]

### 2017-09-15 Meetings/AUGrelated/interim_meeting_150917.tex
Update to the presentation of 15-09-17

@@
 \date{15 September 2017}
-\author[Topic 21 Scientific Team]{N. Vianello and V. Naulin for the
+\author[N. Vianello]{N. Vianello and V. Naulin for the
   Topic 21 Scientific Team}
@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<3->[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
+    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
+    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}
 
@@
         pressure 
-      \item<3-> At comparable edge density Upstream profiles are
+      \item<3|only@3> At comparable edge density Upstream profiles are
         different with the tendency to develop shoulder easier at
         lower current
-      \item<4-> Still need to provide detail evolution of edge
+      \item<3|only@3> Still need to provide detail evolution of edge
         profiles as a function
@@
         although same L$_{\parallel}$
+      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
+        different current even though obtained at different values of $\Lambda_{div}$. 
+      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
+        $\Lambda_{div}$ without sensible difference among the current
       \end{itemize}
@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
-    \centering{\includegraphics<3->[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
-
+    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
+    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantBt}}
   \end{column}
@@
         pressure even though pressure increase earlier at higher current
-      \item<3-> At comparable edge density Upstream profiles are
+      \item<3|only@3> At comparable edge density Upstream profiles are
         different with the tendency to develop shoulder easier at
         lower current
-      \item<4-> Still need to provide detail evolution of edge
+      \item<3|only@3> Still need to provide detail evolution of edge
         profiles as a function
@@
         although same L$_{\parallel}$
+      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
+        different current even though obtained at different values of $\Lambda_{div}$. 
+      \item<4|only@4> Remarkable difference in the shape of typical
+        structure,  even though $\tau_{ac}$ follow usual trend apart
+        from very last points. \alert{To be double-checked}
       \end{itemize}
@@
 
-% \begin{frame}{Compare Similar fueling with/without cryopumps}
-% \Fontvi
-%   \vspace{-1cm}
-% \begin{columns}
-%   \begin{column}{0.65\textwidth}
-%     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
-%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
-%   \end{column}
-%   \begin{column}{0.35\textwidth}
-%     \begin{itemize}
-%       \item<1-> Same fueling but with cryo-pumps. Clearly different in
-%         terms of Edge density and Divertor pressure
-%       \item<2-> Also with this amount of fueling any instance of SOL
-%         saturation observed
-%     \end{itemize}
+\begin{frame}{H-Mode investigation: puffing location}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
+    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item Similar puff from Lower and Upper divertor valves
+        (\alert{we asked for divertor/midplane valves})
+      \item<2-> Edge density profiles from Li-Beam evolution are
+        pretty similar
+      \item<3|alert@3> Similar behavior observed from RIC Antenna 4
+        for the available shot
+    \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
 
-%   \end{column}
-% \end{columns}
-% \end{frame}
+\begin{frame}{Compare Similar fueling with/without cryopumps}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
+    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOff}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1-> Same fueling but with cryo-pumps. Clearly different in
+        terms of Edge density and Divertor pressure
+      \item<2-> Also with this amount of fueling no instance of SOL
+        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
+      \item<3> Comparison of fluctuations during the plunge at higher
+        density (\alert{ELM included}) reveal differences in
+        fluctuations. \alert{ELM resolved measurement to be properly done}
 
-% \begin{frame}{Matching scenarios with cryo-pumps}
-% \Fontvi
-%   \vspace{-1cm}
-% \begin{columns}
-%   \begin{column}{0.65\textwidth}
-%     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
-%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34280}}
-%   \end{column}
-%   \begin{column}{0.35\textwidth}
-%     \begin{itemize}
-%       \item<1-> To match similar edge density and divertor pressure
-%         and to reach the same level of detachment we increase the
-%         fueling by almost a factor of 3, increasing also the rate. In
-%         addition to that we also increase substantially the N puffing
-%       \item<2-> Li-beam profile not yet produced for the same
-%         shots. With a lower level of N (no detachment observed) the
-%         SOL profiles does not flatten as in the case with the cryo-pumps
-%     \end{itemize}
-%   \end{column}
-% \end{columns}
-% \end{frame}
+    \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
 
-% \begin{frame}{Work in progress}
-%   \begin{itemize}
-%     \item Confirmed SXR spikes correlated with the start of ELMs,
-%       strongly suggesting electron accelleration during ELM filament
-%       eruption
-%     \item Evaluation progressing in terms of fluctuation analysis from
-%       MEM, Reflectometry, Li-Beam
-%     \item GPI data available in different density scenarios and also
-%       during L-H transition
-%   \end{itemize}
-% \end{frame}
+\begin{frame}{Matching scenarios with cryo-pumps}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
+    %\centering{\includegraphics<3>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOffMatch}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1-> To match similar edge density and divertor pressure
+        and to reach the same level of detachment we increase the
+        fueling by almost a factor of 3, increasing also the rate. In
+        addition to that we also increase substantially the N puffing
+      \item<2-> Without cryopumps evidence of stronger SOL profile
+        flattening from Li-Be. \alert{To be compared with appropriate
+          variation of $\Lambda_{div}$}
+      % \item<3> Clear difference in the shape of I$_s$ structure and in
+      %   PDF although it is not yet \alert{ELM resolved}
+    \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{What is missing}
+  \Fontvi
+  \begin{enumerate}
+    \item RIC profiles with possible poloidal variation among the
+      antennas in particular in H-Mode. \textcolor{red}{To be done}
+    \item Li-Be ELM resolved profile variation with $\Lambda_{div}$
+      \textcolor{red}{To be done}
+    \item Li-Be fluctuations \textcolor{red}{To be done}
+    \item Structures size and velocities in L-Mode
+      \textcolor{orange}{In progress}
+    \item Radiation front movement \textcolor{orange}{In progress}
+    \item Can we have from stark-broadening the movement of density
+      front towards the X-Point \textcolor{red}{To be done, maybe not
+        feasible}
+    \item Neutrals analysis from D$_{\alpha}$ camera
+      \textcolor{orange}{In progress}
+    \item Fast-camera \textcolor{red}{To be done}
+    \item Other?
+  \end{enumerate}
+\end{frame}
+
+\begin{frame}{2018}
+  \textbf{Just a brainstorming exercise so far}
+  \begin{itemize}
+    \item X-point probe. Realistically there should be man-power for
+      proper operation and we need information below the midplane
+      before entering the divertor region
+    \item NPH evaluation of Ti
+    \item Parallel and perpendicular momentum variation at high
+      density. We already know there is a change in the perpendicular
+      flow to be complemented with parallel flow as well
+    \item Divertor modification? I guess SP movement is not feasible
+      in AUG but keeping the SP at the same position and moving the
+      X-point (vertically/radially) can induce some modification?
+    \item Increasing the density through pellet is feasible?
+    \item Isotope effect? In case campaign is foreseen we could change
+      parallel flow and recycling (?)
+  \end{itemize}
+\end{frame}
 \end{document}

### 2017-09-18 Meetings/AUGrelated/mst1_tfm_200917.tex
Started MST1-TFM presentation and change of figures

--- 2017-09-15 Meetings/AUGrelated/interim_meeting_150917.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=Topic 21,venue=Remote, date=15/09/2017, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=MST1-TFM,venue=Remote, date=20/09/2017, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{{\small Topic 21: AUG experiment analsysis meeting }}
-\date{15 September 2017}
+\title{{\small Topic 21: Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices }}
+\date{20 September 2017}
 \author[N. Vianello]{N. Vianello and V. Naulin for the
@@
 \begin{frame}{Summary of the campaigns}
-  \begin{itemize}[<+-|alert@+>]
-  \item L-Mode experiment, CW 17.
+  \begin{itemize}
+  \item<1-> L-Mode experiment, Calendar week
+    17. It will constitute baseline scenarios to be replicated on
+    the other MST1 devices. \textcolor{ta3scarletred}{Operation without cryopumps}
     \begin{enumerate}
-      \item<1-> Performed similar density ramps in an I$_p$ scan at constant q$_{95}$
-      \item<1-> Performed similar density ramps in an I$_p$ scan at constant B$_t$ 
+      \item<1-> \color<2->{ta3chameleon}{Performed similar density ramps in an I$_p$ scan at constant q$_{95}$}
+      \item<1-> \color<2->{ta3chameleon}{Performed similar density ramps in an I$_p$ scan at
+        constant B$_t$}
+      \item<1-> \color<2->{ta3chameleon}{Prepare scenarios for H-Mode operation}
       \end{enumerate}
-    \item H-Mode experiment, CW 21. 
+    \item<3-> H-Mode experiment, CW 21. 
       \begin{enumerate}
-    \item<2> Compare divertor/midplane fueling effect on filamentary
-      transport and profiles without cryo-pumps
-    \item<2> Compare profiles with the same fueling with/without cryopums
-    \item<2> Determine an H-Mode with the cryopumps matching similar
-      divertor pressure and SOL profiles
+      \item<3-> \color<4->{ta3scarletred}{Compare divertor/midplane fueling effect on filamentary
+        transport and profiles without cryo-pumps}
+      \item<3-> \color<4->{ta3chameleon}{Compare profiles with the same fueling with/without cryopums}
+      \item<3-> \color<4->{orange}{Determine an H-Mode with the cryopumps matching similar
+        divertor pressure and SOL profiles}
       \end{enumerate}
@@
     \begin{itemize}
+      \item<1|only@1> All the shots were performed in the so-called
+        Edge Optmized Configuration (EOC) shape
       \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$

### 2017-09-18 Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -1597,10 +1597,11 @@ while loop:
                   mpl.pylab.subplot2grid((4, 3), (3, 2)))
 
         for shot, col, tL in itertools.izip(
-            shotList, colorLS, tList):
+                shotList, colorLS, tList):
             # get the current and compute the average current in Ip
             Mag = dd.shotfile('MAG', shot)
-            _ii = np.where((Mag('Ipa').time >= 3) & (Mag('Ipa').time <= 3.3))[0]
+            _ii = np.where((Mag('Ipa').time >= 3) &
+                           (Mag('Ipa').time <= 3.3))[0]
             ip = Mag('Ipa').data[_ii]/1e6
             Mag.close()
             # this is the line average density
@@ -1608,7 +1609,8 @@ while loop:
             neEdge = diag('H-5')
             diag.close()
             ax1.plot(neEdge.time, neEdge.data/1e20, '-', color=col, lw=2,
-                     label = r'Shot # %5i' % shot +' I$_p$ = %2.1f' % ip.mean() +' MA')
+                     label=r'Shot # %5i' % shot  +
+                     ' I$_p$ = %2.1f' % ip.mean() + ' MA')
             ax1.set_ylim([0, 1])
             ax1.set_xlim([0, 4.5])
             # load the Li-Beam profiles
@@ -1628,36 +1630,41 @@ while loop:
                     S = UnivariateSpline(rhoP[n, ::-1],
                                          neLB[n, ::-1], s=0)
                     y[_iDummy, :] = S(rhoFake)/S(1)
-                _idx = np.where((neEdge.time >= t-0.02) & (neEdge.time <= t+0.02))[0]
+                _idx = np.where((neEdge.time >= t-0.02) &
+                                (neEdge.time <= t+0.02))[0]
                 enLabel = neEdge.data[_idx].mean()/1e20
                 ax.plot(rhoFake, np.mean(y, axis=0), '-', color=col,
-                              lw=3, label=r'$\overline{n_e}$ = %3.2f' % enLabel +
-                          ' I$_p$ = %2.1f' % ip.mean() +' MA')
-                ax.fill_between(rhoFake, np.mean(y, axis=0)-
-                                      np.std(y, axis=0), np.mean(y, axis=0)+
-                                      np.std(y, axis=0),
-                                      facecolor=col, edgecolor='none',
-                                      alpha=0.5)
[…]

### 2017-09-19 Experiments/AUG/analysis/python/scriptAnalysisShot.py
tweaks on figure for MST1 presentation

@@ -194,7 +194,7 @@ while loop:
         colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')        
 
         fig, ax = mpl.pylab.subplots(figsize=(17, 15),
-                                     nrows=3, ncols=2, sharex=True)
+                                     nrows=4, ncols=2, sharex=True)
         fig.subplots_adjust(hspace=0.05, top=0.96, bottom=0.1)
         for shot, _col, _idx in zip(shotList,
                                     colorLS, range(len(shotList))):
@@ -213,11 +213,19 @@ while loop:
             ax[1, 0].set_ylim([0, 10])
 
             ax[2, 0].plot(diag('H-1').time, diag('H-5').data/1e19, color=_col, lw=3)
-            ax[2, 0].set_xlabel(r't [s]')
+ 
             ax[2, 0].set_ylabel(r'$\overline{n}_e$ H-5 [10$^{19}$]')
             diag.close
             ax[2, 0].set_xlim([0, 4.5])
             ax[2, 0].set_ylim([0, 6])
+            ax[2, 0].axes.get_xaxis().set_visible(False)
+
+            diag = dd.shotfile('TOT', shot)
+            ax[3, 0].plot(diag('P_TOT').time, diag('P_TOT').data/1e6, color=_col, lw=3)
+            ax[3, 0].set_ylabel('P$_{tot}$ [MW]')
+            ax[3, 0].set_xlim([0, 4.5])
+            ax[3, 0].set_ylim([0, .8])
+            diag.close()
 
             diag = dd.shotfile('BPD', shot)
             ax[0, 1].plot(diag('Prad').time, diag('Prad').data/1e6, color=_col, lw=3,
@@ -236,10 +244,18 @@ while loop:
 
             ax[2, 1].plot(Gas.signal['F01']['t'],
                           Gas.signal['F01']['data']/1e21, color=_col, lw=3)
-            ax[2, 1].set_xlabel(r't [s]')
             ax[2, 1].set_ylabel(r'F01 [10$^{21}$m$^{-2}$s$^{-1}$]')
+            ax[2, 1].axes.get_xaxis().set_visible(False)
             diag.close
             ax[2, 1].set_xlim([0, 4.5])
+            diag = dd.shotfile('MAC', shot)
+            ax[3, 1].plot(diag('Tdiv').time, diag('Tdiv').data, color=_col, lw=3)
[…]

### 2017-09-20 Experiments/AUG/analysis/python/scriptAnalysisShot.py
modification to figures of evaluation of Lambda

@@ -1688,9 +1688,10 @@ while loop:
                          ' I$_p$ = %2.1f' % ip.mean() + ' MA')
                 axD.errorbar(rho, en/1e19, yerr=err/1e19,
                              fmt='none', ecolor=col)
-                rho, Lambda = Target.computeLambda(
+                rhoL, Lambda = Target.computeLambda(
                     trange=[t-0.015, t+0.015], Plot=False)
-                axL.plot(rho, Lambda, '-', lw=3, color=col,
+                axL.plot(rhoL[rhoL<rho.max()], Lambda[rhoL<rho.max()],
+                         '-', lw=3, color=col,
                          label=r'$\overline{n_e}$ = %3.2f' % enLabel +
                          ' I$_p$ = %2.1f' % ip.mean() + ' MA')
 
@@ -1704,7 +1705,7 @@ while loop:
         axEnL[0].set_ylabel(r'n$_e$/n$_e(\rho_p = 1)$')
         for i in range(3):
             axEnL[i].axes.get_xaxis().set_visible(False)
-            axEnL[i].set_xlim([0.98, 1.05])
+            axEnL[i].set_xlim([0.98, 1.04])
             axEnL[i].set_ylim([1e-1, 4])
             axEnL[i].set_yscale('log')
             leg = axEnL[i].legend(loc='best', numpoints=1,
@@ -1716,7 +1717,7 @@ while loop:
         axDivL[0].set_ylabel(r'n$_e[10^{19}$m$^{-3}]$')
         for i in range(3):
             axDivL[i].axes.get_xaxis().set_visible(False)
-            axDivL[i].set_xlim([0.98, 1.05])
+            axDivL[i].set_xlim([0.98, 1.04])
             axDivL[i].set_ylim([0, 6])
             leg = axDivL[i].legend(loc='best', numpoints=1,
                                    frameon=False, fontsize=14)
@@ -1726,8 +1727,8 @@ while loop:
         axLamL[0].set_ylabel(r'$\Lambda_{div}$')
         for i in range(3):
             axLamL[i].set_xlabel(r'$\rho_p$')
-            axLamL[i].set_xlim([0.98, 1.05])
-            axLamL[i].set_ylim([1e-1, 15])
+            axLamL[i].set_xlim([0.98, 1.04])
+            axLamL[i].set_ylim([1e-2, 15])
             axLamL[i].axhline(1, ls='--', color='grey', lw=3)
             leg = axLamL[i].legend(loc='best', numpoints=1,
[…]

### 2017-09-20 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the puffing location

@@ -60,6 +60,7 @@ def print_menu():
     print "30. Fluctuations and PDF during Ip scan constant Bt"
     print "31. Fluctuations and PDF Cryo On/OFF"
     print "32. Fluctuations and PDF Match Cryo ON/OFF"
+    print "33. Equilibria with arrow and location of Gas Puffing"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -2313,6 +2314,34 @@ while loop:
         mpl.pylab.savefig('../pdfbox/PdfStructureHmodeCryoOnOffMatch.pdf',
                           bbox_to_inches='tight')
 
+    elif selection == 33:
+        shotList = (34276, 34277)
+        pufL = ('Low Div', 'Up Mid')
+        colorList = ('#C90015', '#7B0Ce7')        
+        import map_equ
+        import equilibrium
+        rg, zg = map_equ.get_gc()
+        fig, ax = mpl.pylab.subplots(figsize=(5, 7), nrows=1, ncols=1)
+        fig.subplots_adjust(left=0.2)
+        for key in rg.iterkeys():
+            ax.plot(rg[key], zg[key], '-k')
+        for shot, col in zip(shotList, colorList):
+            Eq = equilibrium.equilibrium(device='AUG', time=3, shot=shot)
+            ax.contour(Eq.R, Eq.Z, Eq.psiN[:],
+                       np.linspace(0, 0.95, 10), colors=col, linestyles='-')
+            ax.contour(Eq.R, Eq.Z, Eq.psiN[:],
+                       np.linspace(1.01, 1.05, 5), colors=col, linestyles='--')
+            ax.contour(Eq.R, Eq.Z, Eq.psiN[:],
+                       [1], colors=col, linestyles='-', linewidths=3)
+
+        ax.set_xlabel('R(m)')
+        ax.set_ylabel('Z(m)')
+        ax.set_aspect('equal')
+        ax.arrow(1.25, 1.4, 0, -0.3, lw=4, color=colorList[1])
+        ax.arrow(2, -1.4, 0, 0.3, lw=4, color=colorList[0])
+        ax.text(2.4, 1.35, str(shotList[0]), color=colorList[0], fontsize=16)
+        ax.text(2.4, 1.2, str(shotList[1]), color=colorList[1], fontsize=16)
+        mpl.pylab.savefig('../pdfbox/PuffingLocation.pdf', bbox_to_inches='tight')
 
     elif selection == 99:
         loop = False

### 2017-09-20 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added figures for ELMs

@@ -61,6 +61,8 @@ def print_menu():
     print "31. Fluctuations and PDF Cryo On/OFF"
     print "32. Fluctuations and PDF Match Cryo ON/OFF"
     print "33. Equilibria with arrow and location of Gas Puffing"
+    print "34. ELMs and puffing same fueling with/without cryopumps"
+    print "35. ELMS and puffing different fueling with/without cryompumps"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -2342,6 +2344,63 @@ while loop:
         ax.text(2.4, 1.35, str(shotList[0]), color=colorList[0], fontsize=16)
         ax.text(2.4, 1.2, str(shotList[1]), color=colorList[1], fontsize=16)
         mpl.pylab.savefig('../pdfbox/PuffingLocation.pdf', bbox_to_inches='tight')
+
+    elif selection == 34:
+        shotList = (34276, 34278)
+        pufL = ('Off', 'On')
+        colorList = ('#C90015', '#7B0Ce7')
+        fig, ax = mpl.pylab.subplots(figsize=(10, 8), nrows=2,
+                                     ncols=1, sharex=True)
+        for shot, col, _idx, lab in zip(
+            shotList, colorList, range(len(shotList)),
+            pufL):
+            diag = dd.shotfile('MAC', shot)
+            Gas = neutrals.Neutrals(shot)
+            ax[_idx].plot(Gas.gas['D2']['t'], Gas.gas['D2']['data']/1e21, 'k',
+                          label='Cryo ' + lab)
+            ax[_idx].set_ylabel(r'D$_2$ [10$^{21}$s$^{-1}$]')
+            T = ax[_idx].twinx()
+            T.plot(diag('Ipolsola').time, -diag('Ipolsola').data/1e3, color='red')
+            T.set_ylabel(r'Ipolsola [kA]', color='red')
+            T.set_yticks([0, 10, 20, 30])
+            T.set_ylim([-10, 30])
+            for t in T.yaxis.get_ticklabels(): t.set_color('red')
+        ax[0].axes.get_xaxis().set_visible(False)
+        ax[1].set_xlim([0, 7])
+        ax[1].set_xlabel(r't[s]')
+        mpl.pylab.savefig('../pdfbox/PuffingIpolsola%5i' % shotList[0] +
+                          '_%5i' %shotList[1]+'.pdf', bbox_to_inches='tight')
+
+    elif selection == 35:
[…]

### 2017-09-20 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to Figures for Ipolsola

@@ -2356,11 +2356,12 @@ while loop:
             pufL):
             diag = dd.shotfile('MAC', shot)
             Gas = neutrals.Neutrals(shot)
-            ax[_idx].plot(Gas.gas['D2']['t'], Gas.gas['D2']['data']/1e21, 'k',
-                          label='Cryo ' + lab)
+            ax[_idx].plot(Gas.gas['D2']['t'], Gas.gas['D2']['data']/1e21, 'k')
             ax[_idx].set_ylabel(r'D$_2$ [10$^{21}$s$^{-1}$]')
+            ax[_idx].text(1, 16,'Cryo ' + lab, fontsize=16 )
             T = ax[_idx].twinx()
-            T.plot(diag('Ipolsola').time, -diag('Ipolsola').data/1e3, color='red')
+            T.plot(diag('Ipolsola').time, -diag('Ipolsola').data/1e3,
+                   color='red', rasterized=True)
             T.set_ylabel(r'Ipolsola [kA]', color='red')
             T.set_yticks([0, 10, 20, 30])
             T.set_ylim([-10, 30])
@@ -2384,11 +2385,12 @@ while loop:
             pufL):
             diag = dd.shotfile('MAC', shot)
             Gas = neutrals.Neutrals(shot)
-            ax[_idx].plot(Gas.gas['D2']['t'], Gas.gas['D2']['data']/1e21, 'k',
-                          label='Cryo ' + lab)
+            ax[_idx].plot(Gas.gas['D2']['t'], Gas.gas['D2']['data']/1e21, 'k')
             ax[_idx].set_ylabel(r'D$_2$ [10$^{21}$s$^{-1}$]')
+            ax[_idx].text(1, 16,'Cryo ' + lab, fontsize=16 )
             T = ax[_idx].twinx()
-            T.plot(diag('Ipolsola').time, -diag('Ipolsola').data/1e3, color='red')
+            T.plot(diag('Ipolsola').time, -diag('Ipolsola').data/1e3, color='red', 
+                   rasterized=True)
             T.set_ylabel(r'Ipolsola [kA]', color='red')
             T.set_yticks([0, 10, 20, 30])
             T.set_ylim([-10, 30])

### 2017-09-20 Meetings/AUGrelated/mst1_tfm_200917.tex
update To the Tex file for MST1 TFM
Final version of TFM presentation 20 September

@@
       \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
-        MA) whereas we reduced it at lower current to avoid early disruption
-      \item<2|only@2> We have comparable edge density and divertor neutral
-        pressure 
+        MA) whereas we reduced it at lower current to avoid early
+        disruption
+      \item<2|only@2> The total power (Ohmic plus NBI) was kept
+        constant throughout the scan
+      \item<2|only@2> We have comparable edge density, divertor neutral
+        pressure and divertor temperature
       \item<3|only@3> At comparable edge density Upstream profiles are
@@
   \begin{column}{0.65\textwidth}
-    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
-    \centering{\includegraphics<2-3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}}
+    \centering{\includegraphics<1>[height=0.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingLocation}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
+    \only<3>{
+      \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}
+        \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
+        \draw [->, ultra thick, white] (0.62, 0.45) -- (0.72, 0.55);
+      \end{tikzonimage}   
+    }
   \end{column}
@@
     \begin{itemize}
-      \item Similar puff from Lower and Upper divertor valves
+      \item<1-> Similar puff from Lower and Upper divertor valves
         (\alert{we asked for divertor/midplane valves})
-      \item<2-> Edge density profiles from Li-Beam evolution are
+      \item<2-> Discharge with a total amount 6.5 heating power
+        with equivalent behavior also in the lower divertor
+        independently from the puffing location
+      \item<3-> Edge density profiles from Li-Beam evolution are
         pretty similar
@@
     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
-    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}}
-    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOff}}
+    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
+    \only<3>{
+    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
+      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
+      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
+    \end{tikzonimage}}
+  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOff}}
   \end{column}
@@
     \begin{itemize}
-      \item<1-> Same fueling but with cryo-pumps. Clearly different in
-        terms of Edge density and Divertor pressure
-      \item<2-> Also with this amount of fueling no instance of SOL
+    \item<1-> Same fueling but with cryo-pumps
+      \item<1-> H-5 density is different and remain constant, both
+        divertor and midplane pressure are reduced (to 1/3
+        approximately) no sign of detachment
+      \item<2-> Different ELMy regimes reached with reduced size and
+        increased frequency without the crypumps
+      \item<3-> Also with this amount of fueling no instance of SOL
         saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
-      \item<3> Comparison of fluctuations during the plunge at higher
+      \item<4> Comparison of fluctuations during the plunge at higher
         density (\alert{ELM included}) reveal differences in
@@
     \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
-    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
-    %\centering{\includegraphics<3>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOffMatch}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
+    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
+    4\centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/PdfStructureHmodeCryoOnOffMatch}}
   \end{column}
@@
         fueling by almost a factor of 3, increasing also the rate. In
-        addition to that we also increase substantially the N puffing
-      \item<2-> Without cryopumps evidence of stronger SOL profile
+        addition to that we also increase substantially the N
+        puffing. \alert{Degraded H-Mode reached earlier in density
+          without the cryopumps}
+      \item<2-> Similar ELMy behavior obtained during the density ramp  
+      \item<3-> Without cryopumps evidence of stronger SOL profile
         flattening from Li-Be. \alert{To be compared with appropriate
           variation of $\Lambda_{div}$}
-      % \item<3> Clear difference in the shape of I$_s$ structure and in
-      %   PDF although it is not yet \alert{ELM resolved}
+       \item<4> The shape of the PDF is rather similar with closer
+         values of autocorrelation time at similar values of divertor
+         collisionality. \alert{Not yet ELM resolved}
     \end{itemize}
@@
   \Fontvi
+  The analysis is still in progress and we are not ready yet to draw
+  final conclusions. Among the future on going analysis we can list:
   \begin{enumerate}
@@
     \item Radiation front movement \textcolor{orange}{In progress}
-    \item Can we have from stark-broadening the movement of density
-      front towards the X-Point \textcolor{red}{To be done, maybe not
-        feasible}
-    \item Neutrals analysis from D$_{\alpha}$ camera
+    \item Evolution of divertor profiles from Spectroscopy
+      \textcolor{orange}{In progres}
+    \item Neutrals analysis from D$_{\alpha}$ camera combined with
+      KN1D code for evolution of neutrals
       \textcolor{orange}{In progress}
     \item Fast-camera \textcolor{red}{To be done}
-    \item Other?
   \end{enumerate}
@@
 
-\begin{frame}{2018}
-  \textbf{Just a brainstorming exercise so far}
-  \begin{itemize}
-    \item X-point probe. Realistically there should be man-power for
-      proper operation and we need information below the midplane
-      before entering the divertor region
-    \item NPH evaluation of Ti
-    \item Parallel and perpendicular momentum variation at high
-      density. We already know there is a change in the perpendicular
-      flow to be complemented with parallel flow as well
-    \item Divertor modification? I guess SP movement is not feasible
-      in AUG but keeping the SP at the same position and moving the
-      X-point (vertically/radially) can induce some modification?
-    \item Increasing the density through pellet is feasible?
-    \item Isotope effect? In case campaign is foreseen we could change
-      parallel flow and recycling (?)
-  \end{itemize}
-\end{frame}
 \end{document}

### 2017-10-12 Codes/python/general/timeseries.py
Various modification on timeseries which now handles the method with rmsNormalization

@@ -1,3 +1,5 @@
+from __future__ import print_function
+
 __author__ = 'N. Vianello and N. Walkden'
 __version__ = '0.2'
 __data__ = '19.04.2017'
@@ -7,39 +9,36 @@ import scipy
 import pycwt as wav
 import astropy.stats as Astats
 from scipy.interpolate import UnivariateSpline
+from scipy import signal
 import copy
+import bottleneck
 
 
 class Timeseries(object):
-    """
-    Python class for turbulent signal analysis
+    def __init__(self, signal, time, dtS=0.0002):
+        """
 
-    The class implement standard and non standard
-    methods for turbulent signal analysis
-
-    Parameters
-    ----------
-    signal : :obj:`ndarray`
-      signal to be analyzed
-    time  : :obj:`ndarray`
-      time basis
-
-
-    Attributes
-    ----------
-    dt : Floating. Sampling rate of the signal
-    nsamp : :obj:`int`. Size of the signal
-    signorm : :obj: `ndarray`
-        Normalized copy of the signal (signal-<signal>)/std(signal)
-    Dependences
-    -----------
-    numpy
-    scipy
-    pycwt https://github.com/regeirk/pycwt.git
-    astropy for better histogram function
-    """
-
-    def __init__(self, signal, time):
+        Parameters
+        ----------
+        signal : ndarray
+            signal to be analyzed
+        time : ndarray
+            time basis
+        dtS : floating
+            At the init we also compute a normalize
+            signal where normalization is of the form
+            (x-<x>)/std(x) where the mean and average
+            is a rolling mean and standard deviation on
+            a window of the time dtS/dt
+        Dependences
+        -----------
+            numpy
+            scipy
+            pycwt https://github.com/regeirk/pycwt.git
+            astropy for better histogram function
+            bottleneck (https://pypi.python.org/pypi/Bottleneck)
+            for moving average
+        """
 
         self.sig = copy.deepcopy(signal)
         self.time = copy.deepcopy(time)
@@ -50,6 +49,11 @@ class Timeseries(object):
         # foundamental quantities we compute them
         # at the initial
         self.moments()
+        _nPoint = int(dtS / self.dt)
+        self.rmsnorm = (
+                           self.sig -
+                           bottleneck.move_mean(self.sig, window=_nPoint)) / \
+                       bottleneck.move_std(self.sig, window=_nPoint)
 
     def moments(self):
         """
@@ -87,37 +91,45 @@ class Timeseries(object):
         except BaseException:
             return False
 
[…]

### 2017-10-12 Codes/python/tcv/tcvFilaments.py
modication to tcvFilaments which now works correctly with method basd on LIM and on THRESHOLD

@@ -6,13 +6,10 @@ from __future__ import print_function
 import MDSplus as mds
 import numpy as np
 from scipy.interpolate import UnivariateSpline
-from scipy import io
-from scipy import stats
-from scipy.signal import detrend as Detrend
+from scipy.interpolate import interp1d
 from scipy import constants
 import eqtools
-from langmuir import LP
-import tcv.diag.frp as frp
+import langmuir
 import timeseries
 import xarray as xray
 import bottleneck
@@ -41,22 +38,36 @@ class Turbo(object):
     export PATH="/home/vianello/NoTivoli/anaconda2/bin":$PATH
     and adding the following whenever you start python
     >>> import sys
-    >>> sys.path.append('/home/vianello/pythonlib/submodules/tcvpy')
+    >>> sys.path.append('/home/vianello/work/topic21/Codes/python/general')
+    >>> sys.path.append('/home/vianello/work/topic21/Codes/python/tcv')
 
        eqtools
        MDSplus
-       FastRP from tcvpy diagnostic
-       pandas
        bottleneck
-       xray
+       xarray
        langmuir
        scipy
        quickspikes
     """
 
     def __init__(self, shot, gas='D2', Lp='Div'):
+        """
+
+        Parameters
+        ----------
+        shot :
+            Shot number
+        gas :
+            String indicating the gas. 'D2','H','He'
+        Lp :
+            String indicating if the parallel connection
+            length should be considered from target to
+            midplane 'Mid' or from target to X-point
+            'Div'
+
+        """
         self.shot = shot
-        self.Lp=Lp
+        self.Lp = Lp
         # globally define the gas
         self.gas = gas
         if gas == 'D2':
@@ -77,29 +88,21 @@ class Turbo(object):
         self._eq = eqtools.TCVLIUQETree(self.shot)
         # this is the iP in the time bases of LIUQE
         self._tLiuqe = self._eq.getTimeBase()
-        self.Ip = self._eq.getIpMeas()
         self.BtSign = np.sign(self._eq.getBtVac().mean())
-        # this is for different quantities
-        self._tree = mds.Tree('tcv_shot', shot)
-        # average density node
-        self._enavgNode = self._tree.getNode(r'\results::fir:n_average')
         # now define the tree where the probe data are saved
         self._filament = mds.Tree('tcv_topic21', shot)
-#        self._doubleDir = '/home/tsui/idl/library/data/double/dpm' + \
-#                          str(int(self.shot)) + '_'
[…]

### 2017-10-13 Codes/python/tcv/tcvFilaments.py
local changes to tcvFilaments

@@ -1,0 +1,862 @@
+"""
+Global class for the analysis of the shot for Topic 21
+experiment based on the structure, lambda and profile analysis
+"""
+from __future__ import print_function
+import MDSplus as mds
+import numpy as np
+from scipy.interpolate import UnivariateSpline
+from scipy import io
+from scipy import stats
+from scipy.signal import detrend as Detrend
+from scipy import constants
+import eqtools
+from langmuir import LP
+import tcv.diag.frp as frp
+import timeseries
+import xarray as xray
+import bottleneck
+import quickspikes as qs
+
+
+class Turbo(object):
+    """
+    Python class for the evaluation of
+    different quantities and analysis for
+    the TCV15-2.2-3 Filamentary studies.
+    It does have a lot of dependences
+    Inputs:
+    ------
+       shot = shot number
+       gas = 'D2' (Default), 'H', 'He' according to the gas
+              used
+       Lp = 'Div' (Default), 'All' it states if the Lparallel
+             used in the computation is the Lp from LFS target to
+             X-point (the )
+
+    Dependencies:
+    ------------
+    On lac all the dependencies can be solved by adding the
+    following to your .bashrc
+    export PATH="/home/vianello/NoTivoli/anaconda2/bin":$PATH
+    and adding the following whenever you start python
+    >>> import sys
+    >>> sys.path.append('/home/vianello/pythonlib/submodules/tcvpy')
+
+       eqtools
+       MDSplus
+       FastRP from tcvpy diagnostic
+       pandas
+       bottleneck
+       xray
+       langmuir
+       scipy
+       quickspikes
+    """
+
+    def __init__(self, shot, gas='D2', Lp='Div'):
+        self.shot = shot
+        self.Lp=Lp
+        # globally define the gas
+        self.gas = gas
+        if gas == 'D2':
+            self.Z = 1
+            self.mu = 2
+        elif gas == 'H':
+            self.Z = 1
+            self.mu = 1
+        elif gas == 'He':
+            self.Z = 4
+            self.mu = 4
+        else:
+            print('Gas not found, assuming Deuterium')
+            self.gas = 'D2'
+            self.Z = 1
+            self.mu = 2
+        # equilibrium quantities
+        self._eq = eqtools.TCVLIUQETree(self.shot)
+        # this is the iP in the time bases of LIUQE
+        self._tLiuqe = self._eq.getTimeBase()
+        self.Ip = self._eq.getIpMeas()
+        self.BtSign = np.sign(self._eq.getBtVac().mean())
[…]

### 2017-10-13 Codes/python/tcv/tcvFilaments.py
local changes to tcvFilaments

@@ -117,7 +117,9 @@ class Turbo(object):
         :param Z: int. Effective charge
         :param iwin: int. Half of the window for Conditional Average Sampling
            in number of points
-        :param thr: Threshold for the evaluation of the blob
+        :param thr: Threshold for the evaluation of the blob, This is given in
+           standard deviation unit (i.e. giving thr=3 implies we search for values
+           above 3 sigma plus the mean)
         :param normalize: Boolean. If True (default) normalize to local std
            each of the window before average
         :param detrend: Boolean. If False (default) does not perform a linear

### 2017-10-13 Meetings/TCVrelated/tcvmeeting_131017_vianello.tex
Added the slides for the meeting of 13 October

--- 2017-06-23 Meetings/TCVrelated/mondaymeeting_260617_vianello.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=TCV-Topic21 KoM,venue=Lausanne, date=15/05/2017, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=TCV-Topic21 Interim,venue=Lausanne, date=13/10/2017, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Topic 21 experiment Week 24}
-\date{26 June 2017}
-\author[Topic 21 ST]{N . VianTllo and V. Naulin for the
+\title{Topic 21 experiment}
+\date{13 Octobe 2017}
+\author[Topic 21 ST]{N . Vianello and V. Naulin for the
   Topic 21 SC team}
@@
 \maketitle
-\begin{frame}{Scientific Team}
-  \begin{description}
-  \item[EPFL:] H. De Oliveira, R. Maurizio, B. Labit,
-    C. Tsui, K. Verhaegh, H. Reimerdes, C. Theiler
-  \item[DTU:] J.J. Rasmussen and V. Naulin
-  \item[RFX:] N. Vianello, M. Spolaore, M. Agostini
-  \item[OEAW:] B. Schneider, S. Costea, R. Schrittwieser
-  \item[CCFE:] F. Militello
-  \item[JSI:] J. Kovacic
-  \end{description}
-\end{frame}
 \begin{frame}{TCV experiments: boundary condition}
@@
   \end{enumerate}
-\item We have a total number of \textbf{\# 23 Shots} originally split into two
-    operational window. Calendar week 24 (12.06-16.06) and Calendar
-    week 43 (23.10-27.10)
+\item We still have a \# 18 Shots available between Week 43 and 44
 \end{itemize}
@@
 
-\begin{frame}{Experimental plan}
-\Fontvi
-    \alert{For the first week of operation we originally planned L-mode shots
-      only. Shots 1-3 I$_p$ scan at constant toroidal field. Shots
-      1, 4 and 5 I$_p$ scan at constant q$_{95}$ to be compared with
-      analogous experiments in AUG and MAST-U. Shots 6-7 Low
-      collisionality scan. Shots 8-9 DN current scan: this will be
-      compared directly with Mast-U which will run predominantly in DN
-    configuration. Shot 10-11 Current scan in forward field to check
-    the role of $\nabla\times B$ direction.}
-\begin{enumerate}
-\item Shape from 57088, I$_p$ = 245 kA,  Reverse B$_t$,
-    density ramp from Line Average Density = 3.8e19 @ 0.5 s to 11e19 @ 1.6s,  Bt = 1.4T. Plunge @ 0.65, 1.52
-\item  Repeat \# 1 with I$_p$=330 kA Bt=1.4T, same density ramp, same timing for plunges
-\item  Repeat \# 1 with I$_p$=180 kA, Bt=1.4T, same density ramp, same timing for plunges
-\item  Repeat \# 1 with q95=2.44 as \# 2, adjust Bt consequently (Bt = 1.02T)
-\item  Repeat \# 3 with q95=2.44 as \# 2, adjust Bt consequently (Bt=0.8T)
-\item  Shape and current from \# 1. Stop puffing once the divertor is
-  formed to get low collisionality case. ECRH ramp from 0.9s (150
-  kW--500 kW)
-\item  Repeat \# 6 with intermediate density value between \# 6 and
-  \#1 density at 0.65s. 
-\item  Repeat density ramp of Shot \# 2 in DN configuration 
-\item  Repeat density ramp of Shot \# 3 in DN configuration 
-\item Repeat \# 1 in forward field
-\item Repeat \# 3 in forward field
-\end{enumerate}
-\end{frame}
-
-\begin{frame}{Current scan at constant B$_{\phi}$}
-\Fontvi
-  \begin{columns}[c]
-    \begin{column}{0.7\textwidth}
-      \includegraphics<1>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
-      \includegraphics<2>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantBtSOL}
-      \includegraphics<3>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantBt}
-    \end{column}
-    \begin{column}{0.3\textwidth}
-      \begin{itemize}
-        \item Confirming results from Topic-25 increasing the current
-          reduces the ion flux rollover density threshold
-        \item Neutral compression seems slightly reduced at higher current
-        \item<2-> Profiles from RCP are not yet clear, with the only
-          robust variation between 245 and 330 kA
-        \item<3-> If we combine with Thomson scattering there are still
-          unresolved issue
-        \end{itemize}
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}{Current scan at constant q$_{95}$}
-\Fontvi
-  \begin{columns}[c]
-    \begin{column}{0.7\textwidth}
-      \includegraphics<1>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
-      \includegraphics<2>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantQ95SOL}
-      \includegraphics<3>[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/DensityProfileCurrentScanConstantQ95}
-    \end{column}
-    \begin{column}{0.3\textwidth}
-      \begin{itemize}
-        \item Unusual scenarios with B$_{phi}$ up to 0.8T. \alert{No rollover
-          on at any of the current}
-        \item Expected higher target neutral pressure increase at
-          higher current
-        \item<2-> Profiles from RCP suggest slight flattening in the
-          far SOL at higher current
-        \item<3-> Confirmed even combining with Thomson data
-        \end{itemize}
-    \end{column}
-  \end{columns}
-\end{frame}
-\begin{frame}{Attempt for low collisionality}
-  \begin{columns}[c]
-    \begin{column}{0.7\textwidth}
-      \includegraphics[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/LowCollisionalityAttempt}
-    \end{column}
-    \begin{column}{0.3\textwidth}
-      All the attempt to perform a low collisionality case disrupted
-      whenever density decreases below a certain threshold
-    \end{column}
-  \end{columns}
-\end{frame}
-
-\begin{frame}{Conclusion}
+\begin{frame}{Accomplished program with respect to foreseen one}
   \Fontvi
@@
 
+\begin{frame}{Current scan at constant B$_{\phi}$}
+\Fontvi
+  \begin{columns}[c]
+    \begin{column}{0.6\textwidth}
+      \includegraphics<1>[width=7.cm]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
+      \includegraphics<2>[height=0.8\textheight]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}
+      \includegraphics<3>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}
+      \includegraphics<4>[width=6.cm]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item Confirming results from Topic-25 increasing the current
+          reduces the ion flux rollover density threshold
+        \item Neutral compression seems slightly reduced at higher current
+        \item Ohmic power different but power radiated from the LFS
+          divertor seems similar among the shots
+        \item Comparable H$_{\alpha}$ emission from target
+        \item<2-> Profiles from RCP suggests that at lower I$_p$
+          flattening is easier even with similar values of $\Lambda_{div}$
+        \item<3-> Confirmed by similar observation in AUG
+        \item<4> No clear evidences in terms of blob-size actually but
+          analysis is limited to a single spatial region (5-10 mm from
+          the separatrix) 
+        \end{itemize}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Current scan at constant q$_{95}$}
+\Fontvi
+  \begin{columns}[c]
+    \begin{column}{0.6\textwidth}
+      \includegraphics<1>[width=7.cm]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
+      \includegraphics<2>[height=0.8\textheight]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}
+      \includegraphics<3>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}
+      \includegraphics<4>[width=7.cm]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item Unusual scenarios with B$_{phi}$ up to 0.8T. \alert{No rollover
+          on at any of the current}
+        \item Expected higher target neutral pressure increase at
+          higher current
+        \item<2-> Profiles from RCP does not exhibit a clear trend
+          with the current. \alert{We should increase the number of
+            points in reciproation. We lack at high density at low
+            current or eventually a point at even higher current}
+        \item<3|only@3> In AUG the things are different and even with the
+          same q$_{95}$ flattening is easier at lower current
+        \item<4> No clear evidences in terms of blob-size actually but
+          analysis is limited to a single spatial region (5-10 mm from
+          the separatrix)
+        \end{itemize}
+    \end{column}
+  \end{columns}
+\end{frame}
+\begin{frame}{Attempt for low collisionality}
+  \begin{columns}[c]
+    \begin{column}{0.7\textwidth}
+      \includegraphics[width=8.cm]{../../Experiments/TCV/analysis/pdfbox/LowCollisionalityAttempt}
+    \end{column}
+    \begin{column}{0.3\textwidth}
+      All the attempt to perform a low collisionality case disrupted
+      whenever density decreases below a certain threshold
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{To be done}
+  \Fontvi
+  \begin{enumerate}
+    \item \textcolor{orange}{ Evaluation of parallel flow profile (in
+    progress)}
+  \item \textcolor{orange}{ Further statistical analysis on RCP}
+  \item \textcolor{red}{We could repeat a couple of shots with wall
+      mounted probe in J$_{sat}$ for statistics at the wall to be
+      compared with AUG}
+  \item \textcolor{red}{DSS and multicam analysis}
+  \end{enumerate}  
+\end{frame}
+
+\begin{frame}{To be done in L-Mode}
+  \Fontvi
+  \begin{enumerate}
+\item  Low collisionality case useful for baseline scenario with no
+  shoulder at all
+\item  A point at higher current at constant B$_{\phi}$ (I don't think
+  we have still room for reducing the field further)
+\item  Repeat density ramp of Shot \# 2 in DN configuration at fixed B$_{\phi}$
+\item  Repeat density ramp of Shot \# 3 in DN configuration at fixed B$_{\phi}$
+\item  2 Shots for performing a current scan in forward B field
+\end{enumerate}
+\end{frame}
+
+\begin{frame}{To be done in H-Mode}
+  \Fontvi
+  \begin{columns}[c]
+    \begin{column}{0.5\textwidth}
+      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}
+    \only<2->{
+      \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}
+        \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
+        \draw [->, ultra thick, white] (0.62, 0.45) -- (0.72, 0.55);
+      \end{tikzonimage}   
+    }
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+        \item This is the scenario obtained in AUG without cryo-pump
+          which is the best comparison possible with TCV. Density ramp
+          together with N seeding for divertor cooling up to the
+          degraded H-Mode
+          \item<2-> This clearly exhibits a saturation of SOL profile
+            which is our target
+          \item<3> We will hear from Benoit and Christian which are
+            the reliable scenarios which can actually been obtained so
+            far on TCV
+        \end{itemize}
+    \end{column}
+  \end{columns}
+\end{frame}
 \end{document}

### 2017-11-06 Experiments/TCV/analysis/python/scriptAnalysis.py
new figures concernign the comparison between target profiles

@@ -40,6 +40,10 @@ def print_menu():
     print "17. Compare upper/lower divertor front movement DN discharges"
     print "18. Compare current scan at constant Bt forward/reverse Bt"
     print "19. Compare current scan at constant Bt LSN/DN"
+    print "20. Compare DN/LSN profiles evolution Ip=190kA"
+    print "21. Compare DN/LSN profiles evolution Ip=330kA"
+    print "22. Compare FF/RF profiles evolution Ip=190kA"
+    print "23. Compare FF/RF profiles evolution Ip=330kA"
     print "99: End"
     print 67 * "-"
 
@@ -1875,10 +1879,223 @@ while loop:
         inS.set_xlim([0.6, 1.2])
         inS.set_ylim([-0.75, -0.25])
         inS.axis('off')
-        
-        
         mpl.pylab.savefig('../pdfbox/CompareLSN-DN.pdf',
                           bbox_to_inches='tight')
+    elif selection == 20:
+        # we plot the profiles before and
+        # after roll-over mediated
+        shotList = (57437, 58623)
+        Type = ('LSN', 'DN')
+        colorList = ('#BE4248', '#586473')
+        fig = mpl.pylab.figure(figsize=(12, 9))
+        fig.subplots_adjust(wspace=0.3, hspace=0.3,
+                            top=0.96, right=0.98, bottom=0.15)
+        ax = mpl.pylab.subplot2grid((2, 2), (0, 0), colspan=2)
+        ax1 = mpl.pylab.subplot2grid((2, 2), (1, 0))
+        ax2 = mpl.pylab.subplot2grid((2, 2), (1, 1))
+        for shot, col, ty in zip(shotList, colorList, Type):
+            Target = langmuir.LP(shot, Type='floor')
+            Tree = mds.Tree('tcv_shot', shot)
+            eNode = Tree.getNode(r'\results::fir:n_average')
+            enF = interp1d(signal.decimate(
+                eNode.getDimensionAt().data(), 10),
+                           signal.decimate(eNode.data(), 10)/1e19,
+                           fill_value='extrapolate')
+            ax.plot(enF(Target.t2), Target.TotalSpIonFlux()/1e27,
+                    color=col, label='# %5i' % shot + ' ' + ty)
+            ax.axvspan(4, 5, ec='white', color='grey', alpha=0.5)
[…]

### 2017-11-06 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Added slides for GPM

\documentclass[10pt, compress]{beamer}
\usetheme[conference=MST1-GPM17,venue=Culham, date=14/11/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{{\small Filamentary transport in high-power H-mode conditions and in
  no/small-ELM regimes to predict heat and particle loads on PFCs for
  future devices}}
\date{{\footnotesize 14 November 2017}}
\author[N. Vianello and V. Naulin]{N. Vianello, V. Naulin for Topic-21
Scientific Team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}
\textbf{Include scientific team and logos}
\end{frame}

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Objectives:
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$
\item \only<2>{\color{orange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor conditioon
\item \only<2>{\color{orange}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{orange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{orange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{red}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenarion in high-density NBH heated plasma on TCV has been established
}
\end{frame}

% \begin{frame}{Outline}
% 	\begin{itemize}
% 		\item Background 
% 		\item Plans (we will not make a detailed list of the
%                   proposal, we already tried to combine and summarize them)
% 		\item Discussion
% 	\end{itemize}	
% \end{frame}

% \section{Background}
% \begin{frame}{Present status}
%   \setbeamercovered{transparent}
%   \begin{enumerate}[<+(1) | invisible@-+>]
%     \item Experimental and theoretical investigations suggest that SOL density profiles are
%       determined by the balance between radial filamentary transport and parallel dynamics
%     \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
%     \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
%       TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
%     \item Observations exhibit various other dependencies e.g., divertor
%       collisionality, plasma current, seeding. \alert{Results from
%         different devices not fully reconciled and the underlying mechanism is not fully understood.}
%     \item Studies of shoulder formation in H-Mode are so far limited 
% 	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
% %    \item First we will report a summary of the achievements and then
%  %    personal comments and plans
%     \end{enumerate}
% \end{frame}
% \section{L-Mode}
% \begin{frame}{L-Mode studies: AUG/1}
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
%         \begin{equation*}
%         \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
%       \end{equation*}
%       controls filaments size
%         \item<2-> \textcolor{red}{Tested by changing n$_e$
%             and $T_e$ through fueling/seeding/heating}
%         \item<3-> This determines a change of the velocity-size
%           scaling from
%             \textcolor{ta3chameleon}{sheath-limited}
%         to \textcolor{blue}{inertial regime}.
%        \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
%            length}}
%        \item<5> This finally determines the shoulder formation
%         \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \only<1-2>{
%       \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15a}
%           \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
%         \only<2>{
%           \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
%         }
%       \end{tikzonimage}}
%     \only<3-4>{
%       \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15b}
%           \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
%           \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
%       \end{tikzonimage}
%     }
%     \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15c}
%     \end{column}
%   \end{columns}
% \end{frame}

% \begin{frame}{L-Mode studies: AUG/2}
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1-> Profile modified by an increase of blob-size and change of
%         \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
%         \onslide<2->{\textcolor{blue}{and filament relative density}
%           {\footnotesize (Carralero 2016 in preparation)}}
%       \item<3-> As a consequence the contribution of filaments to
%         radial transport increases
%       \item<4|only@4> \alert{Beware the change of frequency may be due to a
%         modification of fluctuation velocity which is known to vary
%         with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
%       \item<5> Parallel flow is strongly reduced whenever we increase
%         the divertor collisionality
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16b}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16c}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/AgostiniNF2011}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16d}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode studies:AUG/3}
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1-> Electron and ions behave differently
%       \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
%         accross the SOL and slightly affected by the increase of
%         divertor collisionality
%       \item<3|only@3> Ions are strongly affected: for
%         \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
%           and $\lambda_{T_i} \sim 30$
%           mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
%           T$_{i, bk}\sim 25$ eV
%           and $\lambda_{T_i} \sim 8$ mm}
%        \item<4-> Ion energy spectrum from
%          $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
%          energy for $\Lambda_{div} > 1$
%        \item<5> EMC3-Eirene simulation suggests that such a reduction
%          can't be accounted for thermalization process. An
%          \alert{ionization front builds in front of the limiter shadow}   
%        \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16e}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16f}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16g}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16h}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode: TCV}
%     \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
%         dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
%         \begin{equation*}
%           f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
%         \end{equation*}
%         in ohmic density ramps \parencite{vianello:iaea2016}
%       \item<2|only@2> Slight variation of density profiles at the target but
%         due to direct dependence on L$_{\parallel}$ large increase of
%         $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
%         we reach a certain amount of $\langle n_e \rangle$}
%        \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
%         \onslide<4-5>{\textcolor{red}{also on a statistical
%             basis}}. \onslide<5>{Strong dependence on average density,
%           independent of L$_{\parallel}$}}
%        \item<6|only@6> $\lambda_n$ depends clearly on blob-size
%          whereas the dependence on divertor condition is less
%          obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16a}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16b}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16c}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16d}
%         \includegraphics<6>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16e}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode: JET}
%     \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1|only@1> The shoulder formation strongly depends on
%         divertor geometry, disappear with vertical target and strike
%         point closest to cryogenics pumps \parencite{Wynn:EPS2016}
%       \item<2|only@2> The midplane pressure from baratrons is
%         equivalent between the different divertor. \alert{This would
%           indicate that SOL neutral density at the outboard midplane does not play any role}
%        \item<3|only@3> In the horizontal target configuration the
%          results indicate that the shoulder forms right at the
%          transition from sheath-limited to high-recycling where also
%          $\Lambda_{div}$ strongly increase
%        \item<4|only@4> Shoulder amplitude correlates with strike
%          points position. \alert{Shoulder, ionization and
%            $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
%          from the pump}
%        \item<5|only@5> In seeded discharges the transition observed at
%          very high level of $\Lambda_{div} >> 1$
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16b}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16c}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16d}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16e}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode: MAST}
%     \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1|only@1> Strong dependence on
%         I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
%         constant toroidal field shoulder disappears. Consistent with
%         observation in other devices
%       \item<2|only@2> Filaments binormal dimension increases with
%         current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
%        \item<3|only@3> Filament radial velocity decreases with current
%          as well as the radial dimension \parencite{Kirk:2016jj}
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MilitelloNF16a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16a}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16c}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \section{H-Mode}
%   \begin{frame}{AUG: H-Mode}
%     \begin{columns}
%     \begin{column}{0.4\textwidth}
%       \begin{itemize}
%       \item<1|only@1> SOL profiles in H-Mode so far investigated on
%         AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
%       \item<2|only@2> Differently from L-Mode, complete detachment
%         suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
%        \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
%          shoulder depends on a combination of $\Lambda_{div}$ and
%          fueling rate. Complete detachment seems instead not necessary
%          although very weak shoulder
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.6\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MuellerJNM15a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/SunPPCF15a}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16i}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \section{Open issues}
%   \begin{frame}{Open and unresolved issues}
%   \setbeamercovered{transparent}
%   \begin{enumerate}[<+(1) | invisible@-+>]
%     \item Does $\Lambda_{div}$ unify the picture among the devices?
%       \alert{No, does neutral pressure play a role?}
%     \item If neutrals play a role is it at the divertor and/or at the midplane?
%       \alert{Contradictory results if one include experiments with
%         midplane puffing, JET and EIRENE simulations}
%     \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
%       dependence from f$_x$ scan but both TCV and MAST observe an
%       I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
%       increases with L$_{\parallel}$ }
%     \item Is cooling the divertor with fueling or seeding equivalent? \alert{Contradictory observations in AUG and JET}
%     \item Do we observe same behavior in L and H-Mode? \alert{So
%       far no as shown in H-Mode AUG. We need higher detachment
%       condition and we need enough fueling}
%       \item Is the density shoulder accompanied with an ion temperature shoulder?
% %      \item What are the underlying mechanisms? 
%     \end{enumerate}
%   \end{frame}

% \section{Topic 21 experiments }
% \begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
% 	\begin{itemize}
% 		\item 15 were proposals submitted to Topic 21
% 		\item Proposals include experiments on all three machines 
% 		\item There are overlaps between several of the proposals 
% 		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 
% 		\item However, total number of proposed shots:  \textbf{449}
% 		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
% 		\item Reaching all goals is not possible with the current number of allocated shots.
% 	\end{itemize}
% \end{frame}

% \begin{frame}{Focal points}
% \begin{itemize}
% 	\item MST1 uniquely facilitates cross comparison between machines
% 	\item Several of the proposed experiments overlap and will be combined
% 	\item A cross machine experiment has the makings of settling open issues
% 	\item Therefore, we will allocate shots for cross-machine
%           comparison but we must strive after similar machine configuration
% 	\item ....but also to other proposed experiments
% 	\item Cross machine L-mode experiments: 
% 	\begin{enumerate}
% 		\item Investigate the role of neutrals 
% 		\item $I_p$ and $q_{95}$ scans
% 	\end{enumerate}
% 	\item Cross machine H-mode experiments. 
% \end{itemize}	
% \end{frame}

% \begin{frame}{L-mode experiments}
% 	\begin{itemize}
% 		\item The role of neutrals in the shoulder
%                   formation is not understood
%                   {\scriptsize(proponents: Carralero (\# 7), Militello
%                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9))}
% 		\begin{enumerate}
% 		\item We envisage to measure neutral gas profiles at the outboard midplane
%                   using fast cameras with D$_{\alpha}$ filter, density
%                   and temperature SOL profiles and appropriate code
%                   (e.g. KN1D as in \parencite{Lipschultz:2005gg,Lipschultz:2016vk})
% 		\item Reciprocating probes and profiles available on
%                   all machines
%                 \item Investigate role of fueling location (MAST)
% 		\end{enumerate}
% 		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$.
%                   {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, Carralero (\# 7), Militello
%                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9), Tsui
%                     (\# 15))}
% 		\begin{enumerate}
% 			\item Carry out parameter scans on all machines

% 		\end{enumerate}
% 	\end{itemize}
% \end{frame}

% \begin{frame}{H-mode experiments}
% \begin{itemize}
% 	\item ITER and DEMO will operate in H-mode
% 	\item We must know what parameters control shoulder formation 
% 	\item Shoulder formation parameter regime is unclear on all machines
% 	\item Main priorities: 
% 	\begin{enumerate}
% 		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
% 		\item Investigate the SOL (filamentary) transport properties.
%                   Whenever main diagnostic is reciprocating probes $\rightarrow$ limits heating power
% 		\item Experiments must gradually increase power and density. 
% 	\end{enumerate}
% 	\item Fueling in H-mode is problematic due to transport
%           barrier. Is there a way to overcome it? NBI, pellet fueling?
% 	\item H-mode density limit \parencite{Bernert:2015bq} must be dealt with
% \end{itemize}

% \end{frame}

% \begin{frame}{Optimizing cross machine comparison}
% \begin{itemize}
% 	\item Machines are fundamentally differently designed
% 	\item Strive for similar configurations of the machines:
% 	\begin{enumerate} 
% 		\item Single-Null
% 		\item $\bm{B} \times \nabla B$ towards active divertor 
% 		\item Strike-point and cryo pump location (AUG and MAST-U)
% 		\item Heating 
% 		\item Fueling location 
% 		\item Seeding (species, location, rate)
% 	\end{enumerate}
% \end{itemize} 
% %things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,

% \end{frame}

% \begin{frame}{Required diagnostics and competences}
% In order to compare experiments the following diagnostics must be available: 
% \begin{enumerate}
% 	\item Filaments analysis in the Outboard midplane: 
% 	\begin{itemize} 
% 		\item Through Reciprocating probe then $I_{sat}$  on minimum three pins poloidally and radially separated
% 		 (filaments speed and size). 
% 		\item Electron temperature (fast T$_e$ measurements
%                   can be achieved with BPP in MAST-U {\footnotesize
%                     (N. Walkden \#11)})
% 		\item If possible $M_{\|}$
% 	 \end{itemize}
% 	 \item Camera viewing OM for measuring neutrals 
% 	 \item Divertor measurements of $n$ and $T_e$ (probes) plus
%            spectroscopy and bolometry 
% 	 \item Density profile measurements (Li-Bes, Reflectometry (\#
%            6 Acquiam, \# 8 Vicente), Edge Thomson scattering) 
%          \item Sami and Field for fast particles accelleration (piggy
%            back on developed scenarion \# 4 McClements)
% %	\item H-mode quality diagnostics(div current, magnetics)
% \end{enumerate}
% \end{frame}

% \begin{frame}[allowframebreaks]{Proposed shot plan - AUG}
% \vspace{-1cm}
% Allocated shots $\sim$ 14 + contingency 
% \begin{itemize}
% 	\item L-Mode (6 shots)
% 	\begin{enumerate}
% 		\item Reference shot \# 30276
% 		\item Perform $I_p$ scan (three values) with fixed $B_T$
% 		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
% 		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
% 		\item should we add OM puff to validate neutral measurements?
% 		\item Possibility of strike-point sweeping during shot
% 		\item RFEA measurements in internal program. 
% 		\item These shots combines experiments proposed by:
%                   Carralero (\# 7), Militello (\#1), Vianello (\#13)

% 	\end{enumerate}
% 	\item H-mode (9 shots)
% 	\begin{enumerate}
% 		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions
%                   in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
% 		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
% 		\item Strike-point sweep if feasible? 
% 		\item In all shots, particle acceleration in ELMs will be studied using microwaves,
%                   soft X-rays, and FILD 
% 		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
% 		\item These shots combine experiments proposed by:
%                   Aguiam (\#6), Carralero (\#7), McClements (\#4),
%                   Militello (\# 1, 2), Vianello (\#13), Vicente (\#8)

% 	\end{enumerate}
% \end{itemize}
% \end{frame}

% \begin{frame}{Proposed shot plan - TCV}
% 	\begin{itemize}
% 		\item L-mode (11 shots)
% 		\begin{enumerate}
% 			\item Reference shot \# 53514
% 			\item Same $I_p$ and $q_{95}$ scans as on AUG
% 			\item Two shots with reversed $\bm{B} \times \nabla B$
% 			\item Move plasma vertically. Disentangle
%                           $q_{95}$ and $L_{\|}$	
%                         \item These shots combines proposal: Vianello
%                           (\#13), Tsui (\#15), Militello (\#1, 2)
% 		\end{enumerate}
% 		\item H-mode (12 shots)
% 		\begin{enumerate}
% 			\item Reference shot \# 53352
% 			\item Since H-mode shoulder is new territory on TCV first shots will be scenario development
% 			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
%                         \item These shots combines proposal: Vianello
%                           (\#13), Tsui (\#15), Militello (\#1, 2)
% 		\end{enumerate}
% 	\end{itemize}
% \end{frame}

% \begin{frame}{Preliminary shot plan  - MAST-U}
% 	\begin{itemize}
% 		\item L-mode (6 shots)
% 		\begin{enumerate}		
% 			\item New machine. No reference shot yet			
% 			\item Same $I_p$ and $q_95$ scan to allow
%                           cross-machine comparison. Availability of multi pin probe? 
% 			\item Try varying fueling location
% 			\item RFEA measurements during shoulder
%                           formation 
%                         \item These shots combines proposal: Militello
%                           (\#1, 2, 3), Walkden (\#11), Vianello (\#13)
% 		\end{enumerate}
% 		\item H-mode (7 shots)
% 		\begin{enumerate}
% 			\item These experiments require the existence of H-mode reference shot. Perhaps not available in 2017
% 			\item Similar scenario development as on other emachines
%                         \item These shots combines proposal: Militello
%                           (\#1, 2, 3),  Vianello (\#13)
% 		\end{enumerate}
% 		\item Probe head must be changed to allow
%                   investigation of both fast T$_e$ (BPP),  and T$_i$
%                   (RFEA) but this require careful schedule of machine time
% 	\end{itemize}
% \end{frame}

% \begin{frame}{COMPASS collaboration}
% \begin{itemize}
% \item COMPASS is not an MST1 device, therefore no operational cost
%   will be provided by MST1
% \item However GA agrees that MST1 can provide part of the ppy for
%   running experiments in line with MST1 topics
% \item Proposal \# 14 is focused filaments dynamics and shoulder
%   formation both in L and H-Mode
% \item Experimental plan can be therefore agreed in order to perform
%   similar experiments (e.g. I$_p$ and $q_{95}$ scan in L-Mode)
%   ensuring proper comparison between devices
% \item COMPASS suppose 3ppy for running and evaluation of experiment
%   pertaining Topic-21, among Czeck and other european laboratories.
% \end{itemize}
% \end{frame}

% \begin{frame}{There are urgent experiment which cannot be addressed}
% \begin{itemize}
% 	\item Detailed ion temp measurements. Must eventually be
%           completed in internal programs. Are you willing to share the
%           information among Topic 21 even though done internally?
% 	\item Topology investigations? For example the comparison
%           USN/LSN/DN is not included. Diagnostic capability of upper
%           divertor is weaker than the lower one.
%           Better to use reverse B$_t$  which is known
%           to have influences in detachment as
%           well \parencite{McLean}
% 	\item Strikepoint sweeping and cryo pump
% 	\item Parameters scans in H-mode
% 	\item X-point probes
% \end{itemize}
% \end{frame}

% \begin{frame}{Modeling require}
%   \begin{enumerate}
%     \item Mean field modeling, in particular for neutral investigation.
%       Available for AUG (EMC3-EIRENCE) and
%       MAST-U (SOLPS). So far we lack investigation for these scenario
%       targeting TCV. Manpower needed from edge and SOL modeling
%     \item Turbulence code: we should need self-consistent interaction
%       with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
%       \texttt{GBS}, \texttt{Tokam-3X}.
%       Some of them can be run by people who will, very
%       likely, apply for this topic, some other not
%   \end{enumerate}
% \end{frame}

% \begin{frame}{Future and Miscellaneous}
% 	\begin{itemize}
% 		\item Possibility to piggybag on
%                   Quiescent/small ELM H-mode shots (Topic 5,6, 18)
% 		\item Shortly after this meeting we will organize
%                   a follow-up meeting to reconcile ideas
%                   from this discussion (date not fixed yet)
% 		\item All information will be gathered on the wiki
%                 \item Other channels for discussion/sharing. e.g. Slack
%                   (mst1-topic21.slack.com), Github for code sharing, \ldots
% 		\item We aim to arrive to a proper shared database of
%                   filaments between the machines, where properties
%                   will be obtained using agreed approaches so that a
%                   cross-machine comparison paper could at the end be
%                   finalized at a certain point		
% 	\end{itemize}
% \end{frame}

% \begin{frame}{Discussion agenda}
% 	\begin{enumerate}
% 		\item Priorities. These are our personal ideas. Do we agree? 
% 		\item \underline{Common measurement techniques}. Filament
%                   properties, $\Lambda_{div}$ estimate and location,
%                   Neutrals, packing fraction, \ldots 
%  	\end{enumerate}
% \end{frame}

\end{document}

### 2017-11-08 Codes/python/tcv/tcvFilaments.py
now tcvFilaments is sync with TCV branch

@@ -6,13 +6,10 @@ from __future__ import print_function
 import MDSplus as mds
 import numpy as np
 from scipy.interpolate import UnivariateSpline
-from scipy import io
-from scipy import stats
-from scipy.signal import detrend as Detrend
+from scipy.interpolate import interp1d
 from scipy import constants
 import eqtools
-from langmuir import LP
-import tcv.diag.frp as frp
+import langmuir
 import timeseries
 import xarray as xray
 import bottleneck
@@ -41,22 +38,36 @@ class Turbo(object):
     export PATH="/home/vianello/NoTivoli/anaconda2/bin":$PATH
     and adding the following whenever you start python
     >>> import sys
-    >>> sys.path.append('/home/vianello/pythonlib/submodules/tcvpy')
+    >>> sys.path.append('/home/vianello/work/topic21/Codes/python/general')
+    >>> sys.path.append('/home/vianello/work/topic21/Codes/python/tcv')
 
        eqtools
        MDSplus
-       FastRP from tcvpy diagnostic
-       pandas
        bottleneck
-       xray
+       xarray
        langmuir
        scipy
        quickspikes
     """
 
     def __init__(self, shot, gas='D2', Lp='Div'):
+        """
+
+        Parameters
+        ----------
+        shot :
+            Shot number
+        gas :
+            String indicating the gas. 'D2','H','He'
+        Lp :
+            String indicating if the parallel connection
+            length should be considered from target to
+            midplane 'Mid' or from target to X-point
+            'Div'
+
+        """
         self.shot = shot
-        self.Lp=Lp
+        self.Lp = Lp
         # globally define the gas
         self.gas = gas
         if gas == 'D2':
@@ -77,29 +88,21 @@ class Turbo(object):
         self._eq = eqtools.TCVLIUQETree(self.shot)
         # this is the iP in the time bases of LIUQE
         self._tLiuqe = self._eq.getTimeBase()
-        self.Ip = self._eq.getIpMeas()
         self.BtSign = np.sign(self._eq.getBtVac().mean())
-        # this is for different quantities
-        self._tree = mds.Tree('tcv_shot', shot)
-        # average density node
-        self._enavgNode = self._tree.getNode(r'\results::fir:n_average')
         # now define the tree where the probe data are saved
         self._filament = mds.Tree('tcv_topic21', shot)
-#        self._doubleDir = '/home/tsui/idl/library/data/double/dpm' + \
-#                          str(int(self.shot)) + '_'
[…]

### 2017-11-09 Codes/python/aug/augFilaments.py
update to augFilaments to compute all the relevant quantities needed for computation of size and Lambda

@@ -5,7 +5,10 @@ import numpy as np
 import matplotlib as mpl
 import copy
 from scipy.signal import savgol_filter
+from scipy.interpolate import UnivariateSpline
 from time_series_tools import identify_bursts2
+import langmuir
+import xarray as xray
 
 
 class Filaments(object):
@@ -48,6 +51,10 @@ class Filaments(object):
             self._loadHHF()
         else:
             print('Other probe head not implemented yet')
+        # load the data from Langmuir probes
+        self.Target = langmuir.Target(self.shot)
+        
+
 
     def _HHFGeometry(self, angle=80.):
         """
@@ -144,6 +151,9 @@ class Filaments(object):
         Mhg.close()
         # generate a class aware time basis
         self._timebasis = self.vfArr[self.vfName[0]]['t']
+        # generate a class aware dt
+        self.dt = (self._timebasis.max()-self._timebasis.min())/(
+            self._timebasis.size-1)
 
     def plotProbeSetup(self, save=False):
         """
@@ -186,7 +196,7 @@ class Filaments(object):
         ax.text(-40, 60, r'I$_s$', fontsize=18, color='red')
         ax.text(-40, 50, r'V$_f$', fontsize=18, color='blue')
 
-    def loadPosition(self):
+    def loadPosition(self, trange=None):
         """
         Load the position and compute for each of the pin the
         corresponding rho values taking into account the
@@ -214,17 +224,28 @@ class Filaments(object):
         R = (2188 - (self.Xprobe - self.Xlim) - sPos + 100) / 1e3
         # smooth it
         R = self.smooth(R, window_len=100)
-        # convert in Rhopoloidal
+        # check if trange exist or not
+        if not trange:
+            # convert in Rhopoloidal
         
-        self.rhoProbe = np.zeros(R.size)
-        for r, t, i in zip(R, tPos, range(R.size)):
-            self.rhoProbe[i]=self.Eq.rz2psinorm(r, self.Zmem*1e-3, t, sqrt=True)
-        self.tPos = tPos
+            self.rhoProbe = np.zeros(R.size)
+            for r, t, i in zip(R, tPos, range(R.size)):
+                self.rhoProbe[i]=self.Eq.rz2psinorm(r, self.Zmem*1e-3, t, sqrt=True)
+            self.tPos = tPos
+        else:
+            _idx = np.where(((tPos >= trange[0]) & (tPos <= trange[1])))[0]
+            _R = R[_idx]
+            _t = tPos[_idx]
[…]

### 2017-11-12 Experiments/TCV/analysis/python/scriptAnalysis.py
analysis/pdfbox/EquilibriaLparallelConstant*

@@ -45,6 +45,8 @@ def print_menu():
     print "22. Compare FF/RF profiles evolution Ip=190kA"
     print "23. Compare FF/RF profiles evolution Ip=330kA"
     print "24. Save timing blobs for Strokes"
+    print "25. Equilibria and Lparallel current scant at constant Bt"
+    print "26. Equilibria and Lparallel current scant at constant q95"
     print "99: End"
     print 67 * "-"
 
@@ -2114,6 +2116,76 @@ while loop:
 
             np.savetxt('../data/FilamentsShot%5i' % shot +'.txt', np.c_[timing],
                        fmt='%7.6f')
+    elif selection == 25:
+        shotList = (57425, 57437, 57497)
+        colorList = ('#1f77b4', '#ff7f0e', '#2ca02c')
+        fig, Ax = mpl.pylab.subplots(figsize=(6, 10),
+                                     nrows=2, ncols=1)
+        for shot, col in zip(shotList, colorList):
+            Eq = eqtools.TCVLIUQETree(shot)
+            # normalize the poloidal flux at 1s
+            i0 = np.argmin(np.abs(Eq.getTimeBase()-1))
+            psiN = (Eq.getFluxGrid()[i0]-
+                    Eq.getFluxAxis()[i0])/(Eq.getFluxLCFS()[i0]-
+                                           Eq.getFluxAxis()[i0])
+            Ax[0].contour(Eq.getRGrid(), Eq.getZGrid(), psiN[:],
+                          np.linspace(0., 1, 10), colors=col,
+                          linestyles='-')
+            Ax[0].contour(Eq.getRGrid(), Eq.getZGrid(), psiN[:],
+                          np.linspace(1.01, 1.1, 5), colors=col,
+                          linestyles='--')
+            # now load the parallel connection length
+            # and find the profiles closest to 1
+            Tree = mds.Tree('tcv_topic21', shot)
+            LpT = Tree.getNode(r'\LPDIVX').getDimensionAt(0).data()
+            _i0 = np.argmin(np.abs(LpT-1))
+            Lp = Tree.getNode(r'\LPDIVX').data()[_i0, :]
+            Rho = Tree.getNode(r'\LPRHO').data()[_i0, :]
+            Ax[1].plot(Rho, Lp, '-', color=col, label='# %5i' % shot)
+            Ax[1].legend(loc='best', numpoints=1, frameon=False)
+            Tree.quit()
[…]

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to gpm_november2017.tex file
continue preparation of slides

@@
 \vspace{-1cm}
-Objectives:
+Deliverables listed during the call for manning of last December 
 \begin{enumerate}
@@
   fuelling/neutral profiles/divertor conditioon
-\item \only<2>{\color{orange}}Use the new HHF probe on AUG to study
-  filamentary transport under high-power H-Mode conditions and under
+\item \only<2>{\color{green}}Use the new HHF probe on AUG to study
+  filamentary transport under high-power H-Mode conditions \only<2>{\color{red}}and under
   different plasma configurations (SN, DN)
@@
 }
+\end{frame}
+
+\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
+    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
+    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}
+
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1|only@1> All the shots were performed in the so-called
+        Edge Optmized Configuration (EOC) shape
+      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
+        here shown from outer divertor plate up to X-point 
+      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
+        MA) whereas we reduced it at lower current to avoid early
+        disruption
+      \item<2|only@2> The total power (Ohmic plus NBI) was kept
+        constant throughout the scan
+      \item<2|only@2> We have comparable edge density, divertor neutral
+        pressure and divertor temperature
+      \item<3|only@3> At comparable edge density Upstream profiles are
+        different with the tendency to develop shoulder easier at
+        lower current
+      \item<3|only@3> Still need to provide detail evolution of edge
+        profiles as a function
+        of $\Lambda_{div}$ which are different at different current
+        although same L$_{\parallel}$
+      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
+        different current even though obtained at different values of $\Lambda_{div}$. 
+      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
+        $\Lambda_{div}$ without sensible difference among the current
+      \end{itemize}
+    \end{column}
+\end{columns}
 \end{frame}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Slide 1 GPM

@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
-    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}
+    \centering{\includegraphics<3>[height=.8\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibraLparallelConstantQ95}}
+    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
+    %\centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}
 
@@
         pressure and divertor temperature
-      \item<3|only@3> At comparable edge density Upstream profiles are
-        different with the tendency to develop shoulder easier at
-        lower current
-      \item<3|only@3> Still need to provide detail evolution of edge
-        profiles as a function
-        of $\Lambda_{div}$ which are different at different current
-        although same L$_{\parallel}$
-      \item<4|only@4> No sensible difference of PDFs of J$_{sat}$ at
-        different current even though obtained at different values of $\Lambda_{div}$. 
-      \item<4|only@4> Autocorrelation time $\tau_{ac}$ increases with
-        $\Lambda_{div}$ without sensible difference among the current
+      \item<3|only@3> We repeat the same excercise at TCV with a
+        slight difference in the profile of parallel connection
+        length. This required operation at unusual low toroidal field
+        (up to 0.8T)
+      \item<4|only@4> At TCV,  no additional heating
+        used. Nevertheless the difference in power crossing the separatrix
+        is small
+      \item<4|only@4> Observed and higher neutral pressure at the
+        target whenever current is increased  
       \end{itemize}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to slides GPM

@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<3>[height=.8\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibraLparallelConstantQ95}}
+    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
     \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
-    %\centering{\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PdfStructureCurrentScan_ConstantQ95}}
-
+    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
+    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
   \end{column}
@@
     \begin{itemize}
-      \item<1|only@1> All the shots were performed in the so-called
+      \item<1|only@1> AUG: All the shots were performed in the so-called
         Edge Optmized Configuration (EOC) shape
-      \item<1|only@1> We matched correctly the shape and the L$_{\parallel}$
+      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
         here shown from outer divertor plate up to X-point 
-      \item<2|only@2> The scan was performed with similar puffing rate (0.8-1
+      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
         MA) whereas we reduced it at lower current to avoid early
         disruption
-      \item<2|only@2> The total power (Ohmic plus NBI) was kept
+      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
         constant throughout the scan
-      \item<2|only@2> We have comparable edge density, divertor neutral
+      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
         pressure and divertor temperature
-      \item<3|only@3> We repeat the same excercise at TCV with a
+      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
         slight difference in the profile of parallel connection
@@
         (up to 0.8T)
-      \item<4|only@4> At TCV,  no additional heating
+      \item<4|only@4> TCV: no additional heating
         used. Nevertheless the difference in power crossing the separatrix
         is small
-      \item<4|only@4> Observed and higher neutral pressure at the
-        target whenever current is increased  
+      \item<4|only@4> TCV: The difference in target pressure similar
+        to AUG behavior
+      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
+        different with the tendency to develop shoulder easier at
+        lower current
+      \item<6|only@6> TCV: This tendency is not observed for TCV where
+        profiles seem resilient to modification of Bt.
+
       \end{itemize}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Stil on first slides of GPM

@@
     \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
+    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
   \end{column}
@@
         different with the tendency to develop shoulder easier at
-        lower current
+        lower current. \alert{We have flattening of the upstream
+          profiles only when $\Lambda_{div}$ is well above one on all
+          the profile}
       \item<6|only@6> TCV: This tendency is not observed for TCV where
-        profiles seem resilient to modification of Bt.
-
+        profiles seem resilient to modification of Bt even though we
+        reached pretty high value of $\Lambda_{div}$ all along the profile.
+      \item<7|only@7> TCV: This is due to the fact that we can't
+        observed during the density ramp any signature of rollover or detachment,
+        whereas upstream profile modification at TCV are only observed
+        well after rollover
       \end{itemize}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Included comments on Current scan Constant Bt

@@
     \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
+    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
+    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
+
   \end{column}
@@
           the profile}
-      \item<6|only@6> TCV: This tendency is not observed for TCV where
+      \item<6|only@6> Neutrals estimated using calibrated D$_{\alpha}$
+        images coupled with values of density and temperature at the
+        target suggest a larger   
+      \item<7|only@7> TCV: This tendency is not observed for TCV where
         profiles seem resilient to modification of Bt even though we
         reached pretty high value of $\Lambda_{div}$ all along the profile.
-      \item<7|only@7> TCV: This is due to the fact that we can't
+      \item<8|only@8> TCV: This is due to the fact that we can't
         observed during the density ramp any signature of rollover or detachment,
@@
         well after rollover
+      \item<9|only@9> AUG: There is the tendency towards larger blobs
+        at lower current
+      \item<10|only@10> TCV: this is not confirmed for TCV but in line
+        with the lack of shoulder and detachment
+      \end{itemize}
+    \end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
+\Fontvi
+  \vspace{-1cm}
+  \begin{columns}    
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
+    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
+    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
+    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
+    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
+    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
+    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
+    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
+
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1|only@1> AUG: We matched correctly the shape the parallel
+        connection length L$_{\parallel}$ is modified consistently
+      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
+        MA) whereas we reduced it at lower current to avoid early disruption
+      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
+        pressure even though pressure increase earlier at higher current
+      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
+        constant throughout the scan
+      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
+        consistent variation of parallel connection length
+      \item<4|only@4> TCV: no additional heating
+        used. Nevertheless the difference in power crossing the separatrix
+        is small
+      \item<4|only@4> TCV: Neutral compression is roughly constant between
+      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
+        different with the tendency to develop shoulder easier at
+        lower current. \alert{We have flattening of the upstream
+          profiles only when $\Lambda_{div}$ is well above one on all
+          the profile}
+      \item<6|only@6> TCV: This tendency is substantially confirmed at
+        TCV where
+        profiles  
+      \item<7|only@7> TCV: This is consistent with onset of detachment
+        (at least in intermediate and lower current)
+      \item<8|only@8> AUG: While the general observation of increasing
+        blob size with $\Lambda_{div}$ is confirmed there are no
+        differences between the current
+      \item<9|only@9> TCV: confirm the observation of AUG. 
       \end{itemize}

### 2017-11-12 Experiments/TCV/analysis/python/batchevaluationblobsize.py
added the evaluation of blobsize for DN and FF

@@ -7,7 +7,7 @@ import numpy as np
 import MDSplus as mds
 import pandas as pd
 
-shotList = (57418, 57425, 57437, 57454, 57461, 57497)
+shotList = (58629, 58635)
 Shots = np.asarray([])
 # quantity
 Ip = np.asarray([])
@@ -130,6 +130,6 @@ outdict = {'Shots': Shots,
 df = pd.DataFrame.from_dict(outdict)
 df['Z'] = np.repeat(1, df.index.size)
 df['Mu'] = np.repeat(2, df.index.size)
-df['Conf'] = np.repeat('LSN', df.index.size)
-df.to_csv('../../data/BlobDatabse.csv')
+df['Conf'] = np.repeat('LSN-FF', df.index.size)
+df.to_csv('../../data/BlobDatabseFF.csv')
 

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
continue the GPM slides

@@
     \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
-    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
-    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
-    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
-    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
+    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
+    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
+    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
+    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
+    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
 
@@
     \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
-    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
-    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
-    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
-    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
+    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
+    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
+    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
+    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
+    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
 
@@
           the profile}
-      \item<6|only@6> TCV: This tendency is substantially confirmed at
+        \item<6|only@6> Neutrals at lower current are substantially
+          higher even with similar edge density profiles.
+      \item<7|only@7> TCV: This tendency is substantially confirmed at
         TCV where
         profiles  
-      \item<7|only@7> TCV: This is consistent with onset of detachment
+      \item<8|only@8> TCV: This is consistent with onset of detachment
         (at least in intermediate and lower current)
-      \item<8|only@8> AUG: While the general observation of increasing
+      \item<9|only@9> AUG: While the general observation of increasing
         blob size with $\Lambda_{div}$ is confirmed there are no
         differences between the current
-      \item<9|only@9> TCV: confirm the observation of AUG. 
+      \item<10|only@10> TCV: confirm the observation of AUG. 
       \end{itemize}
@@
 
-% \begin{frame}{Outline}
+\begin{frame}{LSN \textit{vs} Double null on TCV}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
+      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{H-Mode effect of puffing location}
+
+\end{frame}
+
+\begin{frame}{H-Mode effect of cryopumps}
+
+\end{frame}
+
+\begin{frame}{Comments on different divertor geometry which can be explored}
+
+\end{frame}
+
+\begin{frame}{Program for 2018: AUG}
+\end{frame}
+
+\begin{frame}{Program for 2018: TCV}
+\end{frame}
+
+\begin{frame}{Program for 2018: MAST-U}
+\end{frame}
+
+%\begin{frame}{Outline}
 % 	\begin{itemize}

### 2017-11-12 Experiments/TCV/analysis/python/scriptAnalysis.py
added the blob-size LSN vs DN

@@ -49,6 +49,7 @@ def print_menu():
     print "26. Equilibria and Lparallel current scant at constant q95"
     print "27. Roll over vs Density Constant q95"
     print "28. Roll over vs Density constant Bt"
+    print "29. Compare blob LSN-DN"
     print "99: End"
     print 67 * "-"
 
@@ -2300,7 +2301,42 @@ while loop:
         mpl.pylab.savefig('../pdfbox/CompareTargetProfilesConstantBT.pdf',
                           bbox_to_inches='tight')
         
+    elif selection == 29:
+        shotList = (57437, 58623)
+        Type = ('LSN', 'DN')
+        colorList = ('#BE4248', '#586473')
+        fig, ax = mpl.pylab.subplots(figsize=(8, 6))
+        fig.subplots_adjust(bottom=0.16, left=0.18, right=0.98)
+        ax.set_title(r'I$_p$ scan at constant B$_{\phi}$')
+        for shot, col in zip(shotList, colorList):
+            if shot == 57437:
+                df = pd.read_csv('../../data/BlobDatabse.csv')
+            else:
+                df = pd.read_csv('../../data/BlobDatabseDN.csv')
 
+            ax.plot(df.loc[((df['Shots'] == shot) &
+                            (df['Rho'] >= 1.04))]['Lambda Div'],
+                    df.loc[((df['Shots'] == shot) &
+                            (df['Rho'] >= 1.04))]['Blob Size [rhos]'],
+                    'o', color=col, ms=15)
+            ax.errorbar(df.loc[((df['Shots'] == shot) &
+                            (df['Rho'] >= 1.04))]['Lambda Div'],
+                        df.loc[((df['Shots'] == shot) &
+                            (df['Rho'] >= 1.04))]['Blob Size [rhos]'],
+                        xerr=df.loc[((df['Shots'] == shot) &
+                            (df['Rho'] >= 1.04))]['Lambda Div Err'],
+                        yerr=df.loc[((df['Shots'] == shot) &
+                            (df['Rho'] >= 1.04))][
+                            'Blob size Err [rhos]'], fmt='none', ecolor=col)
+        ax.set_xscale('log')
+        ax.set_xlabel(r'$\Lambda_{div}$')
+        ax.set_ylabel(r'$\delta_b [\rho_s]$')
+        for t, col, i in zip(Type, colorList, range(2)):
+            ax.text(0.1, 0.9-i*0.06, t,
[…]

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
continue to work on slides

@@
       \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
+      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
     \end{column}
@@
 \begin{frame}{H-Mode effect of cryopumps}
-
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}
+      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+    \end{column}
+  \end{columns}
 \end{frame}
@@
 \begin{frame}{Program for 2018: AUG}
+  \begin{itemize}
+     \item X-point manipulator (hopefully with NPH) triggered at
+	the same time as MPM
+     \item X-point vertical shift in order to have SP at different
+	vertical heigth at the target
+     \item DN discharges. With slow movement of the second X-point into the vessel
+	to be performed at constant power/density where shoulder alreay exists
+     \item USN with midplane/X-point manipulator to monitor the upstream SOL  \end{itemize}
 \end{frame}
@@
 \begin{frame}{Program for 2018: TCV}
+  \begin{itemize}
+     \item H-Mode ?
+      \item Long divertor legs (probe in the lower port)
+      \item SnowFlake to monitor the fluctuations in between the 2 separatrix
+	to be done in high density discharges
+       \item Try to move the second X-point in SN divertor at a different
+	Z position while keeping the same radial distances between the
+	points
+\end{itemize}
 \end{frame}
@@
 \begin{frame}{Program for 2018: MAST-U}
+  \begin{itemize}
+     \item Influence of neutral recycling source in establishing upstream profiles
+	and comparison between Low-RT and Vertical target. Look also ath the heat
+	loads
+      \item Current scan at constant q95/constant Bt
+      \end{itemize}
 \end{frame}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
improvement on gpm

@@
     \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
-    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
-    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
-    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
-    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
+    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
+    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
+    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
+    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
+    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
 
@@
           the profile}
-      \item<6|only@6> Neutrals estimated using calibrated D$_{\alpha}$
+      \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
         images coupled with values of density and temperature at the
         target suggest a larger   
-      \item<7|only@7> TCV: This tendency is not observed for TCV where
+      \item<7|only@7> AUG: At all the current a clear roll-over in
+        peak density observed and we can also track the radiation
+        front move away from target earlier in density at lower current
+      \item<8|only@8> TCV: This tendency is not observed for TCV where
         profiles seem resilient to modification of Bt even though we
         reached pretty high value of $\Lambda_{div}$ all along the profile.
-      \item<8|only@8> TCV: This is due to the fact that we can't
+      \item<9|only@9> TCV: This is due to the fact that we can't
         observed during the density ramp any signature of rollover or detachment,
@@
         well after rollover
-      \item<9|only@9> AUG: There is the tendency towards larger blobs
+      \item<10|only@10> AUG: There is the tendency towards larger blobs
         at lower current
-      \item<10|only@10> TCV: this is not confirmed for TCV but in line
+      \item<11|only@11> TCV: this is not confirmed for TCV but in line
         with the lack of shoulder and detachment
@@
     \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
-    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
-    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
-    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
-    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
+    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
+    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
+    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
+    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
+    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}
 
@@
           higher even with similar edge density profiles.
-      \item<7|only@7> TCV: This tendency is substantially confirmed at
+        \item<7|only@7> Neutrals at lower current are substantially
+          higher even with similar edge density profiles.
+      \item<8|only@8> TCV: This tendency is substantially confirmed at
         TCV where
         profiles  
-      \item<8|only@8> TCV: This is consistent with onset of detachment
+      \item<9|only@9> TCV: This is consistent with onset of detachment
         (at least in intermediate and lower current)
-      \item<9|only@9> AUG: While the general observation of increasing
+      \item<10|only@10> AUG: While the general observation of increasing
         blob size with $\Lambda_{div}$ is confirmed there are no
         differences between the current
-      \item<10|only@10> TCV: confirm the observation of AUG. 
+      \item<11|only@11> TCV: confirm the observation of AUG. 
       \end{itemize}
@@
 
-\begin{frame}{H-Mode effect of puffing location}
-
-\end{frame}
-
-\begin{frame}{H-Mode effect of cryopumps}
+\begin{frame}{H-Mode investigation: puffing location}
+\Fontvi
+  \vspace{-1cm}
 \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}
-      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[height=0.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingLocation}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
+    \only<3>{
+      \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}
+        \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
+        \draw [->, ultra thick, white] (0.62, 0.45) -- (0.72, 0.55);
+      \end{tikzonimage}   
+    }
   \end{column}
-    \begin{column}{0.5\textwidth}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1-> Similar puff from Lower and Upper divertor valves
+        (\alert{we asked for divertor/midplane valves})
+      \item<2-> Discharge with a total amount 6.5 heating power
+        with equivalent behavior also in the lower divertor
+        independently from the puffing location
+      \item<3-> Edge density profiles from Li-Beam evolution are
+        pretty similar
+      \item<3|alert@3> Similar behavior observed from RIC Antenna 4
+        for the available shot
+    \end{itemize}
   \end{column}
@@
 
+\begin{frame}{Compare fueling with/without cryopumps}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
+    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
+    \only<3>{
+    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
+      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
+      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
+    \end{tikzonimage}}
+  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+    \item<1-> Same fueling but with cryo-pumps
+      \item<1-> H-5 density is different and remain constant, both
+        divertor and midplane pressure are reduced (to 1/3
+        approximately) no sign of detachment
+      \item<2-> Different ELMy regimes reached with reduced size and
+        increased frequency without the cryopumps
+      \item<3-> Also with this amount of fueling weaker indication of SOL
+        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
+      \item<4> Inter-ELM resolved profile suggest a flattening even
+        with the cryompumps still even though $\Lambda_{div}$ is
+        marginal above 1 only in the near SOL
+
+    \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Matching scenarios with cryo-pumps}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
+    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
+    4\centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1-> To match similar edge density and divertor pressure
+        and to reach the same level of detachment we increase the
+        fueling by almost a factor of 3, increasing also the rate. In
+        addition to that we also increase substantially the N
+        puffing. \alert{Degraded H-Mode reached earlier in density
+          without the cryopumps}
+      \item<2-> Similar ELMy behavior obtained during the density ramp  
+      \item<3-> Without cryopumps evidence of stronger SOL profile
+        flattening from Li-Be. \alert{To be compared with appropriate
+          variation of $\Lambda_{div}$}
+       \item<4> Inter-ELM resolved Li-Be profiles 
+    \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Comments on difficulties for H-Mode in TCV}
+
+\end{frame}
 \begin{frame}{Comments on different divertor geometry which can be explored}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
update to Slides for GPM

@@
 \begin{frame}{LSN \textit{vs} Double null on TCV}
-  \begin{columns}
-    \begin{column}{0.5\textwidth}
-      \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
-      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
-      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
-    \end{column}
-    \begin{column}{0.5\textwidth}
-    \end{column}
-  \end{columns}
+%  \begin{columns}
+%    \begin{column}{0.5\textwidth}
+      \centering{\includegraphics<1>[width=.6\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
+      \centering{\includegraphics<2>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
+      \centering{\includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58624}}
+      \centering{\includegraphics<4>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
+%    \end{column}
+%    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+        \item<1|only@1> Comparing similar L-Mode density ramp at same
+          current in LSN and DN with ion $\mathbf{B}\times\nabla B$
+          pointing towards the floor. Lower ion flux to lower target
+          observed in DN and profiles before rollover seem more broad
+          in LSN. After rollover the profiles are actually similar
+      \item<2|only@2>  From bolometry we can observe an
+          unbalanced movement of the radiation front suggesting a non
+          perfectly balanced DN
+      \item<3|only@3> This is confirmed at higher current where the
+        more active X-point is the upper one with a consequent higher
+        radiation from bolometry chords    
+      \end{itemize}
+%    \end{column}
+%  \end{columns}
 \end{frame}

### 2017-11-13 Experiments/TCV/analysis/python/scriptAnalysis.py
now the script for TCv compare blob size at two currents

@@ -2302,14 +2302,13 @@ while loop:
                           bbox_to_inches='tight')
         
     elif selection == 29:
-        shotList = (57437, 58623)
+        shotList = (57437, 58623, 57497, 58624)
         Type = ('LSN', 'DN')
         colorList = ('#BE4248', '#586473')
         fig, ax = mpl.pylab.subplots(figsize=(8, 6))
         fig.subplots_adjust(bottom=0.16, left=0.18, right=0.98)
-        ax.set_title(r'I$_p$ scan at constant B$_{\phi}$')
         for shot, col in zip(shotList, colorList):
-            if shot == 57437:
+            if (shot == 57437) or (shot == 57497):
                 df = pd.read_csv('../../data/BlobDatabse.csv')
             else:
                 df = pd.read_csv('../../data/BlobDatabseDN.csv')
@@ -2320,13 +2319,13 @@ while loop:
                             (df['Rho'] >= 1.04))]['Blob Size [rhos]'],
                     'o', color=col, ms=15)
             ax.errorbar(df.loc[((df['Shots'] == shot) &
-                            (df['Rho'] >= 1.04))]['Lambda Div'],
+                                (df['Rho'] >= 1.04))]['Lambda Div'],
                         df.loc[((df['Shots'] == shot) &
-                            (df['Rho'] >= 1.04))]['Blob Size [rhos]'],
+                                (df['Rho'] >= 1.04))]['Blob Size [rhos]'],
                         xerr=df.loc[((df['Shots'] == shot) &
-                            (df['Rho'] >= 1.04))]['Lambda Div Err'],
+                                     (df['Rho'] >= 1.04))]['Lambda Div Err'],
                         yerr=df.loc[((df['Shots'] == shot) &
-                            (df['Rho'] >= 1.04))][
+                                     (df['Rho'] >= 1.04))][
                             'Blob size Err [rhos]'], fmt='none', ecolor=col)
         ax.set_xscale('log')
         ax.set_xlabel(r'$\Lambda_{div}$')

### 2017-11-13 Experiments/TCV/analysis/python/scriptAnalysis.py
LSN-DN comparison LambdaSize correct

@@ -2304,11 +2304,13 @@ while loop:
     elif selection == 29:
         shotList = (57437, 58623, 57497, 58624)
         Type = ('LSN', 'DN')
-        colorList = ('#BE4248', '#586473')
+        colorList = ('#BE4248', '#586473', '#BE4248', '#586473')
         fig, ax = mpl.pylab.subplots(figsize=(8, 6))
         fig.subplots_adjust(bottom=0.16, left=0.18, right=0.98)
         for shot, col in zip(shotList, colorList):
-            if (shot == 57437) or (shot == 57497):
+            if (shot == 57437):
+                df = pd.read_csv('../../data/BlobDatabse.csv')
+            elif (shot == 57497):
                 df = pd.read_csv('../../data/BlobDatabse.csv')
             else:
                 df = pd.read_csv('../../data/BlobDatabseDN.csv')

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
update to slides of gpm

@@
       \item<2-> Similar ELMy behavior obtained during the density ramp  
-      \item<3-> Without cryopumps evidence of stronger SOL profile
-        flattening from Li-Be. \alert{To be compared with appropriate
-          variation of $\Lambda_{div}$}
-       \item<4> Inter-ELM resolved Li-Be profiles 
+      \item<3-> Now the scenario suggest a strong profile flattening
+        even with the cryopumps
+       \item<4> Inter-ELM resolved Li-Be profiles confirm this with
+         shoulder formed with similar strength even with the cryopumps
+         in operation.
     \end{itemize}
@@
 \end{columns}
+\end{frame}
+
+\begin{frame}{Fast electron generation}
+
 \end{frame}

### 2017-11-13 Experiments/AUG/analysis/python/scriptAnalysisShot.py
AUG script have the part comparing CAS 34278, 34281

@@ -81,6 +81,7 @@ def print_menu():
     print "43. Blob size vs Lambda All L-Mode"
     print "44. Evolution of single inter-ELM profiles different-puffing"
     print "45. Evolution of single inter-ELM profiles different fueling H-Mode"
+    print "45. Compare CAS 34278-34281"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -3144,8 +3145,21 @@ while loop:
         mpl.pylab.savefig('../pdfbox/Shot_%5i' % shotList[0]
                           + '_'+'%5i' % shotList[1]+'_InterELMprofiles.pdf',
                           bbox_to_inches='tight')
-
-
+    elif selection == 45:
+        shotList = (34278, 34281)
+        colorList = ('#C90015', '#7B0Ce7')
+        fig, ax = mpl.pylab.subplots(figsize=(7, 5), nrows=1, ncols=1)
+        for shot, col in zip(shotList, colorList):
+            Data = xray.open_dataarray('../data/Shot%5i' % shot + '_5Stroke.nc')
+            ax.plot(Data.time, Data.sel(sig='Isat_m06'), color=col, lw=3, label='# %5i' % shot)
+            ax.fill_between(Data.time, Data.sel(sig='Isat_m06')-Data.err[0, :],
+                            Data.sel(sig('Isat_m06')+Data.err[0, :]), ec='white', fc=color,
+                            alpha=0.5)
+        ax.set_xlabel(r't [$\mu$s]')
+        ax.set_ylabel(r'$\delta I_s/\sigma$')
+        ax.legend(loc='best', numpoints=1, frameon=False)
+        mpl.pylab.savefig('../pdfbox/CompareCas%5i' % shotList[0]+'_%5i' % shotlist[1]+'.pdf',
+                          bbox_to_inches='tight')
     elif selection == 99:
         loop = False
     else:

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update slides
The slides have been updated including the pdf file from Ken on AUG

@@
 \begin{frame}{Fast electron generation}
+\Fontvi
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/SXR_ken}}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+\begin{itemize}
+      \item Bursts of nonthermal 2nd harmonic electron cyclotron emission and edge soft X-ray emission often occur at start of ELM filament eruption in low collisionality AUG pulses – evidence of filament reconnection
+\item Soft X-ray bursts were seen at start of ELM filament eruption in T21-AUG pulses, but not ECE bursts, probably due to higher collisionality in these pulses
+\item Peak nonthermal ECE emission appears to originate from top of pedestal
+\item Work is ongoing to determine conditions for occurrence of ECE \& SXR bursts, e.g. in terms of pedestal collisionality – there is no clear correlation between ELM size \& SXR flux
+\end{itemize}
+\end{column}
 
+  \end{columns}
 \end{frame}

### 2017-11-13 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the figure which compare the Cas different fueling

@@ -81,7 +81,7 @@ def print_menu():
     print "43. Blob size vs Lambda All L-Mode"
     print "44. Evolution of single inter-ELM profiles different-puffing"
     print "45. Evolution of single inter-ELM profiles different fueling H-Mode"
-    print "45. Compare CAS 34278-34281"
+    print "46. Compare CAS 34278-34281"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -3145,20 +3145,23 @@ while loop:
         mpl.pylab.savefig('../pdfbox/Shot_%5i' % shotList[0]
                           + '_'+'%5i' % shotList[1]+'_InterELMprofiles.pdf',
                           bbox_to_inches='tight')
-    elif selection == 45:
+    elif selection == 46:
         shotList = (34278, 34281)
         colorList = ('#C90015', '#7B0Ce7')
         fig, ax = mpl.pylab.subplots(figsize=(7, 5), nrows=1, ncols=1)
+        fig.subplots_adjust(bottom=0.15)
         for shot, col in zip(shotList, colorList):
             Data = xray.open_dataarray('../data/Shot%5i' % shot + '_5Stroke.nc')
-            ax.plot(Data.time, Data.sel(sig='Isat_m06'), color=col, lw=3, label='# %5i' % shot)
-            ax.fill_between(Data.time, Data.sel(sig='Isat_m06')-Data.err[0, :],
-                            Data.sel(sig('Isat_m06')+Data.err[0, :]), ec='white', fc=color,
+            ax.plot(Data.t*1e6, Data.sel(sig='Isat_m06'), color=col, lw=3, label='# %5i' % shot)
+            err = Data.err.reshape(3, 501)
+            ax.fill_between(Data.t*1e6, Data.sel(sig='Isat_m06')-err[0, :],
+                            Data.sel(sig='Isat_m06')+err[0, :], edgecolor='white',
+                            facecolor=col,
                             alpha=0.5)
         ax.set_xlabel(r't [$\mu$s]')
         ax.set_ylabel(r'$\delta I_s/\sigma$')
-        ax.legend(loc='best', numpoints=1, frameon=False)
-        mpl.pylab.savefig('../pdfbox/CompareCas%5i' % shotList[0]+'_%5i' % shotlist[1]+'.pdf',
+        ax.legend(loc=2, numpoints=1, frameon=False)
[…]

### 2017-11-13 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the CAS comparison

@@ -3148,19 +3148,57 @@ while loop:
     elif selection == 46:
         shotList = (34278, 34281)
         colorList = ('#C90015', '#7B0Ce7')
-        fig, ax = mpl.pylab.subplots(figsize=(7, 5), nrows=1, ncols=1)
-        fig.subplots_adjust(bottom=0.15)
+        fig, ax = mpl.pylab.subplots(figsize=(7, 10), nrows=2, ncols=1)
+        fig.subplots_adjust(bottom=0.15, hspace=0.25, wspace=0.25)
         for shot, col in zip(shotList, colorList):
             Data = xray.open_dataarray('../data/Shot%5i' % shot + '_5Stroke.nc')
-            ax.plot(Data.t*1e6, Data.sel(sig='Isat_m06'), color=col, lw=3, label='# %5i' % shot)
+            ax[0].plot(Data.t*1e6, Data.sel(sig='Isat_m06'), color=col, lw=3, label='# %5i' % shot)
             err = Data.err.reshape(3, 501)
-            ax.fill_between(Data.t*1e6, Data.sel(sig='Isat_m06')-err[0, :],
+            ax[0].fill_between(Data.t*1e6, Data.sel(sig='Isat_m06')-err[0, :],
                             Data.sel(sig='Isat_m06')+err[0, :], edgecolor='white',
                             facecolor=col,
                             alpha=0.5)
-        ax.set_xlabel(r't [$\mu$s]')
-        ax.set_ylabel(r'$\delta I_s/\sigma$')
-        ax.legend(loc=2, numpoints=1, frameon=False)
+            Size = Data.TauB*np.sqrt(
+                np.power(4e-3/Data.Lags[0], 2) +
+                np.power(6.9e-3/Data.Lags[1], 2))           
+ 
+            ax[1].semilogx(Data.Lambda, Size*1e3, 'o', ms=12, color=col)
+
+
+        ax[0].set_xlabel(r't [$\mu$s]')
+        ax[0].set_ylabel(r'$\delta I_s/\sigma$')
+        ax[0].legend(loc=2, numpoints=1, frameon=False)
+        ax[1].set_xlabel(r'$\Lambda_{div}$')
+        ax[1].set_ylabel(r'$\delta_b$ [mm]')
+
+        mpl.pylab.savefig('../pdfbox/CompareCas%5i' % shotList[0]+'_%5i' % shotList[1]+'.pdf',
+                          bbox_to_inches='tight')
+
[…]

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to GPM slides

@@
   constant $q_{95}$
-\item \only<2>{\color{orange}}Establish robust scenario for density
+\item \only<2>{\color{taorange}}Establish robust scenario for density
   shoulder profile in H-Mode and establish dependence on
   fuelling/neutral profiles/divertor conditioon
-\item \only<2>{\color{green}}Use the new HHF probe on AUG to study
-  filamentary transport under high-power H-Mode conditions \only<2>{\color{red}}and under
+\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
+  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
   different plasma configurations (SN, DN)
-\item \only<2>{\color{orange}}Study the role of ELM regimes,  neutral
+\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
   compression and particle density in filamentary transport and
   related shoulder formation
-\item \only<2>{\color{orange}} Identify the contribution of
+\item \only<2>{\color{taorange}} Identify the contribution of
   collisionality and seeding on filamentary transport and related
   shoulder formation
-\item \only<2>{\color{red}}Determine the effect of filaments and
+\item \only<2>{\color{consorziored}}Determine the effect of filaments and
   shoulder formation on target heat loads in different H-mode plasmas
@@
     \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
-    4\centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
+    \centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
+    \centering{\includegraphics<5>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/CompareCas34278_34281}}
   \end{column}
@@
         even with the cryopumps
-       \item<4> Inter-ELM resolved Li-Be profiles confirm this with
+       \item<4-> Inter-ELM resolved Li-Be profiles confirm this with
          shoulder formed with similar strength even with the cryopumps
          in operation.
+         \item<5> We can also confirm that additional fueling change
+           substantially the blob size which increases consistently
+           with the modification of $\Lambda_{div}$
     \end{itemize}
@@
      \item X-point vertical shift in order to have SP at different
-	vertical heigth at the target
+	vertical heigth at the target. \alert{This could suggest us if
+        similar behavior as the one observed on JET are visible at AUG}
      \item DN discharges. With slow movement of the second X-point into the vessel
-	to be performed at constant power/density where shoulder alreay exists
-     \item USN with midplane/X-point manipulator to monitor the upstream SOL  \end{itemize}
+	to be performed at constant power/density where shoulder
+        alreay exists. \alert{This is mandatory to complement the
+          information obtained on TCV}
+     \item USN with midplane/X-point manipulator to monitor the upstream SOL 
+\end{itemize}
  \end{frame}

### 2017-11-13 Experiments/TCV/analysis/python/scriptAnalysis.py
added the patch for vessel to Equilibra figures

@@ -2105,8 +2105,9 @@ while loop:
     elif selection == 25:
         shotList = (57425, 57437, 57497)
         colorList = ('#1f77b4', '#ff7f0e', '#2ca02c')
-        fig, Ax = mpl.pylab.subplots(figsize=(6, 10),
+        fig, Ax = mpl.pylab.subplots(figsize=(6, 6),
                                      nrows=2, ncols=1)
+        fig.subplots_adjust(top=0.98)
         for shot, col in zip(shotList, colorList):
             Eq = eqtools.TCVLIUQETree(shot)
             # normalize the poloidal flux at 1s
@@ -2130,8 +2131,13 @@ while loop:
             Ax[1].plot(Rho, Lp, '-', color=col, label='# %5i' % shot)
             Ax[1].legend(loc='best', numpoints=1, frameon=False)
             Tree.quit()
+
+        tilesP, vesselP = Eq.getMachineCrossSectionPatch()
         Ax[0].set_aspect('equal')
-        Ax[0].axis('off')
+        Ax[0].add_patch(tilesP)
+        Ax[0].add_patch(vesselP)
+        Ax[0].set_xlabel('R [m]')
+        Ax[0].set_ylabel('Z [m]')
         Ax[1].set_xlabel(r'$\rho_p$')
         Ax[1].set_ylabel(r'L$_{\parallel}$ [m]')
         mpl.pylab.savefig('../pdfbox/EquilibriaLparallelConstantBt.pdf',
@@ -2143,6 +2149,7 @@ while loop:
         colorList = ('#1f77b4', '#ff7f0e', '#2ca02c')
         fig, Ax = mpl.pylab.subplots(figsize=(6, 10),
                                      nrows=2, ncols=1)
+        fig.subplots_adjust(top=0.98)
         for shot, col in zip(shotList, colorList):
             Eq = eqtools.TCVLIUQETree(shot)
             # normalize the poloidal flux at 1s
@@ -2166,8 +2173,13 @@ while loop:
             Ax[1].plot(Rho, Lp, '-', color=col, label='# %5i' % shot)
             Ax[1].legend(loc='best', numpoints=1, frameon=False)
             Tree.quit()
+
+        tilesP, vesselP = Eq.getMachineCrossSectionPatch()
         Ax[0].set_aspect('equal')
-        Ax[0].axis('off')
+        Ax[0].add_patch(tilesP)
[…]

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
still update to gpm

@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
-    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
+    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
     \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
-    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
+    \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
     \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update GPM TeX slide

@@
 \maketitle
-\begin{frame}
-\textbf{Include scientific team and logos}
+\begin{frame}{Scientific Team}
+\begin{center}
+  Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
+Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
+Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
+Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente,
+Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum
+\end{center}
 \end{frame}
@@
 \begin{enumerate}
-\item \only<2>{\color{ta3chameleon}} Provide cross-machine L-Mode
+\item \only<2>{\color{ta3chameleon}} Cross-machine L-Mode
   shoulder dependence on current both at constant B$_t$ and at
-  constant $q_{95}$
+  constant $q_{95}$. Rationale: disentangle the effect of current and
+  parallel connection length
 \item \only<2>{\color{taorange}}Establish robust scenario for density
@@
   So far H-Mode operation has been limited to AUG since no operational
-  scenarion in high-density NBH heated plasma on TCV has been established
+  scenario in high-density NBH heated plasma on TCV has been established
 }
@@
     \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
-    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
+    \includegraphics<2>[height=.81\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
     \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
@@
     \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
-    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
+    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GPI_blobs_AUG}}
+    \centering{\includegraphics<12>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}
 
@@
       \item<1|only@1> AUG: All the shots were performed in the so-called
-        Edge Optmized Configuration (EOC) shape
+        Edge Optmized Configuration (EOC) shape. 
       \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
         here shown from outer divertor plate up to X-point 
-      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
+      \item<2|only@2> AUG: The scan was performed with similar puffing
+        rates for intermediate and higher current (0.8-1
         MA) whereas we reduced it at lower current to avoid early
@@
       \item<4|only@4> TCV: no additional heating
-        used. Nevertheless the difference in power crossing the separatrix
+        has been used. Nevertheless the difference in power crossing the separatrix
         is small
       \item<4|only@4> TCV: The difference in target pressure similar
-        to AUG behavior
+        to AUG behavior. 
       \item<5|only@5> AUG: At comparable edge density Upstream profiles are
@@
       \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
-        images coupled with values of density and temperature at the
-        target suggest a larger   
+        cameras coupled with values of density and temperature at the
+        target suggest a larger neutral density at lower current (even
+        with comparable values of edge electron density)
       \item<7|only@7> AUG: At all the current a clear roll-over in
@@
         observed during the density ramp any signature of rollover or detachment,
-        whereas upstream profile modification at TCV are only observed
-        well after rollover
+        \alert{whereas upstream profile modification at TCV are only observed
+        well after rollover}
       \item<10|only@10> AUG: There is the tendency towards larger blobs
-        at lower current
-      \item<11|only@11> TCV: this is not confirmed for TCV but in line
-        with the lack of shoulder and detachment
+        at lower current at all values of $\Lambda_{div}$
+      \item<11|only@11> AUG: This need to be further confirmed
+        independently by GPI measurements. The present setup allows
+        for space resolution of the order of mm with a 397 kframe/s
+        sampling rate. Small amount of He gas flux needed ($\sim
+        1.5e^{17} atoms/ms$)
+      \item<12|only@12> TCV: this is not confirmed for TCV where blob
+        sizes is rather constant over a rather large range of
+        $\Lambda_{div}$. At the same time we do not observe target
+        density rollover neither upstream profile flattening 
       \end{itemize}
@@
     \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
-    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
+    \centering{\includegraphics<2>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
     \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}

### 2017-11-13 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the zoom for radiation front movement

@@ -1619,7 +1619,7 @@ while loop:
 
     elif selection == 24:
         shotList = (34103, 34102, 34104)
-        colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
+        colorLS = ('#C90015', '#7B0Ce7', '#437356')
         tList = ((2.57, 2.9),
                  (2.57, 3.03, 3.5),
                  (1.83, 2.44, 3.15))
@@ -1758,7 +1758,7 @@ while loop:
 
     elif selection == 25:
         shotList = (34105, 34102, 34106)
-        colorLS = ('#C90015', '#7B0Ce7', '#F0CA37')
+        colorLS = ('#C90015', '#7B0Ce7', '#437356')
         tList = ((1.1, 2.83),
                  (1.1, 2.83, 3.41),
                  (1.1, 2.34, 3.09))
@@ -2436,9 +2436,7 @@ while loop:
 
         for shot, col, ip in zip(shotList, colorL, currentL):
             # load equilibrium
- 
-           
-            # load the H-5
+             # load the H-5
             Dcn = dd.shotfile('DCN', shot)
             H5 = Dcn('H-5')
             # spline evaluation (shorter time faster)
@@ -2513,6 +2511,92 @@ while loop:
         ax[4].set_ylabel(r'kW/m$^2$')
         mpl.pylab.savefig('../pdfbox/RadiationPeakDensityIpScan_constantQ95.pdf',
                           bbox_to_inches='tight', dpi=400)
+
+        # ----------------------
+        # same with just one LoS
+        shotList = (34103, 34102, 34104)
+        currentL = (0.6, 0.8, 0.99)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        Diods = {'D10': {'Name': 'S2L0A09',
+                       'xchord': [1.519, 1.606],
+                       'ychord': [-1.131, -1.11]}}
+        # create the figure
+        fig, ax = mpl.pylab.subplots(figsize=(6, 8),
+                                     ncols=1, nrows=2, sharex=True)
+        fig.subplots_adjust(left=0.15, wspace=0.05, top=0.98)
+
+        for shot, col, ip in zip(shotList, colorL, currentL):
+            # load equilibrium
+             # load the H-5
+            Dcn = dd.shotfile('DCN', shot)
+            H5 = Dcn('H-5')
+            # spline evaluation (shorter time faster)
[…]

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
update gpm TeX
new version of NPH figure and update to slides

@@
     \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
-    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
+    \centering{\includegraphics<4>[height=.9\textheight]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
     \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
@@
     \centering{\includegraphics<3>[height=.85\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
-    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
+    \centering{\includegraphics<4>[height=.9\textheight]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
     \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
@@
 
-\begin{frame}{Comments on difficulties for H-Mode in TCV}
-
-\end{frame}
-\begin{frame}{Comments on different divertor geometry which can be explored}
+\begin{frame}{Comments on different divertor geometry}
 
@@
   \begin{itemize}
-     \item X-point manipulator (hopefully with NPH) triggered at
-	the same time as MPM
+     \item X-point manipulator (NPH ?) simultaneously with MEM
      \item X-point vertical shift in order to have SP at different
-	vertical heigth at the target. \alert{This could suggest us if
-        similar behavior as the one observed on JET are visible at AUG}
+	vertical height at the target. \alert{We will observe similar
+          observation as obtained in JET when moving from horizontal
+          to vertical target?}
      \item DN discharges. With slow movement of the second X-point into the vessel
@@
 \end{itemize}
+ \end{frame}
+ \begin{frame}{MST2-NPH}
+   \begin{columns}
+     \begin{column}{0.5\textwidth}
+       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
+     \end{column}
+     \begin{column}{0.5\textwidth}
+       \begin{itemize}
+         \item MST2 founded project for the realization of a New Probe
+           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
+         \item Simultaneous information on Ion temperature (2 RFAs),
+           Plasma potential and electron temperature (Emissive probe
+           coupled with floating potential) and magnetic fluctuations
+           from 2 3-axial magnetic pick up coil
+         \item Potentially tested on TCV beginning of 2018 and then
+           moved to other MST1 devices
+       \end{itemize}
+     \end{column}
+   \end{columns}
+
  \end{frame}
@@
       \item Current scan at constant q95/constant Bt
+      \end{itemize}
+\end{frame}
+
+\begin{frame}{Code requirements}
+  \begin{itemize}
+    \item 
   \end{itemize}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
added further slides to GPM

@@
     \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
-    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
+    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95Zoom}}
     \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
@@
       \item<11|only@11> AUG: This need to be further confirmed
-        independently by GPI measurements. The present setup allows
+        independently by GPI measurements (I. Cziegler \textit{et al.}). The present setup allows
         for space resolution of the order of mm with a 397 kframe/s
@@
     \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
-    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
+    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBTZoom}}
     \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
@@
 
-\begin{frame}{Fast electron generation}
+\begin{frame}{Fast electron generation (K. McClements \textit{et al})}
 \Fontvi
@@
   \begin{itemize}
-    \item 
+    \item Dedicated simulations with first principles codes (GBS,
+      HESEL)
+    \item Check if trends can be reproduced
+    \item potential input for future experiments regarding role of
+        f.x. neutrals and recycling
   \end{itemize}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
updated to GpM slides

@@
           information obtained on TCV}
-     \item USN with midplane/X-point manipulator to monitor the upstream SOL 
+     \item USN with midplane/X-point manipulator to monitor the
+       upstream SOL 
+\item
 \end{itemize}
@@
            moved to other MST1 devices
+         \item Heat load
        \end{itemize}
@@
   \begin{itemize}
-     \item H-Mode ?
-      \item Long divertor legs (probe in the lower port)
-      \item SnowFlake to monitor the fluctuations in between the 2 separatrix
-	to be done in high density discharges
-       \item Try to move the second X-point in SN divertor at a different
+     \item \textcolor{consorziored}{H-Mode} 
+      \item Long divertor legs (probe in the lower port) to check if
+        increase of filamentary transport along the divertor leg
+        exists in high density scenarios
+      \item \textcolor{taorange}{SnowFlake to monitor the fluctuations in between the 2 separatrix
+	to be done in high density discharges}
+       \item \textcolor{taorange}{Try to move the second X-point in SN divertor at a different
 	Z position while keeping the same radial distances between the
-	points
+	points}
 \end{itemize}
@@
   \begin{itemize}
+      \item Current scan at constant q95/constant Bt
       \item Influence of neutral recycling source in establishing upstream profiles
-	and comparison between Low-RT and Vertical target. Look also ath the heat
-	loads
-      \item Current scan at constant q95/constant Bt
+	and comparison between Low-RT and Vertical target. Look also a
+        the heat loads
       \end{itemize}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
updte
Update to slides which a first possible version

@@
         radiation from bolometry chords
+      \item<4|only@4> No clear difference in blob size but needs
+        further investigation  
       \end{itemize}
@@
 
-\begin{frame}{Comments on different divertor geometry}
-
+\begin{frame}{Cross-machine: different divertor geometry}
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+  \includegraphics[width=\textwidth]{../generalFigures/Divertors}
+\end{column}
+\begin{column}{0.5\textwidth}
+  \begin{itemize}
+    \item Cross-machine experiments (including comparison with
+      possible JET experiment) could help to disentangle how divertor
+      geometry influence upstream profiles in term of neutral
+      compression and recycling
+    \item \alert{f.x. Vertical target on JET and AUG has very
+        different behavior in terms of shoulder formation}
+    \end{itemize}
+  \end{column}
+\end{columns}
 \end{frame}
@@
        upstream SOL 
-\item
+     \item Heat load
 \end{itemize}
@@
            moved to other MST1 devices
-         \item Heat load
        \end{itemize}
@@
    \end{columns}
-
  \end{frame}
@@
 \end{frame}
-
-%\begin{frame}{Outline}
-% 	\begin{itemize}
-% 		\item Background 
-% 		\item Plans (we will not make a detailed list of the
-%                   proposal, we already tried to combine and summarize them)
-% 		\item Discussion
-% 	\end{itemize}	
-% \end{frame}
-
-% \section{Background}
-% \begin{frame}{Present status}
-%   \setbeamercovered{transparent}
-%   \begin{enumerate}[<+(1) | invisible@-+>]
-%     \item Experimental and theoretical investigations suggest that SOL density profiles are
-%       determined by the balance between radial filamentary transport and parallel dynamics
-%     \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
-%     \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
-%       TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
-%     \item Observations exhibit various other dependencies e.g., divertor
-%       collisionality, plasma current, seeding. \alert{Results from
-%         different devices not fully reconciled and the underlying mechanism is not fully understood.}
-%     \item Studies of shoulder formation in H-Mode are so far limited 
-% 	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
-% %    \item First we will report a summary of the achievements and then
-%  %    personal comments and plans
-%     \end{enumerate}
-% \end{frame}
-% \section{L-Mode}
-% \begin{frame}{L-Mode studies: AUG/1}
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
-%         \begin{equation*}
-%         \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
-%       \end{equation*}
-%       controls filaments size
-%         \item<2-> \textcolor{red}{Tested by changing n$_e$
-%             and $T_e$ through fueling/seeding/heating}
-%         \item<3-> This determines a change of the velocity-size
-%           scaling from
-%             \textcolor{ta3chameleon}{sheath-limited}
-%         to \textcolor{blue}{inertial regime}.
-%        \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
-%            length}}
-%        \item<5> This finally determines the shoulder formation
-%         \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-%       \only<1-2>{
-%       \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15a}
-%           \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
-%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
-%         \only<2>{
-%           \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
-%         }
-%       \end{tikzonimage}}
-%     \only<3-4>{
-%       \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15b}
-%           \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
-%           \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
-%       \end{tikzonimage}
-%     }
-%     \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15c}
-%     \end{column}
-%   \end{columns}
-% \end{frame}
-
-% \begin{frame}{L-Mode studies: AUG/2}
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1-> Profile modified by an increase of blob-size and change of
-%         \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
-%         \onslide<2->{\textcolor{blue}{and filament relative density}
-%           {\footnotesize (Carralero 2016 in preparation)}}
-%       \item<3-> As a consequence the contribution of filaments to
-%         radial transport increases
-%       \item<4|only@4> \alert{Beware the change of frequency may be due to a
-%         modification of fluctuation velocity which is known to vary
-%         with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
-%       \item<5> Parallel flow is strongly reduced whenever we increase
-%         the divertor collisionality
-%       \end{itemize}
-%     \end{column}
-%       \begin{column}{0.5\textwidth}
-%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16a}
-%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16b}
-%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16c}
-%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/AgostiniNF2011}
-%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16d}
-%       \end{column}
-%     \end{columns}
-%   \end{frame}
-
-%   \begin{frame}{L-Mode studies:AUG/3}
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1-> Electron and ions behave differently
-%       \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
-%         accross the SOL and slightly affected by the increase of
-%         divertor collisionality
-%       \item<3|only@3> Ions are strongly affected: for
-%         \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
-%           and $\lambda_{T_i} \sim 30$
-%           mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
-%           T$_{i, bk}\sim 25$ eV
-%           and $\lambda_{T_i} \sim 8$ mm}
-%        \item<4-> Ion energy spectrum from
-%          $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
-%          energy for $\Lambda_{div} > 1$
-%        \item<5> EMC3-Eirene simulation suggests that such a reduction
-%          can't be accounted for thermalization process. An
-%          \alert{ionization front builds in front of the limiter shadow}   
-%        \end{itemize}
-%     \end{column}
-%       \begin{column}{0.5\textwidth}
-%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16e}
-%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16f}
-%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16g}
-%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16h}
-%       \end{column}
-%     \end{columns}
-%   \end{frame}
-
-%   \begin{frame}{L-Mode: TCV}
-%     \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
-%         dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
-%         \begin{equation*}
-%           f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
-%         \end{equation*}
-%         in ohmic density ramps \parencite{vianello:iaea2016}
-%       \item<2|only@2> Slight variation of density profiles at the target but
-%         due to direct dependence on L$_{\parallel}$ large increase of
-%         $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
-%         we reach a certain amount of $\langle n_e \rangle$}
-%        \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
-%         \onslide<4-5>{\textcolor{red}{also on a statistical
-%             basis}}. \onslide<5>{Strong dependence on average density,
-%           independent of L$_{\parallel}$}}
-%        \item<6|only@6> $\lambda_n$ depends clearly on blob-size
-%          whereas the dependence on divertor condition is less
-%          obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
-%       \end{itemize}
-%     \end{column}
-%       \begin{column}{0.5\textwidth}
-%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16a}
-%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16b}
-%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16c}
-%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16d}
-%         \includegraphics<6>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16e}
-%       \end{column}
-%     \end{columns}
-%   \end{frame}
-
-%   \begin{frame}{L-Mode: JET}
-%     \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1|only@1> The shoulder formation strongly depends on
-%         divertor geometry, disappear with vertical target and strike
-%         point closest to cryogenics pumps \parencite{Wynn:EPS2016}
-%       \item<2|only@2> The midplane pressure from baratrons is
-%         equivalent between the different divertor. \alert{This would
-%           indicate that SOL neutral density at the outboard midplane does not play any role}
-%        \item<3|only@3> In the horizontal target configuration the
-%          results indicate that the shoulder forms right at the
-%          transition from sheath-limited to high-recycling where also
-%          $\Lambda_{div}$ strongly increase
-%        \item<4|only@4> Shoulder amplitude correlates with strike
-%          points position. \alert{Shoulder, ionization and
-%            $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
-%          from the pump}
-%        \item<5|only@5> In seeded discharges the transition observed at
-%          very high level of $\Lambda_{div} >> 1$
-%       \end{itemize}
-%     \end{column}
-%       \begin{column}{0.5\textwidth}
-%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16a}
-%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16b}
-%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16c}
-%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16d}
-%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16e}
-%       \end{column}
-%     \end{columns}
-%   \end{frame}
-
-%   \begin{frame}{L-Mode: MAST}
-%     \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item<1|only@1> Strong dependence on
-%         I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
-%         constant toroidal field shoulder disappears. Consistent with
-%         observation in other devices
-%       \item<2|only@2> Filaments binormal dimension increases with
-%         current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
-%        \item<3|only@3> Filament radial velocity decreases with current
-%          as well as the radial dimension \parencite{Kirk:2016jj}
-%       \end{itemize}
-%     \end{column}
-%       \begin{column}{0.5\textwidth}
-%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MilitelloNF16a}
-%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16a}
-%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16c}
-%       \end{column}
-%     \end{columns}
-%   \end{frame}
-
-%   \section{H-Mode}
-%   \begin{frame}{AUG: H-Mode}
-%     \begin{columns}
-%     \begin{column}{0.4\textwidth}
-%       \begin{itemize}
-%       \item<1|only@1> SOL profiles in H-Mode so far investigated on
-%         AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
-%       \item<2|only@2> Differently from L-Mode, complete detachment
-%         suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
-%        \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
-%          shoulder depends on a combination of $\Lambda_{div}$ and
-%          fueling rate. Complete detachment seems instead not necessary
-%          although very weak shoulder
-%       \end{itemize}
-%     \end{column}
-%       \begin{column}{0.6\textwidth}
-%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MuellerJNM15a}
-%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/SunPPCF15a}
-%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16i}
-%       \end{column}
-%     \end{columns}
-%   \end{frame}
-
-%   \section{Open issues}
-%   \begin{frame}{Open and unresolved issues}
-%   \setbeamercovered{transparent}
-%   \begin{enumerate}[<+(1) | invisible@-+>]
-%     \item Does $\Lambda_{div}$ unify the picture among the devices?
-%       \alert{No, does neutral pressure play a role?}
-%     \item If neutrals play a role is it at the divertor and/or at the midplane?
-%       \alert{Contradictory results if one include experiments with
-%         midplane puffing, JET and EIRENE simulations}
-%     \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
-%       dependence from f$_x$ scan but both TCV and MAST observe an
-%       I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
-%       increases with L$_{\parallel}$ }
-%     \item Is cooling the divertor with fueling or seeding equivalent? \alert{Contradictory observations in AUG and JET}
-%     \item Do we observe same behavior in L and H-Mode? \alert{So
-%       far no as shown in H-Mode AUG. We need higher detachment
-%       condition and we need enough fueling}
-%       \item Is the density shoulder accompanied with an ion temperature shoulder?
-% %      \item What are the underlying mechanisms? 
-%     \end{enumerate}
-%   \end{frame}
-
-% \section{Topic 21 experiments }
-% \begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
-% 	\begin{itemize}
-% 		\item 15 were proposals submitted to Topic 21
-% 		\item Proposals include experiments on all three machines 
-% 		\item There are overlaps between several of the proposals 
-% 		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 
-% 		\item However, total number of proposed shots:  \textbf{449}
-% 		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
-% 		\item Reaching all goals is not possible with the current number of allocated shots.
-% 	\end{itemize}
-% \end{frame}
-
-% \begin{frame}{Focal points}
-% \begin{itemize}
-% 	\item MST1 uniquely facilitates cross comparison between machines
-% 	\item Several of the proposed experiments overlap and will be combined
-% 	\item A cross machine experiment has the makings of settling open issues
-% 	\item Therefore, we will allocate shots for cross-machine
-%           comparison but we must strive after similar machine configuration
-% 	\item ....but also to other proposed experiments
-% 	\item Cross machine L-mode experiments: 
-% 	\begin{enumerate}
-% 		\item Investigate the role of neutrals 
-% 		\item $I_p$ and $q_{95}$ scans
-% 	\end{enumerate}
-% 	\item Cross machine H-mode experiments. 
-% \end{itemize}	
-% \end{frame}
-
-% \begin{frame}{L-mode experiments}
-% 	\begin{itemize}
-% 		\item The role of neutrals in the shoulder
-%                   formation is not understood
-%                   {\scriptsize(proponents: Carralero (\# 7), Militello
-%                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9))}
-% 		\begin{enumerate}
-% 		\item We envisage to measure neutral gas profiles at the outboard midplane
-%                   using fast cameras with D$_{\alpha}$ filter, density
-%                   and temperature SOL profiles and appropriate code
-%                   (e.g. KN1D as in \parencite{Lipschultz:2005gg,Lipschultz:2016vk})
-% 		\item Reciprocating probes and profiles available on
-%                   all machines
-%                 \item Investigate role of fueling location (MAST)
-% 		\end{enumerate}
-% 		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$.
-%                   {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, Carralero (\# 7), Militello
-%                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9), Tsui
-%                     (\# 15))}
-% 		\begin{enumerate}
-% 			\item Carry out parameter scans on all machines
-
-% 		\end{enumerate}
-% 	\end{itemize}
-% \end{frame}
-
-% \begin{frame}{H-mode experiments}
-% \begin{itemize}
-% 	\item ITER and DEMO will operate in H-mode
-% 	\item We must know what parameters control shoulder formation 
-% 	\item Shoulder formation parameter regime is unclear on all machines
-% 	\item Main priorities: 
-% 	\begin{enumerate}
-% 		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
-% 		\item Investigate the SOL (filamentary) transport properties.
-%                   Whenever main diagnostic is reciprocating probes $\rightarrow$ limits heating power
-% 		\item Experiments must gradually increase power and density. 
-% 	\end{enumerate}
-% 	\item Fueling in H-mode is problematic due to transport
-%           barrier. Is there a way to overcome it? NBI, pellet fueling?
-% 	\item H-mode density limit \parencite{Bernert:2015bq} must be dealt with
-% \end{itemize}
-
-% \end{frame}
-
-% \begin{frame}{Optimizing cross machine comparison}
-% \begin{itemize}
-% 	\item Machines are fundamentally differently designed
-% 	\item Strive for similar configurations of the machines:
-% 	\begin{enumerate} 
-% 		\item Single-Null
-% 		\item $\bm{B} \times \nabla B$ towards active divertor 
-% 		\item Strike-point and cryo pump location (AUG and MAST-U)
-% 		\item Heating 
-% 		\item Fueling location 
-% 		\item Seeding (species, location, rate)
-% 	\end{enumerate}
-% \end{itemize} 
-% %things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,
-
-% \end{frame}
-
-% \begin{frame}{Required diagnostics and competences}
-% In order to compare experiments the following diagnostics must be available: 
-% \begin{enumerate}
-% 	\item Filaments analysis in the Outboard midplane: 
-% 	\begin{itemize} 
-% 		\item Through Reciprocating probe then $I_{sat}$  on minimum three pins poloidally and radially separated
-% 		 (filaments speed and size). 
-% 		\item Electron temperature (fast T$_e$ measurements
-%                   can be achieved with BPP in MAST-U {\footnotesize
-%                     (N. Walkden \#11)})
-% 		\item If possible $M_{\|}$
-% 	 \end{itemize}
-% 	 \item Camera viewing OM for measuring neutrals 
-% 	 \item Divertor measurements of $n$ and $T_e$ (probes) plus
-%            spectroscopy and bolometry 
-% 	 \item Density profile measurements (Li-Bes, Reflectometry (\#
-%            6 Acquiam, \# 8 Vicente), Edge Thomson scattering) 
-%          \item Sami and Field for fast particles accelleration (piggy
-%            back on developed scenarion \# 4 McClements)
-% %	\item H-mode quality diagnostics(div current, magnetics)
-% \end{enumerate}
-% \end{frame}
-
-% \begin{frame}[allowframebreaks]{Proposed shot plan - AUG}
-% \vspace{-1cm}
-% Allocated shots $\sim$ 14 + contingency 
-% \begin{itemize}
-% 	\item L-Mode (6 shots)
-% 	\begin{enumerate}
-% 		\item Reference shot \# 30276
-% 		\item Perform $I_p$ scan (three values) with fixed $B_T$
-% 		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
-% 		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
-% 		\item should we add OM puff to validate neutral measurements?
-% 		\item Possibility of strike-point sweeping during shot
-% 		\item RFEA measurements in internal program. 
-% 		\item These shots combines experiments proposed by:
-%                   Carralero (\# 7), Militello (\#1), Vianello (\#13)
-
-% 	\end{enumerate}
-% 	\item H-mode (9 shots)
-% 	\begin{enumerate}
-% 		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions
-%                   in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
-% 		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
-% 		\item Strike-point sweep if feasible? 
-% 		\item In all shots, particle acceleration in ELMs will be studied using microwaves,
-%                   soft X-rays, and FILD 
-% 		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
-% 		\item These shots combine experiments proposed by:
-%                   Aguiam (\#6), Carralero (\#7), McClements (\#4),
-%                   Militello (\# 1, 2), Vianello (\#13), Vicente (\#8)
-
-% 	\end{enumerate}
-% \end{itemize}
-% \end{frame}
-
-% \begin{frame}{Proposed shot plan - TCV}
-% 	\begin{itemize}
-% 		\item L-mode (11 shots)
-% 		\begin{enumerate}
-% 			\item Reference shot \# 53514
-% 			\item Same $I_p$ and $q_{95}$ scans as on AUG
-% 			\item Two shots with reversed $\bm{B} \times \nabla B$
-% 			\item Move plasma vertically. Disentangle
-%                           $q_{95}$ and $L_{\|}$	
-%                         \item These shots combines proposal: Vianello
-%                           (\#13), Tsui (\#15), Militello (\#1, 2)
-% 		\end{enumerate}
-% 		\item H-mode (12 shots)
-% 		\begin{enumerate}
-% 			\item Reference shot \# 53352
-% 			\item Since H-mode shoulder is new territory on TCV first shots will be scenario development
-% 			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
-%                         \item These shots combines proposal: Vianello
-%                           (\#13), Tsui (\#15), Militello (\#1, 2)
-% 		\end{enumerate}
-% 	\end{itemize}
-% \end{frame}
-
-% \begin{frame}{Preliminary shot plan  - MAST-U}
-% 	\begin{itemize}
-% 		\item L-mode (6 shots)
-% 		\begin{enumerate}		
-% 			\item New machine. No reference shot yet			
-% 			\item Same $I_p$ and $q_95$ scan to allow
-%                           cross-machine comparison. Availability of multi pin probe? 
-% 			\item Try varying fueling location
-% 			\item RFEA measurements during shoulder
-%                           formation 
-%                         \item These shots combines proposal: Militello
-%                           (\#1, 2, 3), Walkden (\#11), Vianello (\#13)
-% 		\end{enumerate}
-% 		\item H-mode (7 shots)
-% 		\begin{enumerate}
-% 			\item These experiments require the existence of H-mode reference shot. Perhaps not available in 2017
-% 			\item Similar scenario development as on other emachines
-%                         \item These shots combines proposal: Militello
-%                           (\#1, 2, 3),  Vianello (\#13)
-% 		\end{enumerate}
-% 		\item Probe head must be changed to allow
-%                   investigation of both fast T$_e$ (BPP),  and T$_i$
-%                   (RFEA) but this require careful schedule of machine time
-% 	\end{itemize}
-% \end{frame}
-
-% \begin{frame}{COMPASS collaboration}
-% \begin{itemize}
-% \item COMPASS is not an MST1 device, therefore no operational cost
-%   will be provided by MST1
-% \item However GA agrees that MST1 can provide part of the ppy for
-%   running experiments in line with MST1 topics
-% \item Proposal \# 14 is focused filaments dynamics and shoulder
-%   formation both in L and H-Mode
-% \item Experimental plan can be therefore agreed in order to perform
-%   similar experiments (e.g. I$_p$ and $q_{95}$ scan in L-Mode)
-%   ensuring proper comparison between devices
-% \item COMPASS suppose 3ppy for running and evaluation of experiment
-%   pertaining Topic-21, among Czeck and other european laboratories.
-% \end{itemize}
-% \end{frame}
-
-% \begin{frame}{There are urgent experiment which cannot be addressed}
-% \begin{itemize}
-% 	\item Detailed ion temp measurements. Must eventually be
-%           completed in internal programs. Are you willing to share the
-%           information among Topic 21 even though done internally?
-% 	\item Topology investigations? For example the comparison
-%           USN/LSN/DN is not included. Diagnostic capability of upper
-%           divertor is weaker than the lower one.
-%           Better to use reverse B$_t$  which is known
-%           to have influences in detachment as
-%           well \parencite{McLean}
-% 	\item Strikepoint sweeping and cryo pump
-% 	\item Parameters scans in H-mode
-% 	\item X-point probes
-% \end{itemize}
-% \end{frame}
-
-% \begin{frame}{Modeling require}
-%   \begin{enumerate}
-%     \item Mean field modeling, in particular for neutral investigation.
-%       Available for AUG (EMC3-EIRENCE) and
-%       MAST-U (SOLPS). So far we lack investigation for these scenario
-%       targeting TCV. Manpower needed from edge and SOL modeling
-%     \item Turbulence code: we should need self-consistent interaction
-%       with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
-%       \texttt{GBS}, \texttt{Tokam-3X}.
-%       Some of them can be run by people who will, very
-%       likely, apply for this topic, some other not
-%   \end{enumerate}
-% \end{frame}
-
-% \begin{frame}{Future and Miscellaneous}
-% 	\begin{itemize}
-% 		\item Possibility to piggybag on
-%                   Quiescent/small ELM H-mode shots (Topic 5,6, 18)
-% 		\item Shortly after this meeting we will organize
-%                   a follow-up meeting to reconcile ideas
-%                   from this discussion (date not fixed yet)
-% 		\item All information will be gathered on the wiki
-%                 \item Other channels for discussion/sharing. e.g. Slack
-%                   (mst1-topic21.slack.com), Github for code sharing, \ldots
-% 		\item We aim to arrive to a proper shared database of
-%                   filaments between the machines, where properties
-%                   will be obtained using agreed approaches so that a
-%                   cross-machine comparison paper could at the end be
-%                   finalized at a certain point		
-% 	\end{itemize}
-% \end{frame}
-
-% \begin{frame}{Discussion agenda}
-% 	\begin{enumerate}
-% 		\item Priorities. These are our personal ideas. Do we agree? 
-% 		\item \underline{Common measurement techniques}. Filament
-%                   properties, $\Lambda_{div}$ estimate and location,
-%                   Neutrals, packing fraction, \ldots 
-%  	\end{enumerate}
-% \end{frame}
-
 \end{document}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to slides for GPM

@@
       \item<7|only@7> AUG: At all the current a clear roll-over in
-        peak density observed and we can also track the radiation
+        peak density at the target observed and we can also track the radiation
         front move away from target earlier in density at lower current
@@
           the profile}
-        \item<6|only@6> Neutrals at lower current are substantially
+        \item<6|only@6> AUG: Neutrals at lower current are substantially
           higher even with similar edge density profiles.
-        \item<7|only@7> Neutrals at lower current are substantially
-          higher even with similar edge density profiles.
+        \item<7|only@7> AUG: Similarly to the observation at constant
+          q$_{95}$ target peak density rollover and radiation movement
+          from the target occurs earlier in density at lower plasma current
       \item<8|only@8> TCV: This tendency is substantially confirmed at

### 2017-11-14 Experiments/TCV/analysis/python/scriptAnalysis.py
update to IpConstantBt plot

@@ -1055,13 +1055,13 @@ while loop:
                 _ax2.plot(rhoLambda[_idx, :], Lambda[_idx, :],
                           '-', color=col, lw=3)
                 _ax2.axhline(1, ls='--', lw=2, color='grey')
-        ax2.set_ylim([0.01, 3])
+        ax2.set_ylim([0.06, 3])
         ax2.set_yscale('log')
         ax2.set_xlim([0.98, 1.08])
         ax2.legend(loc='best', numpoints=1, frameon=False, fontsize=14)
         ax2.axes.get_xaxis().set_visible(False)
         ax2.set_ylabel(r'n$_e$/n$_e(\rho_p = 1)$')
-        ax3.set_ylim([0.01, 3])
+        ax3.set_ylim([0.06, 3])
         ax3.set_yscale('log')
         ax3.set_xlim([0.98, 1.08])
         ax3.legend(loc='best', numpoints=1, frameon=False, fontsize=14)

### 2017-11-14 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Started correction of GPM slides

@@
   shoulder profile in H-Mode and establish dependence on
-  fuelling/neutral profiles/divertor conditioon
+  fuelling/neutral profiles/divertor condition
 \item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
@@
       \item<3|only@3> TCV: We repeat the same excercise at TCV with a
-        consistent variation of parallel connection length
+        consistent variation of parallel connection
+        length. \alert{L$_{\parallel} at TCV is almost one order of
+          magnitude larger than AUG$}
       \item<4|only@4> TCV: no additional heating
@@
       \item<8|only@8> TCV: This tendency is substantially confirmed at
-        TCV where
-        profiles  
+        TCV even though larger scatter in the data has been
+        obtained. To be combined with similar experiment performed
+        under MST1-2015  
       \item<9|only@9> TCV: This is consistent with onset of detachment
@@
         differences between the current
-      \item<11|only@11> TCV: confirm the observation of AUG. 
+      \item<11|only@11> TCV: Even at TCV no big differences in blob
+        size has been observed. Statistics should be increased
+        including past experiment from MST1-2015 
       \end{itemize}

### 2017-11-14 Experiments/AUG/analysis/python/scriptAnalysisShot.py
changed the size of marker for blob plot

@@ -3070,7 +3070,7 @@ while loop:
                         np.power(6.9e-3/Data.Lags[1], 2))
                     if Size*1e3 > 100:
                         Size /= 2.
-                    ax.plot(Data.Lambda, Size*1e3, 'o', color=col, ms=10)
+                    ax.plot(Data.Lambda, Size*1e3, 'o', color=col, ms=18)
                 except:
                     pass
         ax.set_xscale('log')
@@ -3104,7 +3104,8 @@ while loop:
                                 np.abs(Data.rhoLambda-1.03))]
                     else:
                         L=Data.Lambda
-                    ax.plot(L, Size*1e3, 'o', color=col, ms=10)
+                    ax.plot(L, Size*1e3, 'o', color=col,
+                            ms=18)
                     print Size
                     print Data.Lambda
                     print L

### 2017-11-14 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to PDF slides
Final amendment to slides

@@
     \begin{itemize}
-    \item<1-> Same fueling but with cryo-pumps
+    \item<1-> Same fueling but with cryo-pumps. \alert{To check role
+        of neutral density in H-Mode}
       \item<1-> H-5 density is different and remain constant, both
@@
           observation as obtained in JET when moving from horizontal
-          to vertical target?}
+          to vertical target or during horizontal target SP sweeping?}
      \item DN discharges. With slow movement of the second X-point into the vessel
@@
      \item \textcolor{consorziored}{H-Mode} 
-      \item Long divertor legs (probe in the lower port) to check if
+      \item \textcolor{ta2orange}{Long divertor legs (probe in the lower port) to check if
         increase of filamentary transport along the divertor leg
-        exists in high density scenarios
-      \item \textcolor{taorange}{SnowFlake to monitor the fluctuations in between the 2 separatrix
+        exists in high density scenarios}
+      \item \textcolor{gray}{SnowFlake to monitor the fluctuations in between the 2 separatrix
 	to be done in high density discharges}
-       \item \textcolor{taorange}{Try to move the second X-point in SN divertor at a different
+       \item \textcolor{gray}{Try to move the second X-point in SN divertor at a different
 	Z position while keeping the same radial distances between the
@@
     \item Check if trends can be reproduced
-    \item potential input for future experiments regarding role of
+    \item Potential input for future experiments regarding role of
         f.x. neutrals and recycling

### 2017-11-14 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to GPM
small correction from Volker

@@
 
-\begin{frame}{2017 Top Objectives 
-    12.12.2016}
+\begin{frame}{Motivation and deliverables}
   \Fontvi
   \vspace{-1cm}
-Deliverables listed during the call for manning of last December 
+  \begin{itemize}
+    \item \alert{Relation between downstream divertor conditions and
+        up-stream SOL profiles is not well understood. Influence of
+        SOL blob structures on shoulder formation and divertor
+        conditions is element towards predictive capabilities. }
+  \end{itemize}
+  \onslide<2->{Deliverables listed during the call for manning of last December
 \begin{enumerate}
-\item \only<2>{\color{ta3chameleon}} Cross-machine L-Mode
+\item \only<3>{\color{ta3chameleon}} Cross-machine L-Mode
   shoulder dependence on current both at constant B$_t$ and at
@@
   parallel connection length
-\item \only<2>{\color{taorange}}Establish robust scenario for density
+\item \only<3>{\color{taorange}}Establish robust scenario for density
   shoulder profile in H-Mode and establish dependence on
   fuelling/neutral profiles/divertor condition
-\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
-  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
+\item \only<3>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
+  filamentary transport under high-power H-Mode conditions \only<3>{\color{consorziored}}and under
   different plasma configurations (SN, DN)
-\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
+\item \only<3>{\color{taorange}}Study the role of ELM regimes,  neutral
   compression and particle density in filamentary transport and
   related shoulder formation
-\item \only<2>{\color{taorange}} Identify the contribution of
+\item \only<3>{\color{taorange}} Identify the contribution of
   collisionality and seeding on filamentary transport and related
   shoulder formation
-\item \only<2>{\color{consorziored}}Determine the effect of filaments and
+\item \only<3>{\color{consorziored}}Determine the effect of filaments and
   shoulder formation on target heat loads in different H-mode plasmas
-\end{enumerate}
-\onslide<2>{
+\end{enumerate}}
+\onslide<3>{
   So far H-Mode operation has been limited to AUG since no operational

### 2018-01-22 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
added the Tex File for 25th ITPA

\documentclass[10pt, compress]{beamer}
\usetheme[conference=25th ITPA-DivSOL,venue=Chengdu, date=29/01/2018, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{SOL Filamentary transport: update from joint AUG-TCV MST1 experiment}
\date{29 January 2018}
\author[N.Vianello]{presented by N. Vianello}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

\begin{frame}{Motivation and deliverables}
  \Fontvi
  \vspace{-1cm}
  \begin{itemize}
    \item \alert{Relation between downstream divertor conditions and
        up-stream SOL profiles is not well understood. Influence of
        SOL blob structures on shoulder formation and divertor
        conditions is key element towards predictive
        capabilities. Joint effort within the EUROfusion framework to
        address this issue on all the MST1 devices (AUG, TCV and MAST-U)}
  \end{itemize}
  \onslide<2->{A series of deliverables are foreseen for 2017-2018 program
\begin{enumerate}
\item \only<3>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<3>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<3>{\color{ta3chameleon}}Fluctuations mesurement on AUG to study
  filamentary transport under high-power H-Mode conditions \only<3>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<3>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<3>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<3>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}}
\onslide<3>{
I will report only on few of the deliverables since part of them will
be studied in forthcoming campaigns
}
\end{frame}

\begin{frame}{Current scan at constant B$_t$}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      %\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. AUG exhibit a parallel connection length
          which is 5 times smaller then TCV
        \item<2|only@2> AUG: Fueling reduced only at smaller current to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor.
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data.
        \item<5|only@5> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}  
\end{document}

### 2018-01-22 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the scripts and the figures with the shoulder amplitude behavior

@@ -8,7 +8,7 @@ import dd
 import itertools
 import matplotlib as mpl
 from mpl_toolkits.axes_grid.inset_locator import inset_axes
-from scipy.interpolate import UnivariateSpline
+from scipy.interpolate import UnivariateSpline, interp1d
 from scipy.signal import savgol_filter
 from scipy.signal import find_peaks_cwt
 from scipy.signal import decimate
@@ -17,6 +17,7 @@ import map_equ
 import equilibrium
 import libes
 import xarray as xray
+import h5py
 sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/submodules/pycwt/')
 sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/')
 sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/aug/')
@@ -87,6 +88,8 @@ def print_menu():
     print "49. Compare neutral evolution same current different field"
     print "50. Neutral density vs density and normalized greenwald fraction for Ip scan"
     print "51. Shoulder amplitude vs neutral density"
+    print "52. Shoulder amplitude vs LambdaDiv"
+    print "53. Shoulder amplitude vs Greenwalrd fraction"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -3628,7 +3631,7 @@ while loop:
         currentL = (0.6, 0.8, 0.99)
         fig2, ax2 = mpl.pylab.subplots(figsize=(10, 5), nrows=1, ncols=1)
         fig2.subplots_adjust(bottom=0.15)
-        for shot, _ip, col in zip(shotList, currentL, colorL):
+        for shot, _ip, col in zip(shotList, currentL, colorL): 
                 N = neutrals.Neutrals(shot)
                 # load also the edge density
                 Tot = dd.shotfile('TOT', shot)
@@ -3684,61 +3687,377 @@ while loop:
         shotList = (34103, 34102, 34104)
         currentL = (0.6, 0.8, 0.99)
         colorL = ('#82A17E', '#1E4682', '#DD6D3D')        
+        # this is the far and near SOL shoulde amplitude for current scant at consant q95
         fig, ax = mpl.pylab.subplots(figsize=(10, 10), nrows=2, ncols=1, sharex=True)
[…]

### 2018-01-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to figures of amplitude behavior

@@ -3825,11 +3825,11 @@ while loop:
             # restore now the value of LambdaDiv from the save data in the IAEA2018 folder
             File = h5py.File(Directory+'Shot%5i' % shot + '.h5')
             _idx = np.where((File['LambdaDivRho'].value >= 1) &
-                            (File['LambdaDivRho'].value < 1.02))
-            LNear = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=1).ravel()
+                            (File['LambdaDivRho'].value < 1.02))[0]
+            LNear = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=0).ravel()
             _idx = np.where((File['LambdaDivRho'].value >= 1.02) &
-                            (File['LambdaDivRho'].value < 1.06))
-            LFar = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=1).ravel()
+                            (File['LambdaDivRho'].value < 1.06))[0]
+            LFar = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=0).ravel()
             # Univariate and plot
             S = interp1d(File['LambdaDivTime'].value.ravel(), LNear,
                          kind='linear', fill_value='extrapolate')
@@ -3895,11 +3895,11 @@ while loop:
             # restore now the value of LambdaDiv from the save data in the IAEA2018 folder
             File = h5py.File(Directory+'Shot%5i' % shot + '.h5')
             _idx = np.where((File['LambdaDivRho'].value >= 1) &
-                            (File['LambdaDivRho'].value < 1.03))
-            LNear = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=1).ravel()
-            _idx = np.where((File['LambdaDivRho'].value >= 103) &
-                            (File['LambdaDivRho'].value < 1.06))
-            LFar = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=1).ravel()
+                            (File['LambdaDivRho'].value < 1.025))[0]
+            LNear = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=0).ravel()
+            _idx = np.where((File['LambdaDivRho'].value >= 1.025) &
+                            (File['LambdaDivRho'].value < 1.06))[0]
+            LFar = np.nanmean(File['LambdaDiv'].value[_idx, :], axis=0).ravel()
             # Univariate and plot
             S = interp1d(File['LambdaDivTime'].value.ravel(), LNear, kind='linear',
                          fill_value='extrapolate')

### 2018-01-23 Codes/python/aug/libes.py
amend libes and scriptAnalysis

@@ -146,8 +146,7 @@ class Libes(object):
             Amplitude.append(pDummy-pN)
             Location.append(rhoDummy[np.argmax(pDummy-pN)])
             time[i] = (start+i*dt+dt/2)
-            Rmid = self.eq.rho2rho('sqrtpsinorm', 'Rmid', self.rho, time[i])
-            Efold.append(c)
+            Efold.append(c[self.rho>1])
 
             
         self.Amplitude = np.asarray(Amplitude)

### 2018-01-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -89,7 +89,9 @@ def print_menu():
     print "50. Neutral density vs density and normalized greenwald fraction for Ip scan"
     print "51. Shoulder amplitude vs neutral density"
     print "52. Shoulder amplitude vs LambdaDiv"
-    print "53. Shoulder amplitude vs Greenwalrd fraction"
+    print "53. Shoulder amplitude vs Greenwald fraction"
+    print "54. Shoulder amplitude vs Edge density fraction"
+    print "55. Neutrals vs Edge density"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -3588,6 +3590,7 @@ while loop:
         currentL = (0.6, 0.8, 0.99)
         colorL = ('#82A17E', '#1E4682', '#DD6D3D')        
         fig, ax = mpl.pylab.subplots(figsize=(10, 10), nrows=2, ncols=1, sharex=True)
+        fig.subplots_adjust(bottom=0.15)
         fig2, ax2 = mpl.pylab.subplots(figsize=(10, 5), nrows=1, ncols=1)
         fig2.subplots_adjust(bottom=0.15)
         for shot, _ip, col in zip(shotList, currentL, colorL):
@@ -4056,7 +4059,202 @@ while loop:
         fig.savefig('../pdfbox/AmplitudeVsGreenwaldIpConstantBt.pdf',
                     bbox_ot_inches='tight')
 
+    elif selection == 54:
+        # produce amplitude vs Greenwald fraction
+        # for current scan at constant Q95
+        shotList = (34103, 34102, 34104)
+        currentL = (0.6, 0.8, 0.99)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')      
+        fig, ax = mpl.pylab.subplots(figsize=(8, 6), nrows=2, ncols=1, sharex=True)
+        fig.subplots_adjust(bottom=0.15)
+        Directory = '/afs/ipp-garching.mpg.de/home/n/nvianell/analisi/iaea2018/data/aug/'
+        for shot, _ip, col in zip(shotList, currentL, colorL):
+            # compute the amplitude of the LiB
+            LiB = libes.Libes(shot)
+            dt = 0.05
+            LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
+            # now integrate in the near and far SOL defining respectively for
+            # (1<rho<1.02 and 1.02<rho<1.04)
[…]

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX

@@
 \usepackage{rfxcolor}
+% multiple figure location
+%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
 % for drawing
@@
       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
-      %\includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
-      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
+      \includegraphics<4>[width=\textwidth]{NeutralsVsGreenwaldConstantBt}
+      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
+      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
     \end{column}
@@
           keep power in the SOL approximately constant
-        \item<3|only@3> TCV: Similar neutral compression reached and
+        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
           D$_{\alpha}$ radiation from the floor. 
@@
           from D$_{\alpha}$ calibrated camera and using electron
-          density and temperature from LP data.
-        \item<5|only@5> For both AUG and TCV flattening of normalized
+          density and temperature from LP data. Neutral density
+          increase earlier in edge density at smaller current
+        \item<5|only@5> Neutrals behavior reconciled whenever
+          comparison considered as a function of Greenwald fractin  
+        \item<6|only@6> For both AUG and TCV flattening of normalized
           upstream profile reached \alert{earlier in density at lower

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX for itpa

@@
       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
-      \includegraphics<4>[width=\textwidth]{NeutralsVsGreenwaldConstantBt}
+      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
       \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
       \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
+      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
     \end{column}
@@
           density and temperature from LP data. Neutral density
-          increase earlier in edge density at smaller current
+          increases earlier in edge density at lower current
         \item<5|only@5> Neutrals behavior reconciled whenever
-          comparison considered as a function of Greenwald fractin  
+          comparison considered as a function of Greenwald fraction  
         \item<6|only@6> For both AUG and TCV flattening of normalized
@@
           reached for larger values of $\Lambda_{div}$
+        \item<7|only@7> Quantifying profile evolution using the
+          \alert{shoulder amplitude metric} introduce by Wynn and
+          Lipschultz for JET. \alert{Amplitude is the difference
+            between normalized upstream density profiles}  
       \end{itemize}

### 2018-01-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py
Update to scriptAnalysis to have Figure with Efold

@@ -3686,43 +3686,77 @@ while loop:
     elif selection == 51:
         shotList = (34103, 34102, 34104)
         currentL = (0.6, 0.8, 0.99)
-        colorL = ('#82A17E', '#1E4682', '#DD6D3D')        
-        # this is the far and near SOL shoulde amplitude for current scant at consant q95
-        fig, ax = mpl.pylab.subplots(figsize=(10, 10), nrows=2, ncols=1, sharex=True)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        # this is the far and near SOL shoulde amplitude
+        # for current scant at consant q95
+        fig, ax = mpl.pylab.subplots(figsize=(10, 10),
+                                     nrows=2, ncols=1, sharex=True)
         fig.subplots_adjust(bottom=0.15)
-        for shot, _ip,_idx, col in zip(
-            shotList, currentL,
-            range(len(shotList)), colorL):
+        # open a second figure where we will plot also
+        # the evolution of lambda_n
+        fig2, ax2 = mpl.pylab.subplots(figsize=(10, 10),
+                                       nrows=2, ncols=1, sharex=True)
+        fig2.subplots_adjust(bottom=0.15)
+        for shot, _ip, _idx, col in zip(shotList, currentL,
+                                        range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
             LiB = libes.Libes(shot)
             dt = 0.05
-            LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=N.n0Time.min())
+            LiB.amplitudeShoulder(dt=dt,
+                                  reference=[1.2, 1.4], start=N.n0Time.min())
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
-            _idA = np.where((LiB.rhoAmplitude >= 1) & (LiB.rhoAmplitude < 1.03))[0]
-            _idB = np.where((LiB.rhoAmplitude >= 1.03) & (LiB.rhoAmplitude < 1.06))[0]
+            _idA = np.where((LiB.rhoAmplitude >= 1) &
+                            (LiB.rhoAmplitude < 1.03))[0]
+            _idB = np.where((LiB.rhoAmplitude >= 1.03) &
[…]

### 2018-01-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to script Analysis
Now we have also the evolution of Efolding length

@@ -3689,43 +3689,77 @@ while loop:
     elif selection == 51:
         shotList = (34103, 34102, 34104)
         currentL = (0.6, 0.8, 0.99)
-        colorL = ('#82A17E', '#1E4682', '#DD6D3D')        
-        # this is the far and near SOL shoulde amplitude for current scant at consant q95
-        fig, ax = mpl.pylab.subplots(figsize=(10, 10), nrows=2, ncols=1, sharex=True)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        # this is the far and near SOL shoulde amplitude
+        # for current scant at consant q95
+        fig, ax = mpl.pylab.subplots(figsize=(10, 10),
+                                     nrows=2, ncols=1, sharex=True)
         fig.subplots_adjust(bottom=0.15)
-        for shot, _ip,_idx, col in zip(
-            shotList, currentL,
-            range(len(shotList)), colorL):
+        # open a second figure where we will plot also
+        # the evolution of lambda_n
+        fig2, ax2 = mpl.pylab.subplots(figsize=(10, 10),
+                                       nrows=2, ncols=1, sharex=True)
+        fig2.subplots_adjust(bottom=0.15)
+        for shot, _ip, _idx, col in zip(shotList, currentL,
+                                        range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
             LiB = libes.Libes(shot)
             dt = 0.05
-            LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=N.n0Time.min())
+            LiB.amplitudeShoulder(dt=dt,
+                                  reference=[1.2, 1.4], start=N.n0Time.min())
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
-            _idA = np.where((LiB.rhoAmplitude >= 1) & (LiB.rhoAmplitude < 1.03))[0]
-            _idB = np.where((LiB.rhoAmplitude >= 1.03) & (LiB.rhoAmplitude < 1.06))[0]
+            _idA = np.where((LiB.rhoAmplitude >= 1) &
+                            (LiB.rhoAmplitude < 1.03))[0]
+            _idB = np.where((LiB.rhoAmplitude >= 1.03) &
[…]

### 2018-01-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to scriptAnalysis and few figures
# Conflicts:
#	Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -89,7 +89,9 @@ def print_menu():
     print "50. Neutral density vs density and normalized greenwald fraction for Ip scan"
     print "51. Shoulder amplitude vs neutral density"
     print "52. Shoulder amplitude vs LambdaDiv"
-    print "53. Shoulder amplitude vs Greenwalrd fraction"
+    print "53. Shoulder amplitude vs Greenwald fraction"
+    print "54. Shoulder amplitude vs Edge density fraction"
+    print "55. Neutrals vs Edge density"
     print "99: End"
     print 67 * "-"
 loop = True
@@ -3588,6 +3590,7 @@ while loop:
         currentL = (0.6, 0.8, 0.99)
         colorL = ('#82A17E', '#1E4682', '#DD6D3D')        
         fig, ax = mpl.pylab.subplots(figsize=(10, 10), nrows=2, ncols=1, sharex=True)
+        fig.subplots_adjust(bottom=0.15)
         fig2, ax2 = mpl.pylab.subplots(figsize=(10, 5), nrows=1, ncols=1)
         fig2.subplots_adjust(bottom=0.15)
         for shot, _ip, col in zip(shotList, currentL, colorL):
@@ -3686,43 +3689,77 @@ while loop:
     elif selection == 51:
         shotList = (34103, 34102, 34104)
         currentL = (0.6, 0.8, 0.99)
-        colorL = ('#82A17E', '#1E4682', '#DD6D3D')        
-        # this is the far and near SOL shoulde amplitude for current scant at consant q95
-        fig, ax = mpl.pylab.subplots(figsize=(10, 10), nrows=2, ncols=1, sharex=True)
+        colorL = ('#82A17E', '#1E4682', '#DD6D3D')
+        # this is the far and near SOL shoulde amplitude
+        # for current scant at consant q95
+        fig, ax = mpl.pylab.subplots(figsize=(10, 10),
+                                     nrows=2, ncols=1, sharex=True)
         fig.subplots_adjust(bottom=0.15)
-        for shot, _ip,_idx, col in zip(
-            shotList, currentL,
-            range(len(shotList)), colorL):
+        # open a second figure where we will plot also
+        # the evolution of lambda_n
+        fig2, ax2 = mpl.pylab.subplots(figsize=(10, 10),
+                                       nrows=2, ncols=1, sharex=True)
[…]

### 2018-01-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to scriptAnalysis and few figures

@@ -3699,7 +3699,7 @@ while loop:
         # the evolution of lambda_n
         fig2, ax2 = mpl.pylab.subplots(figsize=(10, 10),
                                        nrows=2, ncols=1, sharex=True)
-        fig2.subplots_adjust(bottom=0.15)
+        fig2.subplots_adjust(bottom=0.15, left=0.15)
         for shot, _ip, _idx, col in zip(shotList, currentL,
                                         range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
@@ -3721,14 +3721,14 @@ while loop:
             EfoldA = np.nanmean(LiB.Efold[:, _idA], axis=1)
             EfoldB = np.nanmean(LiB.Efold[:, _idB], axis=1)
             EfoldAS = np.nanstd(LiB.Efold[:, _idA], axis=1)
-            EfoldBS = np.nanstd(LiB.Efodl[:, _idB], axis=1)
+            EfoldBS = np.nanstd(LiB.Efold[:, _idB], axis=1)
 
             # interpolate the neutrals on the same time basis
             S = UnivariateSpline(N.n0Time, N.n0, s=0)
             x, y, e = S(LiB.timeAmplitude[AmpA > 0]), AmpA[AmpA > 0], AmpAS[AmpA > 0]
             ax[0].errorbar(x[np.argsort(x)],
                            y[np.argsort(x)],
-                           err=e[np.argsort(x)],
+                           yerr=e[np.argsort(x)],
                            fmt='o', ms=8, mec=col, color=col,
                            capsize=0)
             ax[0].text(0.15, 0.85,
@@ -3751,7 +3751,7 @@ while loop:
                             fmt='o', ms=8, mec=col, color=col,
                             capsize=0)
             ax2[0].text(0.15, 0.85, r'$1\leq \rho< 1.03$',
-                        transform=ax[0].transAxes)
+                        transform=ax2[0].transAxes)
             x, y, e = S(LiB.timeAmplitude), EfoldB*1e2, EfoldBS*1e2
             ax2[1].errorbar(x[np.argsort(x)],
                             y[np.argsort(x)],
@@ -3759,7 +3759,7 @@ while loop:
                             fmt='o', ms=8, mec=col, color=col,
[…]

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
update to TeX

@@
       \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
+      \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
+      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
     \end{column}
@@
             between normalized upstream density profiles}
+        \item<8-9> Amplitude evolve faster in density at lower
+          current \onslide<9>{\alert{but once evolution \textit{vs} greenwald
+            fraction is considered the evolution is equivalent between
+          different current}}  
       \end{itemize}

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Still improving the tex file for ITPA

@@
 I will report only on few of the deliverables since part of them will
-be studied in forthcoming campaigns
+be studied in forthcoming campaigns. \textcolor{red}{Remember this is
+  still a work in progress}
 }
@@
       \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
+      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
+      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
     \end{column}
@@
             between normalized upstream density profiles}
-        \item<8-9> Amplitude evolve faster in density at lower
-          current \onslide<9>{\alert{but once evolution \textit{vs} greenwald
+        \only<8-9>{\item Amplitude evolve faster in density at lower
+          current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
             fraction is considered the evolution is equivalent between
-          different current}}  
+            different current}}}
+        \item<10|only@10> Amplitude evolution still reconciled in AUG if
+          considered as a function of local evolution of $\Lambda_{div}$
+        \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
+          with blob size without significant difference within the
+          current explored
       \end{itemize}
@@
 \end{frame}
+
+\begin{frame}{Current scan at constant q$_{95}$}
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
+      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
+      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
+      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
+      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
+      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
+      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
+      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item<1|only@1> Shape matched in within the single scan even
+          though this required for TCV operation with very low
+          toroidal field (0.8T)
+        \item<1|only@1> The parallel connection length remains almost unchanged
+        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
+          pretty reproducible behavior matching basically the plasma
+          condition in within the current scan
+        \item<3|only@3> TCV: Even at such an high density at lower
+          current (and lower B$_t$) no sign of target ion flux
+          rollover/detachment
+        \item<4|only@4> AUG: Divertor neutral density exhibits still
+          the same behavior is considered as a function of greenwald fraction
+        \item<5|only@5> For AUG upstream and target profiles exhibit
+          the same behavior with flattening observed at large values
+          of $\Lambda_{div}$. TCV actually even at high value of
+          density no sign of upstream profile flattening \alert{even
+            at very large values of $\Lambda_{div}$}
+        \item<6|only@6> This is due to the fact we did not reach
+          divertor detachment which \alert{seems necessary for
+            upstream profile modification}  
+        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
+          still reconcile the explored current scan
+
+      \end{itemize}
+    \end{column}
+  \end{columns}
+
+\end{frame}
+
 \end{document}

### 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
update to TeX

@@
       \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
-      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
+      \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
+      \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
     \end{column}
@@
           still reconcile the explored current scan
+        \item<8|only@8> AUG exhibit consistently an increase of
+          $\lambda_n$ with blob-size whereas for TCV the profile
+          remains flat consistently with a small variation of
+          $\delta_b$
+        \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$
 

### 2018-01-24 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to scriptAnalysisShot to compare shots 34276 34278 34281

@@ -92,6 +92,9 @@ def print_menu():
     print "53. Shoulder amplitude vs Greenwald fraction"
     print "54. Shoulder amplitude vs Edge density fraction"
     print "55. Neutrals vs Edge density"
+    print "56. Compare shots 34276-34278-34281 general"
+    print "57. Compare shots 34276-34278-34281 profiles"
+    print "58. Elm behavior 34276-34278-34281 "
     print "99: End"
     print 67 * "-"
 loop = True
@@ -275,7 +278,7 @@ while loop:
             ax[1, 1].set_ylabel(r'D$_2$  [10$^{21}$]')
 
             ax[2, 1].plot(Gas.signal['F01']['t'],
-                          Gas.signal['F01']['data']/1e21, color=_col, lw=3)
+                          Gas.signal['F01']['data']/1e22, color=_col, lw=3)
             ax[2, 1].set_ylabel(r'F01 [10$^{21}$m$^{-2}$s$^{-1}$]')
             ax[2, 1].axes.get_xaxis().set_visible(False)
             diag.close
@@ -4700,6 +4703,154 @@ while loop:
         for t, c in zip(leg.get_texts(), colorL):
             t.set_color(c)
         fig2.savefig('../pdfbox/NeutralsVsNe5IpConstantBt.pdf', bbox_to_inches='tight')
+
+    elif selection == 56:
+        shotList = (34276, 34278, 34281)
+        colorList = ('#324D5C', '#E37B40', '#60A65F')
+        fig, ax = mpl.pylab.subplots(figsize=(10, 14), nrows=5, ncols=1, sharex=True)
+        fig.subplots_adjust(hspace=0.05, top=0.96, bottom=0.1)
+        for shot, col in zip(shotList, colorList):
+            diag = dd.shotfile('DCN', shot)('H-5')
+            ax[0].plot(diag.time, diag.data/1e19, color=col, lw=3, label='# %5i' % shot)
+            diag = dd.shotfile('UVS', shot)('D_tot')
+            ax[1].plot(diag.time, diag.data/1e21, color=col, lw=3)
+            diag = dd.shotfile('UVS', shot)('N_tot')
+            ax[2].plot(diag.time, diag.data/1e21, color=col, lw=3)
+            diag = dd.shotfile('IOC', shot)('F01')
+            ax[3].plot(diag.time, diag.data/1e22, color=col, lw=3)
+            diag = dd.shotfile('MAC', shot)('Tdiv')
[…]

### 2018-01-24 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX file

@@
         \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$
-
       \end{itemize}
@@
   \end{columns}
-
+\end{frame}
+%% H-Mode same fueling
+\begin{frame}{H-Mode compare fueling with/wo
+      cryopump}
+    \Fontvi
+  \vspace{-1cm}
+  \begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
+    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
+    \only<3>{
+    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
+      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
+      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
+    \end{tikzonimage}}
+  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}}
+  \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+    \item<1|only@1> Same fueling but with cryo-pumps. \alert{To check role
+        of neutral density in H-Mode}
+      \item<1|only@1> H-5 density is different and remain constant, both
+        divertor and midplane pressure are reduced (to 1/3
+        approximately) no sign of detachment
+      \item<2|only@2> Different ELMy regimes reached with reduced size and
+        increased frequency without the cryopumps
+      \item<3|only@3> Also with this amount of fueling weaker indication of SOL
+        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
+      \item<4|only@4> Inter-ELM resolved profile suggest a flattening even
+        with the cryompumps still even though $\Lambda_{div}$ is
+        marginal above 1 only in the near SOL
+       \item<5|only@5> Without the cryopumps, we reached flatter
+         profiles with comparable inter-ELM resolved blob-size. This
+         indicates strong neutral pressure effects in determining
+         upstream profiles
+      \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
+%% H-Mode different torus
+\begin{frame}{Matching scenarios with cryo-pumps}
+\Fontvi
+  \vspace{-1cm}
+\begin{columns}
+  \begin{column}{0.65\textwidth}
+    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
+    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
+    \centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
+    \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34281}}
+  \end{column}
+  \begin{column}{0.35\textwidth}
+    \begin{itemize}
+      \item<1|only@1> To match similar edge density and divertor pressure
+        and to reach the same level of detachment we increase the
+        fueling by almost a factor of 3, increasing also the rate. In
+        addition to that we also increase substantially the N
+        puffing. \alert{Degraded H-Mode reached earlier in density
+          without the cryopumps}
+      \item<2|only@2> Similar ELMy behavior obtained during the density ramp  
+      \item<3|only@3> Now the scenario suggest a strong profile flattening
+        even with the cryopumps
+       \item<4|only@4> Inter-ELM resolved Li-Be profiles confirm this with
+         shoulder formed with similar strength even with the cryopumps
+         in operation.
+         \item<5|only@5> Both size and $\lambda_n$ closer with/wo the cryopumps 
+       \end{itemize}
+  \end{column}
+\end{columns}
 \end{frame}

### 2018-01-24 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex

--- 2018-01-23 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
@@
 \usepackage{rfxcolor}
+\definecolor{colorA}{HTML}{324D5C}
+\definecolor{colorB}{HTML}{E37B40}
+\definecolor{colorC}{HTML}{60A65F}
 % multiple figure location
@@
 \date{29 January 2018}
-\author[N.Vianello]{presented by N. Vianello}
+\author[N.Vianello]{presented by N. Vianello for the MST1-Topic 21
+  scientific team}
 \begin{document}
@@
   \end{columns}
+\end{frame}
+%% H-Mode same fueling
+\begin{frame}{H-Mode analysis on AUG}
+    \Fontvi
+  \vspace{-1cm}
+  \begin{columns}
+  \begin{column}{0.55\textwidth}
+    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
+  \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
+  \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
+  \end{column}
+  \begin{column}{0.45\textwidth}
+    \begin{itemize}
+    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
+      total heating power where we changed the fueling and the
+      efficiency of cryopumps. Specifically we have
+      \begin{itemize}
+        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
+            cryompumps}
+        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
+            fueling as \# 34276 but with the cryompump}
+        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
+            fueling and seeding trying to mimic the same subdivertor
+            pressure as \# 34276}
+      \end{itemize}
+    \item<1|only@1> Keeping the same fueling with the cryopump clearly
+      reduce the pressure in the the sub-divertor area, we don't reach
+      clear detachment and the edge density is constant even during
+      the fueling ramp. Degraded H-mode reached later without the cryopump
 
+    \item<2|only@2> Different behavior of ELM during the fueling
+      ramp. ELM size and frequency changes strongly without the
+      cryopump or during extreme fueling case
+    \item<3|only@3> Profiles
+    \item<4|only@4> Without the cryopumps, we reached flatter
+         profiles with comparable inter-ELM resolved blob-size. This
+         indicates strong neutral pressure effects in determining
+         upstream profiles
+    \item<5|only@5> Increasing the fueling and correspondingly the
+      divertor neutral pressure move towards a situation similar to
+      \# 34276 without the cryopump
+      \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
+
+\begin{frame}{Conclusion}
+  \Fontvi
+  \begin{itemize}
+    \item Current scan at constant B$_t$ and at constant q$_{95}$
+      performed during density ramps L-Mode experiments both at AUG
+      and TCV
+    \item In both the case shoulder appear earlier in density at lower
+      current but AUG shows reconciliation of behavior if considered
+      as a function of greenwald fraction and $\Lambda_{div}$
+    \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
+      blob size is increasing, independently from the current. The
+      same behavior is observed during current scan at constant
+      q$_{95}$ \alert{only on AUG}
+    \item On TCV during the current scan at constant q$_{95}$
+      detachment not reached and this \alert{prevent upstream profile
+        flattening}
+    \item H-Mode experiments performed on AUG where fueling and
+      pumping have been varied. Proved inter-ELM profile flattening
+      also in H-Mode with a more efficient puffing without the
+      cryopump. \alert{Hints on the role of neutrals also in H-Mode}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{D$_{\alpha}$ tomography: work in progress}
+\Fontvi
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
+      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
+      \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+        \item \alert{Preliminary} results from inversion tomography
+          from calibrated D$_{\alpha}$ camera under the assumption of
+          toroidally symmetric emission limited to the region outside
+          the LCFS
+        \item \emph{Simultaneous Algebraic Reconstruction Technique
+            (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
+            \textbf{6},  81 (1984))}
+        \item As time evolves during the L-Mode ramp we observe
+          D$_{\alpha}$ radiation moving from HFS towards the LFS
+          common flux region
+        \item \alert{This is consistent with JET observation in
+            Horizontal target regime whenever shoulder is observed}
+      \end{itemize}
+    \end{column}
+  \end{columns}
 \end{frame}

### 2018-01-24 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the comparison of 34276 34278 and 34281 upstream and target profiles

@@ -4759,9 +4759,9 @@ while loop:
         ax6 = mpl.pylab.subplot2grid((4, 3), (2, 1))        
         ax7 = mpl.pylab.subplot2grid((4, 3), (2, 2))
         # these are the panel for Lambda
-        ax8 = mpl.pylab.subplot2grid((4, 3), (2, 0))
-        ax9 = mpl.pylab.subplot2grid((4, 3), (2, 1))        
-        ax10 = mpl.pylab.subplot2grid((4, 3), (2, 2))
+        ax8 = mpl.pylab.subplot2grid((4, 3), (3, 0))
+        ax9 = mpl.pylab.subplot2grid((4, 3), (3, 1))        
+        ax10 = mpl.pylab.subplot2grid((4, 3), (3, 2))
         # list of axes
         axProf = (ax2, ax3, ax4)
         axTarg = (ax5, ax6, ax7) 
@@ -4781,20 +4781,22 @@ while loop:
             for t, _axp, _axt, _axl, _tr in zip(
                 tList, axProf, axTarg, axLamb, thresh):
                 ax1.axvline((t[0]+t[1])/2, ls='-', lw=2, color='gray')
-                p, e, ef, pN, eN = LiB.averageProfiles(
+                p, e, ef, pN, eN = LiB.averageProfile(
                     trange=[t[0], t[1]],
                     interelm=True, threshold=_tr)
                 _axp.semilogy(LiB.rho, pN, color=col, lw=2)
-                _axp.fill_between(LiB.rho, pN-eN, pN+eN, color=col, alpha=0.3)
+                _axp.errorbar(LiB.rho, pN, yerr=eN, fmt='none',
+                              ecolor=col, alpha=0.3)
                 
                 rho, en, err = Target.PlotEnProfile(
                     trange=[t[0], t[1]], interelm=True,
                     threshold=_tr, Plot=False)
-                _axt.errorbar(rho, en/1e19, yerr=err/1e19,
-                              fmt='--o', capsize=0, color=col)
+                _axt.errorbar(rho, en/1e19, yerr=err/1e19/2,
+                              fmt='--o', capsize=0, color=col, ms=12,
+                              mec=col, alpha=0.5)
                 rhoL, Lambda = Target.computeLambda(
                     trange=[t[0], t[1]], interelm=True,
-                    threshold=_thr, Plot=False)
[…]

### 2018-01-24 Experiments/AUG/analysis/python/scriptAnalysisShot.py
added the comparison of 34276 34278 and 34281 upstream and target profiles
# Conflicts:
#	Experiments/AUG/analysis/python/scriptAnalysisShot.py

@@ -92,6 +92,9 @@ def print_menu():
     print "53. Shoulder amplitude vs Greenwald fraction"
     print "54. Shoulder amplitude vs Edge density fraction"
     print "55. Neutrals vs Edge density"
+    print "56. Compare shots 34276-34278-34281 general"
+    print "57. Compare shots 34276-34278-34281 profiles"
+    print "58. Elm behavior 34276-34278-34281 "
     print "99: End"
     print 67 * "-"
 loop = True
@@ -275,7 +278,7 @@ while loop:
             ax[1, 1].set_ylabel(r'D$_2$  [10$^{21}$]')
 
             ax[2, 1].plot(Gas.signal['F01']['t'],
-                          Gas.signal['F01']['data']/1e21, color=_col, lw=3)
+                          Gas.signal['F01']['data']/1e22, color=_col, lw=3)
             ax[2, 1].set_ylabel(r'F01 [10$^{21}$m$^{-2}$s$^{-1}$]')
             ax[2, 1].axes.get_xaxis().set_visible(False)
             diag.close
@@ -4700,6 +4703,165 @@ while loop:
         for t, c in zip(leg.get_texts(), colorL):
             t.set_color(c)
         fig2.savefig('../pdfbox/NeutralsVsNe5IpConstantBt.pdf', bbox_to_inches='tight')
+
+    elif selection == 56:
+        shotList = (34276, 34278, 34281)
+        colorList = ('#324D5C', '#E37B40', '#60A65F')
+        fig, ax = mpl.pylab.subplots(figsize=(10, 14), nrows=5, ncols=1, sharex=True)
+        fig.subplots_adjust(hspace=0.05, top=0.96, bottom=0.1)
+        for shot, col in zip(shotList, colorList):
+            diag = dd.shotfile('DCN', shot)('H-5')
+            ax[0].plot(diag.time, diag.data/1e19, color=col, lw=3, label='# %5i' % shot)
+            diag = dd.shotfile('UVS', shot)('D_tot')
+            ax[1].plot(diag.time, diag.data/1e21, color=col, lw=3)
+            diag = dd.shotfile('UVS', shot)('N_tot')
+            ax[2].plot(diag.time, diag.data/1e21, color=col, lw=3)
+            diag = dd.shotfile('IOC', shot)('F01')
+            ax[3].plot(diag.time, diag.data/1e22, color=col, lw=3)
+            diag = dd.shotfile('MAC', shot)('Tdiv')
[…]

### 2018-01-24 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update and correction to TeX file for ITPA

@@
 \date{29 January 2018}
-\author[N.Vianello]{presented by N. Vianello for the MST1-Topic 21
+\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
   scientific team}
@@
 
-\begin{frame}{Current scan at constant B$_t$}
+\begin{frame}{Current scan at constant B$_t$ in L-Mode plasma}
   \begin{columns}
@@
           which is 5 times smaller then TCV
-        \item<2|only@2> AUG: Fueling reduced only at smaller current to
+        \item<2|only@2> AUG: Fueling reduced only at lower I$_p$ to
           avoid earlier disruption. Similar neutral pressure in the
@@
         \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
-          D$_{\alpha}$ radiation from the floor. 
+          D$_{\alpha}$ radiation from the floor. Ion flux rollover
+          reached in all the three current,  although marginally at
+          330 kA
         \item<4|only@4> Divertor neutral density estimated starting
@@
           rollover/detachment
-        \item<4|only@4> AUG: Divertor neutral density exhibits still
-          the same behavior is considered as a function of greenwald fraction
-        \item<5|only@5> For AUG upstream and target profiles exhibit
-          the same behavior with flattening observed at large values
-          of $\Lambda_{div}$. TCV actually even at high value of
-          density no sign of upstream profile flattening \alert{even
+        \item<4|only@4> AUG: Divertor neutral density exhibits 
+          the same behavior if considered as a function of greenwald fraction
+        \item<5|only@5> For AUG upstream and target profiles still
+          exhibit flattening earlier in density at lower current but
+          \alert{always at large values of 
+          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
             at very large values of $\Lambda_{div}$}
         \item<6|only@6> This is due to the fact we did not reach
-          divertor detachment which \alert{seems necessary for
+          divertor detachment which \alert{seems mandatory for
             upstream profile modification}  
@@
           $\delta_b$
-        \item<9|only@9> And for TCV this is true even at high value of $\Lambda_{div}$
+        \item<9|only@9> And for TCV this is true even at high value of
+          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
+          guarantee flat profiles on TCV.}
       \end{itemize}

### 2018-01-25 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to UpstreamDivertorProfiles figure

@@ -4747,8 +4747,9 @@ while loop:
     elif selection == 57:
         shotList = (34276, 34278, 34281)
         colorList = ('#324D5C', '#E37B40', '#60A65F')
+        colorTimeList = ('#FF4F00', '#00A963', '#0080B6')
         fig = mpl.pylab.figure(figsize=(14, 14))
-        fig.subplots_adjust(hspace=0.25, right=0.96, top=0.96)
+        fig.subplots_adjust(hspace=0.28, right=0.96, top=0.96)
         ax1 = mpl.pylab.subplot2grid((4, 3), (0, 0), colspan=3)
         # these are the panel for upstream profiles
         ax2 = mpl.pylab.subplot2grid((4, 3), (1, 0))
@@ -4767,48 +4768,49 @@ while loop:
         axTarg = (ax5, ax6, ax7) 
         axLamb = (ax8, ax9, ax10)
         # tranges
-        tList = ((3, 3.1), (4, 4.1), (4.9, 5))
+        tList = ((3, 3.1), (3.8, 3.9), (5.1, 5.2))
         # now we need to find for each of the time intervals
         # the appropriate threshold for inter-ELM
         thresholdList = ((1000, 500, 250),
-                         (1800, 1200, 1200),
-                         (1000, 500, 350))
-        for shot, col, thresh in zip(shotList, colorList, thresholdList):
+                         (1800, 1200, 800),
+                         (1000, 500, 250))
+        for shot, col, thresh, _axp, _axt, _axl in itertools.izip(
+            shotList, colorList, thresholdList, axProf, axTarg, axLamb):
             diag = dd.shotfile('DCN', shot)('H-5')
             ax1.plot(diag.time, diag.data/1e19, color=col, label='# %5i' % shot, lw=3)
             LiB = libes.Libes(shot)
             Target = langmuir.Target(shot)
-            for t, _axp, _axt, _axl, _tr in zip(
-                tList, axProf, axTarg, axLamb, thresh):
-                ax1.axvline((t[0]+t[1])/2, ls='-', lw=2, color='gray')
+            for t, _tr, _colorT in zip(
+                tList, thresh, colorTimeList):
                 p, e, ef, pN, eN = LiB.averageProfile(
                     trange=[t[0], t[1]],
                     interelm=True, threshold=_tr)
-                _axp.semilogy(LiB.rho, pN, color=col, lw=2)
[…]

### 2018-01-25 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX and pdf for ITPA presentation

@@
     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
+  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
   \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
@@
       cryopump or during extreme fueling case
-    \item<3|only@3> Profiles
+    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
+      and lower fueling remains more steep in all the three timing
+      wind and the plasma is still attached. Interestingly for shot \#
+      34281 with the cryopumps and higher fueling the detachment is
+      more pronounced
     \item<4|only@4> Without the cryopumps, we reached flatter

### 2018-01-25 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex

@@
   \centering{
-  Volker Naulin, Jiri Adamek, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
+  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
 Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
-Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov, Jernej Kovacic, Benoît Labit, Florian Laggner, Jens Madsen, 
+Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
+Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
 Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente,
@@
             \textbf{6},  81 (1984))}
-        \item As time evolves during the L-Mode ramp we observe
+        \item<2-> As time evolves during the L-Mode ramp we observe
           D$_{\alpha}$ radiation moving from HFS towards the LFS
           common flux region
-        \item \alert{This is consistent with JET observation in
+        \item<3-> \alert{This is consistent with JET observation in
             Horizontal target regime whenever shoulder is observed}

### 2018-01-31 Experiments/TCV/analysis/matlab/saveconnectionlength.m
modify some of the script to add the new shots given by Oliver'

@@ -3,7 +3,7 @@
 % time basis of LP probes for each of the shots 
 % analyzed
 
-shotList = [51180];
+shotList = [52022 52126 52128 52129 52131 52198 52121 52205];
 for shot = 1:length(shotList)
         disp(['Working on shot ' num2str(shotList(shot))])
         % get the time basis

### 2018-01-31 Experiments/TCV/analysis/python/createpulsefile.py

@@ -1,6 +1,7 @@
 import topic21Mds
 
-shotL = (51180)
+shotL = (52022, 52126, 52128, 52129,
+         52131, 52198, 52121, 52205)
 for shot in shotL:
     try:
         Out = topic21Mds.Tree(shot)

### 2018-02-01 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to the ITPA presentation

@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=25th ITPA-DivSOL,venue=Chengdu, date=29/01/2018, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=25th ITPA-DivSOL,venue=Chengdu, date=31/01/2018, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 % multiple figure location
-%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
+%\graphicspath{{/Users/nicola/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
 % for drawing
@@
 \title{SOL Filamentary transport: update from joint AUG-TCV MST1 experiment}
-\date{29 January 2018}
+\date{31 January 2018}
 \author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
@@
 Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
-j\end{frame}
+\end{frame}
 
@@
     \begin{column}{0.6\textwidth}
-      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
+      \includegraphics<1>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
@@
       \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
-      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
-      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
+      \includegraphics<6>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
+      \includegraphics<7>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
       \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
@@
       \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
-      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
+      \includegraphics<11>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
     \end{column}
@@
           330 kA
-        \item<4|only@4> Divertor neutral density estimated starting
+        \item<4|only@4> AUG: Divertor neutral density estimated starting
           from D$_{\alpha}$ calibrated camera and using electron
@@
           increases earlier in edge density at lower current
-        \item<5|only@5> Neutrals behavior reconciled whenever
+        \item<5|only@5> AUG: Neutrals behavior reconciled whenever
           comparison considered as a function of Greenwald fraction  
@@
             current.} For both the machine the increase of $\lambda_n$
-          reached for larger values of $\Lambda_{div}$
+          reached for larger values of divertor collisionality $\Lambda_{div}$
         \item<7|only@7> Quantifying profile evolution using the
@@
           considered as a function of local evolution of $\Lambda_{div}$
-        \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
+        \item<11|only@11> For both AUG and TCV density decay length
+          $\lambda_n$ increases
           with blob size without significant difference within the
@@
     \begin{column}{0.6\textwidth}
-      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
+      \includegraphics<1>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
-      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
-      \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
-      \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
-      \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
-      \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
-      \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
+      % \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
+      \includegraphics<4>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
+      % \includegraphics<5>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
+      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
+      \includegraphics<6>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
+      \includegraphics<7>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
     \end{column}
@@
           rollover/detachment
-        \item<4|only@4> AUG: Divertor neutral density exhibits 
-          the same behavior if considered as a function of greenwald fraction
-        \item<5|only@5> For AUG upstream and target profiles still
+        % \item<4|only@4> AUG: Divertor neutral density exhibits 
+        %   the same behavior if considered as a function of greenwald fraction
+        \item<4|only@4> For AUG upstream and target profiles still
           exhibit flattening earlier in density at lower current but
@@
           $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
-            at very large values of $\Lambda_{div}$}
-        \item<6|only@6> This is due to the fact we did not reach
-          divertor detachment which \alert{seems mandatory for
-            upstream profile modification}  
-        \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
+            at very large values of $\Lambda_{div}$. No clear sign of detachment which is mandatory for
+            upstream profile modication in TCV}
+        % \item<5|only@5> TCV: This is due to the fact we did not reach
+        %   divertor detachment which \alert{seems mandatory for
+        %     upstream profile modification}  
+        \item<5|only@5> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
           still reconcile the explored current scan
-        \item<8|only@8> AUG exhibit consistently an increase of
+        \item<6|only@6> AUG exhibit consistently an increase of
           $\lambda_n$ with blob-size whereas for TCV the profile
@@
           $\delta_b$
-        \item<9|only@9> And for TCV this is true even at high value of
+        \item<7|only@7> And for TCV this is true even at high value of
           $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
@@
   \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
-  \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
-  \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
+  \centering{\includegraphics<4>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
+  \centering{\includegraphics<5>[width=\textwidth]{\string~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
   \end{column}
@@
     \begin{itemize}
-    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
+    \item<1|only@1> We perform a series of shots in H-Mode with 6.5 MW 
       total heating power where we changed the fueling and the
@@
       \end{itemize}
-    \item<1|only@1> Keeping the same fueling with the cryopump clearly
-      reduce the pressure in the the sub-divertor area, we don't reach
-      clear detachment and the edge density is constant even during
-      the fueling ramp. Degraded H-mode reached later without the cryopump
-
+    \item<1|only@1> Keeping the same fueling with the cryopump in
+      operation clearly
+      reduce the pressure in the the sub-divertor area, plasma
+      detachment is not reached and edge density is constant despite
+      the increase fueling. Degraded H-mode reached later without the cryopump
     \item<2|only@2> Different behavior of ELM during the fueling
@@
       cryopump or during extreme fueling case
-    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
-      and lower fueling remains more steep in all the three timing
-      wind and the plasma is still attached. Interestingly for shot \#
-      34281 with the cryopumps and higher fueling the detachment is
-      more pronounced
+    \item<3|only@3> The profiles for shot \# 34278 with the cryopump
+      and lower fueling remains steeper in all the three timing
+      window and the plasma is still attached. Interestingly for shot \#
+      34281 with the cryopumps and higher fueling target profiles are broader
     \item<4|only@4> Without the cryopumps, we reached flatter
-         profiles with comparable inter-ELM resolved blob-size. This
+         profiles and relatively large inter-ELM resolved blob-size of
+         the same size as L-Mode. This
          indicates strong neutral pressure effects in determining
-         upstream profiles
+         upstream profiles. \alert{Preliminary work. Further analysis
+           needed to confirm the observed values.}
     \item<5|only@5> Increasing the fueling and correspondingly the
       divertor neutral pressure move towards a situation similar to
-      \# 34276 without the cryopump
+      \# 34276 without the cryopump. \alert{Preliminary work. Further analysis
+           needed to confirm the observed values.}
       \end{itemize}
@@
       and TCV
-    \item In both the case shoulder appear earlier in density at lower
+    \item For the scan at constant B$_t$ nn both the machines shoulder
+      appear earlier in density at lower
       current but AUG shows reconciliation of behavior if considered
@@
     \item On TCV during the current scan at constant q$_{95}$
-      detachment not reached and this \alert{prevent upstream profile
+      detachment not reached and this \alert{prevents upstream profile
         flattening}
@@
       pumping have been varied. Proved inter-ELM profile flattening
-      also in H-Mode with a more efficient puffing without the
-      cryopump. \alert{Hints on the role of neutrals also in H-Mode}
+      also in H-Mode with a more efficient shoulder formation with
+      high neutral pressure (no cryopumps or very high fueling).
+      \alert{Hints on the role of neutrals also in H-Mode}
   \end{itemize}

### 2018-02-01 Codes/python/general/timeseries.py
modifying timeseries to hold also the old method. Does not work yet

@@ -277,10 +277,8 @@ class Timeseries(object):
         else:
             if rmsNorm:
                 threshold = 3
- #               print('Threshold is 3 in rmsNormalized')
-            else:
+             else:
                 threshold = 3 * np.sqrt(self.variance) + self.mean
- #               print('Threshold is 3 sigma in signal not normalized')
         if 'nw' in kwargs:
             nw = kwargs['nw']
         else:
@@ -289,7 +287,11 @@ class Timeseries(object):
             Type = kwargs['Type']
         else:
             Type='THRESHOLD'
-
+        if 'oldmethod' in kwargs:
+            oldmethod = kwargs['oldmethod']
+        else:
+            oldmethod = False
+            
         nSig = inputS.shape[0]
         if Type == 'LIM':
             if 'frequency' in kwargs:
@@ -318,7 +320,8 @@ class Timeseries(object):
             csO, tau, errO = self.cas(
                 Type='THRESHOLD',
                 normalize=normalize, detrend=detrend,
-                rmsNorm=rmsNorm, threshold=threshold,nw=nw)
+                rmsNorm=rmsNorm, threshold=threshold,
+                nw=nw, oldmethod=oldmethod)
         maxima = np.zeros(self.nsamp, dtype='intp')
         maxima[self._locationindex] = 1
         # we need to ensure that we have 0 up to iwin
@@ -484,6 +487,10 @@ class Timeseries(object):
             rmsNorm = kwargs['rmsNorm']
         else:
             rmsNorm = False
+        if 'oldmethod' in kwargs:
+            oldmethod = kwargs['oldmethod']
+        else:
+            oldmethod = False
 
         if Type == 'LIM':
             peaks = kwargs.get('peaks', False)
@@ -540,41 +547,79 @@ class Timeseries(object):
                 else:
                     thresh = 3 * np.sqrt(self.variance) + self.mean
                     print('Threshold is 3 sigma in signal not normalized')
-            Nbursts, ratio, av_width, windows = self.identify_bursts(
-                thresh, rmsNorm=rmsNorm)
+            if not 'oldmethod':
+                Nbursts, ratio, av_width, windows = self.identify_bursts(
+                    thresh, rmsNorm=rmsNorm)
+                print('Using new threshold method')
+                if nw is None:
+                    print('Window length not set assumed 501 points')
+                    nw = 501
+                if nw % 2 == 0:
+                    nw += 1
+                csTot = np.ones((nw, Nbursts))
[…]

### 2018-02-01 Codes/python/general/timeseries.py
bug on timeseries indent

@@ -277,7 +277,7 @@ class Timeseries(object):
         else:
             if rmsNorm:
                 threshold = 3
-             else:
+            else:
                 threshold = 3 * np.sqrt(self.variance) + self.mean
         if 'nw' in kwargs:
             nw = kwargs['nw']
@@ -286,7 +286,7 @@ class Timeseries(object):
         if 'Type' in kwargs:
             Type = kwargs['Type']
         else:
-            Type='THRESHOLD'
+            Type = 'THRESHOLD'
         if 'oldmethod' in kwargs:
             oldmethod = kwargs['oldmethod']
         else:

### 2018-02-01 Codes/python/general/timeseries.py
working on timeseries to get back to old results on TCV

@@ -50,11 +50,16 @@ class Timeseries(object):
         # at the initial
         self.moments()
         _nPoint = int(dtS / self.dt)
+        # self.rmsnorm = (
+        #                    self.sig -
+        #                    bottleneck.move_mean(self.sig, window=_nPoint)) / \
+        #                bottleneck.move_std(self.sig, window=_nPoint)
         self.rmsnorm = (
                            self.sig -
-                           bottleneck.move_mean(self.sig, window=_nPoint)) / \
-                       bottleneck.move_std(self.sig, window=_nPoint)
+                           self._smooth(self.sig, window_len=_nPoint)) / \
+                           bottleneck.move_std(self.sig, window=_nPoint)
 
+        
     def moments(self):
         """
         Compute moments of the signal
@@ -547,7 +552,7 @@ class Timeseries(object):
                 else:
                     thresh = 3 * np.sqrt(self.variance) + self.mean
                     print('Threshold is 3 sigma in signal not normalized')
-            if not 'oldmethod':
+            if not oldmethod:
                 Nbursts, ratio, av_width, windows = self.identify_bursts(
                     thresh, rmsNorm=rmsNorm)
                 print('Using new threshold method')
@@ -585,16 +590,19 @@ class Timeseries(object):
                     csTot = csTot[:, :-1]
             else:
                 maxima, allmaxima = self._threshold(thresh,rmsNorm=rmsNorm)
-                print('Using new threshold method')
-
+                print('Using old threshold method')
+                print('method', oldmethod)
                 if nw is None:
                     print('Window length not set assumed 501 points')
                     nw = 501
                 if nw % 2 == 0:
+                    iwin = nw/2
                     nw += 1
+                else:
+                    iwin = (nw-1)/2
                 self.location = self.time[maxima == 1]
                 self._locationindex = np.where(maxima == 1)[0]
-                self._allmaxima = allmax
+                self._allmaxima = allmaxima
                 iwin = np.int(iwin)
                 maxima[0: iwin - 1] = 0
                 maxima[-iwin:] = 0
@@ -620,6 +628,7 @@ class Timeseries(object):
                         _dummy /= _dummy.std()
 
                     csTot[:, i] = _dummy
+                    oldmethod=None
         self.nw = nw
         self.iwin = (nw - 1) / 2
         cs = np.mean(csTot, axis=1)
@@ -806,3 +815,52 @@ class Timeseries(object):
                     d = signal[imin: imax].argmax()
[…]

### 2018-05-08 Experiments/AUG/analysis/python/scriptAnalysisShot.py
start scripting for saving netcdf values

@@ -4881,16 +4881,44 @@ while loop:
                        'xchord': [1.437, 2.173],
                        'ychord': [-1.063, -0.282]}}
         for shot in shotList:
-            # load the greenwald fraction
+            
 
             # load the target density
             Target = langmuir.Target(shot)
             peakTarget = decimate(bottleneck.move_mean(
-                np.nanmax(Target.OuterTargetNe, axis=0)/1e20, window=30),
+                np.nanmax(Target.OuterTargetNe, axis=0)/1e20, window=300),
                                   10, ftype='fir', zero_phase=True)
             tPeak = decimate(Target.time, 10, ftype='fir', zero_phase=True)
-
-
+            peakTarget = peakTarget[np.where(tPeak >= 1)[0]]
+            tPeak = tPeak[np.where(tPeak >= 1)[0]]
+            # load the greenwald fraction, limit to time greater than 1
+            # smooth and decimate
+            Tot = dd.shotfile('TOT', shot)
+            nGWA = Tot('n/nGW')
+            nGW = decimate(bottleneck.move_mean(nGWA.data, window=30), 10, ftype='fir',
+                           zero_phase=True)
+            tGW = decimate(nGWA.time, 10, ftype='fir', zero_phase=True) 
+            nGW = nGW[np.where(tGW >= 1)[0]]
+            tGW = tGW[np.where(tGW >= 1)[0]]
+            # now spline the peak target 
+            S = UnivariateSpline(tPeak[~np.isnan(peakTarget)], peakTarget[~np.isnan(peakTarget)], s=0)
+            Peak = S(tGW)
+            # and now cycle through the two diods
+            XVS = dd.shotfile('XVS', shot)
+            
+            for key in Diods.keys():
+                dummy=XVS(Diods[key]['Name'])
+                Fs = 500e3
+                sig = bw_filter(dummy.data, 200e3, Fs, 'lowpass', order=6)
+                # now downsampling the data two times
+                sig = decimate(decimate(sig, 10, ftype='fir', zero_phase=True),
+                               10, ftype='fir', zero_phase=True)
+                t = decimate(decimate(dummy.time, 10, ftype='fir', zero_phase=True),
+                             10, ftype='fir', zero_phase=True)
+                sig = sig[np.where(t>= 1)[0]]
+                t = t[np.where(t >= 1)[0]]
+                S = UnivariateSpline(t[~np.isnan(sig)], sig[~np.isnan(sig)], s=0)
+                
     elif selection == 99:
         loop = False
     else:

### 2018-05-08 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
started the TeX for analysis meeting of 17 of may

\documentclass[10pt, compress]{beamer}
\usetheme[conference=Topic21-Analysis-Meeting,venue=Remote, date=17/05/2018, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{tangocolors}
\usepackage{rfxcolor}
\definecolor{colorA}{HTML}{324D5C}
\definecolor{colorB}{HTML}{E37B40}
\definecolor{colorC}{HTML}{60A65F}
% multiple figure location
%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{onimage}
\usepackage[export]{adjustbox}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Topic 21 Experiment and analysis}
\date{17 May 2018}
\author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
  scientific team}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle
\begin{frame}{Scientific team}
  \centering{
  Volker Naulin, Matteo Agostini, Diogo Aguiam, Scott Allan, Matthias Bernert, Daniel Carralero Ortiz, 
Stefan Costea, Istvan Cziegler, Hugo De Oliveira, Joaquin Galdon-Quiroga, Gustavo Grenfell, Antti Hakola, 
Codrina Ionita-Schrittwieser, Heinz Isliker, Alexander Karpushov,
Jernej Kovacic, Benoît Labit, Bruce Lipschultz, 
Roberto Maurizio, Ken McClements, Fulvio Militello, Jeppe Miki Busk Olsen, Jens Juul Rasmussen, Timo Ravensbergen, Bernd Sebastian Schneider, Roman Schrittwieser, Jakub Seidl, Monica Spolaore, Christian Theiler, Cedric Kar-Wai Tsui, Kevin Verhaegh, Jose Vicente, 
Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
j\end{frame}

\begin{frame}{Motivation and deliverables}
  \Fontvi
  \vspace{-1cm}
  \begin{itemize}
    \item \alert{Relation between downstream divertor conditions and
        up-stream SOL profiles is not well understood. Influence of
        SOL blob structures on shoulder formation and divertor
        conditions is key element towards predictive
        capabilities. Joint effort within the EUROfusion framework to
        address this issue on all the MST1 devices (AUG, TCV and MAST-U)}
  \end{itemize}
  \onslide<2->{A series of deliverables were foreseen by 2017 program
\begin{enumerate}
\item \only<3>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<3>{\color{ta3chameleon}}Establish robust scenario for density
  shoulder profile in H-Mode and \only<3>{\color{ta3orange}}establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<3>{\color{ta3chameleon}}Fluctuations mesurement on AUG to study
  filamentary transport under high-power H-Mode conditions \only<3>{\color{ta2plum}}and under
  different plasma configurations (SN, DN)
\item \only<3>{\color{ta3orange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<3>{\color{ta3orange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<3>{\color{ta3orange}}Determine the effect of filaments and
  shoulder formation on target heat loads \only<3>{\color{ta2plum}}in different H-mode plasmas
\end{enumerate}}
\onslide<3>{
\textcolor{red}{Remember this is
  still a work in progress}
}
\end{frame}

\begin{frame}{Current scan at constant B$_t$ in L-Mode plasma}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
      \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
        \item<1|only@1> Shape matched in within the single scan done for each of
          the machine
        \item<1|only@1> The scan implies a modification of the
          L$_{\parallel}$. There is a factor of 5 difference between
          the two machines due to the very long outer divertor leg of TCV
        \item<2|only@2> AUG: Fueling reduced only at lower I$_p$ to
          avoid earlier disruption. Similar neutral pressure in the
          subdivertor region reached. NBI additional power added to
          keep power in the SOL approximately constant
        \item<3|only@3> TCV: Ohmic heating only. Similar neutral compression reached and
          D$_{\alpha}$ radiation from the floor. Ion flux rollover
          reached in all the three current,  although marginally at
          330 kA
        \item<4|only@4> Divertor neutral density estimated starting
          from D$_{\alpha}$ calibrated camera and using electron
          density and temperature from LP data. Neutral density
          increases earlier in edge density at lower current
        \item<5|only@5> Neutrals behavior reconciled whenever
          comparison considered as a function of Greenwald fraction  
        \item<6|only@6> For both AUG and TCV flattening of normalized
          upstream profile reached \alert{earlier in density at lower
            current.} For both the machine the increase of $\lambda_n$
          reached for larger values of $\Lambda_{div}$
        \item<7|only@7> Quantifying profile evolution using the
          \alert{shoulder amplitude metric} introduce by Wynn and
          Lipschultz for JET. \alert{Amplitude is the difference
            between normalized upstream density profiles}
        \only<8-9>{\item Amplitude evolve faster in density at lower
          current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
            fraction is considered the evolution is equivalent between
            different current}}}
        \item<10|only@10> Amplitude evolution still reconciled in AUG if
          considered as a function of local evolution of $\Lambda_{div}$
        \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
          with blob size without significant difference within the
          current explored
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

% \begin{frame}{Current scan at constant q$_{95}$}
%   \begin{columns}
%     \begin{column}{0.6\textwidth}
%       \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
%       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
%       \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
%       \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
%       \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
%       \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
%       \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
%       \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
%     \end{column}
%     \begin{column}{0.4\textwidth}
%       \begin{itemize}
%         \item<1|only@1> Shape matched in within the single scan even
%           though this required for TCV operation with very low
%           toroidal field (0.8T)
%         \item<1|only@1> The parallel connection length remains almost unchanged
%         \item<2|only@2> AUG: As for the case of constant B$_t$ we have
%           pretty reproducible behavior matching basically the plasma
%           condition in within the current scan
%         \item<3|only@3> TCV: Even at such an high density at lower
%           current (and lower B$_t$) no sign of target ion flux
%           rollover/detachment
%         \item<4|only@4> AUG: Divertor neutral density exhibits 
%           the same behavior if considered as a function of greenwald fraction
%         \item<5|only@5> For AUG upstream and target profiles still
%           exhibit flattening earlier in density at lower current but
%           \alert{always at large values of 
%           $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
%             at very large values of $\Lambda_{div}$}
%         \item<6|only@6> This is due to the fact we did not reach
%           divertor detachment which \alert{seems mandatory for
%             upstream profile modification}  
%         \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
%           still reconcile the explored current scan
%         \item<8|only@8> AUG exhibit consistently an increase of
%           $\lambda_n$ with blob-size whereas for TCV the profile
%           remains flat consistently with a small variation of
%           $\delta_b$
%         \item<9|only@9> And for TCV this is true even at high value of
%           $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
%           guarantee flat profiles on TCV.}
%       \end{itemize}
%     \end{column}
%   \end{columns}
% \end{frame}
% %% H-Mode same fueling
% \begin{frame}{H-Mode analysis on AUG}
%     \Fontvi
%   \vspace{-1cm}
%   \begin{columns}
%   \begin{column}{0.55\textwidth}
%     \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
%   \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
%   \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
%   \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
%   \end{column}
%   \begin{column}{0.45\textwidth}
%     \begin{itemize}
%     \item<1|only@1> We perform a series of shots in H-Mode with 6.5
%       total heating power where we changed the fueling and the
%       efficiency of cryopumps. Specifically we have
%       \begin{itemize}
%         \item<1|only@1>\textcolor{colorA}{\# 34276 without the
%             cryompumps}
%         \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
%             fueling as \# 34276 but with the cryompump}
%         \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
%             fueling and seeding trying to mimic the same subdivertor
%             pressure as \# 34276}
%       \end{itemize}
%     \item<1|only@1> Keeping the same fueling with the cryopump clearly
%       reduce the pressure in the the sub-divertor area, we don't reach
%       clear detachment and the edge density is constant even during
%       the fueling ramp. Degraded H-mode reached later without the cryopump

%     \item<2|only@2> Different behavior of ELM during the fueling
%       ramp. ELM size and frequency changes strongly without the
%       cryopump or during extreme fueling case
%     \item<3|only@3> The profiles for shot \# 34278 with the cryopum
%       and lower fueling remains more steep in all the three timing
%       wind and the plasma is still attached. Interestingly for shot \#
%       34281 with the cryopumps and higher fueling the detachment is
%       more pronounced
%     \item<4|only@4> Without the cryopumps, we reached flatter
%          profiles with comparable inter-ELM resolved blob-size. This
%          indicates strong neutral pressure effects in determining
%          upstream profiles
%     \item<5|only@5> Increasing the fueling and correspondingly the
%       divertor neutral pressure move towards a situation similar to
%       \# 34276 without the cryopump
%       \end{itemize}
%   \end{column}
% \end{columns}
% \end{frame}

% \begin{frame}{Conclusion}
%   \Fontvi
%   \begin{itemize}
%     \item Current scan at constant B$_t$ and at constant q$_{95}$
%       performed during density ramps L-Mode experiments both at AUG
%       and TCV
%     \item In both the case shoulder appear earlier in density at lower
%       current but AUG shows reconciliation of behavior if considered
%       as a function of greenwald fraction and $\Lambda_{div}$
%     \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
%       blob size is increasing, independently from the current. The
%       same behavior is observed during current scan at constant
%       q$_{95}$ \alert{only on AUG}
%     \item On TCV during the current scan at constant q$_{95}$
%       detachment not reached and this \alert{prevent upstream profile
%         flattening}
%     \item H-Mode experiments performed on AUG where fueling and
%       pumping have been varied. Proved inter-ELM profile flattening
%       also in H-Mode with a more efficient puffing without the
%       cryopump. \alert{Hints on the role of neutrals also in H-Mode}
%   \end{itemize}
% \end{frame}

% \begin{frame}{D$_{\alpha}$ tomography: work in progress}
% \Fontvi
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
%       \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%         \item \alert{Preliminary} results from inversion tomography
%           from calibrated D$_{\alpha}$ camera under the assumption of
%           toroidally symmetric emission limited to the region outside
%           the LCFS
%         \item \emph{Simultaneous Algebraic Reconstruction Technique
%             (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
%             \textbf{6},  81 (1984))}
%         \item<2-> As time evolves during the L-Mode ramp we observe
%           D$_{\alpha}$ radiation moving from HFS towards the LFS
%           common flux region
%         \item<3-> \alert{This is consistent with JET observation in
%             Horizontal target regime whenever shoulder is observed}
%       \end{itemize}
%     \end{column}
%   \end{columns}
% \end{frame}

\end{document}

### 2018-05-09 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update to netcdf with target density and radiation

@@ -4870,7 +4870,7 @@ while loop:
         mpl.pylab.savefig('../pdfbox/PuffingIpolsola%5i' % shotList[0] +
                           '_%5i' %shotList[1]+'_%5i' % shotList[2] + '.pdf', bbox_to_inches='tight')
 
-    elif selection == 58:
+    elif selection == 59:
         # we save in netcdf format the decimated evolution of peak density
         # and XUV diods with corresponding names
         shotList = (34102, 34103, 34104, 34105, 34106)
@@ -4881,28 +4881,40 @@ while loop:
                        'xchord': [1.437, 2.173],
                        'ychord': [-1.063, -0.282]}}
         for shot in shotList:
-            
-
+            # load the greenwald fraction, limit to time greater than 1
+            # smooth and decimate
+            Tot = dd.shotfile('TOT', shot)
+            nGWA = Tot('n/nGW')
+            nGW = decimate(bottleneck.move_mean(nGWA.data, window=30), 5, ftype='fir',
+                           zero_phase=True)
+            tGW = decimate(nGWA.time, 10, ftype='fir', zero_phase=True) 
+            nGW = nGW[np.where(tGW >= 1)[0]]
+            tGW = tGW[np.where(tGW >= 1)[0]]
             # load the target density
             Target = langmuir.Target(shot)
             peakTarget = decimate(bottleneck.move_mean(
                 np.nanmax(Target.OuterTargetNe, axis=0)/1e20, window=300),
                                   10, ftype='fir', zero_phase=True)
             tPeak = decimate(Target.time, 10, ftype='fir', zero_phase=True)
-            peakTarget = peakTarget[np.where(tPeak >= 1)[0]]
-            tPeak = tPeak[np.where(tPeak >= 1)[0]]
-            # load the greenwald fraction, limit to time greater than 1
-            # smooth and decimate
-            Tot = dd.shotfile('TOT', shot)
-            nGWA = Tot('n/nGW')
-            nGW = decimate(bottleneck.move_mean(nGWA.data, window=30), 10, ftype='fir',
-                           zero_phase=True)
-            tGW = decimate(nGWA.time, 10, ftype='fir', zero_phase=True) 
-            nGW = nGW[np.where(tGW >= 1)[0]]
-            tGW = tGW[np.where(tGW >= 1)[0]]
+            peakTarget = peakTarget[np.where((tPeak >= tGW.min()) &
[…]

### 2018-05-10 Experiments/TCV/analysis/python/scriptAnalysis.py
update to radiation density for one shot

@@ -2924,9 +2924,15 @@ while loop:
             _idx = np.where((tIp >= tmin) & (tIp <= tmax))[0]
             sIp = UnivariateSpline(tIp[_idx], np.abs(iP)[_idx]/1e6, s=0)
             # UnivariateSpline of the peak density
-            sNePeak = interp1d(Target.t,
-                               np.nanmax(Target.en, axis=1)/1e19,
-                               fill_value='extrapolate')
+            if shot != 57454:
+                sNePeak = interp1d(Target.t,
+                                   np.nanmax(Target.en, axis=1)/1e19,
+                                   fill_value='extrapolate')
+            else:
+                _dummy = np.nanmax(Target.en, axis=1)/1e19
+                sNePeak = interp1d(Target.t[np.where(_dummy<= 3)[0]],
+                                   _dummy[np.where(_dummy<=3)[0]],
+                                   fill_value='extrapolate')
             # UnivariateSpline of the total ion flux_gaz
             sIonFlux = UnivariateSpline(Target.t2,
                                         Target.TotalSpIonFlux()/1e27, s=0)

### 2018-05-10 Experiments/Comparison/python/scriptAnalysis.py
Update to script and figures for AUG/TCV comparison

@@ -37,19 +37,236 @@ while loop:
         iPTcv = (.19, 0.245, 0.33)
         # now the plot target peak density and radiation vs density
         fig, ax = mpl.pylab.subplots(figsize=(10, 7), nrows=2, ncols=2)
-        fig.subplots_adjust(wspace=0.25, hspace=0.05)
+        fig.subplots_adjust(wspace=0.25, hspace=0.05,
+                            bottom=0.15, left=0.15, right=0.98)
         colorList = ('#01406C', '#F03C07', '#28B799')
         for i, (shot, ip, col) in enumerate(zip(shotAug, iPAug, colorList)):
             # load the data
             df = xray.open_dataarray(
-                '../../AUG/analysis/data/Shot%5i' % shot + '_DensityRadiation.nc')
-            ax[0, 0].p
+                '../../AUG/analysis/data/Shot%5i' % shot +
+                '_DensityRadiation.nc')
+            ax[0, 0].plot(df.sel(sig='H-5')[:-10]/10,
+                          df.sel(sig='neTarget')[:-10], '.', color=col,
+                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
+            ax[1, 0].plot(df.sel(sig='H-5')[:-10]/10,
+                          df.sel(sig='D10')[:-10]/1e3, '.', color=col,
+                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
+        ax[0, 0].set_xlim([0.1, 0.5])
+        ax[0, 0].set_ylabel(r'n$^{peak}_{target} [10^{20}$m$^{-3}]$')
+        ax[0, 0].axes.get_xaxis().set_visible(False)
+        ax[0, 0].set_title(r'AUG')
+        ax[1, 0].set_xlim([0.1, 0.5])
+        ax[1, 0].set_ylabel(r'kw/m$^2$')
+        ax[1, 0].set_xlabel(r'n$_e^{Edge}[10^{20}$m$^{-2}]$')
+        leg = ax[0, 0].legend(loc='best', numpoints=1,
+                              frameon=False, fontsize=14)
+        for text, color in zip(leg.get_texts(), colorList):
+            text.set_color(color)
+
+        for i, (shot, ip, col) in enumerate(zip(shotTcv, iPTcv, colorList)):
+            # load the data
+            df = xray.open_dataarray(
[…]

### 2018-05-10 Experiments/Comparison/python/scriptAnalysis.py
Big update in file for comparison
We have added the same data used for the IAEA synopsis in the repository and produced the corresponding files

@@ -1,14 +1,9 @@
 from __future__ import print_function
 import numpy as np
 import matplotlib as mpl
-import pandas as pd
-import MDSplus as mds
 import xarray as xray
-import smooth
-from sklearn.gaussian_process import GaussianProcessRegressor
-from sklearn.gaussian_process.kernels import (RBF,
-                                              ConstantKernel,
-                                              WhiteKernel)
+import h5py
+from scipy.interpolate import UnivariateSpline
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=18)
 mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica']})
@@ -21,6 +16,8 @@ def print_menu():
     print("2. Target density and radiation vs Greenwald Fraction Constant Bt")
     print("3. Target density and radiation vs Density Constant q95")
     print("4. Target density and radiation vs Greenwald constant q95")
+    print('5. Upstream and target profiles Constant Bt')
+    print('6. Upstream and target profiles Constant q95')
     print("99: End")
     print(67 * "-")
 
@@ -69,10 +66,10 @@ while loop:
                 '../../TCV/data/Shot%5i' % shot +
                 '_DensityRadiation.nc')
             ax[0, 1].plot(df.sel(sig='en'),
-                          df.sel(sig='neMaxTarget')/10, '.',
+                          df.sel(sig='neMaxTarget')/10, '.', color=col,
                           label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
             ax[1, 1].plot(df.sel(sig='en'),
-                          df.sel(sig='Bolo')/1e3, '.',
+                          df.sel(sig='Bolo')/1e3, '.',  color=col,
                           label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
         ax[0, 1].set_xlim([0.1, 1.2])
         ax[0, 1].set_ylabel(r'n$^{peak}_{target} [10^{20}$m$^{-3}]$')
@@ -80,7 +77,7 @@ while loop:
         ax[0, 1].set_title(r'TCV')
         ax[1, 1].set_xlim([0.1, 1.2])
         ax[1, 1].set_ylabel(r'kW/m$^{2}$')
-        ax[1, 1].set_xlabel(r'$\langle$n$_e[10^{20}$m$^{-3}]\rangle$')
+        ax[1, 1].set_xlabel(r'$\langle$n$_e\rangle[10^{20}$m$^{-3}]$')
[…]

### 2018-05-11 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Update to TeX file for meeting and figures

@@
       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
-      \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsNe5IpConstantBt}
-      \includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantBt}
-      \includegraphics<6>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantBt}
-      \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
-      \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
-      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
-      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
-      \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
+      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantBt}
+      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantBt}
+      \only<6>{
+        \begin{tikzonimage}[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantBt}
+          \draw [thick, ta3orange, ->] (0.27, 0.9) -- (0.27, 0.8);
+          \draw [thick, ta3orange, ->] (0.77, 0.45) -- (0.77, 0.55);
+        \end{tikzonimage}
+      }
+      \includegraphics<7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}
+      % \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
+      % \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
+      % \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
+      % \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
+      % \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
     \end{column}
@@
           330 kA
-        \item<4|only@4> Divertor neutral density estimated starting
-          from D$_{\alpha}$ calibrated camera and using electron
-          density and temperature from LP data. Neutral density
-          increases earlier in edge density at lower current
-        \item<5|only@5> Neutrals behavior reconciled whenever
-          comparison considered as a function of Greenwald fraction  
-        \item<6|only@6> For both AUG and TCV flattening of normalized
+        \item<4|only@4> In both the machines both the peak target
+          density and the radiation close to divertor target exhibit
+          rollover at increasing density with increasing current
+        \item<5|only@5> Whenever considered as a a function of
+          Greenwald fraction the behaviors at different currents
+          almost reconciled for AUG \alert{but not for TCV}
+        \item<6|only@6> We now consider the Target and upstream
+          profiles at the same level of densities
+        \item<7|only@7> For both AUG and TCV flattening of normalized
           upstream profile reached \alert{earlier in density at lower
@@
           reached for larger values of $\Lambda_{div}$
-        \item<7|only@7> Quantifying profile evolution using the
-          \alert{shoulder amplitude metric} introduce by Wynn and
-          Lipschultz for JET. \alert{Amplitude is the difference
-            between normalized upstream density profiles}
-        \only<8-9>{\item Amplitude evolve faster in density at lower
-          current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
-            fraction is considered the evolution is equivalent between
-            different current}}}
-        \item<10|only@10> Amplitude evolution still reconciled in AUG if
-          considered as a function of local evolution of $\Lambda_{div}$
-        \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
-          with blob size without significant difference within the
-          current explored
+        % \item<7|only@7> Quantifying profile evolution using the
+        %   \alert{shoulder amplitude metric} introduce by Wynn and
+        %   Lipschultz for JET. \alert{Amplitude is the difference
+        %     between normalized upstream density profiles}
+        % \only<8-9>{\item Amplitude evolve faster in density at lower
+        %   current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
+        %     fraction is considered the evolution is equivalent between
+        %     different current}}}
+        % \item<10|only@10> Amplitude evolution still reconciled in AUG if
+        %   considered as a function of local evolution of $\Lambda_{div}$
+        % \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
+        %   with blob size without significant difference within the
+        %   current explored
       \end{itemize}

### 2018-05-11 Experiments/Comparison/python/scriptAnalysis.py

@@ -282,7 +282,8 @@ while loop:
         ipListT = ('0.185', '0.24', '0.34')
         for shot, t, c, _ip in zip(shotListA, tListA, colorList, ipListA):
             # open the HDF file
-            File = h5py.File('../data/aug/Shot%5i' % shot + '.h5', 'r')
+            DirectoryAug = '/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/data/aug/'
+            File = h5py.File(DirectoryAug + 'Shot%5i' % shot + '.h5', 'r')
             neLBtime = File['timeLiB'].value
             # limit to the interval
             _idx = np.where((neLBtime >= t-0.02) & (neLBtime <= t+0.02))[0]
@@ -358,7 +359,9 @@ while loop:
             text.set_color(c)
             handle.set_visible(False)
         # Now TCV
-        File = h5py.File('../data/tcv/ProfilesConstantBt.h5', 'r')
+        DirectoryTcv = "/Users/vianello/Documents/Fisica/Conferences/" \
+                       "IAEA/iaea2018/data/tcv/"
+        File = h5py.File(DirectoryTcv + 'ProfilesConstantBt.h5', 'r')
         for shot, col, _ip in zip(
                 shotListT, colorList, ipListT):
             Up = File['%5i/Upstream' % shot]
@@ -448,7 +451,8 @@ while loop:
         ipListT = ('0.24', '0.34')
         for shot, t, c, _ip in zip(shotListA, tListA, colorList, ipListA):
             # open the HDF file
-            File = h5py.File('../data/aug/Shot%5i' % shot + '.h5', 'r')
+            DirectoryAug = '/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/data/aug/'
+            File = h5py.File(DirectoryAug + 'Shot%5i' % shot + '.h5', 'r')
             neLBtime = File['timeLiB'].value
             # limit to the interval
             _idx = np.where((neLBtime >= t-0.02) & (neLBtime <= t+0.02))[0]
@@ -525,7 +529,9 @@ while loop:
             text.set_color(c)
             handle.set_visible(False)
         # Now TCV
-        File = h5py.File('../data/tcv/ProfilesConstantQ95.h5', 'r')
+        DirectoryTcv = "/Users/vianello/Documents/Fisica/Conferences/" \
+                       "IAEA/iaea2018/data/tcv/"
[…]

### 2018-05-11 Experiments/AUG/analysis/python/scriptAnalysisShot.py
change colorList cycle for plot of amplitude

@@ -19,10 +19,12 @@ import libes
 import xarray as xray
 import h5py
 sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/submodules/pycwt/')
-sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/')
+sys.path.append(
+    '/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/')
 sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/aug/')
 sys.path.append('/afs/ipp/home/n/nvianell/pythonlib/signalprocessing/')
-sys.path.append('/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/cyFieldlineTracer')
+sys.path.append(
+    '/afs/ipp/home/n/nvianell/analisi/topic21/Codes/python/general/cyFieldlineTracer')
 import augFilaments
 import neutrals
 import peakdetect
@@ -33,7 +35,8 @@ from cyfieldlineTracer import get_fieldline_tracer
 import eqtools
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=22)
-mpl.rc('font',**{'family':'sans-serif','sans-serif':['Tahoma']})
+mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Tahoma']})
+
 
 def print_menu():
     print 30 * "-", "MENU", 30 * "-"
@@ -98,6 +101,8 @@ def print_menu():
     print "59. Radiation and peak density vs Greenwald fraction (data saved)"
     print "99: End"
     print 67 * "-"
+
+
 loop = True
 
 while loop:
@@ -119,13 +124,13 @@ while loop:
         axL = (ax2, ax3, ax4)
 
         for shot, ip, cc, i, _ax in itertools.izip(
-            shotList, currentL, colorLS, range(len(shotList)), axL):
+                shotList, currentL, colorLS, range(len(shotList)), axL):
             # this is the line average density
             diag = dd.shotfile('TOT', shot)
             neAvg = diag('H-1/(2a)')
             diag.close()
             ax1.plot(neAvg.time, neAvg.data/1e20, '-', color=cc, lw=2,
-                     label = r'Shot # %5i' % shot +' I$_p$ = %2.1f' % ip +' MA')
[…]

### 2018-05-11 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update color table for some figures

@@ -3708,7 +3708,7 @@ while loop:
                                         range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt,
                                   reference=[1.2, 1.4], start=N.n0Time.min())
             # now integrate in the near and far SOL defining respectively for
@@ -3824,7 +3824,7 @@ while loop:
                 range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4],
                                   start=N.n0Time.min())
             # now integrate in the near and far SOL defining respectively for
@@ -3934,7 +3934,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
             # compute the amplitude of the LiB
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
@@ -4060,7 +4060,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
             # compute the amplitude of the LiB
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
@@ -4197,7 +4197,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
             # compute the amplitude of the LiB
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
@@ -4305,7 +4305,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
[…]

### 2018-05-11 Experiments/AUG/analysis/python/scriptAnalysisShot.py
update color table for some figures

@@ -3766,7 +3766,7 @@ while loop:
                                         range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt,
                                   reference=[1.2, 1.4], start=N.n0Time.min())
             # now integrate in the near and far SOL defining respectively for
@@ -3885,7 +3885,7 @@ while loop:
                 range(len(shotList)), colorL):
             N = neutrals.Neutrals(shot)
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4],
                                   start=N.n0Time.min())
             # now integrate in the near and far SOL defining respectively for
@@ -3997,7 +3997,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
             # compute the amplitude of the LiB
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
@@ -4125,7 +4125,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
             # compute the amplitude of the LiB
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
@@ -4264,7 +4264,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
             # compute the amplitude of the LiB
             LiB = libes.Libes(shot)
-            dt = 0.05
+            dt = 0.1
             LiB.amplitudeShoulder(dt=dt, reference=[1.2, 1.4], start=1.2)
             # now integrate in the near and far SOL defining respectively for
             # (1<rho<1.02 and 1.02<rho<1.04)
@@ -4374,7 +4374,7 @@ while loop:
         for shot, _ip, col in zip(shotList, currentL, colorL):
[…]

### 2018-05-11 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Update for May meeting

@@
 uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
-\bibliography{biblio}
+\bibliography{../biblio}
 \renewcommand*{\bibfont}{\footnotesize}
@@
       \includegraphics<7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}
-      % \includegraphics<7>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/ExampleShoulderAmplitude}
-      % \includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
-      % \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
-      % \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
+      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleShoulderAmplitude}
+      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
+      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
+      \includegraphics<11>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
       % \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
@@
           almost reconciled for AUG \alert{but not for TCV}
-        \item<6|only@6> We now consider the Target and upstream
+        \item<only@6-7> We now consider the Target and upstream
           profiles at the same level of densities  
-        \item<7|only@7> For both AUG and TCV flattening of normalized
+        \item<only@7> For both AUG and TCV flattening of normalized
           upstream profile reached \alert{earlier in density at lower
@@
           reached for larger values of $\Lambda_{div}$
-        % \item<7|only@7> Quantifying profile evolution using the
-        %   \alert{shoulder amplitude metric} introduce by Wynn and
-        %   Lipschultz for JET. \alert{Amplitude is the difference
-        %     between normalized upstream density profiles}
-        % \only<8-9>{\item Amplitude evolve faster in density at lower
-        %   current in the far SOL \onslide<9>{\alert{but once evolution \textit{vs} greenwald
-        %     fraction is considered the evolution is equivalent between
-        %     different current}}}
-        % \item<10|only@10> Amplitude evolution still reconciled in AUG if
-        %   considered as a function of local evolution of $\Lambda_{div}$
+        \item<only@8> Quantifying profile evolution using the
+          \alert{shoulder amplitude metric} introduce by Wynn and
+          Lipschultz for JET \parencite{Wynn:2018gp}.
+        \item<only@8>  \alert{Amplitude is the difference
+            between normalized upstream density profiles}
+        \item<only@8> Distinguishing behavior on the near and far SOL  
+        \only<9-10>{\item Amplitude evolve faster in density at lower
+          current in the far SOL \onslide<10>{\alert{but once evolution \textit{vs} greenwald
+            fraction is considered the evolution is equivalent between
+            different current.}
+          \item \textcolor{ta3chameleon}{Still some inconsistency at lower
+            current in agreement with different detachment evolution}}}
+        \item<only@11> Amplitude evolution still reconciled in AUG if
+          considered as a function of local evolution of $\Lambda_{div}$
         % \item<11|only@11> For both AUG and TCV $\lambda_n$ increases

### 2018-05-11 Experiments/Comparison/python/scriptAnalysis.py

@@ -18,6 +18,7 @@ def print_menu():
     print("4. Target density and radiation vs Greenwald constant q95")
     print('5. Upstream and target profiles Constant Bt')
     print('6. Upstream and target profiles Constant q95')
+    print('7. Example of shoulder amplitude')
     print("99: End")
     print(67 * "-")
 
@@ -601,6 +602,55 @@ while loop:
             handle.set_visible(False)
 
         fig.savefig('../pdfbox/UpstreamTargetProfilesConstantQ95.pdf',
+                    bbox_to_inches='tight')
+    elif selection == 7:
+        DirectoryAug = '/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/data/aug/'
+        File = h5py.File(DirectoryAug + 'Shot34102.h5', 'r')
+        LiBN = File['LiBNorm'].value
+        rho = File['rhoLiB'].value
+        time = File['timeLiB'].value
+        _idx = np.where((time >= 1.2) & (time <= 1.3))[0]
+        pNA = np.nanmean(LiBN[_idx, :], axis=0)
+        eNA = np.nanstd(LiBN[_idx, :], axis=0)
+        _idx = np.where((time >= 3.1) & (time <= 3.2))[0]
+        pNB = np.nanmean(LiBN[_idx, :], axis=0)
+        eNB = np.nanstd(LiBN[_idx, :], axis=0)
+        fig, ax = mpl.pylab.subplots(figsize=(7, 7),
+                                     nrows=2, ncols=1, sharex=True)
+        fig.subplots_adjust(bottom=0.18, left=0.18, top=0.98, hspace=0.06)
+        _idx = np.where(rho >= 0.995)[0]
+        Amplitude = pNB-pNA
+        errAmplitude = np.sqrt(np.power(eNB, 2) + np.power(eNA, 2))
+        ax[0].plot(rho[_idx], pNA[_idx], '-', lw=4, color='#F0CA4D')
+        ax[0].fill_between(rho[_idx], pNA[_idx]-eNA[_idx],
+                           pNA[_idx]+eNA[_idx], color='#F0CA4D',
+                           edgecolor='none',
+                           alpha=0.2)
+        ax[0].plot(rho[_idx], pNB[_idx], '-', lw=4, color='#F53855')
+        ax[0].fill_between(rho[_idx], pNB[_idx]-eNB[_idx],
+                           pNB[_idx]+eNB[_idx],
[…]

### 2018-05-16 Codes/python/tcv/tcvFilaments.py
added to tcvFilaments the compuation of Efolding using the GPR tools and profiletools

@@ -16,7 +16,7 @@ import xarray as xray
 import bottleneck
 import quickspikes as qs
 from lmfit.models import GaussianModel
-
+import tcvProfiles
 
 class Turbo(object):
     """
@@ -50,6 +50,7 @@ class Turbo(object):
        langmuir
        scipy
        quickspikes
+       profiletools
     """
 
     def __init__(self, shot, gas='D2', Lp='Div'):
@@ -296,6 +297,8 @@ class Turbo(object):
                         (self.rhoArray <= self.RRsep[_idx].max())))[0]
         data.attrs['Efold'] = self.Efolding[_idx].mean()
         data.attrs['EfoldErr'] = self.Efolding[_idx].std()
+        data.attrs['EfoldGpr'] = self.EfoldingGpr[_idx].mean()
+        data.attrs['EfoldGprErr'] = self.EfoldingGpr[_idx].mean()
         # add also the results of the conditional average
         # which is useful
         data.attrs['CAS'] = cs
@@ -485,7 +488,7 @@ class Turbo(object):
         if _ii.size < npoint:
             self.profileEn = xray.DataArray(
                 _data[_ii] / 1e19,
-                coords={'drsep': _rho[_ii]})
+                coords=[_rho[ii]], dims=['drsep'])
             self.profileEn.attrs['err'] = _err[_ii] / 1e19
         else:
             # density profile and corresponding spline
@@ -493,10 +496,43 @@ class Turbo(object):
                 _rho[_ii],
                 _data[_ii] / 1e19,
                 npoint=npoint)
+        _idx0 = np.where(self.profileEn.err == 0)[0]
+        if _idx0.size != 0:
+            self.profileEn.err[_idx0]  =  \
+                np.mean(self.profileEn.err[np.where(self.profileEn.err != 0)[0]])
         self.splineEn = UnivariateSpline(self.profileEn.rho.values,
                                          self.profileEn.values,
                                          w=1. / self.profileEn.err,
                                          ext=0)
+        # we had the computation of the profiles using the profiletools
+        # which allows to combine also with Thomson data
+        Profile = tcvProfiles.tcvProfiles(self.shot)
+        EnProf = Profile.profileNe(t_min = _time.min()-0.05,
+                                   t_max = _time.max() + 0.05,
+                                   abscissa = 'Rmid')
+        # Compute the GPR estimate of the Fit
[…]

### 2018-05-16 Experiments/TCV/analysis/python/batchevaluationblobsize.py
update to database with efold GPR

@@ -68,6 +68,8 @@ RhosErr = np.asarray([])
 SizeErr = np.asarray([])
 Efold = np.asarray([])
 EfoldErr = np.asarray([])
+EfoldGpr = np.asarray([])
+EfoldGprErr = np.asarray([])
 Size2Err = np.asarray([])
 Size3Err = np.asarray([])
 for shot in shotList:
@@ -156,6 +158,7 @@ for shot in shotList:
                 Size = np.append(Size, _size)
                 Cs = np.append(Cs, Blob.Cs)
                 Efold = np.append(Efold, Blob.Efold)
+                EfoldGpr = np.append(EfoldGpr, Blob.EfoldGpr)
                 Size2 = np.append(Size2, _size2)
                 vR2 = np.append(vR2, Blob.vrad2)
                 vP2 = np.append(vP2, Blob.vpol2)
@@ -175,6 +178,7 @@ for shot in shotList:
                 SizeErr = np.append(SizeErr, _dSize)
                 Size3Err = np.append(Size3Err, _dSize3)                
                 EfoldErr = np.append(EfoldErr, Blob.EfoldErr)
+                EfoldGprErr = np.append(EfoldGprErr, Blob.EfoldGprErr)
                 print('Computed for Shot %5i' % shot +' Plunge %1i' % plunge)
     Tree.quit()
 
@@ -206,7 +210,8 @@ outdict = {'Shots': Shots,
            'Efold':Efold,
            'EfoldErr':EfoldErr,
            'Bt': Bt,
-           'vBin3':vBin}
+           'vBin3':vBin,
+           'Efold GPR':EfoldGpr, 'Efold GPR Err':EfoldGprErr}
 
 df = pd.DataFrame.from_dict(outdict)
 df['Z'] = np.repeat(1, df.index.size)

### 2018-05-16 Experiments/Comparison/python/scriptAnalysis.py
update to figures

@@ -3,11 +3,21 @@ import numpy as np
 import matplotlib as mpl
 import xarray as xray
 import h5py
-from scipy.interpolate import UnivariateSpline
+from scipy.interpolate import UnivariateSpline, interp1d
+import pandas as pd
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=18)
 mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica']})
 mpl.rc("lines", linewidth=2)
+Data = pd.read_csv(
+    '~/Desktop/Topic-21/Experiments/TCV/data/BlobDatabase.csv')
+DataTCV = Data[((Data['Rho'] > 1.025) &
+                (Data['Rho'] <= 1.05) &
+                (Data['Conf'] == 'LSN') &
+                (Data['Lambda Div'] < 40) &
+                (Data['Blob Size [rhos]'] > 1))]
+# limit the otlier of the poloidal velocity
+DataTCV = DataTCV[DataTCV['vP'].abs() <= DataTCV['vP'].std()]
 
 
 def print_menu():
@@ -19,6 +29,10 @@ def print_menu():
     print('5. Upstream and target profiles Constant Bt')
     print('6. Upstream and target profiles Constant q95')
     print('7. Example of shoulder amplitude')
+    print('8. Statistics at constant Bt')
+    print('9. Statistics at constant q95')
+    print('10. Shoulder and Target density evolution Constant Bt')
+    print('11. Shoulder and Target density evolution Constant q95')
     print("99: End")
     print(67 * "-")
 
@@ -652,6 +666,502 @@ while loop:
 
         fig.savefig('../pdfbox/ExampleShoulderAmplitude.pdf',
                     bbox_to_inches='tight')
+
+    elif selection == 8:
+        shotListA = (34105, 34102, 34106)
+        btAsdex = (0.6, 0.8, 1)
+        colorList = ('#01406C', '#F03C07', '#28B799')
+        Directory = "/Users/vianello/Desktop/Topic-21/" \
+                    "Experiments/AUG/analysis/data/"
+        # this is the figure of Blob-size vs Lambda
+        fig, ax = mpl.pylab.subplots(figsize=(8, 8), nrows=2, ncols=1,
+                                     sharex=True, sharey=True)
+        fig.subplots_adjust(bottom=0.15, left=0.17, hspace=0.05, top=0.97)
+        # this is the figure of Efold vs Lambda
[…]

### 2018-05-16 Experiments/Comparison/python/scriptAnalysis.py
update to figures

@@ -1123,7 +1123,7 @@ while loop:
         ax2[0].set_ylim([0, 1])
         ax2[1].set_ylim([0, 1])
         ax2[2].set_ylim([0, 1])
-        ax2[2].set_xlim([0.25, 1])
+        ax2[2].set_xlim([0.25, 0.7])
         ax2[2].set_ylabel(r'n$^{peak}_{target} [10^{20}$m$^{-3}]$')
         ax2[0].set_ylabel(r'Amp [a.u]')
         ax2[0].text(0.5, 0.8, r'$1\leq \rho < 1.03$',

### 2018-05-16 Experiments/Comparison/python/scriptAnalysis.py
update script for comparison
Now should handle home directory and add the script for the evolution of quantity for constant Q95

@@ -5,12 +5,16 @@ import xarray as xray
 import h5py
 from scipy.interpolate import UnivariateSpline, interp1d
 import pandas as pd
+from os.path import expanduser
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=18)
 mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica']})
 mpl.rc("lines", linewidth=2)
+homeDir = expanduser("~")
+EuroFusionDir = homeDir + "/Dropbox/Work/Collaboration/EuroFusion/"
 Data = pd.read_csv(
-    '~/Desktop/Topic-21/Experiments/TCV/data/BlobDatabase.csv')
+    EuroFusionDir +
+    'MST1-2017-2018/Topic-21/Repository/Experiments/TCV/data/BlobDatabase.csv')
 DataTCV = Data[((Data['Rho'] > 1.025) &
                 (Data['Rho'] <= 1.05) &
                 (Data['Conf'] == 'LSN') &
@@ -297,7 +301,8 @@ while loop:
         ipListT = ('0.185', '0.24', '0.34')
         for shot, t, c, _ip in zip(shotListA, tListA, colorList, ipListA):
             # open the HDF file
-            DirectoryAug = '/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/data/aug/'
+            DirectoryAug = homeDir+"/Documents/" \
+                           "Fisica/Conferences/IAEA/iaea2018/data/aug/"
             File = h5py.File(DirectoryAug + 'Shot%5i' % shot + '.h5', 'r')
             neLBtime = File['timeLiB'].value
             # limit to the interval
@@ -374,7 +379,7 @@ while loop:
             text.set_color(c)
             handle.set_visible(False)
         # Now TCV
-        DirectoryTcv = "/Users/vianello/Documents/Fisica/Conferences/" \
+        DirectoryTcv = homeDir + "/Documents/Fisica/Conferences/" \
                        "IAEA/iaea2018/data/tcv/"
         File = h5py.File(DirectoryTcv + 'ProfilesConstantBt.h5', 'r')
         for shot, col, _ip in zip(
@@ -1163,6 +1168,178 @@ while loop:
         fig3.savefig('../pdfbox/AmplitudeVsLambdaConstantBt.pdf',
                      bbox_to_inches='tight')
 
+    elif selection == 11:
[…]

### 2018-05-16 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
update to script for Figure and TeX
Update to script for the comparison of H-Mode on AUG and corresponding description on TeX file

@@
     \begin{column}{0.6\textwidth}
-      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
+      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
@@
       \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleShoulderAmplitude}
-      \includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsNe5IpConstantBt}
-      \includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsGreenwaldIpConstantBt}      
-      \includegraphics<11>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantBt}
-      % \includegraphics<11>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldBlobAllColor}         
+      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsDensityConstantBt}
+      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}      
+      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
+      \includegraphics<12>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantBt}         
+      \includegraphics<13>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantBt}         
     \end{column}
@@
         \only<9-10>{\item Amplitude evolve faster in density at lower
-          current in the far SOL \onslide<10>{\alert{but once evolution \textit{vs} greenwald
+          current in the far SOL. Amplitude starts increasing close to
+          the transition to highly-recycling regime in analogy to
+          JET HT \parencite{Wynn:2018gp} \onslide<10>{\alert{but once evolution \textit{vs} greenwald
             fraction is considered the evolution is equivalent between
@@
             current in agreement with different detachment evolution}}}
-        \item<only@11> Amplitude evolution still reconciled in AUG if
+        \item<only@11> Amplitude evolution reconciled in AUG if
           considered as a function of local evolution of $\Lambda_{div}$
-        % \item<11|only@11> For both AUG and TCV $\lambda_n$ increases
-        %   with blob size without significant difference within the
-        %   current explored
+        \item<only@12> For both AUG and TCV $\lambda_n$ increases
+          with blob size without significant difference within the
+          current explored
+        \item<only@13> \alert{The evaluation of $\lambda_n$ as a
+          function of $\Lambda_{div}$ confirms that this variable is
+          insufficient to completely reconcile AUG and TCV}
       \end{itemize}
@@
 
-% \begin{frame}{Current scan at constant q$_{95}$}
-%   \begin{columns}
-%     \begin{column}{0.6\textwidth}
-%       \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
-%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
-%       \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
-%       \includegraphics<4>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NeutralsVsGreenwaldConstantQ95}
-%       \includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/UpstreamTargetProfilesConstantQ95}
-%       \includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}
-%       \includegraphics<7>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/AmplitudeVsLambdaIpConstantQ95}
-%       \includegraphics<8>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldVBlobAllColorConstantQ95}         
-%       \includegraphics<9>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/BlobLambdaAllColorConstantQ95}         
-%     \end{column}
-%     \begin{column}{0.4\textwidth}
-%       \begin{itemize}
-%         \item<1|only@1> Shape matched in within the single scan even
-%           though this required for TCV operation with very low
-%           toroidal field (0.8T)
-%         \item<1|only@1> The parallel connection length remains almost unchanged
-%         \item<2|only@2> AUG: As for the case of constant B$_t$ we have
-%           pretty reproducible behavior matching basically the plasma
-%           condition in within the current scan
-%         \item<3|only@3> TCV: Even at such an high density at lower
-%           current (and lower B$_t$) no sign of target ion flux
-%           rollover/detachment
-%         \item<4|only@4> AUG: Divertor neutral density exhibits 
-%           the same behavior if considered as a function of greenwald fraction
-%         \item<5|only@5> For AUG upstream and target profiles still
-%           exhibit flattening earlier in density at lower current but
-%           \alert{always at large values of 
-%           $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
-%             at very large values of $\Lambda_{div}$}
-%         \item<6|only@6> This is due to the fact we did not reach
-%           divertor detachment which \alert{seems mandatory for
-%             upstream profile modification}  
-%         \item<7|only@7> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
-%           still reconcile the explored current scan
-%         \item<8|only@8> AUG exhibit consistently an increase of
-%           $\lambda_n$ with blob-size whereas for TCV the profile
-%           remains flat consistently with a small variation of
-%           $\delta_b$
-%         \item<9|only@9> And for TCV this is true even at high value of
-%           $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
-%           guarantee flat profiles on TCV.}
-%       \end{itemize}
-%     \end{column}
-%   \end{columns}
-% \end{frame}
+\begin{frame}{Current scan at constant q$_{95}$}
+  \begin{columns}
+    \begin{column}{0.6\textwidth}
+      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
+      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
+      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
+      \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
+      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationGreenwaldConstantQ95}
+      \includegraphics<6>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
+      \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
+      \includegraphics<9>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeVsLambdaConstantBt}
+      \includegraphics<10>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldBlobConstantQ95}         
+      \includegraphics<11>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldLambdaConstantQ95}         
+    \end{column}
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+        \item<1|only@1> Shape matched in within the single scan even
+          though this required for TCV operation with very low
+          toroidal field (0.8T)
+        \item<1|only@1> The parallel connection length remains almost unchanged
+        \item<2|only@2> AUG: As for the case of constant B$_t$ we have
+          pretty reproducible behavior matching basically the plasma
+          condition in within the current scan
+        \item<3|only@3> TCV: Even at such an high density at lower
+          current (and lower B$_t$) no sign of target ion flux
+          rollover/detachment
+        \item<4|only@4> Again for AUG peak target density rollover
+          occurs at lower density for lower current as well as
+          radiation front movement. For TCV rollover achieved only at
+          higher current whereas lower I$_p$ does not exhibit sign of
+          detachment even if high density is
+          achieved. \alert{Consistent with lack of signature of
+            volumetric recombination from DSS}
+         \item<only@5> Interestingly considering the behavior as a
+           function of greenwald fraction does not reconcile the
+           different current neither on AUG.  
+        \only<6-7>{\item For AUG upstream and target profiles still
+          exhibit flattening earlier in density at lower current but
+          \alert{always at large values of 
+          $\Lambda_{div}$}. For TCV no sign of upstream profile flattening \alert{even
+          at very large values of $\Lambda_{div}$}
+        \item<only@7>  This is due to the fact we did not reach
+          divertor detachment which \alert{seems mandatory for
+            upstream profile modification}  
+        \item<only@8> AUG: Amplitude evolution as a function of
+          greenwald fraction confirms that shoulder starts appearing
+          at the onset of highly recycling regime 
+        \item<only@9> AUG: Amplitude evolution as a function of $\Lambda_{div}$ 
+          still reconcile the explored current scan
+        \item<only@10> AUG exhibit consistently an increase of
+          $\lambda_n$ with blob-size whereas for TCV the profile
+          remains flat consistently with a small variation of
+          $\delta_b$
+        \item<only@11> And for TCV this is true even at high value of
+          $\Lambda_{div}$. \alert{$\Lambda_{div}$ is not sufficient to
+          guarantee flat profiles on TCV.}
+      \end{itemize}
+    \end{column}
+  \end{columns}
+\end{frame}
 % %% H-Mode same fueling
-% \begin{frame}{H-Mode analysis on AUG}
-%     \Fontvi
-%   \vspace{-1cm}
-%   \begin{columns}
-%   \begin{column}{0.55\textwidth}
-%     \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
-%     \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
-%   \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
-%   \centering{\includegraphics<4>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278}}
-%   \centering{\includegraphics<5>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EfoldSizeShots34276_34278_34281}}
-%   \end{column}
-%   \begin{column}{0.45\textwidth}
-%     \begin{itemize}
-%     \item<1|only@1> We perform a series of shots in H-Mode with 6.5
-%       total heating power where we changed the fueling and the
-%       efficiency of cryopumps. Specifically we have
-%       \begin{itemize}
-%         \item<1|only@1>\textcolor{colorA}{\# 34276 without the
-%             cryompumps}
-%         \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
-%             fueling as \# 34276 but with the cryompump}
-%         \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
-%             fueling and seeding trying to mimic the same subdivertor
-%             pressure as \# 34276}
-%       \end{itemize}
-%     \item<1|only@1> Keeping the same fueling with the cryopump clearly
-%       reduce the pressure in the the sub-divertor area, we don't reach
-%       clear detachment and the edge density is constant even during
-%       the fueling ramp. Degraded H-mode reached later without the cryopump
+\begin{frame}{H-Mode analysis on AUG}
+    \Fontvi
+  \vspace{-1cm}
+  \begin{columns}
+  \begin{column}{0.55\textwidth}
+    \centering{\includegraphics<1>[height=0.8\textheight]{../../Experiments/AUG/analysis/pdfbox/GeneralComparisonShot34276_34278_34281.pdf}}
+    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278_34281}}
+  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
+  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
+  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
+  \end{column}
+  \begin{column}{0.45\textwidth}
+    \begin{itemize}
+    \item<1|only@1> We perform a series of shots in H-Mode with 6.5
+      total heating power where we changed the fueling and the
+      efficiency of cryopumps. Specifically we have
+      \begin{itemize}
+        \item<1|only@1>\textcolor{colorA}{\# 34276 without the
+            cryompumps}
+        \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
+            fueling as \# 34276 but with the cryompump}
+        \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
+            fueling and seeding trying to mimic the same subdivertor
+            pressure as \# 34276}
+      \end{itemize}
+    \item<1|only@1> Keeping the same fueling with the cryopump clearly
+      reduce the pressure in the the sub-divertor area, we don't reach
+      clear detachment and the edge density is constant even during
+      the fueling ramp. Degraded H-mode reached later without the cryopump
 
-%     \item<2|only@2> Different behavior of ELM during the fueling
-%       ramp. ELM size and frequency changes strongly without the
-%       cryopump or during extreme fueling case
-%     \item<3|only@3> The profiles for shot \# 34278 with the cryopum
-%       and lower fueling remains more steep in all the three timing
-%       wind and the plasma is still attached. Interestingly for shot \#
-%       34281 with the cryopumps and higher fueling the detachment is
-%       more pronounced
-%     \item<4|only@4> Without the cryopumps, we reached flatter
-%          profiles with comparable inter-ELM resolved blob-size. This
-%          indicates strong neutral pressure effects in determining
-%          upstream profiles
-%     \item<5|only@5> Increasing the fueling and correspondingly the
-%       divertor neutral pressure move towards a situation similar to
-%       \# 34276 without the cryopump
-%       \end{itemize}
-%   \end{column}
-% \end{columns}
-% \end{frame}
+    \item<2|only@2> Different behavior of ELM during the fueling
+      ramp. ELM size and frequency changes strongly without the
+      cryopump or during extreme fueling case
+    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
+      and lower fueling remains more steep in all the three timing
+      wind and the plasma is still attached. Interestingly for shot \#
+      34281 with the cryopumps and higher fueling the detachment is
+      more pronounced
+    \item<4|only@4> Without the cryopumps, we reached flatter
+         profiles with comparable inter-ELM resolved blob-size. This
+         indicates strong neutral pressure effects in determining
+         upstream profiles
+    \item<5|only@5> Increasing the fueling and correspondingly the
+      divertor neutral pressure move towards a situation similar to
+      \# 34276 without the cryopump
+      \end{itemize}
+  \end{column}
+\end{columns}
+\end{frame}
 

### 2018-05-16 Experiments/Comparison/python/scriptAnalysis.py

@@ -37,6 +37,9 @@ def print_menu():
     print('9. Statistics at constant q95')
     print('10. Shoulder and Target density evolution Constant Bt')
     print('11. Shoulder and Target density evolution Constant q95')
+    print("12. Efold vs Lambda same fueling with/wo cryopumps")
+    print("13. Efold vs Lambda different fueling with/wo cryopumps")
+    print("14. Efold vs Lambda H-Mode/L-Mode")
     print("99: End")
     print(67 * "-")
 
@@ -1340,6 +1343,238 @@ while loop:
             bbox_to_inches='tight')
         fig3.savefig('../pdfbox/AmplitudeVsLambdaConstantQ95.pdf',
                      bbox_to_inches='tight')
+
+    elif selection == 12:        
+        shotListA = (34276, 34278, 34102)
+        cryo = ('#34276 H-Mode cryo off',
+                '#34278 H-Mode cryon on',
+                '#34102 L-mode')
+#        colorList = ('#324D5C', '#E37B40', '#60A65F')
+        colorList = ('#324D5C', '#E37B40', 'k')
+        Directory = '../../AUG/analysis/data/'
+        # figure with Efold vs blob Size
+        fig, ax = mpl.pylab.subplots(figsize=(8, 5), nrows=1, ncols=1)
+        fig.subplots_adjust(bottom=0.17, left=0.17, hspace=0.05, top=0.9)
+        # figure for Blob vs Lambda
+        fig2, ax2 = mpl.pylab.subplots(figsize=(8, 5), nrows=1, ncols=1)
+        fig2.subplots_adjust(bottom=0.17, left=0.17, hspace=0.05, top=0.9)
+        # first the plot for AUG
+        for shot, col in zip(shotListA, colorList):
+            for s in ('1', '2', '3', '4', '5'):
+                try:
+                    Data = xray.open_dataarray(Directory +
+                                               'Shot%5i' % shot +
+                                               '_'+s+'Stroke.nc')
+                    Vperp = Data.Vperp
+                    Size = 0.5*Data.TauB*np.abs(Vperp)/1e-4
+                    SizeErr = np.sqrt(
+                        np.power(Data.Vperp*Data.TauBErr, 2) +
+                        np.power(Data.TauB*Data.VperpErr, 2))/2/1e-4
+                    if SizeErr > 0.5*Size:
+                        SizeErr = 0.5*Size
[…]

### 2018-05-17 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Added figure,scripts and TeX
For analysis meeting of 17 of May

@@
 
+\begin{frame}{Devices, diagnostics and methods}
+\only<1>{
+  \centering{\includegraphics[width=0.8\textwidth]{../generalFigures/Divertor-AUG-TCV}}
+
+  \begin{itemize}
+    \item \textbf{AUG:} Metallic wall, cryopumps, closed divertor with
+      SP on vertical target, short divertor leg
+    \item \textbf{TCV:} Carbon wall, completely open divertor,
+      operated with relative long divertor leg, no cryopump  
+  \end{itemize}
+}
+\only<2>{
+  \vspace{-1.5cm}
+  \centering{\includegraphics[width=0.7\textwidth]{../generalFigures/ProbeHead}}
+\Fontvi
+  \begin{itemize}
+    \item \textbf{AUG:} Ion saturation current measured at different
+      radial/poloidal position to get velocity from 2D cross-correlation
+    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
+      different velocity estimate. $v_r$ from
+      $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
+      on CAS, $v_z$ from 2D cross-correlation analysis
+
+  \end{itemize}
+}
+\end{frame}
+
 \begin{frame}{Current scan at constant B$_t$ in L-Mode plasma}
@@
     \begin{column}{0.6\textwidth}
-      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
+      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
@@
             fraction is considered the evolution is equivalent between
-            different current.}
-          \item \textcolor{ta3chameleon}{Still some inconsistency at lower
-            current in agreement with different detachment evolution}}}
+            different current.}}
+          \item<only@10> \textcolor{ta3chameleon}{Still some inconsistency at lower
+            current in agreement with different detachment evolution}}
         \item<only@11> Amplitude evolution reconciled in AUG if
@@
     \begin{column}{0.6\textwidth}
-      \includegraphics<1>[width=\textwidth]{~/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
+      \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
@@
       \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
-      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationGreenwaldConstantQ95}
-      \includegraphics<6>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
+      \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
+      \includegraphics<6-7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
       \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
@@
           divertor detachment which \alert{seems mandatory for
-            upstream profile modification}  
+            upstream profile modification}}  
         \item<only@8> AUG: Amplitude evolution as a function of
@@
 \end{frame}
-% %% H-Mode same fueling
+% % %% H-Mode same fueling
 \begin{frame}{H-Mode analysis on AUG}
@@
         \item<1|only@1> \textcolor{colorB}{\# 34278 with the same
-            fueling as \# 34276 but with the cryompump}
+            fueling as} \textcolor{colorA}{\# 34276} \textcolor{colorB}{but with the cryompump}
         \item<1|only@1> \textcolor{colorC}{\#34281 where we increase
             fueling and seeding trying to mimic the same subdivertor
-            pressure as \# 34276}
+            pressure as} \textcolor{colorA}{\# 34276}
       \end{itemize}
@@
 
-% \begin{frame}{Conclusion}
-%   \Fontvi
-%   \begin{itemize}
-%     \item Current scan at constant B$_t$ and at constant q$_{95}$
-%       performed during density ramps L-Mode experiments both at AUG
-%       and TCV
-%     \item In both the case shoulder appear earlier in density at lower
-%       current but AUG shows reconciliation of behavior if considered
-%       as a function of greenwald fraction and $\Lambda_{div}$
-%     \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
-%       blob size is increasing, independently from the current. The
-%       same behavior is observed during current scan at constant
-%       q$_{95}$ \alert{only on AUG}
-%     \item On TCV during the current scan at constant q$_{95}$
-%       detachment not reached and this \alert{prevent upstream profile
-%         flattening}
-%     \item H-Mode experiments performed on AUG where fueling and
-%       pumping have been varied. Proved inter-ELM profile flattening
-%       also in H-Mode with a more efficient puffing without the
-%       cryopump. \alert{Hints on the role of neutrals also in H-Mode}
-%   \end{itemize}
-% \end{frame}
+\begin{frame}{Conclusion}
+  \Fontvi
+  \begin{itemize}
+    \item Current scan at constant B$_t$ and at constant q$_{95}$
+      performed during density ramps L-Mode experiments both at AUG
+      and TCV
+    \item In both the case shoulder appear earlier in density at lower
+      current but AUG shows reconciliation of behavior if considered
+      as a function of greenwald fraction and $\Lambda_{div}$ for
+      constant B$_t$ but not for constant q$_{95}$. AUG still well
+      represented by $\Lambda_{div}$. \alert{Shoulder starts
+        developing at the onset of highly recycling regime}
+    \item Both the experiments exhibit at constant B$_t$ flattening of the profile as
+      blob size is increasing, independently from the current. The
+      same behavior is observed during current scan at constant
+      q$_{95}$ \alert{only on AUG}
+    \item On TCV during the current scan at constant q$_{95}$
+      detachment not reached and this \alert{prevents upstream profile
+        flattening}
+    \item H-Mode experiments performed on AUG where fueling and
+      pumping have been varied. \alert{Proved inter-ELM profile flattening
+      also in H-Mode} \alert{but high neutral pressure (not only edge
+      density) is needed}
+  \item<2-> \textbf{\textcolor{ta3scarletred}{Can we find a different parameter to reconcile
+        the experimental observation?}}
+  \end{itemize}
+\end{frame}
 
+\begin{frame}{On going work}
+  A series of works are still on-going \textcolor{ta3scarletred}{or
+    yet to be started}
+  \begin{itemize}[<+->]
+    \item Neutral density estimate from light emission
+      \textbf{M. Agostini}
+    \item Wall embedded probe analysis \textbf{S. Costea,
+        M. Spolaore}
+    \item Shoulder from Reflectometry analysis \textbf{E. Sieglun}
+    \item \textcolor{ta3scarletred}{SOLPS modelling AUG/TCV for modelling collisionality
+      along flux tube and compare to measurement}
+    \item \textcolor{ta3scarletred}{Balmer series analysis for
+        recombination analysis on TCV \textbf{K. Verhaegh}}
+  \item \textcolor{ta3scarletred}{HFSD}
+    \item \textcolor{ta3scarletred}{\ldots}
+
+  \end{itemize}
+\end{frame}
 % \begin{frame}{D$_{\alpha}$ tomography: work in progress}

### 2018-05-17 Experiments/Comparison/python/scriptAnalysis.py

@@ -11,7 +11,7 @@ mpl.rc("font", size=18)
 mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica']})
 mpl.rc("lines", linewidth=2)
 homeDir = expanduser("~")
-EuroFusionDir = homeDir + "/Dropbox/Work/Collaboration/EuroFusion/"
+EuroFusionDir = homeDir + "/Dropbox/Work/Collaborations/EUROFusion/"
 Data = pd.read_csv(
     EuroFusionDir +
     'MST1-2017-2018/Topic-21/Repository/Experiments/TCV/data/BlobDatabase.csv')
@@ -305,7 +305,7 @@ while loop:
         for shot, t, c, _ip in zip(shotListA, tListA, colorList, ipListA):
             # open the HDF file
             DirectoryAug = homeDir+"/Documents/" \
-                           "Fisica/Conferences/IAEA/iaea2018/data/aug/"
+                "Fisica/Conferences/IAEA/iaea2018/data/aug/"
             File = h5py.File(DirectoryAug + 'Shot%5i' % shot + '.h5', 'r')
             neLBtime = File['timeLiB'].value
             # limit to the interval
@@ -383,7 +383,7 @@ while loop:
             handle.set_visible(False)
         # Now TCV
         DirectoryTcv = homeDir + "/Documents/Fisica/Conferences/" \
-                       "IAEA/iaea2018/data/tcv/"
+            "IAEA/iaea2018/data/tcv/"
         File = h5py.File(DirectoryTcv + 'ProfilesConstantBt.h5', 'r')
         for shot, col, _ip in zip(
                 shotListT, colorList, ipListT):
@@ -944,17 +944,30 @@ while loop:
                            yerr=_dummy['Blob size Err [rhos]']/2, fmt='o',
                            ms=15, color=c, alpha=0.3)
             # Efold vs Lambda
-            ax2[1].errorbar(_dummy['Lambda Div'],
-                            _dummy['Efold']*1e2,
-                            xerr=_dummy['Lambda Div Err'],
-                            yerr=_dummy['EfoldErr']*1e2, fmt='o',
-                            ms=15, color=c, alpha=0.3)
-            # Efold vs Blob size
-            ax3[1].errorbar(_dummy['Blob Size [rhos]']/2,
-                            _dummy['Efold']*1e2,
-                            xerr=_dummy['Blob size Err [rhos]']/2,
[…]

### 2018-05-17 Experiments/Comparison/python/scriptAnalysis.py
update to scriptAnalysis for May meeting

@@ -40,6 +40,7 @@ def print_menu():
     print("12. Efold vs Lambda same fueling with/wo cryopumps")
     print("13. Efold vs Lambda different fueling with/wo cryopumps")
     print("14. Efold vs Lambda H-Mode/L-Mode")
+    print("15. CAS example combined")
     print("99: End")
     print(67 * "-")
 
@@ -1587,6 +1588,15 @@ while loop:
                      % shotListA[0] +
                      '_%5i' % shotListA[1] +
                      '_%5i' % shotListA[2] + '.pdf', bbox_to_inches='tight')
+
+    elif selection == 15:
+        DataTCV = xray.open_dataarray(
+            '../../TCV/analysis/data/BlobShot54873_plunge1_rrsep1cm.nc')
+        DataAUG = xray.open_dataarray(
+            '../../AUG/analysis/data/Shot34102_1Stroke.nc')
+        # now the 2 panel with CAS and FWHM
+        fig, ax = mpl.pylab.subplots(figsize=(10, 7), nrows=2, ncols=2)
+        # AUG part
 
     elif selection == 99:
         loop = False

### 2018-05-17 Experiments/Comparison/python/scriptAnalysis.py
added the example of CAS and correlation

@@ -4,8 +4,10 @@ import matplotlib as mpl
 import xarray as xray
 import h5py
 from scipy.interpolate import UnivariateSpline, interp1d
+from scipy.signal import hilbert
 import pandas as pd
 from os.path import expanduser
+from lmfit.models import GaussianModel
 mpl.rcParams['font.family'] = 'sans-serif'
 mpl.rc("font", size=18)
 mpl.rc('font', **{'family': 'sans-serif', 'sans-serif': ['Helvetica']})
@@ -1592,12 +1594,137 @@ while loop:
     elif selection == 15:
         DataTCV = xray.open_dataarray(
             '../../TCV/analysis/data/BlobShot54873_plunge1_rrsep1cm.nc')
+        DataTCVn = xray.open_dataarray(
+            '../../TCV/analysis/data/BlobShot54873_plunge1_rrsep1cm_norm.nc')
         DataAUG = xray.open_dataarray(
             '../../AUG/analysis/data/Shot34102_1Stroke.nc')
         # now the 2 panel with CAS and FWHM
         fig, ax = mpl.pylab.subplots(figsize=(10, 7), nrows=2, ncols=2)
         # AUG part
+        ax[0, 0].plot(DataAUG.t*1e6, DataAUG.sel(sig='Isat_m06'), '-k', lw=2)
+        ax[0, 0].fill_between(DataAUG.t*1e6,
+                              DataAUG.sel(sig='Isat_m06') -
+                              DataAUG.err.reshape(3, 501)[0, :],
+                              DataAUG.sel(sig='Isat_m06') +
+                              DataAUG.err.reshape(
+                                  3, 501)[0, :], facecolor='gray',
+                              alpha=0.5, edgecolor='white')
+        # compute the FWHM
+        _x, _y = DataAUG.t.values, DataAUG.sel(sig='Isat_m06').values
+        _y -= _y.min()
+        S = UnivariateSpline(_x, _y-_y.max()/2, s=0)
+        r1, r2 = S.roots()
+        ax[0, 0].axvspan(r1*1e6, r2*1e6, facecolor='yellow', alpha=0.5)
+        # now the others two
+        colorList = ('#01406C', '#F03C07', '#28B799')
+        ax[1, 0].plot(DataAUG.t*1e6, DataAUG.sel(sig='Isat_m07'), '-',
+                      color=colorList[1], lw=2, label=r'J$_s^{z}$')
[…]

### 2018-05-17 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
Almost finished the May 2018 TeX file

@@
       on CAS, $v_z$ from 2D cross-correlation analysis
-
   \end{itemize}
 }
+\only<3>{
+  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
+  \begin{itemize}
+    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
+    \item $\tau_b$ estimated from FWHM of Conditional Avearage
+      (\alert{different from Carralero}) including asymmetric part
+      (\alert{different from Tsui})
+  \end{itemize}
+}
+\only<4>{
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+  \includegraphics[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCorrelation}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+  \begin{itemize}
+    \item Correlation on TCV computed using a gaussian Fit of the
+      central part (better resolution)
+    \item on AUG the correlation is in general asymmetric. Maximum
+      time lag estimated from the zeros of the imaginary part of the
+      hilbert transform of the correlation function
+  \end{itemize}
+    \end{column}
+  \end{columns}
+}
+
 \end{frame}
@@
         recombination analysis on TCV \textbf{K. Verhaegh}}
+    \item \textcolor{ta3orange}{GPI analysis and comparison with probe
+      \textbf{Walkden, Cziegler}}  
   \item \textcolor{ta3scarletred}{HFSD}

### 2018-05-17 Experiments/Comparison/python/scriptAnalysis.py
Rasterized version of pdf figure

@@ -69,10 +69,12 @@ while loop:
                 '_DensityRadiation.nc')
             ax[0, 0].plot(df.sel(sig='H-5')[:-10]/10,
                           df.sel(sig='neTarget')[:-10], '.', color=col,
-                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
+                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA',
+                          rasterized=True)
             ax[1, 0].plot(df.sel(sig='H-5')[:-10]/10,
                           df.sel(sig='D10')[:-10]/1e3, '.', color=col,
-                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
+                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA',
+                          rasterized=True)
         ax[0, 0].set_xlim([0.1, 0.5])
         ax[0, 0].set_ylabel(r'n$^{peak}_{target} [10^{20}$m$^{-3}]$')
         ax[0, 0].axes.get_xaxis().set_visible(False)
@@ -92,10 +94,12 @@ while loop:
                 '_DensityRadiation.nc')
             ax[0, 1].plot(df.sel(sig='en'),
                           df.sel(sig='neMaxTarget')/10, '.', color=col,
-                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
+                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA',
+                          rasterized=True)
             ax[1, 1].plot(df.sel(sig='en'),
                           df.sel(sig='Bolo')/1e3, '.',  color=col,
-                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA')
+                          label=r'#%5i' % shot + ' %3.2f' % ip + ' MA',
+                          rasterized=True)
         ax[0, 1].set_xlim([0.1, 1.2])
         ax[0, 1].set_ylabel(r'n$^{peak}_{target} [10^{20}$m$^{-3}]$')
         ax[0, 1].axes.get_xaxis().set_visible(False)
@@ -109,7 +113,7 @@ while loop:
         for text, color in zip(leg.get_texts(), colorList):
             text.set_color(color)
         fig.savefig('../pdfbox/TargetDensityRadiationVsDensityConstantBt.pdf',
-                    bbox_to_inches='tight')
+                    bbox_to_inches='tight', dpi=300)
     elif selection == 2:
         shotAug = (34105, 34102, 34106)
[…]

### 2018-05-22 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Update to figures for MST-TFM meeting and TeX files

--- 2018-05-17 Meetings/AnalysisMeetingMay2018/analysis_meeting2018_topic21.tex
@@
 \documentclass[10pt, compress]{beamer}
-\usetheme[conference=Topic21-Analysis-Meeting,venue=Remote, date=17/05/2018, titleprogressbar, logo=RFX-logo]{Eurof}
+\usetheme[conference=MST1-TFM,venue=Padova, date=23/05/2018, titleprogressbar, logo=RFX-logo]{Eurof}
 \usepackage{listings,amsmath,multimedia, amssymb}
@@
 \definecolor{colorC}{HTML}{60A65F}
-% multiple figure location
-%\graphicspath{{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/}{../Experiments/}}
+
 % for drawing
@@
 \newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
-\title{Topic 21 Experiment and analysis}
-\date{17 May 2018}
+\title{Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}
+\date{23 May 2018}
 \author[N.Vianello]{presented by N. Vianello on behalf of  MST1-Topic 21
@@
 Nickolas Walkden, Zhang Wei, Elisabeth Wolfrum, W. Vijvers}
+\end{frame}
+
+\begin{frame}{Background}
+  \only<1>{
+\begin{itemize}
+\item Role of turbulence transport in the SOL saturation is a well
+  know
+  feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
+  density, even without reaching detachment SOL profile tend to flatten}
+\end{itemize}}
+% \only<2-3>{
+%   \begin{columns}
+%     \begin{column}{0.5\textwidth}
+%       \begin{itemize}
+%       \item Present understanding suggests that a transition of filament
+%         propagation regime is dominated by effective
+%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
+%         \begin{equation*}
+%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
+%         \end{equation*}
+%         \item<3> \textcolor{red}{At constant blob size, increasing
+%             collisionality provide a change in the filaments velocity
+%             scaling properties}
+%       \end{itemize}
+%     \end{column}
+%     \begin{column}{0.5\textwidth}
+% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
+%         \begin{tikzonimage}[width=\textwidth]{../generalFigures/FigMyra}
+%           \only<3>{
+%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
+%         \end{tikzonimage}
+%     \end{column}
+%   \end{columns}
+% }
+\only<2-4>{
+  \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+      \item AUG and JET (HT) \parencite{Carralero:2015gu} suggest that $\Lambda_{div}=\frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}$ dominates this
+        process and a transition from
+        \textcolor{ta3chameleon}{sheath-limited}
+        \onslide<3-4>{to \textcolor{blue}{inertial regime}} 
+        \item<4> \textcolor{red}{Tested by changing n$_e$
+            and $T_e$ through fueling/seeding/heating}
+      \end{itemize}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \begin{tikzonimage}[width=\textwidth]{../generalFigures/KoMFig2.png}
+        \only<2-4>{
+          \draw [thick, ta3chameleon, thick] (0.45,0.25) ellipse (0.23 and 0.1);
+      }
+        \only<3-4>{
+          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
+      }
+        \only<4>{
+          \draw [thick, red, thick, dashed] (0.35,0.75) circle (0.25);
+      }
+    \end{tikzonimage}
+  \end{column}
+  \end{columns}
+}
+\only<5-7>{
+  \begin{columns}[c]
+    \begin{column}{0.4\textwidth}
+      \begin{itemize}
+      \item<5|only@5> $\Lambda_{div}$ does not describe properly evolution
+        of upstream profile in JET-VT \parencite{Wynn:2018gp}
+      \item<6-7> On TCV \parencite{Vianello:2017ku} $\Lambda_{div}$
+        necessary but not sufficient to guarantee increase $\lambda_n$
+        in the far SOL
+      \item<7|only@7> Additional mechanism suggested among which
+        \alert{neutral clogging} 
+    \end{itemize}
+  \end{column}
+  \begin{column}{0.6\textwidth}
+    \centering{\includegraphics<5>[width=\textwidth]{../generalFigures/Wynn-HT-VT}}
+    \centering{\includegraphics<6-7>[width=\textwidth]{../generalFigures/Vianello-TCV}}
+  \end{column}
+\end{columns}
+}
+\centering{\includegraphics<1>[width=1.1\textwidth]{../generalFigures/Various-density-profiles}}
 \end{frame}
@@
       on CAS, $v_z$ from 2D cross-correlation analysis
-
+  \end{itemize}
+}
+\only<3>{
+  \centering{\includegraphics[width=0.7\textwidth]{../../Experiments/Comparison/pdfbox/ExampleCas}}
+  \begin{itemize}
+    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
+    \item $\tau_b$ estimated from FWHM of Conditional Avearage
+      binormal blob velocity estimated (although differently in the
+      two devices)
   \end{itemize}
@@
         \item<1|only@1> The scan implies a modification of the
-          L$_{\parallel}$. There is a factor of 5 difference between
+          L$_{\parallel}$ (shown from the X-point height to the outer
+          target).
+          There is a factor of 5 difference between
           the two machines due to the very long outer divertor leg of TCV
@@
           avoid earlier disruption. Similar neutral pressure in the
-          subdivertor region reached. NBI additional power added to
+          subdivertor region reached. 0.5 MW NBI additional power added to
           keep power in the SOL approximately constant
@@
           rollover at increasing density with increasing current
-        \item<5|only@5> Whenever considered as a a function of
+        \item<5|only@5> Whenever considered as a function of
           Greenwald fraction the behaviors at different currents
-          almost reconciled for AUG \alert{but not for TCV}
+          almost reconciled for AUG \alert{but not for TCV and at 0.6
+            MA for AUG}
         \item<only@6-7> We now consider the Target and upstream
@@
           rollover/detachment
-        \item<4|only@4> Again for AUG peak target density rollover
+        \item<4|only@4> AUG peak target density rollover
           occurs at lower density for lower current as well as
           radiation front movement. For TCV rollover achieved only at
-          higher current whereas lower I$_p$ does not exhibit sign of
+          higher current: \alert{lower I$_p$ does not exhibit sign of
           detachment even if high density is
-          achieved. \alert{Consistent with lack of signature of
+          achieved. Consistent with lower 
             volumetric recombination from DSS}
@@
         M. Spolaore}
-    \item Shoulder from Reflectometry analysis \textbf{E. Sieglun}
+    \item Shoulder from Reflectometry analysis \textbf{E. Seliunin}
     \item \textcolor{ta3scarletred}{SOLPS modelling AUG/TCV for modelling collisionality
@@
     \item \textcolor{ta3scarletred}{Balmer series analysis for
-        recombination analysis on TCV \textbf{K. Verhaegh}}
+        recombination analysis on TCV \textbf{K. Verhaegh} and MSI for
+      radiation front neutrals (?)}
+    \item \textcolor{ta3orange}{GPI analysis and comparison with probe
+      \textbf{N. Walkden, I. Cziegler}}  
   \item \textcolor{ta3scarletred}{HFSD}
     \item \textcolor{ta3scarletred}{\ldots}
-
   \end{itemize}
 \end{frame}
-% \begin{frame}{D$_{\alpha}$ tomography: work in progress}
-% \Fontvi
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2000}
-%       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_2700}
-%       \includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/inv_alfa_34104_3100}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%         \item \alert{Preliminary} results from inversion tomography
-%           from calibrated D$_{\alpha}$ camera under the assumption of
-%           toroidally symmetric emission limited to the region outside
-%           the LCFS
-%         \item \emph{Simultaneous Algebraic Reconstruction Technique
-%             (SART) (A.H. Anderson and A.C.Kak,  Ultrasonic Imaging
-%             \textbf{6},  81 (1984))}
-%         \item<2-> As time evolves during the L-Mode ramp we observe
-%           D$_{\alpha}$ radiation moving from HFS towards the LFS
-%           common flux region
-%         \item<3-> \alert{This is consistent with JET observation in
-%             Horizontal target regime whenever shoulder is observed}
-%       \end{itemize}
-%     \end{column}
-%   \end{columns}
-% \end{frame}
-
 \end{document}

### 2018-05-22 Experiments/Comparison/python/scriptAnalysis.py

@@ -698,7 +698,7 @@ while loop:
                     "Experiments/AUG/analysis/data/"
         # this is the figure of Blob-size vs Lambda
         fig, ax = mpl.pylab.subplots(figsize=(8, 8), nrows=2, ncols=1,
-                                     sharex=True, sharey=True)
+                                     sharex=True)
         fig.subplots_adjust(bottom=0.15, left=0.17, hspace=0.05, top=0.97)
         # this is the figure of Efold vs Lambda
         fig2, ax2 = mpl.pylab.subplots(figsize=(8, 8), nrows=2, ncols=1,
@@ -760,23 +760,24 @@ while loop:
                     pass
         ax[0].set_xscale('log')
         ax[0].set_yscale('log')
+        ax[0].set_ylim([1, 20])
         ax[0].axes.get_xaxis().set_visible(False)
         ax[0].set_ylabel(r'$\delta_b [\rho_s]$')
         ax[0].text(0.9, 0.87, 'AUG', transform=ax[0].transAxes)
         # Efold vs Lambda
         ax2[0].set_xscale('log')
         ax2[0].set_yscale('log')
+        ax2[0].set_ylim([1, 20])
         ax2[0].axes.get_xaxis().set_visible(False)
         ax2[0].set_ylabel(r'$\lambda_n [$cm$]$')
         ax2[0].text(0.9, 0.87, 'AUG', transform=ax2[0].transAxes)
-        ax2[0].set_ylim([1, 50])
         # Efold vs Blob-size
         ax3[0].set_xscale('log')
         ax3[0].set_yscale('log')
+        ax3[0].set_ylim([1, 20])
         ax3[0].axes.get_xaxis().set_visible(False)
         ax3[0].set_ylabel(r'$\lambda_n [$cm$]$')
         ax3[0].text(0.9, 0.87, 'AUG', transform=ax3[0].transAxes)
-        ax3[0].set_ylim([1, 50])
         for ip, c, _idx in zip(btAsdex, colorList, range(len(btAsdex))):
             ax[0].text(0.05, 0.8 - 0.13 * _idx, r'I$_p$=%2.1f' % ip + ' MA',
                        color=c, transform=ax[0].transAxes)
@@ -859,7 +860,7 @@ while loop:
                     "Experiments/AUG/analysis/data/"
[…]

### 2018-05-22 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
changed to the TeX file for MST1 23 of May including the comments on the work of Matteo and Daniel

@@
 \end{frame}
+
+\begin{frame}{Neutral behavior investigation on AUG: M. Agostini}
+  \only<1>{
+    \begin{columns}
+      \begin{column}{0.5\textwidth}
+        \begin{itemize}
+          \item Light emission analysis performed using 2 absolute
+            calibrated CCD cameras with D$_{\alpha}$ and D$_{\gamma}$
+            filter
+          \item Tomographic inversion using pixel technique assuming
+            emission only outside the LCFS and neglecting reflection
+          \item Inversion technique based on \textbf{S}imultaneous \textbf{A}lgebraic
+            \textbf{R}econstruction \textbf{T}echnique (SART) with no
+            input from equilibrium and no regolarization
+          \item Evolution during density ramp explored
+        \end{itemize}
+      \end{column}
+      \begin{column}{0.5\textwidth}
+        \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig1.pdf}
+      \end{column}
+    \end{columns}
+  }
+  \only<2>{
+    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}
+    At the beginning of the fueling ramp emission localized in the HFS
+  }
+  \only<3>{
+    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}
+Radiation starts moving along the separatrix with different patterns between the two radiation
+  }
+  \only<4>{
+    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}
+    Emission propagate also towards the LFS and moves towards the CFR
+  }
+\end{frame}
+
+\begin{frame}{Heat transport and power balance: D. Carralero}
+  \only<1>{
+    \begin{columns}
+    \begin{column}{0.5\textwidth}
+      \begin{itemize}
+        \item Using a large database (around 30 discharges) in
+          L-Mode detailed ion and electron temperature profiles
+          collected
+        \item Consistent ion temperature drop observed whenever shoulder
+          is observed
+      \end{itemize}
+    \end{column}
+    \begin{column}{0.5\textwidth}
+      \includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Carralero_ionTemperature}
+    \end{column}
+  \end{columns}
+}
+\only<2>{
+  \centering{\includegraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Carralero_powerbalance}}
+  \Fontvi
+  \begin{itemize}
+    \item Parallel heat flux dominated by ion conduction whereas
+      perpendicular component dominated by ion convection
+    \item In high density regime a substantial fraction of
+      P$_{\mathrm{SOL}}$ still remains in the $Q_{\perp}$ for
+      $r-r_{\mathrm{LCFS}} \sim 20$ cm
+  \end{itemize}
+}
+\end{frame}
 % % %% H-Mode same fueling

### 2018-05-23 Experiments/AUG/analysis/python/scriptAnalysisShot.py
updated scriptAnalysis and add the figure with the comparison also with the L-Mode case

@@ -99,6 +99,7 @@ def print_menu():
     print "57. Compare shots 34276-34278-34281 profiles"
     print "58. Elm behavior 34276-34278-34281 "
     print "59. Radiation and peak density vs Greenwald fraction (data saved)"
+    print "60. Compare profiles including L-Mode"
     print "99: End"
     print 67 * "-"
 
@@ -5022,6 +5023,138 @@ while loop:
             df = xray.DataArray(savedArray, coords=[
                                 coords, tGW], dims=['sig', 't'])
             df.to_netcdf('../data/Shot%5i' % shot + '_DensityRadiation.nc')
+    elif selection == 60:
+        shotList = (34102, 34276, 34281)
+        colorList = ('#324D5C', '#E37B40', '#60A65F')
+        colorTimeList = ('#FF4F00', '#00A963', '#0080B6')
+        fig = mpl.pylab.figure(figsize=(14, 14))
+        fig.subplots_adjust(hspace=0.28, right=0.96, top=0.96)
+        ax1 = mpl.pylab.subplot2grid((4, 3), (0, 0), colspan=3)
+        # these are the panel for upstream profiles
+        ax2 = mpl.pylab.subplot2grid((4, 3), (1, 0))
+        ax3 = mpl.pylab.subplot2grid((4, 3), (1, 1))
+        ax4 = mpl.pylab.subplot2grid((4, 3), (1, 2))
+        # these are the panel for target profiles
+        ax5 = mpl.pylab.subplot2grid((4, 3), (2, 0))
+        ax6 = mpl.pylab.subplot2grid((4, 3), (2, 1))
+        ax7 = mpl.pylab.subplot2grid((4, 3), (2, 2))
+        # these are the panel for Lambda
+        ax8 = mpl.pylab.subplot2grid((4, 3), (3, 0))
+        ax9 = mpl.pylab.subplot2grid((4, 3), (3, 1))
+        ax10 = mpl.pylab.subplot2grid((4, 3), (3, 2))
+        # list of axes
+        axProf = (ax2, ax3, ax4)
+        axTarg = (ax5, ax6, ax7)
+        axLamb = (ax8, ax9, ax10)
+        # tranges
+        tListH = ((3, 3.1), (3.8, 3.9), (5.1, 5.2))
+        tListL = ((1.8, 1.9), (3, 3.1), (3.65, 3.75))
+        _mode = ('L', 'H', 'H')
+        # now we need to find for each of the time intervals
[…]

### 2018-05-23 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Update to TeX file for MST1 meeting 23.05

@@
 % for reducing font on a single slide
-\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
+\newcommand\Fontvi{\fontsize{9}{8.2}\selectfont}
 \title{Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}
@@
 \begin{itemize}
-\item Role of turbulence transport in the SOL saturation is a well
+\item Role of turbulence transport in the SOL density profile evolution is a well
   know
-  feature \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{Increasing
-  density, even without reaching detachment SOL profile tend to flatten}
+  feature
+  \parencite{LaBombard:2001ks,Rudakov:2005ic,Garcia:2007hh,Carralero:2014gs}. \textcolor{red}{By
+    increasing
+  density, even without reaching detachment,  SOL density profile tends to flatten}
 \end{itemize}}
-% \only<2-3>{
-%   \begin{columns}
-%     \begin{column}{0.5\textwidth}
-%       \begin{itemize}
-%       \item Present understanding suggests that a transition of filament
-%         propagation regime is dominated by effective
-%         collisionality $\Lambda$ \parencite{Myra:2006p2754}
-%         \begin{equation*}
-%           \Lambda = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
-%         \end{equation*}
-%         \item<3> \textcolor{red}{At constant blob size, increasing
-%             collisionality provide a change in the filaments velocity
-%             scaling properties}
-%       \end{itemize}
-%     \end{column}
-%     \begin{column}{0.5\textwidth}
-% %      \includegraphics<2>[width=\textwidth]{../pdfbox/Presentation/FigMyra}
-%         \begin{tikzonimage}[width=\textwidth]{../generalFigures/FigMyra}
-%           \only<3>{
-%             \draw [->, ultra thick, red] (0.7,0.3) -- (0.7,0.6);}
-%         \end{tikzonimage}
-%     \end{column}
-%   \end{columns}
-% }
 \only<2-4>{
@@
       \item AUG and JET (HT) \parencite{Carralero:2015gu} suggest that $\Lambda_{div}=\frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}$ dominates this
-        process and a transition from
+        process through a transition from
         \textcolor{ta3chameleon}{sheath-limited}
@@
         in the far SOL
-      \item<7|only@7> Additional mechanism suggested among which
-        \alert{neutral clogging} 
+      \item<7|only@7> Additional mechanisms suggested among which
+        \alert{effect of divertor neutrals (\emph{clogging mechanism})} 
     \end{itemize}
@@
       radial/poloidal position to get velocity from 2D cross-correlation
-    \item \textbf{TCV:} Only 1 j$_{sat}$ measurement available,
-      different velocity estimate. $v_r$ from
+    \item \textbf{TCV:} A single j$_{sat}$ measurement available,
+      which implies different velocity estimate. $v_r$ from
       $\mathbf{E}\times\mathbf{B}$ evaluation from floating potentials
-      on CAS, $v_z$ from 2D cross-correlation analysis
+      $v_z$ from 2D cross-correlation analysis ({\small \textit{see
+          Tsui,  PoP submitted}})
   \end{itemize}
@@
   \begin{itemize}
-    \item Blob-size is $\delta_b = 0.5 * \tau_b*v_{\perp}$
-    \item $\tau_b$ estimated from FWHM of Conditional Avearage
-      binormal blob velocity estimated (although differently in the
-      two devices)
+    \item Blob-size is $\delta_b = \frac{\tau_b*v_{\perp}}{2}$
+    \item $\tau_b$ estimated from FWHM of Conditional Average, 
+      binormal blob velocity estimated 
   \end{itemize}
@@
 \begin{frame}{Current scan at constant B$_t$ in L-Mode plasma}
+  \Fontvi
   \begin{columns}
-    \begin{column}{0.6\textwidth}
+    \begin{column}{0.7\textwidth}
       \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantBt}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}
-      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
+      \includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}
       \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantBt}
@@
       }
-      \includegraphics<7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}
+      \includegraphics<7>[width=.95\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantBt}
       \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/ExampleShoulderAmplitude}
@@
     \end{column}
-    \begin{column}{0.4\textwidth}
+    \begin{column}{0.3\textwidth}
       \begin{itemize}
-        \item<1|only@1> Shape matched in within the single scan done for each of
-          the machine
+        \item<1|only@1> Shape well matched in both the device
         \item<1|only@1> The scan implies a modification of the
@@
           target).
-          There is a factor of 5 difference between
-          the two machines due to the very long outer divertor leg of TCV
+          Factor of 5 difference between
+          the two machines
         \item<2|only@2> AUG: Fueling reduced only at lower I$_p$ to
-          avoid earlier disruption. Similar neutral pressure in the
+          avoid earlier disruption. Comparable neutral pressure in the
           subdivertor region reached. 0.5 MW NBI additional power added to
@@
         \item<5|only@5> Whenever considered as a function of
-          Greenwald fraction the behaviors at different currents
-          almost reconciled for AUG \alert{but not for TCV and at 0.6
-            MA for AUG}
+          Greenwald fraction the $n_e^{peak}$ behaviors at different currents
+          reconciled for both the machine AUG \alert{partially for
+            radiation movement}
         \item<only@6-7> We now consider the Target and upstream
@@
           current in the far SOL. Amplitude starts increasing close to
-          the transition to highly-recycling regime in analogy to
-          JET HT \parencite{Wynn:2018gp} \onslide<10>{\alert{but once evolution \textit{vs} greenwald
-            fraction is considered the evolution is equivalent between
-            different current.}}
+          the transition to highly-recycling regime as in 
+          JET HT \parencite{Wynn:2018gp} \onslide<10>{\alert{but
+              evolution is equivalent if considered \textit{vs} greenwald
+            fraction }}
           \item<only@10> \textcolor{ta3chameleon}{Still some inconsistency at lower
@@
 \begin{frame}{Current scan at constant q$_{95}$}
+\Fontvi
   \begin{columns}
-    \begin{column}{0.6\textwidth}
+    \begin{column}{0.7\textwidth}
       \includegraphics<1>[width=\textwidth]{/Users/vianello/Documents/Fisica/Conferences/IAEA/iaea2018/pdfbox/EquilibriaIpScanConstantQ95}
       \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}
-      \includegraphics<3>[width=.9\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
+      \includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}
       \includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsDensityConstantQ95}
       \includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/TargetDensityRadiationVsGreenwaldConstantQ95}
-      \includegraphics<6-7>[width=\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
+      \includegraphics<6-7>[width=.95\textwidth]{../../Experiments/Comparison/pdfbox/UpstreamTargetProfilesConstantQ95}
       \includegraphics<8>[width=\textwidth]{../../Experiments/Comparison/pdfbox/AmplitudeTargetVsGreenwaldConstantBt}
@@
     \end{column}
-    \begin{column}{0.4\textwidth}
+    \begin{column}{0.3\textwidth}
       \begin{itemize}
@@
 
-\begin{frame}{Neutral behavior investigation on AUG: M. Agostini}
+\begin{frame}{Neutral behavior investigation on AUG}
   \only<1>{
@@
   \only<2>{
-    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}
+    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}
+
+    \vspace{1cm}
+
     At the beginning of the fueling ramp emission localized in the HFS
@@
   \only<3>{
-    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}
+    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}
+
+    \vspace{1cm}
+
 Radiation starts moving along the separatrix with different patterns between the two radiation
@@
   \only<4>{
-    \centering{\includgraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}
+    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}
+
+    \vspace{1cm}
+
     Emission propagate also towards the LFS and moves towards the CFR
+  }
+
+  \vspace{1cm}
+
+{\begin{flushleft}
+{\small \textit{(M. Agostini)}}
+  \end{flushleft}
 }
@@
 
-\begin{frame}{Heat transport and power balance: D. Carralero}
+\begin{frame}{Heat transport and power balance}
   \only<1>{
@@
 \only<2>{
-  \centering{\includegraphics[width=7cm]{../../Experiments/AUG/analysis/pdfbox/Carralero_powerbalance}}
-  \Fontvi
+  \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Carralero_powerbalance}}
   \begin{itemize}
@@
   \end{itemize}
+}
+
+{\begin{flushleft}
+{\small \textit{(D. Carralero)}}
+  \end{flushleft}
 }
@@
       cryopump or during extreme fueling case
-    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
-      and lower fueling remains more steep in all the three timing
-      wind and the plasma is still attached. Interestingly for shot \#
+    \item<3|only@3> The profiles for shot \# 34278 with the cryopump
+      and lower fueling remains more steep in all the three time
+      windows and the plasma is still attached. Interestingly for shot \#
       34281 with the cryopumps and higher fueling the detachment is
       more pronounced
-    \item<4|only@4> Without the cryopumps, we reached flatter
+    \item<4|only@4> The shoulder is almost comparable 
+      w.r.t. L-Mode plasma (even if higher density is needed)
+    \item<5|only@5> Without the cryopumps, we reached flatter
          profiles with comparable inter-ELM resolved blob-size. This
@@
          upstream profiles
-    \item<5|only@5> Increasing the fueling and correspondingly the
+    \item<6|only@6> Increasing the fueling and correspondingly the
       divertor neutral pressure move towards a situation similar to

### 2018-05-23 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Final version of TeX file for MST1-TFM 23.05.18

@@
   \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}
-  \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
-  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
+  \centering{\includegraphics<4>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34102_34276_34281}}
+  \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278}}
+  \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/Comparison/pdfbox/EfoldSizeShots34276_34278_34281}}
   \end{column}
@@
       and TCV
-    \item In both the case shoulder appear earlier in density at lower
-      current but AUG shows reconciliation of behavior if considered
-      as a function of greenwald fraction and $\Lambda_{div}$ for
-      constant B$_t$ but not for constant q$_{95}$. AUG still well
-      represented by $\Lambda_{div}$. \alert{Shoulder starts
+    \item At constant B$_t$ in both the experiments shoulder appears
+      earlier in density at lower current: behavior reconciled if
+      considered as a function of $n_e/n_G$ and for AUG as a function
+      of $\Lambda_{div}$. \alert{Shoulder starts
         developing at the onset of highly recycling regime}
@@
         flattening}
+    \item Evaluation of neutrals patterns in the divertor started on
+      AUG. D$_{\alpha}$ tomography reveal the movement of D$_{\alpha}$
+      radiation towards the LFS CFR in analogy to JET HT
+    \item Heat flux and power balance analysis in L-Mode plasmas on
+      AUG. When shoulder appears a consistent fraction of
+      perpendicular heat flux measured in the far SOL
     \item H-Mode experiments performed on AUG where fueling and
@@
       density) is needed}
-  \item<2-> \textbf{\textcolor{ta3scarletred}{Can we find a different parameter to reconcile
-        the experimental observation?}}
   \end{itemize}
@@
 \begin{frame}{On going work}
-  A series of works are still on-going \textcolor{ta3scarletred}{or
-    yet to be started}
-  \begin{itemize}[<+->]
-    \item Neutral density estimate from light emission
-      \textbf{M. Agostini}
-    \item Wall embedded probe analysis \textbf{S. Costea,
-        M. Spolaore}
-    \item Shoulder from Reflectometry analysis \textbf{E. Seliunin}
-    \item \textcolor{ta3scarletred}{SOLPS modelling AUG/TCV for modelling collisionality
-      along flux tube and compare to measurement}
-    \item \textcolor{ta3scarletred}{Balmer series analysis for
-        recombination analysis on TCV \textbf{K. Verhaegh} and MSI for
-      radiation front neutrals (?)}
-    \item \textcolor{ta3orange}{GPI analysis and comparison with probe
-      \textbf{N. Walkden, I. Cziegler}}  
-  \item \textcolor{ta3scarletred}{HFSD}
-    \item \textcolor{ta3scarletred}{\ldots}
+  A series of works are still on-going 
+  \begin{itemize}
+    \item SOLPS modelling for both AUG and TCV for evaluation of
+      collisionality along flux tube and power balance analysis
+    \item HESEL (coupled to neutrals) for TCV current scan simulations
+      for blob analysis
+    \item Shoulder from Reflectometry analysis (\textbf{E. Seliunin})
+    \item Balmer series analysis for
+        recombination analysis on TCV (\textbf{K. Verhaegh}) and MSI for
+      radiation front neutrals
+    \item GPI analysis and comparison with probe
+      (\textbf{N. Walkden, I. Cziegler})
+    \item Particle acceleration associated to ELM filaments on AUG
+      (\textbf{K.Mc Clements})
+    \item Neutral density estimate on divertor region on AUG
+      (\textbf{M. Agostini})  
   \end{itemize}

### 2018-05-23 Meetings/23.05.2018.mst1tfm/mst1tfm_topic21_vianello.tex
Update to TeX MST1TFM 23.05.18

@@
   \only<2>{
-    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}}
-
-    \vspace{1cm}
+    \begin{center}
+    \begin{tikzonimage}[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig2.pdf}
+        \node at (0.05, -0.02) {\textbf{D$_{\alpha}$}};
+        \node at (0.6, -0.02) {\textbf{D$_{\gamma}$}};
+      \end{tikzonimage}
+    \end{center}
 
@@
   \only<3>{
-    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}}
+    \begin{center}
+    \begin{tikzonimage}[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig3.pdf}
+        \node at (0.05, -0.02) {\textbf{D$_{\alpha}$}};
+        \node at (0.6, -0.02) {\textbf{D$_{\gamma}$}};
+      \end{tikzonimage}
+    \end{center}
 
-    \vspace{1cm}
-
-Radiation starts moving along the separatrix with different patterns between the two radiation
+Radiation starts moving towards the X-point (different patterns D$_{\alpha}$, D$_{\gamma}$)
   }
   \only<4>{
-    \centering{\includegraphics[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}}
-
-    \vspace{1cm}
+    \begin{center}
+    \begin{tikzonimage}[width=10cm]{../../Experiments/AUG/analysis/pdfbox/Dalpha/Agostini_Fig4.pdf}
+        \node at (0.05, -0.02) {\textbf{D$_{\alpha}$}};
+        \node at (0.6, -0.02) {\textbf{D$_{\gamma}$}};
+      \end{tikzonimage}
+    \end{center}
 
@@
   }
-
-  \vspace{1cm}
 

### 2018-05-23 Experiments/Comparison/python/scriptAnalysis.py
update to TeX and figure for MST1TFM 23.05.18

@@ -1166,10 +1166,10 @@ while loop:
         ax[2].set_xlim([0.5, 4])
         ax[2].set_ylabel(r'n$^{peak}_{target} [10^{20}$m$^{-3}]$')
         ax[0].set_ylabel(r'Amp [a.u]')
-        ax[0].text(0.5, 0.8, r'$1\leq \rho < 1.03$',
+        ax[0].text(0.1, 0.8, r'$1\leq \rho < 1.03$',
                    transform=ax[0].transAxes)
         ax[1].set_ylabel(r'Amp [a.u.]')
-        ax[1].text(0.5, 0.8, r'$1.03\leq \rho < 1.06$',
+        ax[1].text(0.1, 0.8, r'$1.03\leq \rho < 1.06$',
                    transform=ax[1].transAxes)
         ax[2].set_xlabel(r'n$_e^{Edge}[10^{20}$m$^{-2}]$')
         leg = ax[0].legend(loc='best', numpoints=1, frameon=False, fontsize=14)
